### 2013-06-29 PAPER/ms_final_bv.tex
Added PAPER folder to new repo

% The command below calls the preprint style^M
% which will produce a one-column, single-spaced document.^M
% Examples of commands for other sub-styles follow. Use^M
% whichever is most appropriate for your purposes.^M

%\documentclass[12pt,preprint]{aastex}
%\documentclass[iop,appendixfloats]{emulateapj}

% manuscript produces a one-column, double-spaced document:

%\documentclass[manuscript]{aastex}
%----------------------------------
% mn2esample.tex
%
% v2.1 released 22nd May 2002 (G. Hutton)
%
% The mnsample.tex file has been amended to highlight
% the proper use of LaTeX2e code with the class file
% and using natbib cross-referencing. These changes
% do not reflect the original paper by A. V. Raveendran.
%
% Previous versions of this sample document were
% compatible with the LaTeX 2.09 style file mn.sty
% v1.2 released 5th September 1994 (M. Reed)
% v1.1 released 18th July 1994
% v1.0 released 28th January 1994

\documentclass[useAMS,usenatbib,letters]{mn2e}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\definecolor{orange}{rgb}{1,0.5,0}
\usepackage[colorlinks=True,citecolor=orange,urlcolor=blue,linkcolor=red]{hyperref}

\newcommand{\figurepath}{.}

%  Definition of fonts

\newcommand{\tom}{\tilde{\omega}}

\newcommand{\ri}{r_{\rm i}}

\newcommand{\ro}{r_{\rm out}}

\newcommand{\rs}{r_{\star}}

\newcommand{\mj}{\dot{M}_{\rm jet}}

\newcommand{\ms}{\dot{M}_{\star}}

\newcommand{\vk}{v_{\rm K}}

\newcommand{\ti}{t_{\rm i}}

\newcommand{\rj}{R_{\rm jet}}

\newcommand{\rk}{R_{\kappa}}

\newcommand{\cs}{c_{\rm s}}

\newcommand{\css}{c_{\rm s}^2}

\newcommand{\bp}{B_{\rm P}}

\newcommand{\bh}{B_{\phi}}

\newcommand{\jp}{\vec{B}_{\rm P}}

\newcommand{\cm}{{\rm cm}}

\newcommand{\msun}{{\rm M}_{\sun}}

\newcommand{\rsun}{{\rm R}_{\sun}}

\newcommand{\rstar}{{\rm R}_{\star}}

\newcommand{\lumsun}{{\rm L}_{\sun}}

\newcommand{\lumstar}{{\rm L}_{\star}}

\newcommand{\lumdisk}{{\rm L}_{\rm disk}}

\newcommand{\etat}{{\eta}_{\rm t}}

\newcommand{\betat}{{\beta}_{\rm t}}

\newcommand{\betai}{{\beta}_{\rm i}}

\newcommand{\deltai}{{\delta}_{\rm i}}

\newcommand{\rhoi}{{\rho}_{\rm i}}

% Bibliography and bibfile
\def\aj{AJ}%
          % Astronomical Journal
\def\actaa{Acta Astron.}%
          % Acta Astronomica
\def\araa{ARA\&A}%
          % Annual Review of Astron and Astrophys
\def\apj{ApJ}%
          % Astrophysical Journal
\def\apjl{ApJ}%
          % Astrophysical Journal, Letters
\def\apjs{ApJS}%
          % Astrophysical Journal, Supplement
\def\ao{Appl.~Opt.}%
          % Applied Optics
\def\apss{Ap\&SS}%
          % Astrophysics and Space Science
\def\aap{A\&A}%
          % Astronomy and Astrophysics
\def\aapr{A\&A~Rev.}%
          % Astronomy and Astrophysics Reviews
\def\aaps{A\&AS}%
          % Astronomy and Astrophysics, Supplement
\def\azh{AZh}%
          % Astronomicheskii Zhurnal
\def\baas{BAAS}%
          % Bulletin of the AAS
\def\bac{Bull. astr. Inst. Czechosl.}%
          % Bulletin of the Astronomical Institutes of Czechoslovakia 
\def\caa{Chinese Astron. Astrophys.}%
          % Chinese Astronomy and Astrophysics
\def\cjaa{Chinese J. Astron. Astrophys.}%
          % Chinese Journal of Astronomy and Astrophysics
\def\icarus{Icarus}%
          % Icarus
\def\jcap{J. Cosmology Astropart. Phys.}%
          % Journal of Cosmology and Astroparticle Physics
\def\jrasc{JRASC}%
          % Journal of the RAS of Canada
\def\mnras{MNRAS}%
          % Monthly Notices of the RAS
\def\memras{MmRAS}%
          % Memoirs of the RAS
\def\na{New A}%
          % New Astronomy
\def\nar{New A Rev.}%
          % New Astronomy Review
\def\pasa{PASA}%
          % Publications of the Astron. Soc. of Australia
\def\pra{Phys.~Rev.~A}%
          % Physical Review A: General Physics
\def\prb{Phys.~Rev.~B}%
          % Physical Review B: Solid State
\def\prc{Phys.~Rev.~C}%
          % Physical Review C
\def\prd{Phys.~Rev.~D}%
          % Physical Review D
\def\pre{Phys.~Rev.~E}%
          % Physical Review E
\def\prl{Phys.~Rev.~Lett.}%
          % Physical Review Letters
\def\pasp{PASP}%
          % Publications of the ASP
\def\pasj{PASJ}%
          % Publications of the ASJ
\def\qjras{QJRAS}%
          % Quarterly Journal of the RAS
\def\rmxaa{Rev. Mexicana Astron. Astrofis.}%
          % Revista Mexicana de Astronomia y Astrofisica
\def\skytel{S\&T}%
          % Sky and Telescope
\def\solphys{Sol.~Phys.}%
          % Solar Physics
\def\sovast{Soviet~Ast.}%
          % Soviet Astronomy
\def\ssr{Space~Sci.~Rev.}%
          % Space Science Reviews
\def\zap{ZAp}%
          % Zeitschrift fuer Astrophysik
\def\nat{Nature}%
          % Nature
\def\iaucirc{IAU~Circ.}%
          % IAU Cirulars
\def\aplett{Astrophys.~Lett.}%
          % Astrophysics Letters
\def\apspr{Astrophys.~Space~Phys.~Res.}%
          % Astrophysics Space Physics Research
\def\bain{Bull.~Astron.~Inst.~Netherlands}%
          % Bulletin Astronomical Institute of the Netherlands
\def\fcp{Fund.~Cosmic~Phys.}%
          % Fundamental Cosmic Physics
\def\gca{Geochim.~Cosmochim.~Acta}%
          % Geochimica Cosmochimica Acta
\def\grl{Geophys.~Res.~Lett.}%
          % Geophysics Research Letters
\def\jcp{J.~Chem.~Phys.}%
          % Journal of Chemical Physics
\def\jgr{J.~Geophys.~Res.}%
          % Journal of Geophysics Research
\def\jqsrt{J.~Quant.~Spec.~Radiat.~Transf.}%
          % Journal of Quantitiative Spectroscopy and Radiative Trasfer
\def\memsai{Mem.~Soc.~Astron.~Italiana}%
          % Mem. Societa Astronomica Italiana
\def\nphysa{Nucl.~Phys.~A}%
          % Nuclear Physics A
\def\physrep{Phys.~Rep.}%
          % Physics Reports
\def\physscr{Phys.~Scr}%
          % Physica Scripta
\def\planss{Planet.~Space~Sci.}%
          % Planetary Space Science
\def\procspie{Proc.~SPIE}%
          % Proceedings of the SPIE
\let\astap=\aap
\let\apjlett=\apjl
\let\apjsupp=\apjs
\let\applopt=\ao

\newcommand{\figpath}{FIGS/}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{SiO Molecular Jets around young stars - A numerical perspective}
\author[B. Vaidya, Tom Douglas, Paola Caselli, Tom Hartquist]{B. Vaidya$^{1}$\thanks{E-mail:
B.Vaidya@leeds.ac.uk (BV)}, Tom Douglas$^{1}$, Paola Caselli$^{1}$, Tom Hartquist$^{1}$\\
$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2
9JT\\
}

\date\today

%\date{Accepted yyyy m dd. Received yyyy m dd; in original yyyy m dd}
\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{yyyy}

\maketitle

\label{firstpage}

\begin{abstract}
  % context heading (optional)
  {}  
  % aims heading (mandatory)
   {}
  % methods heading (mandatory)
   {}
  % results heading (mandatory)
   {}
  % conclusions heading (optional), leave it empty if necessary 
\end{abstract}

   \begin{keywords}
    MHD -- methods:numerical -- ISM: jets and outflows
   \end{keywords}

%
%

%===============================================================

\section{Introduction}

\section{Numerical Setup}
\subsection{Numerical code and Equations}
For our study, we carry out axisymmetric numerical ideal MHD simulations using the PLUTO code \citep{Mignone:2007p644} which is based on a conservative scheme of Godunov type.
We have modified the original code to incorporate molecular cooling
from self-consistent evolution of hydrogen chemistry (see Sect.~\ref{sec:chem}).

In general, the MHD code considers the following set of equations.
The conservation of the mass and the momentum,
%
\begin{equation}\label{masscons}
\frac{\partial \rho}{\partial t} + (\vec{v} \cdot \nabla)\rho  +
\rho \nabla \cdot \vec{v} = 0
\end{equation}
%
\begin{equation}\label{momcons}
\rho(\frac{\partial \vec{v}}{\partial t} +
(\vec{v} \cdot \nabla) \vec{v}) =
- \nabla P + \frac{1}{4\pi} (\nabla \times \vec{B}) \times \vec{B}
\end{equation}
%
where $\rho$ is gas density, $\vec{v}$ the velocity vector, $P$ the gas pressure,
and $\vec{B}$ the magnetic field vector with the poloidal and toroidal
components - $\vec{B}_{\rm p}, {B}_{\phi}$. Note that the forces due
to gravity are neglected for this problem as the domain of interest is
far away from the central object (i.e., star).  
%

The cooling function $\Lambda$ which dependents on temperature $T$, mass density $\rho$ and
chemical abundances {\bf{X}}, appears in the
energy equation as a source term,

\begin{equation}\label{encons1}
\frac{\partial}{\partial t}(\rho E)
+ \nabla \cdot\left[ \rho E \vec{v} + (P + \frac{B^2}{8\pi})\vec{v}\right]  
- \vec{B}(\vec{v}\cdot\vec{B}) = \Lambda(\rho,T,{\bf{X}}),
\end{equation}
%
%\begin{equation}\label{encons1}
%\frac{\partial}{\partial t}(\rho {\rm E}) + \nabla.\left[ (\rho
%{\rm E})\textbf{v} + (\textbf{P} + \frac{B^2}{8
%\pi})\textbf{v}\right] - \textbf{B}(\textbf{v.B}) = \rho\left[
%-\nabla\Phi + (\textbf{F}^{\rm rad})\right].\textbf{v}
%\end{equation}
%
where the total energy density of the flow $E$ comprises contributions from 
the internal energy $\epsilon$, the mechanical energy and the magnetic energy,
%
\begin{equation}\label{encons2}
 E = \epsilon + \frac{v^2}{2} + \frac{B^2}{8 \pi \rho}.
\end{equation}
The gas pressure in the flow is related to the density assuming an equation 
of state with the adiabatic index $\gamma$,
%
\begin{equation}\label{EOS}
P = (\gamma - 1) \rho \epsilon.
\end{equation}

The evolution of chemical abundances for each spiecies is solved via,
%
\begin{equation}\label{chemevol}
\frac{\partial \rho{\bf{X}}_{i}}{\partial t} + \nabla \cdot (\rho
{\bf{X}}_{i} \vec{v})  = \rho {\bf{S}}_{i},
\end{equation}
where ${\bf{S}}_{i}$ represents the net creation or destruction of a
given spiecies through chemical reactions (see Sect.~\ref{sec:chem}).

The evolution of the magnetic field is governed by induction equation,
%
\begin{equation}\label{induction}
\frac{\partial \vec{B}}{\partial t} = \nabla \times \left(\vec{v}\times \vec{B}\right).
\end{equation}
%
In addition to the above set of equations the code obeys the condition of divergence-free 
magnetic fields, $\nabla \cdot \vec{B} = 0$, which is numerically achieved by construction 
since using the Powell's eight wave formulation.
\subsection{Initial Condition}
Describe initial condition - Geometry, domian size, boundary
conditions\\
Physical motivation of initial condition.\\
\section{Chemistry and Cooling}
\label{sec:chem}
Atomic Cooling\\
Molecular cooling fixed abundance -- Tabulated Cooling\\
Molecular cooling with chemistry. \\
Mention briefly Adiabatic and Powerlaw cooling.

\begin{table*}
\begin{minipage}{\textwidth}
\caption{Summary of the chemistry reaction set. T is the temperature
  in Kelvin, $T_{\rm eV}$ is the tempeature in electron-volts, $T_{5}$
  = $T/1\times10^{5}$  and 
$T_{2}$  = T/100}
\begin{tabular}{l l l l}
\hline
No. & Reaction & Rate Coeff ($\rm {cm}^{3} s^{-1}$) &
Reference~\footnote{REFERENCES -- (1) \cite{Cen:1992p13616} [Eq. 26a];
  (2) \cite{Woodall:2007p13623} [UMIST Database] (3)
  \cite{Galli:1998p13066} [Eq. H17]; (4) \cite{Abel:1997p12836}
  [Tab. 3 Eq. 13]; (5) \cite{Hollenbach:1979p12707} [Eq. 3.8]}\\
\hline
1. & H + e$^{-}$ $\rightarrow$ H$^{+}$ + 2e$^{-}$ & $k_1$ = $5.85
\times 10^{-11}$ $T^{0.5}$ \rm{exp}(-157,809.1/T)/(1.0 + $T_{5}^{0.5}$) & 1\\
2. & H$^{+}$ + e$^{-}$ $\rightarrow$ H + h$\nu$ & $k_2$ =
$3.5\times10^{-12} (T/300.0)^{-0.8}$ & 2\\
3. & H$_{2}$ + e$^{-}$ $\rightarrow$ 2H + e$^{-}$ & $k_3$ =
$4.4\times10^{-10} T^{0.35} \rm{exp}(-102,000.0/T)$ & 3\\
4. & H$_{2}$ + H $\rightarrow$ 3H & $k_4$ = $1.067\times10^{-10}
T_{\rm eV}^{2.012}(\rm{exp}(4.463/T_{\rm eV})^{-1}((1. + 0.2472 T_{\rm eV})^{3.512})^{-1} $& 4\\
5. &H$_{2}$ + H$_{2}$ $\rightarrow$ H$_{2}$ + 2H & $k_5$ = $1.0\times 10^{-8} \rm{exp}(-84,100/T)$ & 2\\
6. & H + H $\overset{\rm dust}\longrightarrow$ H$_{2}$ & $k_6 =
3.0\times10^{-17}\sqrt{T_{2}}(1.0 + 0.4\sqrt{T_{2} + 0.15} + 0.2T_{2} + 0.8T_{2}^{2})$ & 5 \\
\hline
\end{tabular}
\end{minipage}
\end{table*}

\section{Radiative Transfer}
Radiative transfer modelling used for post processing.

\subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
The radiative transfer program used is LIME (LIne Modelling Engine; \citealt{Brinch:2010p13078}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model. The method of selecting these points is given in section \ref{subsec:gridding}. At each of these points, the density of the main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+ 0.5 n(H)), gas and dust temperatures, velocity, molecular abundances and unresolved turbulent velocity are specified. These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution. These points are then connected by Delaunay triangulation and it is between the points connected by this method that photon are allowed to propagate (fig.~\ref{grid}). The level populations of the selected molecules are calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated. This is repeated 20 times with the populations of each level converging towards a single value. This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in \citealt{Brinch:2010p13078}) to exceed 1000 for 99\% of the points, ensuring that the simulation has converged on a stable level population. After 20 iterations the model is ray-traced in order to produce synthetic brightness maps. The average of ten separate runs was taken to minimise the artefacts in the output images, resulting from the grid construction (Fig.~\ref{points}).

\begin{figure}
 \includegraphics[width=84mm]{\figpath/eta2Beta10.png}
 \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate for points in the r,z plane. The points are colour coded by the density distribution (in m$^{-3}$, as used in LIME) and are more concentrated in the high density knots.}
\label{grid}
\end{figure}

\subsection{Grid construction} \label{subsec:gridding}
In order to construct the grid, candidate points are randomly selected from the volume to be simulated. These candidates then have their equivalent H$_2$ number density, and the number density of SiO, compared against those of a reference point in order to decide if the candidate point is to be used in the grid or not. Candidate grid points are selected at random in a cylindrical coordinates that is linearly spaced in z and $\theta$ and logarithmically spaced in r. For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold. After selection of random coordinates, the H$_2$ density and SiO density at the candidate point (n and m, respectively) are compared against the densities of a reference point in the unpeturbed ambient medium multipled by $\frac{4\eta}{5}$ (n$_0$ and m$_0$). If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use. Otherwise another r, $\theta$, z co-ordinate is selected and it becomes the candidate point. In addition to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance. This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume. See fig. \ref{points} for an example of the points distribution in r, z. The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all scales while ensuring that the majority of points are located in the inner disc where the density is higher.  \smallskip

\begin{figure}
 \includegraphics[width=63mm]{\figpath/eta2Beta10_histo.png}
 \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions.}
 \label{points}
\end{figure}

\subsection{SiO abundance}
Need refs for this!!\smallskip
The amount of SiO is determined by the local velocity and temperature. The fractional abundance is given by the equation:\smallskip

$log(X)=-2.48\times10^{-8}v^5 + 5.50\times10^{-6}v^4 - 4.28\times10^{-4}v^3 + 1.24\times10^{-2}v^2 + 2.52\times10^{-2}v - 1.20\times10^{1}$\smallskip

where v is in kilometres per second. In addition to this if the temperature at the point is greater than 92,000K (the temperature of the Si-O bond disassociation energy) the abundance is reduced to 10$^{-30}$.

\begin{figure}
 \includegraphics[width=84mm]{\figpath/abun.png}
 \caption{The polynomial used to calculate an abundace of SiO as a function of local velocity.}
 \label{abun}
\end{figure}

\section{Results}
Table 1 -- Parameter runs with changing $\beta$ (magnetic fields) and
$\eta$ (density contrast) for cooling \\
Results should have Peak Intensity after convolution., FWHM at tip of
bow shock.\\
Our reference run -- $\beta$ = 10.0, $\eta$ = 2.0, with cooling and
velocity dependent SiO Abundance. \\
Figure 3 -- Output from MHD simulations (Reference run).\\
Figure 4 -- Output from Rad Transfer (Reference run). Integrated
Intensity Maps for different transitions for three different cooling prescribtions. (TODO : TOM)\\
Figure 5 -- Spectra for the reference runs all transitions. (TODO :
TOM)\\
Figure 6 -- PV diagrams (TODO : TOM) for one transition in two directions.
Figure 7 -- Angle of Inclination dependence

\section{Discussion}
Effects of varying $\beta$, $\eta$\\
Importance of cooling prescriptions\\
RADEX plots ratio of Line intensities???\\
Comparison with Observed results \\
Limitations\\

\section{ALMA view}
ALMA view of the reference run and stress of applying our synthetic techniques
to study the molecular outflows in more details.\\
Figure 6. for ALMA -- \\

\section{Conclusion}
We are the best in modelling SiO outflows.

%\section*{Acknowledgments}

\bibliographystyle{mn2e}
\bibliography{bibfile}
\label{lastpage}
\end{document}

### 2013-07-01 NewJetData/atomic/beta10_eta2/model.c
added files needed for lime runs

@@ -1,0 +1,235 @@
+ /*
+ *  model.c
+ *  LIME, The versatile 3D line modeling tool 
+ *
+ *  Created by Christian Brinch on 11/05/07.
+ *  Copyright 2006-2011, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include "lime.h"
+#include <stdio.h>
+#include "rho.h"
+#include "temp.h"
+#include "vz.h"
+#include "vr.h"
+#include "fH2.h"
+#include "fHII.h"
+#include "fHI.h"
+
+#define length_scale (33.42293086*AU)
+#define centre_z (250)
+#define unit_temp (1)
+#define unit_density (1e6)
+#define unit_velocity (1e3)
+#define arr_size_R (100)
+#define arr_size_Z (500)
+
+
+/******************************************************************************/
+
+void
+input(inputPars *par, image *img){
+/*
+ * Basic parameters. See cheat sheet for details.
+ */
+  par->radius		= 200*length_scale;
+  par->minScale	   	= 0.25*length_scale;
+  par->pIntensity    	= 30000;
+  par->sinkPoints    	= 8000;
+  //par->pregrid          = "populations.pop";
+  //par->dust		= "jena_thin_e6.tab";
+  par->moldatfile[0] 	= "sio.dat";
+  par->outputfile 	= "populations.pop";
+  par->gridfile		= "grid.vtk";
+  par->sampling         = 4;
+  
+/* 
+ * Definitions for image #0. Add blocks for additional images.
+ */
+
+  img[0].nchan =160;
+  //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
+  //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
+  img[0].trans = 0;
+  img[0].velres= 750;
+  img[0].pxls			= 256;	      // Pixels per dimension
+  img[0].imgres			= 1.75;		  // Resolution in arc seconds
+  img[0].theta			= PI/3;		  // 0: face-on, pi/2: edge-on
+  img[0].distance		= length_scale/AU*PC;	  //1" == 1 length scale
[…]

### 2013-07-01 NewJetData/tabulated/fits2h.py

@@ -1,0 +1,41 @@
+#!/opt/epd-7.2-2-rh5-x86_64/bin/python
+import pyfits as P
+import numpy as np
+
+def writer (data, name, opath):
+    S=np.array(data.shape)
+    SS=np.array([S[i:].prod() for i in xrange(-S.size+1,0)])
+    c=0
+    of=open(opath,'w')
+    print SS
+    of.write('const static double '+name+''.join(tuple([str([x]) for x in data.shape]))+' = {')
+    for x in data.flat:
+        c+=1
+        ns=c%SS
+        for n in ns:
+            if n==1: of.write('{')
+        of.write("%.3e"%x)
+        if (ns!=0).all()or c==0: of.write(', ')
+        elif c!=0: 
+            for (i,n) in enumerate(ns[::-1]):
+                if n==0: 
+                    of.write('}')
+                    if i==ns.size-1: 
+                        if c!=data.size: of.write(',\n')
+                        else: of.write('\n')
+                    else:
+                        if ns[::-1][i+1]==0: 
+                            of.write('\n')
+                        else: of.write(',\n')
+    of.write('};')
+
+                                                       
+if __name__ == '__main__':
+    fitsf=raw_input("name of fits file to convert: ")
+    data=P.getdata(fitsf)
+    opath=raw_input("name of output header file: ")
+    if not(opath): opath=fitsf.split('.')[0]+'.h'
+    elif opath.split('.')[-1]!='h' : opath=opath+'.h'
+    name=raw_input("name of array in header file: ")
+    if not(name): name=opath.split('.')[0]
+    writer(data, name, opath)

### 2013-07-01 NewJetData/atomic/beta10_eta10/fits2h.py
set up fits2h for batch processing

@@ -31,7 +31,8 @@ def writer (data, name, opath):
 
                                                        
 if __name__ == '__main__':
-    fitsf=raw_input("name of fits file to convert: ")
+ fitsf=raw_input("name of fits file to convert: ")
+ while fitsf:
     data=P.getdata(fitsf)
     opath=raw_input("name of output header file: ")
     if not(opath): opath=fitsf.split('.')[0]+'.h'
@@ -39,3 +40,4 @@ if __name__ == '__main__':
     name=raw_input("name of array in header file: ")
     if not(name): name=opath.split('.')[0]
     writer(data, name, opath)
+    fitsf=raw_input("name of fits file to convert: ")

### 2013-07-06 NewJetData/atomic/beta01_eta10/model.c
models

@@ -17,17 +17,15 @@
 #include "temp.h"
 #include "vz.h"
 #include "vr.h"
-#include "fH2.h"
-#include "fHII.h"
-#include "fHI.h"
+#include "fneut.h"
 
-#define length_scale (33.42293086*AU)
-#define centre_z (250)
+#define length_scale (16.71146539*AU)
+#define centre_z (600)
 #define unit_temp (1)
 #define unit_density (1e6)
 #define unit_velocity (1e3)
-#define arr_size_R (100)
-#define arr_size_Z (500)
+#define arr_size_R (200)
+#define arr_size_Z (1000)
 
 
 /******************************************************************************/
@@ -52,53 +50,53 @@ input(inputPars *par, image *img){
  * Definitions for image #0. Add blocks for additional images.
  */
 
-  img[0].nchan =160;
+  img[0].nchan =80;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
   //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
   img[0].trans = 0;
-  img[0].velres= 750;
+  img[0].velres= 500;
   img[0].pxls			= 256;	      // Pixels per dimension
-  img[0].imgres			= 1.75;		  // Resolution in arc seconds
-  img[0].theta			= PI/3;		  // 0: face-on, pi/2: edge-on
+  img[0].imgres			= 2.5;		  // Resolution in arc seconds
+  img[0].theta			= PI/2;		  // 0: face-on, pi/2: edge-on
   img[0].distance		= length_scale/AU*PC;	  //1" == 1 length scale
   img[0].source_vel		= 0;          // source velocity in m/s
   img[0].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau
   img[0].filename		= "image_J1-0_60deg_molcool.fits";	// Output filename
 
-  img[1].nchan =160;
+  img[1].nchan =80;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
   //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
   img[1].trans = 1;
[…]

### 2013-07-06 NewJetData/atomic/beta10_eta10/model.c

@@ -17,17 +17,15 @@
 #include "temp.h"
 #include "vz.h"
 #include "vr.h"
-#include "fH2.h"
-#include "fHII.h"
-#include "fHI.h"
+#include "fneut.h"
 
-#define length_scale (33.42293086*AU)
-#define centre_z (250)
+#define length_scale (16.71146539*AU)
+#define centre_z (600)
 #define unit_temp (1)
 #define unit_density (1e6)
 #define unit_velocity (1e3)
-#define arr_size_R (100)
-#define arr_size_Z (500)
+#define arr_size_R (200)
+#define arr_size_Z (1000)
 
 
 /******************************************************************************/
@@ -52,53 +50,53 @@ input(inputPars *par, image *img){
  * Definitions for image #0. Add blocks for additional images.
  */
 
-  img[0].nchan =160;
+  img[0].nchan =80;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
   //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
   img[0].trans = 0;
-  img[0].velres= 750;
+  img[0].velres= 500;
   img[0].pxls			= 256;	      // Pixels per dimension
-  img[0].imgres			= 1.75;		  // Resolution in arc seconds
-  img[0].theta			= PI/3;		  // 0: face-on, pi/2: edge-on
+  img[0].imgres			= 2.5;		  // Resolution in arc seconds
+  img[0].theta			= PI/2;		  // 0: face-on, pi/2: edge-on
   img[0].distance		= length_scale/AU*PC;	  //1" == 1 length scale
   img[0].source_vel		= 0;          // source velocity in m/s
   img[0].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau
   img[0].filename		= "image_J1-0_60deg_molcool.fits";	// Output filename
 
-  img[1].nchan =160;
+  img[1].nchan =80;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
[…]

### 2013-07-06 NewJetData/atomic/beta10_eta2/model.c

@@ -17,17 +17,15 @@
 #include "temp.h"
 #include "vz.h"
 #include "vr.h"
-#include "fH2.h"
-#include "fHII.h"
-#include "fHI.h"
+#include "fneut.h"
 
-#define length_scale (33.42293086*AU)
-#define centre_z (250)
+#define length_scale (16.71146539*AU)
+#define centre_z (600)
 #define unit_temp (1)
 #define unit_density (1e6)
 #define unit_velocity (1e3)
-#define arr_size_R (100)
-#define arr_size_Z (500)
+#define arr_size_R (200)
+#define arr_size_Z (1000)
 
 
 /******************************************************************************/
@@ -52,53 +50,53 @@ input(inputPars *par, image *img){
  * Definitions for image #0. Add blocks for additional images.
  */
 
-  img[0].nchan =160;
+  img[0].nchan =80;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
   //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
   img[0].trans = 0;
-  img[0].velres= 750;
+  img[0].velres= 500;
   img[0].pxls			= 256;	      // Pixels per dimension
-  img[0].imgres			= 1.75;		  // Resolution in arc seconds
-  img[0].theta			= PI/3;		  // 0: face-on, pi/2: edge-on
+  img[0].imgres			= 2.5;		  // Resolution in arc seconds
+  img[0].theta			= PI/2;		  // 0: face-on, pi/2: edge-on
   img[0].distance		= length_scale/AU*PC;	  //1" == 1 length scale
   img[0].source_vel		= 0;          // source velocity in m/s
   img[0].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau
   img[0].filename		= "image_J1-0_60deg_molcool.fits";	// Output filename
 
-  img[1].nchan =160;
+  img[1].nchan =80;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
[…]

### 2013-07-06 NewJetData/tabulated/model.c

@@ -17,17 +17,17 @@
 #include "temp.h"
 #include "vz.h"
 #include "vr.h"
-#include "fH2.h"
-#include "fHII.h"
-#include "fHI.h"
+/* #include "fH2.h" */
+/* #include "fHII.h" */
+/* #include "fHI.h" */
 
-#define length_scale (33.42293086*AU)
-#define centre_z (250)
+#define length_scale (16.71146539*AU)
+#define centre_z (600)
 #define unit_temp (1)
 #define unit_density (1e6)
 #define unit_velocity (1e3)
-#define arr_size_R (100)
-#define arr_size_Z (500)
+#define arr_size_R (200)
+#define arr_size_Z (1000)
 
 
 /******************************************************************************/
@@ -52,53 +52,53 @@ input(inputPars *par, image *img){
  * Definitions for image #0. Add blocks for additional images.
  */
 
-  img[0].nchan =160;
+  img[0].nchan =80;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
   //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
   img[0].trans = 0;
-  img[0].velres= 750;
+  img[0].velres= 500;
   img[0].pxls			= 256;	      // Pixels per dimension
-  img[0].imgres			= 1.75;		  // Resolution in arc seconds
-  img[0].theta			= PI/3;		  // 0: face-on, pi/2: edge-on
+  img[0].imgres			= 2.5;		  // Resolution in arc seconds
+  img[0].theta			= PI/2;		  // 0: face-on, pi/2: edge-on
   img[0].distance		= length_scale/AU*PC;	  //1" == 1 length scale
   img[0].source_vel		= 0;          // source velocity in m/s
   img[0].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau
   img[0].filename		= "image_J1-0_60deg_molcool.fits";	// Output filename
 
-  img[1].nchan =160;
+  img[1].nchan =80;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
[…]

### 2013-07-06 PAPER/ms_final_bv.tex

@@
 
-\newcommand{\figpath}{FIGS/}
+\newcommand{\figpath}{PFIGS/}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Initial Condition}
+Physical motivation of initial condition.\\
 Describe initial condition - Geometry, domian size, boundary
 conditions\\
-Physical motivation of initial condition.\\
+
 \section{Chemistry and Cooling}
 \label{sec:chem}
-Atomic Cooling\\
-Molecular cooling fixed abundance -- Tabulated Cooling\\
-Molecular cooling with chemistry. \\
-Mention briefly Adiabatic and Powerlaw cooling.
+\subsection{Power law cooling}
+\subsection{Atomic Cooling}
+\subsection{Tabulated Cooling}
+
+\subsection{Molecular Cooling}
+The evolution of molecular, atomic and ionized hydrogen is govenerd by
+equations listed in Table~\ref{tab:chemeq}. In this cooling mode,
+these equations are evolved at each times using temperature dependent
+rates mentioned in the table along with their source. The code tracks
+the formation and destruction of three quantities viz, X(HI), X($H_{2}$)
+and X(HII) with a constraint that sum of all three should be unity.
+Further, these abundances are used to update the cooling
+function $\Lambda(n,T,{\bf{X}})$ to consistently derive the
+temperature for next advection step.
+
+For all the models presented in this paper, we have
 
@@
 $T_{2}$  = T/100}
+\label{tab:chemeq}
 \begin{tabular}{l l l l}
@@
 \section{Results}
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
+ \caption{Jet Volume Density for different cooling modes with
+   $\eta$ = 10 and $\beta$ = 10.}
+\label{grid}
+\end{figure*}
+\begin{table*}
+\centering
+\caption{Summary from parameter runs}
+\begin{tabular}{l | l | l | l | l | l }
+\hline
+Run & Cooling Mode & $\eta$ & $\beta$ & Peak Intensity [K] & FWHM at Bow
+Shock \\
+\hline\hline
+adi1010 & Nil (Adiabatic) & 10 & 10 &&\\
+pow1010 & Power law & 10 & 10 &&\\
+atm1010 & Atomic & 10 & 10 &&\\
+atm101 & Atomic & 10 & 1 &&\\
+atm210 & Atomic & 2 & 10 &&\\
+tab1010 & Tabulated & 10 & 10 &&\\
+tab210 & Tabulated & 2 & 10&&\\
+mol1010 & Molecular & 10 & 10&&\\
+mol510 & Molecular & 5 & 10&&\\
+\hline
+\end{tabular}
+\label{tab:result1}
+\end{table*}
+
 Table 1 -- Parameter runs with changing $\beta$ (magnetic fields) and

### 2013-07-08 PAPER/ms_final_bv.tex
Added the initial condition

@@
 
-The evolution of chemical abundances for each spiecies is solved via,
+The evolution of chemical abundances for each species is solved via,
 %
@@
 where ${\bf{S}}_{i}$ represents the net creation or destruction of a
-given spiecies through chemical reactions (see Sect.~\ref{sec:chem}).
+given species through chemical reactions (see Sect.~\ref{sec:chem}).
 
@@
 \subsection{Initial Condition}
-Physical motivation of initial condition.\\
-Describe initial condition - Geometry, domian size, boundary
-conditions\\
+We model the propagation of jet as it interacts with the molecular
+cloud core much further from the central object, i.e., $>$ 1000\,AU. 
+Further away from the central source, the downward pull of gravity plays a
+negligible role and the dynamics of jet is primarily governed by magnetic fields.
+The total magnetic field in jet is dominated by the toroidal
+component. This is because the poloidal field decays as $z^{-2}$ as
+compared to $z^{-1}$ for toroidal field to maintain the force balance ($z$ is the vertical distance from source). 
+The hoop stress due to pinch force from toroidal magnetic fields maintains the
+a highly collimated beam like structure for the jet.
+%
+
+The ambient medium with which the jet interacts primarily
+represents the molecular cloud core. The numerical domain is axi-symmetric
+and in (r,z,$\phi$) cylindrical co-ordinates. Its extent in radial
+direction is 20 $R_{\rm j}$ and 100
+$R_{\rm j}$ along the vertical axis, $R_{\rm j}$ being the radius of
+the jet. The domain is resolved by an uniform grid with 200 cells in
+radial and 1000 cells in vertical direction. For simplicity, we choose this medium
+to be unmagnetized and non-turbulent. The density in the ambient
+medium varies with vertical height $z$ as, $\rho_{\rm amb}\sim (\rho_0/z^{2})$
+consistent with observations \citep{Caselli:2011p13935}. The value of
+$\rho_0$ depends upon the density contrast, $\eta$, between the jet and
+the ambient medium. The number density in the jet is kept fixed such
+that the density in ambient medium lies within a range of $10^{4}-10^{5}
+\rm cm^{-3}$. The pressure in the ambient molecular medium is
+set so to maintain a constant temperature of 50\,K. 
+%
+
+The jet enters into the medium through a nozzle of radius $R_{\rm jet}$
+from the lower boundary (z = 0). The jet density is fixed to
+be $10^{5} \rm cm^{-3}$ and it has a radius of $2.5\times10^{15} \rm cm \sim
+167\,AU$. The jet is injected into the domain with a typical 
+velocity of $v_{\rm jet,0}$ = 100 km/s as is the case for most low mass stellar jets
+specially the low velocity component. The constant jet velocity is
+superimposed with periodic pulsation of the form,
+\begin{equation}
+v_{\rm jet} = v_{\rm jet,0}(1.0 + A\,sin(t/T_{\rm p}))
+\end{equation}
+where the amplitude A is 0.25 and time period $T_{\rm p} = 10$
+years. The pressure at the surface of the jet is $10^{-10} \rm
+dyne\,\,cm^{-2}$ corresponding to a temperature of $T_{\rm jet} \sim
+4\times10^{3}\,K$. Inside the jet beam, a radial variation of thermal
+and magnetic pressure is adopted to maintain a magneto-static
+equilibrium. We adopt the
+same radial profiles used by \cite{Stone:2000p2650} for all our runs. 
+Based on these profiles, the toroidal magnetic field is assumed to be
+zero at the axis and achieves a maximum at some radius, $r_{\rm m}$
+inside the jet. The maximum value, $B_{\phi,\rm m}$, depends on the
+plasma $\beta$ which is a parameter used for our study along with the
+density contrast $\eta$.
+%
+
+In order to consistently model the SiO emission arising from shocks as
+this jet interacts with the medium, we evolve the dynamics along with
+chemistry and cooling prescribtions. They are described in details in
+the next section.
 
@@
 \subsection{Molecular Cooling}
-The evolution of molecular, atomic and ionized hydrogen is govenerd by
+The evolution of molecular, atomic and ionized hydrogen is governed by
 equations listed in Table~\ref{tab:chemeq}. In this cooling mode,
@@
 rates mentioned in the table along with their source. The code tracks
-the formation and destruction of three quantities viz, X(HI), X($H_{2}$)
+the formation and destruction of three quantities viz., X(HI), X($H_{2}$)
 and X(HII) with a constraint that sum of all three should be unity.
@@
 \caption{Summary of the chemistry reaction set. T is the temperature
-  in Kelvin, $T_{\rm eV}$ is the tempeature in electron-volts, $T_{5}$
+  in Kelvin, $T_{\rm eV}$ is the temperature in electron-volts, $T_{5}$
   = $T/1\times10^{5}$  and 
@@
 \hline
-No. & Reaction & Rate Coeff ($\rm {cm}^{3} s^{-1}$) &
+No. & Reaction & Rate Coefficient ($\rm {cm}^{3} s^{-1}$) &
 Reference~\footnote{REFERENCES -- (1) \cite{Cen:1992p13616} [Eq. 26a];
@@
 \section{Radiative Transfer}
-Radiative transfer modelling used for post processing.
+Radiative transfer modeling used for post processing.
 
 \subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
-The radiative transfer program used is LIME (LIne Modelling Engine; \citealt{Brinch:2010p13078}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
+The radiative transfer program used is LIME (LIne Modeling Engine; \citealt{Brinch:2010p13078}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
 The method of selecting these points is given in section \ref{subsec:gridding}.
@@
  \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate for points in the r,z plane.
-The points are colour coded by the density distribution (in m$^{-3}$, as used in LIME) and are more concentrated in the high density knots.}
+The points are color coded by the density distribution (in m$^{-3}$, as used in LIME) and are more concentrated in the high density knots.}
 \label{grid}
@@
 For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random coordinates, the H$_2$ density and SiO density at the candidate point (n and m, respectively) are compared against the densities of a reference point in the unpeturbed ambient medium multipled by $\frac{4\eta}{5}$ (n$_0$ and m$_0$).
+After selection of random coordinates, the H$_2$ density and SiO density at the candidate point (n and m, respectively) are compared against the densities of a reference point in the un-perturbed ambient medium multiplied by $\frac{4\eta}{5}$ (n$_0$ and m$_0$).
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use.
@@
  \includegraphics[width=84mm]{\figpath/abun.png}
- \caption{The polynomial used to calculate an abundace of SiO as a function of local velocity.}
+ \caption{The polynomial used to calculate an abundance of SiO as a function of local velocity.}
  \label{abun}

### 2013-07-08 PAPER/ms_final_bv.tex
Added cooling plots

@@
 \subsection{Molecular Cooling}
+\label{ssec:molcool}
 The evolution of molecular, atomic and ionized hydrogen is governed by
@@
 
-For all the models presented in this paper, we have
+\begin{figure*}
+ \includegraphics[width=1\columnwidth]{\figpath/H2ReactionRates.png}
+ \includegraphics[width=1\columnwidth]{\figpath/H2CoolingFuncs.png}
+ \caption{Variation of $H_2$ chemistry reaction rates, $k_{i}$ and cooling
+   function $\Lambda(n,T,{\bf{X}})$ with temperature for the initial
+   state (see Sect.~\ref{ssec:molcool})}
+\label{fig:tempvar}
+\end{figure*}
 

### 2013-07-08 PAPER/ms_final_bv.tex
first rough figs from paper runs added

--- 2013-07-06 PAPER/ms_final_bv.tex
@@
 \label{tab:result1}
+
 \end{table*}
+
+\begin{figure}
+ \includegraphics[width=84mm]{\figpath/J2-1_mom0maps_cooling.png}
+ \caption{A plot of the integrated SiO J2-1 emission from 5 models, each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
+\label{cooling2-1}
+\end{figure}
+
+\begin{figure*}
+ \includegraphics[width=168mm]{\figpath/tabulated_mom0maps_Trans.png}
+ \caption{The integrated intensity of 4 SiO transitions in the tabulated cooling model in the $\eta$=2 $\beta$=10 model.}
+\label{tabulatedTrans}
+\end{figure*}
+
+\begin{figure}
+ \includegraphics[width=84mm]{\figpath/tab_trans_spectra.png}
+ \caption{The Integrated emission and spectra at he bow shock for 2 transitions of the tabulated cooling model for $\eta$=2 $\beta$=10 (spectra taken from y=50, x=128).}
+\label{grid}
+\end{figure}
 

### 2013-07-08 NewJetData/tabulated/fits2h.py

@@ -1,43 +1,0 @@
-#!/opt/epd-7.2-2-rh5-x86_64/bin/python
-import pyfits as P
-import numpy as np
-
-def writer (data, name, opath):
-    S=np.array(data.shape)
-    SS=np.array([S[i:].prod() for i in xrange(-S.size+1,0)])
-    c=0
-    of=open(opath,'w')
-    print SS
-    of.write('const static double '+name+''.join(tuple([str([x]) for x in data.shape]))+' = {')
-    for x in data.flat:
-        c+=1
-        ns=c%SS
-        for n in ns:
-            if n==1: of.write('{')
-        of.write("%.3e"%x)
-        if (ns!=0).all()or c==0: of.write(', ')
-        elif c!=0: 
-            for (i,n) in enumerate(ns[::-1]):
-                if n==0: 
-                    of.write('}')
-                    if i==ns.size-1: 
-                        if c!=data.size: of.write(',\n')
-                        else: of.write('\n')
-                    else:
-                        if ns[::-1][i+1]==0: 
-                            of.write('\n')
-                        else: of.write(',\n')
-    of.write('};')
-
-                                                       
-if __name__ == '__main__':
- fitsf=raw_input("name of fits file to convert: ")
- while fitsf:
-    data=P.getdata(fitsf)
-    opath=raw_input("name of output header file: ")
-    if not(opath): opath=fitsf.split('.')[0]+'.h'
-    elif opath.split('.')[-1]!='h' : opath=opath+'.h'
-    name=raw_input("name of array in header file: ")
-    if not(name): name=opath.split('.')[0]
-    writer(data, name, opath)
-    fitsf=raw_input("name of fits file to convert: ")

### 2013-07-08 NewJetData/tabulated/model.c

@@ -1,235 +1,0 @@
- /*
- *  model.c
- *  LIME, The versatile 3D line modeling tool 
- *
- *  Created by Christian Brinch on 11/05/07.
- *  Copyright 2006-2011, Christian Brinch, 
- *  <brinch@nbi.dk>
- *  Niels Bohr institutet
- *  University of Copenhagen
- *	All rights reserved.
- *
- */
-
-#include "lime.h"
-#include <stdio.h>
-#include "rho.h"
-#include "temp.h"
-#include "vz.h"
-#include "vr.h"
-/* #include "fH2.h" */
-/* #include "fHII.h" */
-/* #include "fHI.h" */
-
-#define length_scale (16.71146539*AU)
-#define centre_z (600)
-#define unit_temp (1)
-#define unit_density (1e6)
-#define unit_velocity (1e3)
-#define arr_size_R (200)
-#define arr_size_Z (1000)
-
-
-/******************************************************************************/
-
-void
-input(inputPars *par, image *img){
-/*
- * Basic parameters. See cheat sheet for details.
- */
-  par->radius		= 200*length_scale;
-  par->minScale	   	= 0.25*length_scale;
-  par->pIntensity    	= 30000;
-  par->sinkPoints    	= 8000;
-  //par->pregrid          = "populations.pop";
-  //par->dust		= "jena_thin_e6.tab";
-  par->moldatfile[0] 	= "sio.dat";
-  par->outputfile 	= "populations.pop";
-  par->gridfile		= "grid.vtk";
-  par->sampling         = 4;
-  
-/* 
- * Definitions for image #0. Add blocks for additional images.
- */
-
-  img[0].nchan =80;
-  //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
-  //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
-  img[0].trans = 0;
-  img[0].velres= 500;
-  img[0].pxls			= 256;	      // Pixels per dimension
-  img[0].imgres			= 2.5;		  // Resolution in arc seconds
-  img[0].theta			= PI/2;		  // 0: face-on, pi/2: edge-on
-  img[0].distance		= length_scale/AU*PC;	  //1" == 1 length scale
[…]

### 2013-07-10 NewJetData/molecular/eta10beta10/model.c
added all model files

@@ -1,0 +1,263 @@
+ /*
+ *  model.c
+ *  LIME, The versatile 3D line modeling tool 
+ *
+ *  Created by Christian Brinch on 11/05/07.
+ *  Copyright 2006-2011, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include "lime.h"
+#include <stdio.h>
+#include "rho.h"
+#include "temp.h"
+#include "vz.h"
+#include "vr.h"
+//#include "fneut.h"
+#include "fHI.h"
+#include "fHII.h"
+#include "fH2.h"
+
+
+#define length_scale (16.71146539*AU)
+#define centre_z (750)
+#define unit_temp (1)
+#define unit_density (1e6)
+#define unit_velocity (1e3)
+#define arr_size_R (200)
+#define arr_size_Z (1000)
+
+
+/******************************************************************************/
+
+void
+input(inputPars *par, image *img){
+/*
+ * Basic parameters. See cheat sheet for details.
+ */
+  par->radius		= 200*length_scale;
+  par->minScale	   	= 0.25*length_scale;
+  par->pIntensity    	= 30000;
+  par->sinkPoints    	= 8000;
+  //par->pregrid          = "populations.pop";
+  //par->dust		= "jena_thin_e6.tab";
+  par->moldatfile[0] 	= "sio.dat";
+  par->outputfile 	= "populations.pop";
+  par->gridfile		= "grid.vtk";
+  par->sampling         = 4;
+  
+/* 
+ * Definitions for image #0. Add blocks for additional images.
+ */
+
+  /* img[0].nchan =80; */
+  /* //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3; */
+  /* //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth */
+  /* img[0].trans = 0; */
+  /* img[0].velres= 500; */
+  /* img[0].pxls			= 256;	      // Pixels per dimension */
+  /* img[0].imgres			= 2.5;		  // Resolution in arc seconds */
[…]

### 2013-07-10 NewJetData/tabulated/eta02beta10/model.c

@@ -1,0 +1,235 @@
+ /*
+ *  model.c
+ *  LIME, The versatile 3D line modeling tool 
+ *
+ *  Created by Christian Brinch on 11/05/07.
+ *  Copyright 2006-2011, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include "lime.h"
+#include <stdio.h>
+#include "rho.h"
+#include "temp.h"
+#include "vz.h"
+#include "vr.h"
+/* #include "fH2.h" */
+/* #include "fHII.h" */
+/* #include "fHI.h" */
+
+#define length_scale (16.71146539*AU)
+#define centre_z (600)
+#define unit_temp (1)
+#define unit_density (1e6)
+#define unit_velocity (1e3)
+#define arr_size_R (200)
+#define arr_size_Z (1000)
+
+
+/******************************************************************************/
+
+void
+input(inputPars *par, image *img){
+/*
+ * Basic parameters. See cheat sheet for details.
+ */
+  par->radius		= 200*length_scale;
+  par->minScale	   	= 0.25*length_scale;
+  par->pIntensity    	= 30000;
+  par->sinkPoints    	= 8000;
+  //par->pregrid          = "populations.pop";
+  //par->dust		= "jena_thin_e6.tab";
+  par->moldatfile[0] 	= "sio.dat";
+  par->outputfile 	= "populations.pop";
+  par->gridfile		= "grid.vtk";
+  par->sampling         = 4;
+  
+/* 
+ * Definitions for image #0. Add blocks for additional images.
+ */
+
+  img[0].nchan =80;
+  //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
+  //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
+  img[0].trans = 0;
+  img[0].velres= 500;
+  img[0].pxls			= 256;	      // Pixels per dimension
+  img[0].imgres			= 2.5;		  // Resolution in arc seconds
+  img[0].theta			= PI/2;		  // 0: face-on, pi/2: edge-on
+  img[0].distance		= length_scale/AU*PC;	  //1" == 1 length scale
[…]

### 2013-07-10 NewJetData/tabulated/eta10beta10/model.c

@@ -1,0 +1,261 @@
+ /*
+ *  model.c
+ *  LIME, The versatile 3D line modeling tool 
+ *
+ *  Created by Christian Brinch on 11/05/07.
+ *  Copyright 2006-2011, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include "lime.h"
+#include <stdio.h>
+#include "rho.h"
+#include "temp.h"
+#include "vz.h"
+#include "vr.h"
+/* #include "fH2.h" */
+/* #include "fHII.h" */
+/* #include "fHI.h" */
+
+#define length_scale (16.71146539*AU)
+#define centre_z (750)
+#define unit_temp (1)
+#define unit_density (1e6)
+#define unit_velocity (1e3)
+#define arr_size_R (200)
+#define arr_size_Z (1000)
+
+
+/******************************************************************************/
+
+void
+input(inputPars *par, image *img){
+/*
+ * Basic parameters. See cheat sheet for details.
+ */
+  par->radius		= 200*length_scale;
+  par->minScale	   	= 0.25*length_scale;
+  par->pIntensity    	= 30000;
+  par->sinkPoints    	= 8000;
+  //par->pregrid          = "populations.pop";
+  //par->dust		= "jena_thin_e6.tab";
+  par->moldatfile[0] 	= "sio.dat";
+  par->outputfile 	= "populations.pop";
+  par->gridfile		= "grid.vtk";
+  par->sampling         = 4;
+  
+/* 
+ * Definitions for image #0. Add blocks for additional images.
+ */
+
+  img[0].nchan =80;
+  //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
+  //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
+  img[0].trans = 0;
+  img[0].velres= 500;
+  img[0].pxls			= 256;	      // Pixels per dimension
+  img[0].imgres			= 2.5;		  // Resolution in arc seconds
+  img[0].theta			= PI/2;		  // 0: face-on, pi/2: edge-on
[…]

### 2013-07-15 NewJetData/molecular/eta05beta10/model.c
changed moleculae model files to ensure they sample all the jet

@@ -24,7 +24,7 @@
 
 
 #define length_scale (16.71146539*AU)
-#define centre_z (750)
+#define centre_z (800)
 #define unit_temp (1)
 #define unit_density (1e6)
 #define unit_velocity (1e3)
@@ -41,8 +41,8 @@ input(inputPars *par, image *img){
  */
   par->radius		= 200*length_scale;
   par->minScale	   	= 0.25*length_scale;
-  par->pIntensity    	= 30000;
-  par->sinkPoints    	= 8000;
+  par->pIntensity    	= 35000;
+  par->sinkPoints    	= 9000;
   //par->pregrid          = "populations.pop";
   //par->dust		= "jena_thin_e6.tab";
   par->moldatfile[0] 	= "sio.dat";
@@ -119,18 +119,32 @@ input(inputPars *par, image *img){
   /* img[4].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau */
   /* img[4].filename		= "image_J8-7_90deg_molcool.fits";	// Output filename */
 
-  img[0].nchan =120;
+  img[0].nchan =160;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
   //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
   img[0].trans = 4;
-  img[0].velres= 500;
+  img[0].velres= 750;
   img[0].pxls			= 256;	      // Pixels per dimension
-  img[0].imgres			= 2.5;		  // Resolution in arc seconds
+  img[0].imgres			= 2;		  // Resolution in arc seconds
   img[0].theta			= PI/3;		  // 0: face-on, pi/2: edge-on
   img[0].distance		= length_scale/AU*PC;	  //1" == 1 length scale
   img[0].source_vel		= 0;          // source velocity in m/s
   img[0].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau
   img[0].filename		= "image_J5-4_60deg_molcool.fits";	// Output filename
+
+
+  img[1].nchan =160;
+  //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
+  //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
+  img[1].trans = 1;
[…]

### 2013-07-15 NewJetData/molecular/eta10beta10/model.c

@@ -119,11 +119,11 @@ input(inputPars *par, image *img){
   /* img[4].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau */
   /* img[4].filename		= "image_J8-7_90deg_molcool.fits";	// Output filename */
 
-  img[0].nchan =120;
+  img[0].nchan =160;
   //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
   //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
   img[0].trans = 4;
-  img[0].velres= 500;
+  img[0].velres= 750;
   img[0].pxls			= 256;	      // Pixels per dimension
   img[0].imgres			= 2.5;		  // Resolution in arc seconds
   img[0].theta			= PI/3;		  // 0: face-on, pi/2: edge-on
@@ -131,6 +131,20 @@ input(inputPars *par, image *img){
   img[0].source_vel		= 0;          // source velocity in m/s
   img[0].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau
   img[0].filename		= "image_J5-4_60deg_molcool.fits";	// Output filename
+
+
+  img[1].nchan =160;
+  //  img[0].freq                   = 43.587806e9*(1+3.3e5/CLIGHT*cos(PI/2))+4.587806e8/6/3;
+  //  img[0].bandwidth              = 4.587806e8/3.0; // 30km/s across whole bandwidth
+  img[1].trans = 1;
+  img[1].velres= 750;
+  img[1].pxls			= 256;	      // Pixels per dimension
+  img[1].imgres			= 2.5;		  // Resolution in arc seconds
+  img[1].theta			= PI/3;		  // 0: face-on, pi/2: edge-on
+  img[1].distance		= length_scale/AU*PC;	  //1" == 1 length scale
+  img[1].source_vel		= 0;          // source velocity in m/s
+  img[1].unit			= 0;		  // 0:Kelvin 1:Jansky/pixel 2:SI 3:Lsun/pixel 4:tau
+  img[1].filename		= "image_J2-1_60deg_molcool.fits";	// Output filename
 }
 /******************************************************************************/
 

### 2013-07-15 PAPER/ms_final_bv.tex
Added eta3 for molecular run

@@
 \section{Introduction} 
+Interaction of jet with ambient medium , Class 0 sources, momentum and
+energy injection, High mass and low mass outflows \\
+
+Observations of Outflows in CO and SiO in mm, H2 in IR, Optical jets
+HH objects, syncrotron emission \\
+
+Molecules from jet driven or wind driven, Interesting features like
+EHV, low velocity component etc, list interesting outflows from Class 0 \\
+
+Attempts of simulations either only dynamics with analytic approaches
+to compare observational features, or only chemistry to estimate
+abundances. The reality lies in the middle!\\
+
+Combine dynamics of MHD jet with molecular chemistry and comparing
+with observations via post-processing simulations with line radiative
+transfer codes. \\
+
+Paper Layout \\
 
@@
 \begin{equation}
-v_{\rm jet} = v_{\rm jet,0}(1.0 + A\,sin(t/T_{\rm p}))
+v_{\rm jet} = v_{\rm jet,0}(1.0 + A\,sin(2.0\pi t/T_{\rm p}))
 \end{equation}
-where the amplitude A is 0.25 and time period $T_{\rm p} = 10$
+where the amplitude A is 0.25 and time period $T_{\rm p} = 70$
 years. The pressure at the surface of the jet is $10^{-10} \rm
@@
 \end{figure*}
+
+\section{Results}
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/molcjet_510.png}
+ \caption{Fraction of hydrogen species in the run with molecular
+   cooling having $\eta$ = 5 and $\beta$ = 10.}
+\label{grid}
+\end{figure*}
+
 \begin{table*}

### 2013-07-16 src/aux.c
added modified LIME src files

@@ -1,0 +1,316 @@
+/*
+ *  aux.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 16/11/06.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include "lime.h"
+#include <gsl/gsl_sort.h>
+#include <gsl/gsl_statistics.h>
+
+
+void 
+parseInput(inputPars *par, image **img, molData **m){
+  FILE *fp;
+  int i,id;
+  double BB[3];
+  
+  /* Set default values */
+  par->tcmb = 2.728;
+  par->lte_only=0;
+  par->sampling=0;
+  par->blend=0;
+  par->antialias=1;
+  par->polarization=0;
+  
+  /* Allocate space for output fits images */
+  (*img)=malloc(sizeof(image)*100);
+  par->moldatfile=malloc(sizeof(char *) * 100);
+  for(id=0;id<100;id++){
+    (*img)[id].filename=NULL;
+    par->moldatfile[id]=NULL;
+  }
+  input(par, *img);
+  id=0;
+  while((*img)[++id].filename!=NULL);
+  par->nImages=id;
+  if(par->nImages==0) {
+    if(!silent) bail_out("Error: no images defined");
+    exit(1);
+  }
+  
+  free(*img);
+  *img=malloc(sizeof(image)*par->nImages);
+  
+  
+  
+  id=-1;
+  while(par->moldatfile[++id]!=NULL);
+  par->nSpecies=id;
+  
+  free(par->moldatfile);
+  par->moldatfile=malloc(sizeof(char *)*par->nSpecies);
+  
+  
+  /* Set defaults and read inputPars and img[] */
+  for(i=0;i<par->nImages;i++) {
+    (*img)[i].source_vel=0.0;
+    (*img)[i].phi=0.0;
+    (*img)[i].nchan=0;
+    (*img)[i].velres=-1.;
+    (*img)[i].trans=-1;
+    (*img)[i].freq=-1.;
+    (*img)[i].bandwidth=-1.;
+  }
+  input(par,*img);
+  par->ncell=par->pIntensity+par->sinkPoints;
+  
+  /* Check if files exists */
+  for(id=0;id<par->nSpecies;id++){
+    if((fp=fopen(par->moldatfile[id], "r"))==NULL) {
[…]

### 2013-07-16 src/curses.c

@@ -1,0 +1,138 @@
+/*
+ *  curses.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 29/10/08.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include <curses.h>
+#include <time.h>
+
+void
+greetings(){
+	initscr();
+	printw("*** LIME, The versatile line modeling engine, Ver.1.2\n*** Copyright 2006--2012, Christian Brinch <brinch@nbi.dk>\n");
+	refresh();	
+}
+
+void
+screenInfo(){
+  move(4,4);  printw("Building grid      :");
+  move(4,51); printw("|");
+  move(5,4);  printw("Smoothing grid     :");
+  move(5,51); printw("|");
+  move(7,4);  printw("Statistics         :");
+  move(9,4);  printw("Iterations         :"); 
+  move(10,4); printw("Propagating photons:");
+  move(10,51);printw("|");
+  move(13,4); printw("Ray-tracing model  :");
+  move(13,51);printw("|");
+  move(4,60); printw("|      Molecular data");
+  move(5,60); printw("|");
+  move(6,60); printw("|");  
+  move(7,60); printw("|");
+  move(8,60); printw("|");
+  move(9,60); printw("|");
+  move(10,60); printw("|");
+  move(11,60); printw("|");
+  move(12,60); printw("|");
+  move(13,60); printw("|");
+  move(14,60); printw("|");
+  refresh();	
+}
+
+void
+done(int line){
+	move(line,52); printw(" [ok]");
+    refresh();
+}
+
+void
+progressbar(double percent, int line){
+  int i;
+  for(i=0;i<(int)(percent*25.);i++){
+    move(line,25+i);
+    printw("#");
+  }
+  refresh();
+}
+
+void 
+progressbar2(int prog, double percent, double minsnr, double fstquart, double median, double thrdquart){
+  move(7,38); printw("                    ");            
+  move(8,38); printw("                    ");
+  move(7,25); printw("Min/Median(SNR)  %.2e %.2e", minsnr, median);
+  move(8,25); printw("1st/3rd Quartile %.2e %.2e", fstquart, thrdquart);
+  
+  move(9,25+prog); printw("#");
+  if(percent<100) {
[…]

### 2013-07-16 src/grid.c

@@ -1,0 +1,578 @@
+/*
+ *  grid.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 11/16/06.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include <qhull/qhull_a.h>
+#include "lime.h"
+
+
+void 
+gridAlloc(inputPars *par, struct grid **g){
+	int i;
+	double temp[99];	
+  	
+	*g=malloc(sizeof(struct grid)*(par->pIntensity+par->sinkPoints));	
+	memset(*g, 0., sizeof(struct grid) * (par->pIntensity+par->sinkPoints));
+
+	if(par->pregrid) par->collPart=1;
+	else{
+	  for(i=0;i<99;i++) temp[i]=-1;
+	  density(AU,AU,AU,temp);
+	  i=0;
+	  par->collPart=0;
+	  while(temp[i++]>-1) par->collPart++;
+	}
+	
+	for(i=0;i<(par->pIntensity+par->sinkPoints); i++){
+	  (*g)[i].dens=malloc(sizeof(double)*par->collPart);
+      (*g)[i].abun=malloc(sizeof(double)*par->nSpecies);
+	  (*g)[i].nmol=malloc(sizeof(double)*par->nSpecies);
+	  (*g)[i].t[0]=-1;
+	  (*g)[i].t[1]=-1;
+	}
+}
+
+
+
+void
+qhull(inputPars *par, struct grid *g){
+  int i,j,k,id;
+  char flags[255];			    
+  boolT ismalloc = False;		
+  facetT *facet;				
+  vertexT *vertex,**vertexp;	
+  coordT *pt_array;  
+  int simplex[DIM];				
+
+  pt_array=malloc(DIM*sizeof(coordT)*par->ncell);
+
+  for(i=0;i<par->ncell;i++) {
+    for(j=0;j<DIM;j++) {
+	  pt_array[i*DIM+j]=g[i].x[j];
+	}
+  }
+
+  sprintf(flags,"qhull d Qbb");
+  if (!qh_new_qhull(DIM, par->ncell, pt_array, ismalloc, flags, NULL, NULL)) {
+	/* Identify points */
[…]

### 2013-07-16 src/lime.h

@@ -1,0 +1,217 @@
+/*
+ *  lime.h
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 13/11/06.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include <stdlib.h>
+#include <stdio.h> 
+#include <string.h>
+#include <math.h>
+#include <time.h>
+#include <gsl/gsl_matrix.h>
+#include <gsl/gsl_math.h>  
+#include <gsl/gsl_spline.h>
+#include <gsl/gsl_rng.h>
+#include <gsl/gsl_linalg.h>
+
+#define silent 1
+#define verbose 0
+#define DIM 3
+
+/* Physical constants */ 
+#define PI			3.14159265358979323846
+#define SPI			1.77245385
+#define CLIGHT	    2.997924562e8
+#define HPLANCK	    6.626196e-34
+#define KBOLTZ	    1.380622e-23
+#define AMU			1.6605402e-27
+#define HPIP		HPLANCK*CLIGHT/4.0/PI/SPI
+#define HCKB		100.*HPLANCK*CLIGHT/KBOLTZ
+#define PC			3.08568025e16
+#define AU			1.49598e11
+#define maxp		0.15
+#define OtoP		3.
+#define GRAV		6.67428e-11
+	
+/* Other constants */
+#define NITERATIONS 	15
+#define max_phot		10000		/* don't set this value higher unless you have enough memory. */
+#define ininphot		9
+#define minpop			1.e-6
+#define eps				1.0e-30
+#define TOL				1e-6
+#define MAXITER			50
+#define gasIIdust		100
+#define goal			50
+#define fixset			1e-6 
+#define blendmask		1.e4
+#define converged_1stquart      3.0e4
+#define converged_1stpercent    3.0e2
+
+	
+/* input parameters */
+typedef struct {
+	double radius,minScale,tcmb;
+	int ncell,sinkPoints,pIntensity,nImages,nSpecies,blend;
+	char *outputfile, *inputfile;
+	char *gridfile;
+	char *pregrid;
+	char *dust;
+	int sampling,collPart,lte_only,antialias,polarization;
+	char **moldatfile;
+} inputPars;
+
[…]

### 2013-07-16 src/main.c

@@ -1,0 +1,68 @@
+/*
+ *  main.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 16/11/06.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ *  LIME is derived from RATRAN by Michiel Hogerheijde and Floris van der Tak,
+ *  Copyright 2000, Hogerheijde and van der Tak, A&A, 362, 697, 2000.
+ *
+ *  DISCLAIMER: LIME is provided as is and the author does not resume any 
+ *  responsibility for erroneous results due to bugs in the code.
+ *
+ *  Any publication with results obtain using LIME should refer to 
+ *  Brinch & Hogerheijde, A&A, 523, A25, 2010 
+ *
+ */
+
+#include "lime.h"
+#include <stdio.h>
+#include <fcntl.h>
+
+int main () {
+  int i;					
+  int initime=time(0);	
+  int popsdone=0;			
+  molData	  *m;			
+  inputPars	  par;
+  struct grid *g;
+  image		  *img;
+
+  par.dust  	= NULL;
+  par.inputfile = NULL;
+  par.outputfile= NULL;
+  par.gridfile  = NULL;
+  par.pregrid	= NULL;
+
+  int file=open("disk.bdat",O_RDONLY);
+
+  if(!silent) greetings();
+  if(!silent) screenInfo();
+	
+  parseInput(&par,&img,&m);
+  gridAlloc(&par,&g);
+
+  if(par.pregrid) predefinedGrid(&par,g); 
+  else buildGrid(&par,g);
+  popsout(&par,g,m);
+  for(i=0;i<par.nImages;i++){
+    if(img[i].doline==1 && popsdone==0) {
+      levelPops(m,&par,g);
+      popsdone=1;
+    }
+    if(img[i].doline==0) {
+      continuumSetup(i,img,m,&par,g);
+    }
+		
+    raytrace(i,&par,g,m,img);			  	
+    writefits(i,&par,m,img);
+  }
+  dumpGrid(&par,g);
+  if(!silent) goodnight(initime,img[0].filename);
+  return 0;
+}

### 2013-07-16 src/photon.c

@@ -1,0 +1,303 @@
+/*
+ *  photon.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 15/11/06.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *  All rights reserved.
+ *
+ */
+
+#include "lime.h"
+
+int
+sortangles(double *inidir, int id, struct grid *g, const gsl_rng *ran) {
+	int i,n[2];
+	double angle,exitdir[2];
+
+	exitdir[0]=1e30;
+    exitdir[1]=1e31;
+	n[0]=-1;
+    n[1]=-1;
+	for(i=0;i<g[id].numNeigh;i++){
+	  angle=( inidir[0]*g[id].dir[i].xn[0]
+       		 +inidir[1]*g[id].dir[i].xn[1]
+	    	 +inidir[2]*g[id].dir[i].xn[2]);
+	  if(angle<exitdir[0]){
+		exitdir[1]=exitdir[0];
+        n[1]=n[0];
+		exitdir[0]=angle;
+		n[0]=i;
+	  } else if(angle<exitdir[1]) {
+		exitdir[1]=angle;
+		n[1]=i;
+	  }
+	}
+    if(gsl_rng_uniform(ran)<1./((1-exitdir[0])/(1-exitdir[1])+1) ) {
+      if(n[0]==-1){
+        if(!silent) bail_out("Photon propagation error");
+        exit(1);
+      }
+      return n[0];
+	} else {
+      if(n[1]==-1){
+        if(!silent) bail_out("Photon propagation error");
+        exit(1);
+      }
+	  return n[1];
+	}
+}
+
+
+
+void
+velocityspline(struct grid *g, int id, int k, double binv, double deltav, double *vfac){
+  int nspline,ispline,naver,iaver;
+  double v1,v2,s1,s2,sd,v,vfacsub,d;
+	
+  v1=deltav-veloproject(g[id].dir[k].xn,g[id].vel);
+  v2=deltav-veloproject(g[id].dir[k].xn,g[g[id].neigh[k]].vel);
+
+  nspline=(fabs(v1-v2)*binv < 1) ? 1 : (int)(fabs(v1-v2)*binv);
+  *vfac=0.;
+  s2=0;
+  v2=v1;
+	
[…]

### 2013-07-16 src/popsin.c

@@ -1,0 +1,32 @@
+/*
+ *  popsin.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 08/26/10.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include "lime.h"
+
+/*
+void
+popsin(inputPars *par, struct grid *g){
+	FILE *fp;
+	int j,k;
+
+	fp=fopen(par->inputfile,"r");
+	fprintf(fp,"# Column definition: x, y, z, H2 density, kinetic gas temperature, molecular density, pops_0...pops_n\n"); 
+
+	for(j=0;j<par->ncell-par->sinkPoints;j++){
+
+	}	
+	fclose(fp);
+	
+
+}
+*/

### 2013-07-16 src/popsout.c

@@ -1,0 +1,89 @@
+/*
+ *  blowpops.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 14/11/07.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+#include "lime.h"
+
+void
+popsout(inputPars *par, struct grid *g, molData *m){
+	FILE *fp;
+	int j,k,l;
+	double dens;
+	/* int i,mi,c,q=0,best; */
+	/* double vel[3],ra[100],rb[100],za[100],zb[100],min; */
+	
+    if((fp=fopen(par->outputfile, "w"))==NULL){
+      if(!silent) bail_out("Error writing output populations file!");
+      exit(1);
+    }
+	fprintf(fp,"# Column definition: x,y,z,   H2,temp,abun,   vx,vy,vz,    ,pops_0...pops_n\n"); 
+	for(j=0;j<par->ncell-par->sinkPoints;j++){
+	    dens=0.;
+	 	for(l=0;l<par->collPart;l++) dens+=g[j].dens[l];
+		fprintf(fp,"%.5e %.5e %.5e   %.5e %.5e %.5e   %.5e %.5e %.5e    ", g[j].x[0], g[j].x[1], g[j].x[2],   dens, g[j].t[0], g[j].nmol[0]/dens,   g[j].vel[0], g[j].vel[1], g[j].vel[2]);
+		for(k=0;k<m[0].nlev;k++) fprintf(fp,"%e ",g[j].mol[0].pops[k]);
+		fprintf(fp,"\n");
+	}	
+	fclose(fp);
+
+
+/*
+	fp=fopen(par->outputfile,"w");
+	fprintf(fp,"rmax=%e\n", par->radius);
+	fprintf(fp,"zmax=%e\n", par->radius);
+	fprintf(fp,"ncell=100\n");
+        fprintf(fp,"tcmb=2.728\n");
+	fprintf(fp,"gas:dust=100\n");
[…]

### 2013-07-16 src/predefgrid.c

@@ -1,0 +1,66 @@
+/*
+ *  predefgrid.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 08/26/10.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include "lime.h"
+
+void
+predefinedGrid(inputPars *par, struct grid *g){
+  FILE *fp;
+  int i;
+  double x,y,z,scale,abun;
+  const gsl_rng *ran = gsl_rng_alloc(gsl_rng_ranlxs2);
+  gsl_rng_set(ran,time(0));
+	
+  fp=fopen(par->pregrid,"r");
+  par->ncell=par->pIntensity+par->sinkPoints;
+
+  for(i=0;i<par->pIntensity;i++){
+    fscanf(fp,"%d %lf %lf %lf %lf %lf %lf %lf %lf %lf %lf\n", &g[i].id, &g[i].x[0], &g[i].x[1], &g[i].x[2],  &g[i].dens[0], &g[i].t[0], &abun, &g[i].dopb, &g[i].vel[0], &g[i].vel[1], &g[i].vel[2]);
+//    fscanf(fp,"%d %lf %lf %lf %lf %lf %lf %lf\n", &g[i].id, &g[i].x[0], &g[i].x[1], &g[i].x[2],  &g[i].dens[0], &g[i].t[0], &abun, &g[i].dopb);
+	g[i].sink=0;
+	g[i].t[1]=g[i].t[0];
+	g[i].nmol[0]=abun*g[i].dens[0];
+		
+	/* This next step needs to be done, even though it looks stupid */
+	g[i].dir=malloc(sizeof(point)*1);
+	g[i].ds =malloc(sizeof(point)*1);
+	g[i].neigh =malloc(sizeof(int)*1);
+	if(!silent) progressbar((double) i/((double)par->pIntensity-1), 4);	
+  }
+  
+  for(i=par->pIntensity;i<par->ncell;i++){
+	x=2*gsl_rng_uniform(ran)-1.;
+	y=2*gsl_rng_uniform(ran)-1.;
+	z=2*gsl_rng_uniform(ran)-1.;
+	if(x*x+y*y+z*z<1){
[…]

### 2013-07-16 src/statistics.c

@@ -1,0 +1,50 @@
+/*
+ *  statistics.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 18/12/08.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+
+#include "lime.h"
+
+void statistics(int id, molData *m, struct grid *g, int *exceed, double *opops, double *oopops, int *conv){
+	int ilev;
+	double avepops,var=0.,snr1=fixset,snr2=fixset;
+		
+	for(ilev=0;ilev<m[0].nlev;ilev++){
+		avepops=(g[id].mol[0].pops[ilev]+opops[ilev+id*m[0].nlev]+oopops[ilev+id*m[0].nlev])/3.;
+		if(avepops>=0.01){
+			var=gsl_max(fabs(g[id].mol[0].pops[ilev]-avepops)/avepops,
+						gsl_max(fabs( opops[ilev+id*m[0].nlev]-avepops)/avepops,
+								fabs(oopops[ilev+id*m[0].nlev]-avepops)/avepops));
+			snr1 = (snr1>var) ? snr1 : var;		
+		} else if(avepops>=minpop && avepops<0.01){
+			var=gsl_max(fabs(g[id].mol[0].pops[ilev]-avepops)/avepops,
+						gsl_max(fabs( opops[ilev+id*m[0].nlev]-avepops)/avepops,
+								fabs(oopops[ilev+id*m[0].nlev]-avepops)/avepops));
+			snr2 = (snr2>var) ? snr2 : var;	
+		}
+			
+	}
+
+	snr1=1./snr1;
+	snr2=1./snr2;	
+
+	if(snr1>=goal && snr2>=5) {
+		*conv+=1;
+	}else {
+		g[id].nphot=g[id].nphot+10;
+		if(g[id].nphot>(max_phot*200)){
+			g[id].nphot=max_phot*200;
+			*exceed+=1;
+			if(!silent) warning("Warning: limiting nphot reached in a grid point");
+		}
+	}
+}

### 2013-07-16 src/weights.c

@@ -1,0 +1,100 @@
+/*
+ *  weights.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 11/16/06.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include "lime.h"
+/*
+double
+setup(inputPars  *par){
+  double val[99],n0;
+  density  (par->minScale*5,    0,         0, val);
+  n0=val[0];
+  density  (par->minScale*10,    0,         0, val);
+  if (n0<val[0]) n0=val[0];
+  density  (par->minScale*20,    0,         0, val);
+  if (n0<val[0]) n0=val[0];
+  density  (par->minScale*30,    0,         0, val);
+  if (n0<val[0]) n0=val[0];
+  density  (par->minScale*40,    0,         0, val);
+  if (n0<val[0]) n0=val[0];
+  density  (par->minScale*50,    0,         0, val);
+  if (n0<val[0]) n0=val[0];
+  return n0;
+  }*/
+
+int
+pointEvaluation(inputPars *par,double ran, double x, double y, double z){
+  double weight1=0, weight2=0, val[99],m0,n0,val2[99], eta=10;
+//  double t0=200000;
+
+//////// compare with ambient medium /////////  
+  density  (par->radius*sqrt(0.25), par->radius*sqrt(0.25), par->radius*sqrt(0.25), val);
+  n0=val[0]*eta*0.8;
+  m0=1.0e-6;
+    
+
+/////////// compare with central region in z=0 plane ////////
+    /* density  (par->minScale*5,    0,          0, val);  //disc w/ hole */
+    /* n0=val[0]; */
+    /* density  (0,             par->minScale*5, 0, val);  //disc w/ hole */
+    /* n0+=val[0]; */
+    /* n0/=2; */
+    /* //    n0=5.0e12; */
+
+    /* abundance(      0,      par->minScale*5, 0, val2); */
+    /* m0=val2[0]; */
+    /* abundance(par->minScale*5,       0,      0, val2); */
+    /* m0+=val2[0]; m0/=2; */
+    /* m0*=n0; */
+
+
[…]

### 2013-07-16 src/writefits.c

@@ -1,0 +1,124 @@
+/*
+ *  writefits.c
+ *  LIME, The versatile 3D line modeling environment 
+ *
+ *  Created by Christian Brinch on 24/04/08.
+ *  Copyright 2006-2012, Christian Brinch, 
+ *  <brinch@nbi.dk>
+ *  Niels Bohr institutet
+ *  University of Copenhagen
+ *	All rights reserved.
+ *
+ */
+
+#include <cfitsio/fitsio.h>
+#include "lime.h"
+
+void 
+writefits(int im, inputPars *par, molData *m, image *img){
+	double bscale,bzero,epoch,lonpole,equinox,restfreq;
+	double cdelt1,crpix1,crval1,cdelt2,crpix2,crval2;
+	double cdelt3,crpix3,crval3;
+	int velref;
+	float *row;
+	int px,py,ichan;
+	fitsfile *fptr;
+	int status = 0;
+	int naxis=3, bitpix=-32;
+	long naxes[3];
+	long int fpixels[3],lpixels[3];
+	char negfile[100]="! ";
+	
+	row = malloc(sizeof(float)*img[im].pxls);
+	
+	naxes[0]=img[im].pxls;
+	naxes[1]=img[im].pxls;
+	if(img[im].doline==1) naxes[2]=img[im].nchan;
+	else if(img[im].doline==0 && par->polarization) naxes[2]=3;
+	else naxes[2]=1;
+
+	fits_create_file(&fptr, img[im].filename, &status);
+	
+	if(status!=0){
+		if(!silent) warning("Overwriting existing fits file                   ");
+		status=0;
+		strcat(negfile,img[im].filename);
+		fits_create_file(&fptr, negfile, &status);
+	}
+
+	/* Write FITS header */ 
+	fits_create_img(fptr, bitpix, naxis, naxes, &status);
+    epoch   =2.0e3;
+	lonpole =1.8e2;
+	equinox =2.0e3;
+	restfreq=img[im].freq;
+  	velref  =257;
+  	cdelt1  =-1.8e2*img[im].imgres/PI;
+  	crpix1  =(double) img[im].pxls/2+0.5;
+    crval1  =0.0e0;
+  	cdelt2  =1.8e2*img[im].imgres/PI;
+  	crpix2  =(double) img[im].pxls/2+0.5;
+    crval2  =0.0e0;
+	cdelt3  =img[im].velres;
[…]

### 2013-07-16 pop_grid.py
added pop_grid script

@@ -1,0 +1,43 @@
+#!/usr/bin/python
+from numpy import *
+from scipy import interpolate
+from pylab import plot, loglog, semilogx, semilogy, clf, imshow
+import pylab as plt
+from matplotlib.pyplot import gca
+
+def _f(a,b):
+    if   a[0]<b[0] : return -1
+    elif a[0]>b[0] : return 1
+    else           : return _f(a[1:], b[1:])
+
+def datafile(path):
+    lines=[]
+    if isinstance(path, str): f=open(path)
+    else: f=path
+    for line in f: 
+        l=line.strip()
+        if len(l) > 0 and l[0] in '1234567890.-+': lines.append([float(x) for x in l.split()])
+    f.close()
+    return array(lines)
+
+def __main__():
+    g1=g2=g3=g4=g5=0
+    path=raw_input("enter path: ")
+
+    try :dat=datafile (path)
+    except IOError: 
+        print "IOERROR"
+        dat=datafile(raw_input("enter path: "))
+
+    sdat=empty((dat.shape[0],dat.shape[1]-2))
+    sdat[:,1:]=dat[:,3:]
+    sdat[:,0]=sqrt((dat[:,:3]**2).sum(1))
+
+    sdat=array(sorted(list(sdat), cmp=_f))
+
+    r,z = sqrt((dat[:,:2]**2).sum(1)), dat[:,2]
+    H, xedges, yedges = histogram2d(r, z, bins=(20, 100))
+    clf();plt.imshow(log10(H.T+0.1), vmin=0, interpolation='nearest',origin='image', cmap=plt.cm.gist_heat)
+    plt.colorbar()
+    plt.draw()
+    plt.savefig('grid.png')

### 2013-07-17 convolve.py
added convolution routine

@@ -1,0 +1,44 @@
+import numpy,pyfits,os,tarfile,Gnuplot,pprocess
+from math import exp,log,sqrt,pi,ceil
+from numpy.fft import fft2,ifft2, irfft2, rfft2
+from scipy import constants as cnst
+from scipy.interpolate import griddata
+import numpy as np
+import pprocess as pp
+from pylab import imshow
+import pylab as pyl
+from numpy import outer
+import pyfits as P
+
+def garray(shape, sigma):
+    a=numpy.empty(shape, dtype=float)
+    midi,midj=shape[0]/2,shape[1]/2
+    for i in xrange(shape[0]):
+        for j in xrange(shape[1]):
+            a[i,j]=exp(-1*sqrt((i-midi)**2+(j-midj)**2)**2 / (2*sigma*sigma))/(sigma*sqrt(2*pi))**2
+#exp(-1*(i-midi)**2 / (2*sigma*sigma))*exp(-1*(j-midj)**2 / (2*sigma*sigma))/(sqrt(2*pi*sigma**2))    
+    return a
+
+def FWHM2sigma (FWHM): return FWHM/(2*sqrt(2*log(2)))
+
+def next_pow2 (n):
+    if n<0: sign=-1
+    else  : sign=1
+    X=abs(n)
+    ans=1
+    while ans<X: ans*=2
+    return ans
+
+def cube_convolve(imcube, sigma):
+    "performs a convolution with a gaussian beam of width sigma on each yz plane of the cube"
+#    imcube=imcube.copy()
+    shape=imcube.shape[1:]
+    if len(shape)!=2:
+        raise ValueError ("cube is not a cube")
+    gauss_mask=garray(shape,sigma)
+    s=[next_pow2(y*2+1) for y in gauss_mask.shape]
+    ftg=fft2(gauss_mask, s).reshape(s)
+    for i in xrange(imcube.shape[0]):
+        imcube[i,...]=np.real(ifft2(fft2(imcube[i,...],s)*ftg)[shape[0]/2:3*shape[0]/2, shape[1]/2:3*shape[1]/2])
+    return imcube
+ 

### 2013-07-19 NewJetData/molecular/eta10beta10/model.c
rerun power and molecular e10b10 models

@@ -24,7 +24,7 @@
 
 
 #define length_scale (16.71146539*AU)
-#define centre_z (750)
+#define centre_z (800)
 #define unit_temp (1)
 #define unit_density (1e6)
 #define unit_velocity (1e3)

### 2013-07-19 NewJetData/pow/model.c

@@ -22,7 +22,7 @@
 /* #include "fHI.h" */
 
 #define length_scale (16.71146539*AU)
-#define centre_z (600)
+#define centre_z (800)
 #define unit_temp (1)
 #define unit_density (1e6)
 #define unit_velocity (1e3)

### 2013-07-19 NewJetData/tabulated/eta10beta10/model.c

@@ -22,7 +22,7 @@
 /* #include "fHI.h" */
 
 #define length_scale (16.71146539*AU)
-#define centre_z (750)
+#define centre_z (800)
 #define unit_temp (1)
 #define unit_density (1e6)
 #define unit_velocity (1e3)

### 2013-07-19 PAPER/ms_final_bv.tex
Changes in paper and rm Python book

@@
 
-\section{Results}
 \begin{figure*}
@@
    cooling having $\eta$ = 5 and $\beta$ = 10.}
+\label{grid}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/linejets.png}
+ \caption{SiO emission from different line transitions for the run with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10. }
 \label{grid}
@@
 \section{Discussion}
-Effects of varying $\beta$, $\eta$\\
+Effects of varying $\eta$\\
+Lower $\eta$ gives better emission.
+
 Importance of cooling prescriptions\\
-RADEX plots ratio of Line intensities???\\
+Bulk of emission comes from cooling instabilities.
+
+Spectra and PV Digrams\\
+Line - withs $\sim$ 15-25 km\,s$^{-1}$. Wedge shaped PV diagrams
+a signature feature of jet driven molecular outflows.
+
 Comparison with Observed results \\
+Different line transition trace different components of SiO
+emission. The low level transitions trace the region where the jet
+interacts with molecular medium. The clumpy nature in its emission is
+from the turbulent nature of its interaction. The higher transitions
+trace a much more collimated region along with the terminal shock. 
+As seen by Chandler \& Richer 2001 and Hirano 2006.
+
 Limitations\\

### 2013-07-27 PAPER/ms_final_bv.tex
Added Introduction and plots

@@
 \newcommand{\rhoi}{{\rho}_{\rm i}}
+\newcommand{\refer}{{\color{orange}REFERENCE}}
 
@@
 \section{Introduction}
-Interaction of jet with ambient medium , Class 0 sources, momentum and
-energy injection, High mass and low mass outflows \\
+Jets are one of the first manifestations of star
+formation in dense molecular cores. They are ubiquitous in both
+massive and low star forming regions. These supersonic flows
+perpendicular to the underlying accertion disk plays a vital role in
+removing excess angular momentum and thereby aiding in the accretion. 
+For low mass stars, they are believed to be launched by magneto-centrifugally forces and
+further collimated by magnetic hoop stress
+\citep[][]{Blandford:1982p892, Konigl:2000p607}. However, in case of
+high mass stars, radiative forces also contribute to flow dynamics
+during the later evolutionary stages \cite{Vaidya:2011p8992}. 
+Typically, these jets are few parsec size long and can be divided into
+three length-scale domains viz. source and disk scales (1-10$^{2}\,$AU),
+envelope scales ($10^{2} - 10^{5}$\,AU) and parent cloud scales
+($10^{5} - 10^{6}$\,AU) \refer. Among them, the envelope scales are
+the ones where rich chemical evolution occurs as the jet interacts
+with the molecular medium. In this region, the jet propagates into a
+relatively static medium inducing shocks that are interesting from the
+physical and chemical point of view. In addition to shocks, molecular
+material from the surrounding is entrained and accelerated to high
+velocities giving rise to molecular outflows.
+%
 
-Observations of Outflows in CO and SiO in mm, H2 in IR, Optical jets
-HH objects, syncrotron emission \\
+Bipolar molecular outflows from low and high mass stars
+have been studied in details over the past 
+decade \citep[see reviews by][]{Bachiller:1996p4692,Arce:2007p798,
+Tafalla:2011p14051}. Advancement in millimeter interferometers have
+allowed to observe these outflows with high spatial resolution of
+few arc seconds. A large number of studies related to young
+outflows are done using standard outflow and shock tracer
+like CO and SiO respectively. In addition to these molecular tracers,
+shocks from these outflows are detected in molecular hydrogen using
+infra-red telescopes. Based on these observational studies, various
+empirical properties for these outflows have been discovered. For
+example, the CO outflows from single dish studies are seen to be
+highly collimated for both low and high mass stars
+\citep[for e.g.,][]{Gueth:1999p4683, Beuther:2002p3574} they are
+referred to as {\em{molecular jets}}. These outflows also exhibit a
+mass-velocity relation with a power law form $ dM(v)/dv \propto
+v^{-\gamma}$, where values of $\gamma$ range from 1 to 3 \cite{Downes:2003p9946}. Episodic
+knots belived to be caused by variable accretion events are a common property
+of young molecular outflows (for e.g. in L1577:
+\citealt{Gueth:1998p14058}, in HH300: \citealt{Arce:2001p14064}). These knots show their signatures
+as {\em{wedges}} in the position-velocity (PV) diagrams \cite{Arce:2001p14065}. Also, most
+commonly observed in these outflows are signatures of rotation and
+precision (for e.g., in DG Tau: \citealt{Bacciotti:2002p2084}).
+%
 
-Molecules from jet driven or wind driven, Interesting features like
-EHV, low velocity component etc, list interesting outflows from Class 0 \\
+Even with myriad of empirical evidences, the exact nature of SiO and
+CO outflow is not clear. For a complete understanding it is imperative
+to compliment these observations with theoretical models. Many models
+based on hydro-simulations and steady state shock calculations
+were proposed to explain the observational signatures of molecular
+outflows. Among them the two main models are that of wide-angled wind
+driven \cite{Shu:1991p14071} and jet driven outflow
+\cite{Canto:1991p14123}. 
+The most popular among them is the jet driven model as wind
+driven molecular outflows not only fail to match observed PV digarams \cite{Cabrit:1992p14098}
+but also tend to sweep large quantitity of material at the extermities
+of the lobes \cite{Masson:1992p14101}. While the jet driven models could sucessfully
+derive the global outflow shapes and mass velocity relations of CO
+outflows \citep{Raga:1993p9948, Masson:1993p9661} . There have also been some attempts to combine these two
+models into one \cite{Shang:2006p14268} to explain the global observational features. 
+However, most of these dynamical models do not
+account for shock chemsitry. Instead, shock chemistry is studied
+independently without dynamics using plane parallel shock
+models \citep{Schilke:1997p14140,Flower:2003p11236} . The magneto-hydrodynamic (MHD) calculations by \cite{Glassgold:1991p13703} suggested that molecules
+like SiO and CO could as form within the jet. Similar conclusions of
+molecules surving in steady state disk winds have also been shown
+\cite{Panoglou:2012p10039}. Very limited simulations have modelled the outflow
+dynamics including molecular chemistry but in absence of
+magnetic fields \citep{Raga:1995p12965, Smith:2003p9985}.
 
-Attempts of simulations either only dynamics with analytic approaches
-to compare observational features, or only chemistry to estimate
-abundances. The reality lies in the middle!\\
+%
+In the present work, our goal is to take a step further in modelling of
+jet driven molecular outflows. The present model aims to consistently derive observed emission
+properties of molecular outflows, specifically various SiO line
+tranistions, by combining axisymmetric MHD simulations of
+radiative jet propogation. In particular, we evolve the jet dynamical
+quantities in conjunction with different non-equilibrium cooling
+prescriptions of varying complexities. The most complex is that of
+molecular cooling along with H$_{2}$ chemistry. This prescription
+allows us to track the formation and destruction of 
+HI, HII and H2 along with the flow dynamics. 
+The final state of the jet obtained for each cooling model is then
+post-processed using a non-LTE radiative line transfer code
+to obtain emission maps, spectra and PV digram. These emission maps
+are further processed using ALMA-CASA pipeline to obtain synthetic
+images of molecular outflows.
+%
 
-Combine dynamics of MHD jet with molecular chemistry and comparing
-with observations via post-processing simulations with line radiative
-transfer codes. \\
-
-Paper Layout \\
+In the next three section we describe our numerical setup, cooling
+presecriptions and radiative transfer line code respectively. In
+Sect. 5, we will present results from the parameter survey and the
+discussions along with predicted ALMA maps will be presented in
+Section 6 and 7, followed by conclusions.
 
@@
 
-\section{Results}
-\begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
- \caption{Jet Volume Density for different cooling modes with
-   $\eta$ = 10 and $\beta$ = 10.}
-\label{grid}
-\end{figure*}
-
-\begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/molcjet_510.png}
- \caption{Fraction of hydrogen species in the run with molecular
-   cooling having $\eta$ = 5 and $\beta$ = 10.}
-\label{grid}
-\end{figure*}
-
-\begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/linejets.png}
- \caption{SiO emission from different line transitions for the run with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10. }
-\label{grid}
-\end{figure*}
-
+\section{Parameter Survey}
 \begin{table*}
@@
 
+\section{Results}
+\subsection{Comparison of cooling prescription}
+figure nos. 2 -- Similuated images, emission maps for eta = 10.
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
+ \caption{Jet Volume Density for different cooling modes with
+   $\eta$ = 10 and $\beta$ = 10.}
+\label{grid}
+\end{figure*}
+
 \begin{figure}
  \includegraphics[width=84mm]{\figpath/J2-1_mom0maps_cooling.png}
- \caption{A plot of the integrated SiO J2-1 emission from 5 models, each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
+ \caption{A plot of the integrated SiO J2-1 emission from 5 models, 
+each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
 \label{cooling2-1}
@@
 
+\subsection{Molecular cooling and H$_2$ Chemistry}
+figure nos. 2 --> Explain molecular cooling in more details. With the
+mechanism of formation and destruction of HI, H2 and HII using
+figures. 
 \begin{figure*}
- \includegraphics[width=168mm]{\figpath/tabulated_mom0maps_Trans.png}
- \caption{The integrated intensity of 4 SiO transitions in the tabulated cooling model in the $\eta$=2 $\beta$=10 model.}
-\label{tabulatedTrans}
+ \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
+ \caption{Fraction of hydrogen species in the run with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10.}
+\label{grid}
 \end{figure*}
 
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310_molform.png}
+ \caption{Dependence of hydrogen fractions on the temperature at two
+   points in the flow, viz. the interface of the knot with molecular
+   medium and at the bow shock}
+\label{grid}
+\end{figure*}
+
+\subsection{Effects of changing $\eta$ and $\beta$}
+figure nos. 2 -- Simulated images describing lengths, collimation and
+emission for lower eta more stronger. 
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/jetplt2_diffetabeta.png}
+ \caption{Jet Volume Density for atomic cooling with $\eta$ = 10 but $\beta$ = 1 and
+   10 and that with tabulated cooling with $\beta$ = 10 but $\eta$ = 2
+   and 10.}
+\label{grid}
+\end{figure*}
+
+\subsection{SiO Abundance profile}
+figure nos. 2 -- Comparison of three profiles for SiO Abundance,
+Contour maps for two transitions for top hat profile.
+
 \begin{figure}
- \includegraphics[width=84mm]{\figpath/tab_trans_spectra.png}
- \caption{The Integrated emission and spectra at he bow shock for 2 transitions of the tabulated cooling model for $\eta$=2 $\beta$=10 (spectra taken from y=50, x=128).}
+ \includegraphics[width=1.\columnwidth]{\figpath/contourmapsSiOTopHat.png}
+ \caption{Contours of SiO 2-$>$1 and 8-$>$7 emission obtained using the
+   SiO Top Hat profile.}
 \label{grid}
 \end{figure}
+
+\subsection{Spectra and PV diagrams}
+figure nos. 1 -- one transition 3 different angles, Comparison of
+spectra and line ratios
 
@@
 
+Effects of varing abundance profile ... Crucial ingredient in
+modeling molecular bullets \\
+
 Spectra and PV Digrams\\
 Line - withs $\sim$ 15-25 km\,s$^{-1}$. Wedge shaped PV diagrams
-a signature feature of jet driven molecular outflows.
+a signature feature of jet driven molecular outflows. Counterparts in observations.
 
@@
 As seen by Chandler \& Richer 2001 and Hirano 2006.
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/linejets.png}
+ \caption{SiO emission from different line transitions for the run with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10. }
+\label{grid}
+\end{figure*}
+
+Advantage of non-LTE modeling over LVG Cabrit 2007, Lee 2008. 
+Line ratios $\sim$ 1 can be explained well. \\
+
+EHV component ?? \\
 

### 2013-07-29 PAPER/ms_final_bv.tex
Added new figs

@@
 \begin{figure}
- \includegraphics[width=84mm]{\figpath/abun.png}
- \caption{The polynomial used to calculate an abundance of SiO as a function of local velocity.}
+ \includegraphics[width=84mm]{\figpath/diffabun.png}
+ \caption{The different fractional SiO abundances as a function of
+   shock velocity, V${\rm s}$.}
  \label{abun}
@@
 modeling molecular bullets \\
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/EM_diffabun.png}
+ \caption{Variation of 2-$>$1 SiO emission for runs with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
+\label{grid}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/PV_diffabun.png}
+ \caption{Variation of position-velocity diagram for 2-$>$1 SiO emission for runs with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
+\label{grid}
+\end{figure}
 
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/linejets.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/linejets_thnolog.png}
  \caption{SiO emission from different line transitions for the run with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10. }
+   cooling having $\eta$ = 3 and $\beta$ = 10 using top-hat fractional
+   abundance profile. }
 \label{grid}
@@
 Line ratios $\sim$ 1 can be explained well. \\
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/LineRatio_TH_60_Y205.png}
+ \caption{{\em{Top}} Line profiles in SiO J = 2-1, 5-4 and 8-7 at one
+   the inner knot for the molecular cooling run with $\eta$ = 3 and
+   $\beta$ = 10 using top hat abundance profile. The profiles are
+   obatined when the angle of inclination is 60$^{\circ}$ with respect
+ to line of sight. {\em{Bottom}} Line temperature ratios T(8-7)/T(5-4)
+and T(2-1)/T(5-4), as a function of velocity}
+\label{grid}
+\end{figure}
 

### 2013-07-31 PAPER/ms_final_bv.tex
Added bib file

@@
 mol1010 & Molecular & 10 & 10&&\\
-mol510 & Molecular & 5 & 10&&\\
+mol510 & Molecular & 3 & 10&&\\
 \hline
@@
 \label{tab:result1}
-
 \end{table*}
@@
 
-\subsection{Molecular cooling and H$_2$ Chemistry}
-figure nos. 2 --> Explain molecular cooling in more details. With the
-mechanism of formation and destruction of HI, H2 and HII using
-figures. 
-\begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
- \caption{Fraction of hydrogen species in the run with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10.}
-\label{grid}
-\end{figure*}
-
-\begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310_molform.png}
- \caption{Dependence of hydrogen fractions on the temperature at two
-   points in the flow, viz. the interface of the knot with molecular
-   medium and at the bow shock}
-\label{grid}
-\end{figure*}
-
 \subsection{Effects of changing $\eta$ and $\beta$}
@@
 
+\subsection{Molecular cooling and H$_2$ Chemistry}
+In case of molecular outflows, the most appropiate form of cooling
+prescribtion among the ones described in sect.~\ref{sec:chem} is
+that which involves the evolution of H$_2$ chemistry along with
+contributions to cooling from fixed fractions of other molecules like
+CO, OH etc. Figure~\ref{fig:Hfracsim} shows the density of
+various hydrogen species in the outflow. Also shown in the figure is
+the temperature and mean molecular weight $\mu$. As the jet propgates
+into the medium
+
+figure nos. 2 --> Explain molecular cooling in more details. With the
+mechanism of formation and destruction of HI, H2 and HII using
+figures. 
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
+ \caption{Fraction of hydrogen species in the run with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10.}
+\label{fig:Hfracsim}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310_molform.png}
+ \caption{Dependence of hydrogen fractions on the temperature at two
+   points in the flow, viz. the interface of the knot with molecular
+   medium and at the bow shock}
+\label{grid}
+\end{figure*}
+
 \subsection{SiO Abundance profile}
@@
 Contour maps for two transitions for top hat profile.
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/EM_diffabun.png}
+ \caption{Variation of 2-$>$1 SiO emission for runs with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
+\label{grid}
+\end{figure}
 
@@
 
-Table 1 -- Parameter runs with changing $\beta$ (magnetic fields) and
-$\eta$ (density contrast) for cooling \\
-Results should have Peak Intensity after convolution., FWHM at tip of
-bow shock.\\
-Our reference run -- $\beta$ = 10.0, $\eta$ = 2.0, with cooling and
-velocity dependent SiO Abundance. \\
-Figure 3 -- Output from MHD simulations (Reference run).\\
-Figure 4 -- Output from Rad Transfer (Reference run). Integrated
-Intensity Maps for different transitions for three different cooling prescribtions. (TODO : TOM)\\
-Figure 5 -- Spectra for the reference runs all transitions. (TODO :
-TOM)\\
-Figure 6 -- PV diagrams (TODO : TOM) for one transition in two directions.
-Figure 7 -- Angle of Inclination dependence
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/PV_diffabun.png}
+ \caption{Variation of position-velocity diagram for 2-$>$1 SiO emission for runs with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
+\label{grid}
+\end{figure}
 
@@
 modeling molecular bullets \\
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/EM_diffabun.png}
- \caption{Variation of 2-$>$1 SiO emission for runs with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
-\label{grid}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/PV_diffabun.png}
- \caption{Variation of position-velocity diagram for 2-$>$1 SiO emission for runs with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
-\label{grid}
-\end{figure}
 
@@
 
-Advantage of non-LTE modeling over LVG Cabrit 2007, Lee 2008. 
-Line ratios $\sim$ 1 can be explained well. \\
+Advantage of non-LTE modeling over LVG \cite{Cabrit:2007p13804}, \cite{Lee:2008p13697}. 
+Line ratios $\sim$ 1 can be explained well for low mass stars and 
+\cite{Leurini:2013p13165} for high mass stars. \\
 \begin{figure}

### 2013-08-12 PAPER/ms_final_bv.tex
Modified paper tex and added new figures

@@
   % context heading (optional)
-  {}  
+  {A bipolar, violent, collimated outflow is one of the first signpost of star
+formation. Such an outflow is believed to be launched magnetically from
+underlying accretion disk. As it propagates through the molecular
+cloud, it injects energy and momentum via shocks 
+and fosters chemical evolution by forming, destroying and entraining
+molecules along its path.}  
   % aims heading (mandatory)
-   {}
+   {High 
+velocity molecular outflows are extensively studied for both low mass
+and high mass stars. They are usually observed using standard sub-mm outflow and shocks
+tracers like CO and SiO respectively. However, the exact nature of
+excitation of these molecules is not yet clear due to lack of models that
+simultaneously study the dynamics along with complex molecular chemistry.}
   % methods heading (mandatory)
-   {}
+   { For such a study, we have perfomed MHD simulations
+of jet propagation into a molecular cloud using the PLUTO
+code. Firstly, we evolve the jet dynamical quantities in conjunction
+with different non-equilibrium cooling prescriptions of varying complexities. 
+The most complex is that of molecular cooling along with
+H$_2$ chemistry. This prescription allows us to track the formation
+and destruction of HI, HII and H$_2$ along with the flow dynamics. 
+The final state of the jet obtained for each cooling model is then
+post-processed using a non-LTE radiative line transfer code, LIME,  to
+obtain SiO emission maps, spectra and PV digram.}
   % results heading (mandatory)
-   {}
+   {We find that the strength of SiO
+emission depends strongly on the cooling prescription and SiO fractional
+abundance profile. We find that the bulk of SiO emission comes from
+the interface between
+the jet and the ambient molecular medium mainly excited to due to
+shocks. Further, we see that some SiO can be produced within the jet
+specially close to the bow shock due to instabilities associated with
+cooling. We have used these emission maps to give predictions for ALMA
+observations. Also, our model can very well reproduce the observed 
+spectra, line ratios and PV diagrams of young outflows from Class 0 sources.}
   % conclusions heading (optional), leave it empty if necessary 
@@
 account for shock chemsitry. Instead, shock chemistry is studied
-independently without dynamics using plane parallel shock
-models \citep{Schilke:1997p14140,Flower:2003p11236} . The magneto-hydrodynamic (MHD) calculations by \cite{Glassgold:1991p13703} suggested that molecules
+independently using steady state non-dissociative C-type and
+dissociative J-type shocks models \citep{Neufeld:1989p11689, Schilke:1997p14140,Flower:2003p11236}. 
+The magneto-hydrodynamic (MHD) calculations by \cite{Glassgold:1991p13703} suggested that molecules
 like SiO and CO could as form within the jet. Similar conclusions of
 molecules surving in steady state disk winds have also been shown
-\cite{Panoglou:2012p10039}. Very limited simulations have modelled the outflow
+\cite{Panoglou:2012p10039}. 
+Very limited simulations have modelled the outflow
 dynamics including molecular chemistry but in absence of
@@
 inside the jet. The maximum value, $B_{\phi,\rm m}$, depends on the
-plasma $\beta$ which is a parameter used for our study along with the
-density contrast $\eta$.
+plasma $\beta$ which is kept fixed for all our runs to be at a value
+of 10.0. This corresponds to the maximum field strength, $B_{\phi,\rm m}$ $\sim
+16\mu\,G$.
+
 %
@@
 \section{Radiative Transfer}
+\label{sec:radtrans}
 Radiative transfer modeling used for post processing.
@@
 After 20 iterations the model is ray-traced in order to produce synthetic brightness maps.
-The average of ten separate runs was taken to minimise the artefacts in the output images, resulting from the grid construction (Fig.~\ref{points}).
+The average of ten separate runs was taken to minimise the artefacts in the output images, resulting from the grid construction.% (Fig.~\ref{points}).
 
@@
 The points are color coded by the density distribution (in m$^{-3}$, as used in LIME) and are more concentrated in the high density knots.}
-\label{grid}
+\label{grid} % This plots has to be changed. 
 \end{figure}
@@
 
-\begin{figure}
- \includegraphics[width=63mm]{\figpath/eta2Beta10_histo.png}
- \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions.}
- \label{points}
-\end{figure}
+\subsection{SiO abundance}
+\label{ssec:sioabun}
+Need refs for this!!\smallskip
+The amount of SiO is determined by the local velocity and
+temperature. The fractional abundance is given by the equation:
 
-\subsection{SiO abundance}
-Need refs for this!!\smallskip
-The amount of SiO is determined by the local velocity and temperature. The fractional abundance is given by the equation:\smallskip
+\begin{eqnarray}
+log(X)=-2.48\times10^{-8}v^5 + 5.50\times10^{-6}v^4 \nonumber \\
+- 4.28\times10^{-4}v^3 + 1.24\times10^{-2}v^2 \nonumber \\
++ 2.52\times10^{-2}v - 1.20\times10^{1}
+\label{eq:fracSio}
+\end{eqnarray}
 
-$log(X)=-2.48\times10^{-8}v^5 + 5.50\times10^{-6}v^4 - 4.28\times10^{-4}v^3 + 1.24\times10^{-2}v^2 + 2.52\times10^{-2}v - 1.20\times10^{1}$\smallskip
-
-where v is in kilometres per second.
-In addition to this if the temperature at the point is greater than 92,000K (the temperature of the Si-O bond disassociation energy) the abundance is reduced to 10$^{-30}$.
+where v is the shock velocity in kilometres per second. 
+In addition to this if the temperature at the point is greater than 92,000K (the temperature of the Si-O bond disassociation energy) the abundance is reduced to 10$^{-12}$.
 
@@
 \section{Parameter Survey}
+The results and analysis for the present work are divided in two parts,
+viz., the dynamical numerical simulations and the post-processing with
+radiative transfer code. For each part we have used certain parameters
+and the effect of changing them is studied. Ideally all these parameters should come from observational
+results. However, not all quantities needed for our study are well
+constraint by the observations, thus allowing us vary them as
+free parameters. Such a parameter survey provides better handle on the range of allowed
+values on qualitative comparison with observations. 
+%
+
+For the first part of the study concerning the dynamical numerical
+simulations, we will focus on two main parameters. They are the
+prescribtion of cooling and the density contrast between the jet and
+the ambient medium denoted by $\eta$. The various cooling prescribtions used for the present study are
+described in details in section~\ref{sec:chem}. A value of $\eta > 1$, mean that
+that jet is overdense with respect to the medium. In all our runs with
+different cooling prescribtions, we have assumed the jet to be
+overdense by 10 times that of the ambient medium. Additionally, for
+the atomic, tabulated and molecular cooling runs we have used a
+value of $\eta$ of the order of unity indicating similar densities in
+the jet and the medium. 
+The magentic field strength is kept to be fixed using $\beta = 10.0$,
+for all our runs. Table~\ref{tab:result1} lists all the runs with
+varying $\eta$ and cooling prescriptions, along with the peak
+intensity and line widths at the bow shock.
+%
+
+The post-processing phase is done in details for the molecular run
+with $\eta = 3$. To obtain the SiO emission maps and corresponding
+spectra, two additional free parameters are required along with other
+inputs described in section~\ref{sec:radtrans} . They are
+the fractional abundance profile of SiO and the angle of inclination with
+respect to line of sight denoted by $\phi$. Section~\ref{ssec:sioabun}
+describes all the profiles used for the present study. The obivious
+choice for the inclination angle, $\phi$ is 90$^{\circ}$ indicating
+the outflow is in the plane of the sky. 
+Additionally, we have used two other angles of inclination apart from the
+plane of the sky, i.e, $\phi = 45^{\circ}, 60^{\circ}$ to compare
+results with observations. The runs with different fractional
+abundance profiles are described in table~\ref{tab:result2}
+
 \begin{table*}
 \centering
-\caption{Summary from parameter runs}
+\caption{Summary from parameter runs.}
 \begin{tabular}{l | l | l | l | l | l }
 \hline
-Run & Cooling Mode & $\eta$ & $\beta$ & Peak Intensity [K] & FWHM at Bow
-Shock \\
+Run & Cooling Mode & $\eta$ & Peak Intensity [K] & $\Delta$v [km s$^{-1}$] \\
 \hline\hline
-adi1010 & Nil (Adiabatic) & 10 & 10 &&\\
-pow1010 & Power law & 10 & 10 &&\\
-atm1010 & Atomic & 10 & 10 &&\\
-atm101 & Atomic & 10 & 1 &&\\
-atm210 & Atomic & 2 & 10 &&\\
-tab1010 & Tabulated & 10 & 10 &&\\
-tab210 & Tabulated & 2 & 10&&\\
-mol1010 & Molecular & 10 & 10&&\\
-mol510 & Molecular & 3 & 10&&\\
+adi1010 & Nil (Adiabatic) & 10 & &\\
+pow1010 & Power law & 10 & &\\
+atm1010 & Atomic & 10 & &\\
+atm210 & Atomic & 2 & &\\
+tab1010 & Tabulated & 10 & &\\
+tab210 & Tabulated & 2 & &\\
+mol1010 & Molecular & 10 & &\\
+mol310 & Molecular & 3 & &\\
 \hline
@@
 
+\begin{table*}
+\centering
+\caption{Summary of radiative transfer runs with different SiO fractional abundance
+  profiles for dynamical simulation with molecular cooling and $\eta=3$.}
+\begin{tabular}{l | l | l | l | l}
+\hline
+Profile & v$_{\rm j}$ [km s$^{-1}$] & $\delta^{-1}$ = v$_{\rm j}$/v$_{\rm s}$ & Peak Intensity [K] & $\Delta$v [km s$^{-1}$]\\ 
+\hline\hline
+Top Hat & 100.0 & 1.0 & & \\
+Functional & 100.0 & 1.0 & & \\
+Functional & 100.0 & $(1.0 + \eta^{-0.5})$ &
+& \\
+Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
+& \\
+Functional & 125.0 & $(1.0 + \eta(z)^{-0.5})$ &
+& \\
+Functional & 150.0 & $(1.0 + \eta(z)^{-0.5})$ &
+& \\
+\hline
+\end{tabular}
+\label{tab:result2}
+\end{table*}
+
 \section{Results}
 \subsection{Comparison of cooling prescription}
+Importance of cooling prescriptions\\
+Bulk of emission comes from cooling instabilities.
 figure nos. 2 -- Similuated images, emission maps for eta = 10.
@@
 each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
-\label{cooling2-1}
+\label{cooling2-1} % This plots needs to be changed.
 \end{figure}
 
-\subsection{Effects of changing $\eta$ and $\beta$}
-figure nos. 2 -- Simulated images describing lengths, collimation and
-emission for lower eta more stronger. 
-\begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/jetplt2_diffetabeta.png}
- \caption{Jet Volume Density for atomic cooling with $\eta$ = 10 but $\beta$ = 1 and
-   10 and that with tabulated cooling with $\beta$ = 10 but $\eta$ = 2
-   and 10.}
-\label{grid}
-\end{figure*}
+% \subsection{Effects of changing $\eta$ and $\beta$}
+% figure nos. 2 -- Simulated images describing lengths, collimation and
+% emission for lower eta more stronger. 
+% \begin{figure*}
+%  \includegraphics[width=2.\columnwidth]{\figpath/jetplt2_diffetabeta.png}
+%  \caption{Jet Volume Density for atomic cooling with $\eta$ = 10 but $\beta$ = 1 and
+%    10 and that with tabulated cooling with $\beta$ = 10 but $\eta$ = 2
+%    and 10.}
+% \label{grid}
+% \end{figure*}
 
@@
 contributions to cooling from fixed fractions of other molecules like
-CO, OH etc. Figure~\ref{fig:Hfracsim} shows the density of
-various hydrogen species in the outflow. Also shown in the figure is
-the temperature and mean molecular weight $\mu$. As the jet propgates
-into the medium
+CO, OH etc. First three panels of figure~\ref{fig:Hfracsim} shows the density of
+various hydrogen species in the outflow for the simulation run with
+$\eta$ = 3 and $\beta$ = 10. The jet is largely dominated by atmoic
+and molecular hydrogen, however, the fraction of these species have
+considerably changed from their initial values within the
+jet. Ionzied hydrogen is mainly formed at the tip
+of the bow as seen by the increase of fHII to 10\% from an initial value of
+1\% within the jet.
+%
 
-figure nos. 2 --> Explain molecular cooling in more details. With the
-mechanism of formation and destruction of HI, H2 and HII using
-figures. 
+The last two panels of figure~\ref{fig:Hfracsim}
+show the temperature and mean molecular weight $\mu$. The
+highest tempeature of $\sim$ 50000\,K is attained in our flow at the
+tip of the bow shock. While the temperature on the edges (i.e.,interface between
+jet and the ambient medium) is lower than 5000\,K. Also the relatively
+weaker shocks formed due to knots do not heat up the material beyond
+few 10$^{3}$\, K. The mean molecular weight, $\mu$, gives an indication
+on which specie of hydrogen dominates in what regions of the flow. In
+particular, a value of $\mu > 2.$ represents regions dominated by
+molecular hydrogen, regions with lowest values of $\mu$ are where most
+of the ionized hydrogen is present, while along the jet the value
+$\mu$ is close to 1.3 suggesting an atomic jet. 
+%
+
 \begin{figure*}
@@
 
+The distribution of fractions of different hydrogen species along with
+temperature suggests that there are essentially three regions where
+chemistry is evolved due to shocks.
+They are : (1) The tip of the jet , (2) The edges of the jet and
+(3) intermediate knots. As the atomic jet propgates from the lower boundary 
+into the cold molecular medium , it forms a strong shock resulting in
+forming a density and temperature discontinuity. Such a jump in
+dynamical quantities play a crucial role in evolution of
+chemistry. For example, temperatures beyond few 1000\,K produced in the shocks could
+disassociate the molecules and can also lead to ionization if
+temperature reaches above 10$^{4}$\,K.
+
 \begin{figure*}
@@
    medium and at the bow shock}
-\label{grid}
+\label{fig:Hmolform}
 \end{figure*}
@@
 Contour maps for two transitions for top hat profile.
+Effects of varing abundance profile ... Crucial ingredient in
+modeling molecular bullets \\
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/EM_diffabun.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/diffabunEM.png}
  \caption{Variation of 2-$>$1 SiO emission for runs with molecular
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/contourmapsSiOTopHat.png}
- \caption{Contours of SiO 2-$>$1 and 8-$>$7 emission obtained using the
-   SiO Top Hat profile.}
+ \includegraphics[width=1.\columnwidth]{\figpath/PV_diffprof.png}
+ \caption{Contour maps of position-velocity diagram for the internal
+   knots for 2-$>$1 SiO emission for runs with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance
+   profiles. The contours mark different levels of emission in Kelvins, viz.,
+   0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
 \label{grid}
@@
 spectra and line ratios  
+Spectra and PV Digrams\\
+Line - withs $\sim$ 15-25 km\,s$^{-1}$. Wedge shaped PV diagrams
+a signature feature of jet driven molecular outflows. Counterparts in
+observations.
 
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/PV_diffabun.png}
- \caption{Variation of position-velocity diagram for 2-$>$1 SiO emission for runs with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
-\label{grid}
+ \includegraphics[width=1.\columnwidth]{\figpath/imshkvh_21_90_empvspec.png}
+ \caption{Emission map ({\it top left}), PV diagram ({\it top right}
+   and spectra ({\it bottom} for the
+   2-$>$1 SiO transition for the run with molecular cooling with
+   $\eta$ = 3 and fractional abunance of functional form is used
+ along with $\delta < $ 1. The jet is assumed to be in the plane of
+ sky implying an angle of inclination of $90^{\circ}$. The horizontal
+ {\it white dashed} line marks the cuts where the spectra is taken
+ while the vertical {\it magenta dashed} line represents the cut for
+ the PV digram.} 
+\label{empvspec90}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/imshkvh_21_60_empvspec.png}
+ \caption{Same as figure~\ref{empvspec90} but with angle of
+   inclination of $60^{\circ}$.} 
+\label{empvspec60}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/imshkvh_21_45_empvspec.png}
+ \caption{Same as figure~\ref{empvspec90} but with angle of
+   inclination of $45^{\circ}$.} 
+\label{empvspec45}
 \end{figure}
@@
 \section{Discussion}
-Effects of varying $\eta$\\
-Lower $\eta$ gives better emission.
+Here we compare the various results with SiO observation of young low
+mass and high mass outflows.
 
-Importance of cooling prescriptions\\
-Bulk of emission comes from cooling instabilities.
-
-Effects of varing abundance profile ... Crucial ingredient in
-modeling molecular bullets \\
-
-Spectra and PV Digrams\\
-Line - withs $\sim$ 15-25 km\,s$^{-1}$. Wedge shaped PV diagrams
-a signature feature of jet driven molecular outflows. Counterparts in observations.
-
-Comparison with Observed results \\
+\subsection{Line transitions and ratio}
 Different line transition trace different components of SiO
@@
 trace a much more collimated region along with the terminal shock. 
-As seen by Chandler \& Richer 2001 and Hirano 2006.
+As seen by \cite{Chandler:2001p14376} and \cite{Hirano:2006p14411}.
+% \begin{figure*}
+%  \includegraphics[width=2.\columnwidth]{\figpath/linejets_thnolog.png}
+%  \caption{SiO emission from different line transitions for the run with molecular
+%    cooling having $\eta$ = 3 and $\beta$ = 10 using top-hat fractional
+%    abundance profile. }
+% \label{grid}
+% \end{figure*}
+
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/linejets_thnolog.png}
- \caption{SiO emission from different line transitions for the run with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10 using top-hat fractional
-   abundance profile. }
+ \includegraphics[width=2.\columnwidth]{\figpath/imshkvhcontomaps.png}
+ \caption{Contours of SiO emission for different line transitions
+   obtained for the run with molecular cooling with $\eta$ = 3 using
+   the functional form of the SiO fractional abundance with $\delta <$
+   1. The contour colors represent different intensities in Kelvins, i.e,
+   30.0({\it red}), 10.0({\it green}), 5.0({\it blue}), 1.0({\it
+     magenta}), 0.5({\it cyan}), 0.1({\it black}).} 
 \label{grid}
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/LineRatio_TH_60_Y205.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/LineRatio_imshkv60.png}
  \caption{{\em{Top}} Line profiles in SiO J = 2-1, 5-4 and 8-7 at one
@@
 
-EHV component ?? \\
+\subsection{Shock Kinematics}
+C-type vs J-type shocks. \cite{Gueth:1998p14058} shows that SiO
+emission has counterparts to H$_2$ emission and prefers the J-shock
+formation of SiO.
 
-Limitations\\
-
-\section{ALMA view}
+\subsection{ALMA view}
 ALMA view of the reference run and stress of applying our synthetic techniques
 to study the molecular outflows in more details.\\
-Figure 6. for ALMA -- \\
+Figure 6. for ALMA --
 

### 2013-08-24 PAPER/ms_final_bv.tex
Added lastest version of paper and new figures

@@
 \title{SiO Molecular Jets around young stars - A numerical perspective}
-\author[B. Vaidya, Tom Douglas, Paola Caselli, Tom Hartquist]{B. Vaidya$^{1}$\thanks{E-mail:
-B.Vaidya@leeds.ac.uk (BV)}, Tom Douglas$^{1}$, Paola Caselli$^{1}$, Tom Hartquist$^{1}$\\
+\author[B. Vaidya, Tom Douglas, Paola Caselli]{B. Vaidya$^{1}$\thanks{E-mail:
+B.Vaidya@leeds.ac.uk (BV)}, Tom Douglas$^{1}$, Paola Caselli$^{1}$\\
 $^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2
@@
   % methods heading (mandatory)
-   { For such a study, we have perfomed MHD simulations
+   { For such a study, we have performed MHD simulations
 of jet propagation into a molecular cloud using the PLUTO
@@
 massive and low star forming regions. These supersonic flows
-perpendicular to the underlying accertion disk plays a vital role in
+perpendicular to the underlying accretion disk plays a vital role in
 removing excess angular momentum and thereby aiding in the accretion. 
@@
 The most popular among them is the jet driven model as wind
-driven molecular outflows not only fail to match observed PV digarams \cite{Cabrit:1992p14098}
-but also tend to sweep large quantitity of material at the extermities
-of the lobes \cite{Masson:1992p14101}. While the jet driven models could sucessfully
+driven molecular outflows not only fail to match observed PV diagrams \cite{Cabrit:1992p14098}
+but also tend to sweep large quantity of material at the extremities
+of the lobes \cite{Masson:1992p14101}. While the jet driven models could successfully
 derive the global outflow shapes and mass velocity relations of CO
@@
 However, most of these dynamical models do not
-account for shock chemsitry. Instead, shock chemistry is studied
+account for shock chemistry. Instead, shock chemistry is studied
 independently using steady state non-dissociative C-type and
@@
 like SiO and CO could as form within the jet. Similar conclusions of
-molecules surving in steady state disk winds have also been shown
+molecules surviving in steady state disk winds have also been shown
 \cite{Panoglou:2012p10039}. 
@@
 %
-In the present work, our goal is to take a step further in modelling of
+In the present work, our goal is to take a step further in modeling of
 jet driven molecular outflows. The present model aims to consistently derive observed emission
 properties of molecular outflows, specifically various SiO line
-tranistions, by combining axisymmetric MHD simulations of
-radiative jet propogation. In particular, we evolve the jet dynamical
+transitions, by combining axisymmetric MHD simulations of
+radiative jet propagation. In particular, we evolve the jet dynamical
 quantities in conjunction with different non-equilibrium cooling
@@
 In the next three section we describe our numerical setup, cooling
-presecriptions and radiative transfer line code respectively. In
+prescriptions and radiative transfer line code respectively. In
 Sect. 5, we will present results from the parameter survey and the
@@
 this jet interacts with the medium, we evolve the dynamics along with
-chemistry and cooling prescribtions. They are described in details in
+chemistry and cooling prescriptions. They are described in details in
 the next section.
@@
 This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
-See fig.
+%See fig.
 \ref{points} for an example of the points distribution in r, z.
@@
 \label{ssec:sioabun}
-Need refs for this!!\smallskip
-The amount of SiO is determined by the local velocity and
-temperature. The fractional abundance is given by the equation:
-
-\begin{eqnarray}
-log(X)=-2.48\times10^{-8}v^5 + 5.50\times10^{-6}v^4 \nonumber \\
-- 4.28\times10^{-4}v^3 + 1.24\times10^{-2}v^2 \nonumber \\
-+ 2.52\times10^{-2}v - 1.20\times10^{1}
-\label{eq:fracSio}
-\end{eqnarray}
-
-where v is the shock velocity in kilometres per second. 
-In addition to this if the temperature at the point is greater than 92,000K (the temperature of the Si-O bond disassociation energy) the abundance is reduced to 10$^{-12}$.
+Molecular abundance is one of the important ingredients that is
+required by the radiative transfer code described above. 
+Typically, extremely low abundance of SiO is
+found (n(SiO)/n(H2) $< 3\times10^{-12}$) in dark, dense clouds such
+as TMC1 \citep{Ziurys:1989p14699,MartinPintado:1992p14309}. Whereas, in
+outflows like L1448, SiO abundance can increase up to 10$^{-6}$ specially in
+molecular bullets moving with a projected velocity of 60
+km\,s$^{-1}$ \citep{Dutrey:1997p11185}. Thus, there is
+a significant increase of 6 orders of magnitude from quiescent clouds
+to outflows crowded with shocks. Production of
+gaseous SiO due to slow C-type shocks has been suggested to occur via release of
+silicon from grain cores and from grain mantles. Various stationary
+shock models indicate a sudden abundance increase in SiO 
+near a shock speed of 20-30\,km\, s$^{-1}$. However, several young
+outflows have velocities of the order of 100 km\,s$^{-1}$ as in the present
+case. Shocks due to such outflows will dissociate H$_{2}$ and will
+become J ({\em{jump}}) type shocks. Thus molecules observed in such
+energetic outflows must have been reformed in the flow as suggested by
+detailed models of J-shocks by \cite{Neufeld:1989p14322}. SiO formation in J shocks
+have also been modelled recently and have thought to be reasonable
+candidates of SiO line emission in molecular outflows and jets
+\citep{Guillet:2009p11229}.
+%
+
+In-spite of all numerical models relating to the study of enhancement
+of SiO in shocks, very little is known about the dependence of SiO
+abundance on shock speeds. Considering the complex grain
+chemistry that is involved in order to estimate the functional
+dependence of SiO abundance on shock speeds, we prescribe these
+profiles based on limited empirical evidences. The most simple among
+them is the top hat profile in which the SiO abundance is a low value of
+10$^{-12}$ below 20 km s$^{-1}$ and above 100 km s$^{-1}$ and a
+maximum value of 10$^{-6}$ between these two velocities.
+In order to get rid of a discontinuous change of abundance, we also
+prescribe a gaussian such that the peak SiO abundance of 10$^{-6}$ is at
+60\,km\,s$^{-1}$. While the value of n(SiO)/n(H$_{2}$) falls below
+10$^{-9}$ at 20 and 100 km s$^{-1}$. These functional dependences of SiO
+abundance on shock velocity are show in figure~\ref{abun}.  
+In addition to this if the temperature at the point is greater than
+92,000\,K (the temperature of the Si-O bond disassociation energy) 
+the abundance is reduced to 10$^{-12}$. 
+%
 
 \begin{figure}
- \includegraphics[width=84mm]{\figpath/diffabun.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/diffabunprof1.png}
  \caption{The different fractional SiO abundances as a function of
-   shock velocity, V${\rm s}$.}
+   shock velocity, v$_{\rm s}$.}
  \label{abun}
 \end{figure}
+
+Further, the velocities obtained from the dynamical simulations are in fact the
+jet flow velocities. They can well be different from the shock
+velocities depending upon the density contrast between the jet and
+ambient medium. For the present study, we will consider two
+cases. Firstly, the most simple one in which the jet flow velocity is
+same as the shock velocity. Considering that there is a density
+contrast in the simulation setup this assumption is will
+overestimate the shock velocity. In order to correct the same we also
+consider a case in which the shock speed of a dense plug accumulated
+between the jet and medium is estimated by balancing the the respective ram
+pressures \citep{Masson:1993p9661},
+\begin{equation}
+\label{eq:shockjetvel}
+v_{\rm s} = \frac{v_{\rm j}}{1 + \eta^{-0.5}} = \frac{v_{\rm j}}{\delta}
+\end{equation}
+where v$_{\rm s}$ is the velocity of dense plug and v$_{\rm j}$ is the
+jet velocity. A comparative view of using such velocity corrections and
+functional forms of SiO abundances are discussed in
+Sec~\ref{ssec:sioabunem}.
+
+% The fractional abundance is given by the equation:
+
+% \begin{eqnarray}
+% log(X)=-2.48\times10^{-8}v^5 + 5.50\times10^{-6}v^4 \nonumber \\
+% - 4.28\times10^{-4}v^3 + 1.24\times10^{-2}v^2 \nonumber \\
+% + 2.52\times10^{-2}v - 1.20\times10^{1}
+% \label{eq:fracSio}
+% \end{eqnarray}
+
+% where v is the shock velocity in kilometres per second.
 
@@
 
+\subsection{Parameter definitions}
+\label{ssec:paradef}
 For the first part of the study concerning the dynamical numerical
 simulations, we will focus on two main parameters. They are the
-prescribtion of cooling and the density contrast between the jet and
-the ambient medium denoted by $\eta$. The various cooling prescribtions used for the present study are
-described in details in section~\ref{sec:chem}. A value of $\eta > 1$, mean that
-that jet is overdense with respect to the medium. In all our runs with
-different cooling prescribtions, we have assumed the jet to be
-overdense by 10 times that of the ambient medium. Additionally, for
+prescription of cooling and the density contrast between the jet and
+the ambient medium denoted by $\eta$. The various cooling prescriptions used for the present study are
+described in details in section~\ref{sec:chem}. They differ in the
+physical process that is responsible for cooling and chemistry. The
+most simple one is that of power-law cooling with no chemistry and the
+most complex cooling module is where molecular hydrogen chemistry is
+evolved with contributions to cooling from other abundant molecules
+like CO, OH etc. 
+%
+
+A value of $\eta > 1$, mean that
+that jet is over dense with respect to the medium. In all our runs with
+different cooling prescriptions, we have assumed the jet to be
+over-dense by 10 times that of the ambient medium. Additionally, for
 the atomic, tabulated and molecular cooling runs we have used a
@@
 the jet and the medium. 
-The magentic field strength is kept to be fixed using $\beta = 10.0$,
+The magnetic field strength is kept to be fixed using $\beta = 10.0$,
 for all our runs. Table~\ref{tab:result1} lists all the runs with
@@
 
-The post-processing phase is done in details for the molecular run
-with $\eta = 3$. To obtain the SiO emission maps and corresponding
+To obtain the SiO emission maps and corresponding
 spectra, two additional free parameters are required along with other
@@
 respect to line of sight denoted by $\phi$. Section~\ref{ssec:sioabun}
-describes all the profiles used for the present study. The obivious
+describes all the profiles used for the present study. The obvious
 choice for the inclination angle, $\phi$ is 90$^{\circ}$ indicating
@@
 results with observations. The runs with different fractional
-abundance profiles are described in table~\ref{tab:result2}
+abundance profiles are described in table~\ref{tab:result2}. A
+parameter introduced here is $\delta$ which is essentially the ratio
+of shock velocity v$_{\rm s}$ and initial jet velocity v$_{\rm
+  j}$ such that its value depends on density contrast $\eta$
+(see Eq.~\ref{eq:shockjetvel}).
 
@@
 \hline
-Profile & v$_{\rm j}$ [km s$^{-1}$] & $\delta^{-1}$ = v$_{\rm j}$/v$_{\rm s}$ & Peak Intensity [K] & $\Delta$v [km s$^{-1}$]\\ 
+Profile & $\delta$ = v$_{\rm jet}$/v$_{\rm s}$ & Peak Intensity [K] & $\Delta$v [km s$^{-1}$]\\ 
 \hline\hline
-Top Hat & 100.0 & 1.0 & & \\
-Functional & 100.0 & 1.0 & & \\
-Functional & 100.0 & $(1.0 + \eta^{-0.5})$ &
+Top Hat & 1.0 & & \\
+Top Hat & 1/$(1.0 + \eta(z)^{-0.5})$ & & \\
+Gaussian & 1.0 &
 & \\
-Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
+Gaussian & 1/$(1.0 + \eta(z)^{-0.5})$ &
 & \\
-Functional & 125.0 & $(1.0 + \eta(z)^{-0.5})$ &
-& \\
-Functional & 150.0 & $(1.0 + \eta(z)^{-0.5})$ &
-& \\
+%Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
+%& \\
+%Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
+%& \\
 \hline
@@
 
+\subsection{Reference Run}
+\label{ssec:refrun}
+We define a reference run in order to quantify and compare results obtained from such a
+survey of above mentioned parameters. The results shown in this work will be
+pertaining to the reference run and appropriate comparison will be
+discussed with other runs.
+%
+
+The reference run in our calculation has density contrast $\eta$ = 3
+with a plasma beta, $\beta$ = 10. The jet for this run is 89\% atomic,
+10\% molecular and 1\% ionized to begin with. This jet enters the
+ambient medium with a velocity of v$_{\rm jet,0}$ = 100 km
+s$^{-1}$. The cooling in the jet is
+via molecular cooling prescription, whereby the hydrogen fractions are
+evolved with cooling contributions for abundant molecules like CO, OH
+etc. The steady state density, temperature and velocity obtained from this 
+run is post-processed to obtain the observational features
+corresponding to SiO molecule. 
+For the radiative transfer calculation, the source in the reference
+run is stationary and the jet is in plane of the sky ($\phi =
+90^{\circ}$). A gaussian profile is used for the fractional abundance
+of SiO.
+%TheSiO fractional abundance used is that obtained
+%from equation~\ref{eq:fracSio}. 
+Further, the shock velocity which determines
+the fractional abundance, v$_{\rm s}$, is less than the jet velocity in the
+flow, such that their ratio $\delta$ is given by 1./$(1.0 +
+\eta(z)^{-0.5})$, where $\eta(z)$ is the density contrast as a
+function of height from the base of the jet.
+
 \section{Results}
+
 \subsection{Comparison of cooling prescription}
@@
 Bulk of emission comes from cooling instabilities.
-figure nos. 2 -- Similuated images, emission maps for eta = 10.
+figure nos. 2 -- Simulated images, emission maps for eta = 10.
 \begin{figure*}
@@
 \subsection{Molecular cooling and H$_2$ Chemistry}
-In case of molecular outflows, the most appropiate form of cooling
-prescribtion among the ones described in sect.~\ref{sec:chem} is
+In case of molecular outflows, the most appropriate form of cooling
+prescription among the ones described in sect.~\ref{sec:chem} is
 that which involves the evolution of H$_2$ chemistry along with
@@
 various hydrogen species in the outflow for the simulation run with
-$\eta$ = 3 and $\beta$ = 10. The jet is largely dominated by atmoic
+$\eta$ = 3 and $\beta$ = 10. The jet is largely dominated by atomic
 and molecular hydrogen, however, the fraction of these species have
 considerably changed from their initial values within the
-jet. Ionzied hydrogen is mainly formed at the tip
+jet. Ionized hydrogen is mainly formed at the tip
 of the bow as seen by the increase of fHII to 10\% from an initial value of
@@
 show the temperature and mean molecular weight $\mu$. The
-highest tempeature of $\sim$ 50000\,K is attained in our flow at the
+highest temperature of $\sim$ 50000\,K is attained in our flow at the
 tip of the bow shock. While the temperature on the edges (i.e.,interface between
@@
 particular, a value of $\mu > 2.$ represents regions dominated by
-molecular hydrogen, regions with lowest values of $\mu$ are where most
-of the ionized hydrogen is present, while along the jet the value
+molecular hydrogen, while regions close to the bow shock have lowest
+values of $\mu$ where ionized hydrogen is present and along the jet the value
 $\mu$ is close to 1.3 suggesting an atomic jet. 
@@
 They are : (1) The tip of the jet , (2) The edges of the jet and
-(3) intermediate knots. As the atomic jet propgates from the lower boundary 
+(3) intermediate knots. As the atomic jet propagates from the lower boundary 
 into the cold molecular medium , it forms a strong shock resulting in
@@
 temperature reaches above 10$^{4}$\,K.
-
+%
 \begin{figure*}
@@
 
-\subsection{SiO Abundance profile}
-figure nos. 2 -- Comparison of three profiles for SiO Abundance,
-Contour maps for two transitions for top hat profile.
-Effects of varing abundance profile ... Crucial ingredient in
-modeling molecular bullets \\
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/diffabunEM.png}
- \caption{Variation of 2-$>$1 SiO emission for runs with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
-\label{grid}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/PV_diffprof.png}
- \caption{Contour maps of position-velocity diagram for the internal
-   knots for 2-$>$1 SiO emission for runs with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance
-   profiles. The contours mark different levels of emission in Kelvins, viz.,
-   0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
-\label{grid}
-\end{figure}
-
-\subsection{Spectra and PV diagrams}
-figure nos. 1 -- one transition 3 different angles, Comparison of
-spectra and line ratios  
-Spectra and PV Digrams\\
-Line - withs $\sim$ 15-25 km\,s$^{-1}$. Wedge shaped PV diagrams
-a signature feature of jet driven molecular outflows. Counterparts in
-observations.
+For the reference run, the effect of shock in dynamical evolution of
+hydrogen fraction is presented in figure~\ref{fig:Hmolform}. The top
+panel of the figure shows number density of hydrogen in the jet. This
+hydrogen exists in three forms namely, molecular, atomic and
+ionized. The fraction of each of these forms are shown in bottom
+panels of figure~\ref{fig:Hmolform} at two representative regions in
+the jet marked with the arrow. The left bottom panel shows the
+vertical distribution of temperature, molecular and atomic fraction at the
+interface of the knot and the ambient medium. The interaction of the
+knot with the medium raises that temperature to 1200\,K and
+accumulates the matter such the density in that region reaches up to
+10$^{6}$ cm$^{-3}$. Behind the shock as the material cools, atoms
+combine together to form molecules as seen in the increase of fH2 from
+0.44 to 0.52. This rise in molecular fraction comes at an expense of
+reduction in atomic fraction from 0.56 to 0.48. Further away from the
+shock, these species tend to reach a quasi equilibrium as their
+fractions reach towards a value of 0.5. The ionized fraction is
+extremely low in this region due to low temperatures. However at the
+bow-shock, temperatures rise up to 20000\,K. Molecular
+hydrogen species are destroyed, while ionized hydrogen shows an
+increase in its fraction as seen in the bottom right panel of
+figure~\ref{fig:Hmolform}. The peak in ionized fraction of 0.15
+coincides with the peak in temperature profile as expected. The
+molecular fraction shows a considerable dip from 0.3 to 0.03 at 
+this temperature before rising sharply in the ambient molecular
+medium. 
+%
+
+In summary, the axi-symmetric jet flow with periodic knots 
+produce shocks of varied strengths giving rise to density, velocity and
+temperature distribution. Molecular cooling and chemistry also 
+allows us to evolve fractions of different hydrogen species along with the jet
+flow. These jet quantities are then post-processed with a radiative
+transfer code described in section~\ref{sec:radtrans} to obtain emission maps,
+spectra and PV diagrams.
+
+\subsection{Emission Maps, Spectra and PV diagrams}
+\label{ssec:emspecpv}
+The output obtained from the radiative transfer calculation is a data
+cube with velocity being the third axis. This allows us to obtain
+spectra and position velocity diagrams from these data cubes. 
+Figure~\ref{empvspec90} shows all the possible outputs from the data
+cube for the J = 2-$>$1 transition for the reference run. 
+The top left panel in the figure shows the emission map for the jet
+directed downwards. The notable features are the knots close to the
+base of the jet and the emission near the bow shock due to density
+enhancement by cooling instability. The PV diagram shown in the top
+right panel is obtained along the jet as indicated by vertical magenta
+line. The position is shown in terms of pixels, where each pixel has a
+width of about 16\,AU. The channel numbers in the X-axis indicate
+velocities. The whole velocity range of -20 km s$^{-1}$ to 20 km
+s$^{-1}$ is uniformly divided into 80 channels. High velocity features
+are clearly seen in regions corresponding to the knots in the emission
+maps. These features fade along the jet as the knots also disappear in
+the emission map. The region close to the bow shock as well gives
+indication of high velocity features which are seen as broad wings in
+the spectra. 
+%
 
@@
    2-$>$1 SiO transition for the run with molecular cooling with
-   $\eta$ = 3 and fractional abunance of functional form is used
+   $\eta$ = 3 and fractional abundance of functional form is used
  along with $\delta < $ 1. The jet is assumed to be in the plane of
@@
 
+The spectra at three different positions in the flow are shown in the
+bottom panel of figure~\ref{empvspec90}. These three positions are
+basically the two knots close to the base of the flow and region close
+to the bow shocks. They are marked by horizontal white dashed lines in
+the emission maps. The knot closer to the base is the brightest
+showing a peak intensity of 50\,K. As one moves along the jet the
+intensity decreases and reaches to about 10\,K close to the bow shock.
+The line widths seen for this reference run with an angle of
+inclination of 90$^{\circ}$ are typically around 5-10 km s$^{-1}$.
+These line widths increase substantially as the angle of inclination
+decreases. Figures~\ref{empvspec60} and \ref{empvspec45} show the
+emission map, PV diagram and spectra for the same reference run but
+with angle of inclination of 60$^{\circ}$ and 45$^{\circ}$
+respectively. These runs are done assuming the the source has a
+velocity of 20 and 30 km s$^{-1}$ respectively.
+The spectra for low inclination angles are much broader
+and less bright at the same three positions in the flow (shown by
+three white dashed lines). The line 
+widths now are typically of the order of 20 km s$^{-1}$ and the peak
+intensity of the brightest knot is approximately 10\,K. 
+The PV diagrams in these runs are not anymore symmetric unlike the run
+with the jet in plane of the sky. Instead, they show a distinct {\it zig-zag}
+pattern at each of the knots and region close to the bow shock.
+
 \begin{figure}
@@
 
+%
+The predicted emission maps, spectra and PV diagrams are shown above to depend
+on the angle of inclination. In the next section, we focus on the
+dependence of these observational features on the 
+different fractional abundance profiles of SiO.
+
+\subsection{SiO Abundance profile}
+\label{ssec:sioabunem}
+Input profiles in the radiative transfer code for the
+fractional abundance of SiO are a very modest approximation from 
+observed values (see sec~\ref{ssec:sioabun}). In
+figure~\ref{fig:diffabunem}, we compare the maps for J = 2-$>$1
+emission for two different abundance profiles and ratio of jet to
+shock velocities. There is a striking difference with regards to
+emission from the internal knots in these images. All the internal
+knots show emission in the J=2-$>$1 line whilst using a top hat profile
+and accounting for shock speeds (i.e. $\delta < 1$). However, some of
+these knots are not observed when using the same top-hat profile but
+assuming the shock velocity to be same as the jet velocity (i.e.,
+$\delta$ = 1). Similar qualitative characteristics are seen in case of a gaussian
+abundance profile. In particular, the case with $\delta$ = 1 only
+produce emission from the knot closest to the bow shock, while the internal
+knots do not show any appreciable emission. Further, the emission from
+the knot closer to the bow shock varies considerably with different
+profiles and value of $\delta$. It is the brightest for the case with
+a top-hat profile and $\delta < 1$. The peak emission and line widths at this knot
+are listed in table~\ref{tab:result2}
+%
+
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/EM_gaussandth.png}
+ \caption{Variation of 2-$>$1 SiO emission for runs with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
+\label{fig:diffabunem}
+\end{figure}
+
+The dependence of emission on SiO abundance profile is expected due to
+the distribution of jet velocity obtained from dynamical
+simulations. We see that the velocity of internal knots lie around
+70-90\,km\,s$^{-1}$, while the pulsed jet was injected with a mean of
+100\,km\,s$^{-1}$. The knots slow down during the evolutionary
+phase as they interact with the ambient medium. Interestingly, younger
+knots closer to the base of the jet are brighter compared to older
+ones further away from the jet (see panels 1 and 3 of
+fig~\ref{fig:diffabunem}). This is attributed to the fact that the
+ambient medium has a density gradient that goes as $\sim
+z^{-2}$. Thus, the younger knots suffer the most deceleration closer
+to the base of flow. This fact is taken into account when the shock
+velocity is consistently calculated using the density contrast and
+using a value of $\delta <$ 1. This process is further validated by
+the lack of emission from internal knots in panel 4 of the
+fig~\ref{fig:diffabunem}. 
+%
+
+Additionally, the internal knots show their distinct signatures in
+form of {\em Hubble wedges} as seen in the PV diagrams for these
+different profiles (see
+~\ref{ssec:emspecpv}). Figure~\ref{fig:pvdiffabun} shows a zoomed
+version of the bottom four internal knots in form PV diagram for these
+different abundance profile. As expected, the signatures of knotty
+emission is missing for the case with gaussian profile with $\delta$ =
+1. Further, the wedges formed in panels 1 and 2 of the figure in
+general slightly more extended in position space as compared to ones
+formed in panel 4 of the same figure. This is indeed because of the
+discontinuous nature of top-hat abundance profile as the SiO is
+enhanced to a maximum abundance for all velocities between 20 and 100
+km\,s$^{-1}$, which is not the case in a more continuos gaussian
+distribution.
+
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/PV_gaussandth.png}
+ \caption{Contour maps of position-velocity diagram for the internal
+   knots for 2-$>$1 SiO emission for runs with molecular
+   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance
+   profiles. The contours mark different levels of emission in Kelvins, viz.,
+   0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
+\label{fig:pvdiffabun}
+\end{figure}
+
+\section{ALMA view}
+ALMA view of the reference run and stress of applying our synthetic techniques
+to study the molecular outflows in more details.\\
+Figure 6. for ALMA --
+
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/ALMAmaps2.png}
+ \caption{Channel maps from ALMA 5-4 with 45 deg. at channels 10,20,30,40.}
+\label{grid}
+\end{figure}
+
 \section{Discussion}
@@
 mass and high mass outflows.
+
+\subsection{EHV component and J-type shocks}
+\label{ssec:EHV}
+C-type vs J-type shocks. \cite{Gueth:1998p14058} shows that SiO
+emission has counterparts to H$_2$ emission and prefers the J-shock
+formation of SiO. Formation of molecules formed behind the shock.
 
@@
    $\beta$ = 10 using top hat abundance profile. The profiles are
-   obatined when the angle of inclination is 60$^{\circ}$ with respect
+   obtained when the angle of inclination is 60$^{\circ}$ with respect
  to line of sight. {\em{Bottom}} Line temperature ratios T(8-7)/T(5-4)
@@
 
-\subsection{Shock Kinematics}
-C-type vs J-type shocks. \cite{Gueth:1998p14058} shows that SiO
-emission has counterparts to H$_2$ emission and prefers the J-shock
-formation of SiO.
-
-\subsection{ALMA view}
-ALMA view of the reference run and stress of applying our synthetic techniques
-to study the molecular outflows in more details.\\
-Figure 6. for ALMA --
+\subsection{Limitations}
+Better handle on Molecular fraction in jets.\\
+Zero order approximation of SiO fractional abundance profile.\\ 
+Wider CO and H2O component.\\
 
 \section{Conclusion}
-We are the best in modelling SiO outflows.
+We are the best in modeling SiO outflows.
 

### 2013-08-24 makeALMAplot.py
Added python code to make the required ALMA map

@@ -1,0 +1,98 @@
+from numpy import *
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+import pyfits as pf
+import os
+import matplotlib.gridspec as gridspec
+import sys
+import nice_plots as nplt
+nplt.nice_plots(fs=15)
+
+def RA2ICRS(arr):
+    arr1 = []
+    for i in arr:
+        RAdeg = (i/360.0)*24.0 
+        RAh = int(floor(RAdeg))
+        RAm = (RAdeg-RAh)*60.0
+        RAm2 = int(floor(RAm))
+        RAs = (RAm-RAm2)*60.0
+        arr1.append(str(RAh)+'h'+str(RAm2)+'m'+str('%.1f'%RAs)+'s')
+    return arr1
+
+def DEC2ICRS(arr):
+    arr1 = []
+    for i in arr:
+        DECdeg = int(floor(i))
+        DECm = (i - DECdeg)*60.0
+        DECm2 = int(floor(DECm))
+        DECs = (DECm-DECm2)*60.0
+        arr1.append(str(DECdeg)+'$^\circ$'+str(DECm2)+"'"+str('%.1f'%DECs)+"''")
+    return arr1
+
+def Velarr(ang,V0, A):
+    arr1 = [i - 120.0 for i in range(A['NAXIS3'])]
+    return arr1
+
+def fig11():
+    hdulist1 = fits.open('/Users/bhargavvaidya/pyCODES/run4ALMA/imageShock_J2-1_45deg_molcool_dirty.fits.gz')
+    hdulist2 = fits.open('/Users/bhargavvaidya/pyCODES/run4ALMA/imageShock_J5-4_45deg_molcool_dirty.fits.gz')
+    hdulist3 = fits.open('/Users/bhargavvaidya/pyCODES/run4ALMA/imageShock_J8-7_45deg_molcool_dirty.fits.gz')
+    
+    
+    A = hdulist1[0].header
+
+    RAarr = [A['CRVAL1'] - i*A['CDELT1'] for i in range(A['NAXIS1']/2)] + [A['CRVAL1'] + i*A['CDELT1'] for i in range(A['NAXIS1']/2,A['NAXIS1'])]
[…]

### 2013-08-26 convolve.py
Added new diff cool fig

@@ -1,44 +1,0 @@
-import numpy,pyfits,os,tarfile,Gnuplot,pprocess
-from math import exp,log,sqrt,pi,ceil
-from numpy.fft import fft2,ifft2, irfft2, rfft2
-from scipy import constants as cnst
-from scipy.interpolate import griddata
-import numpy as np
-import pprocess as pp
-from pylab import imshow
-import pylab as pyl
-from numpy import outer
-import pyfits as P
-
-def garray(shape, sigma):
-    a=numpy.empty(shape, dtype=float)
-    midi,midj=shape[0]/2,shape[1]/2
-    for i in xrange(shape[0]):
-        for j in xrange(shape[1]):
-            a[i,j]=exp(-1*sqrt((i-midi)**2+(j-midj)**2)**2 / (2*sigma*sigma))/(sigma*sqrt(2*pi))**2
-#exp(-1*(i-midi)**2 / (2*sigma*sigma))*exp(-1*(j-midj)**2 / (2*sigma*sigma))/(sqrt(2*pi*sigma**2))    
-    return a
-
-def FWHM2sigma (FWHM): return FWHM/(2*sqrt(2*log(2)))
-
-def next_pow2 (n):
-    if n<0: sign=-1
-    else  : sign=1
-    X=abs(n)
-    ans=1
-    while ans<X: ans*=2
-    return ans
-
-def cube_convolve(imcube, sigma):
-    "performs a convolution with a gaussian beam of width sigma on each yz plane of the cube"
-#    imcube=imcube.copy()
-    shape=imcube.shape[1:]
-    if len(shape)!=2:
-        raise ValueError ("cube is not a cube")
-    gauss_mask=garray(shape,sigma)
-    s=[next_pow2(y*2+1) for y in gauss_mask.shape]
-    ftg=fft2(gauss_mask, s).reshape(s)
-    for i in xrange(imcube.shape[0]):
-        imcube[i,...]=np.real(ifft2(fft2(imcube[i,...],s)*ftg)[shape[0]/2:3*shape[0]/2, shape[1]/2:3*shape[1]/2])
-    return imcube
- 

### 2013-08-29 PAPER/ms_final_bv.tex
Added new diff cool fig
Added Discussions

@@
   % context heading (optional)
-  {A bipolar, violent, collimated outflow is one of the first signpost of star
+  {A bipolar, violent, collimated outflow is one of the first signposts of star
 formation. Such an outflow is believed to be launched magnetically from
@@
 post-processed using a non-LTE radiative line transfer code, LIME,  to
-obtain SiO emission maps, spectra and PV digram.}
+obtain SiO emission maps, spectra and PV digrams.}
   % results heading (mandatory)
@@
 shocks. Further, we see that some SiO can be produced within the jet
-specially close to the bow shock due to instabilities associated with
+especially close to the bow shock due to instabilities associated with
 cooling. We have used these emission maps to give predictions for ALMA
-observations. Also, our model can very well reproduce the observed 
+and single dish observations . Also, our model can very well reproduce the observed 
 spectra, line ratios and PV diagrams of young outflows from Class 0 sources.}
@@
 during the later evolutionary stages \cite{Vaidya:2011p8992}. 
-Typically, these jets are few parsec size long and can be divided into
+Typically, these jets are few parsec in size long and can be divided into
 three length-scale domains viz. source and disk scales (1-10$^{2}\,$AU),
@@
 physical and chemical point of view. In addition to shocks, molecular
-material from the surrounding is entrained and accelerated to high
+material from the surroundings is entrained and accelerated to high
 velocities giving rise to molecular outflows.
@@
 v^{-\gamma}$, where values of $\gamma$ range from 1 to 3 \cite{Downes:2003p9946}. Episodic
-knots belived to be caused by variable accretion events are a common property
+knots believed to be caused by variable accretion events are a common property
 of young molecular outflows (for e.g. in L1577:
@@
 
-Even with myriad of empirical evidences, the exact nature of SiO and
-CO outflow is not clear. For a complete understanding it is imperative
+Even with a myriad of such empirical evidences, the exact nature of
+these SiO and CO outflows is not clear. For a complete understanding it is imperative
 to compliment these observations with theoretical models. Many models
@@
 The magneto-hydrodynamic (MHD) calculations by \cite{Glassgold:1991p13703} suggested that molecules
-like SiO and CO could as form within the jet. Similar conclusions of
+like SiO and CO could form within the jet. Similar conclusions of
 molecules surviving in steady state disk winds have also been shown
 \cite{Panoglou:2012p10039}. 
-Very limited simulations have modelled the outflow
+Very few simulations have modelled the outflow
 dynamics including molecular chemistry but in absence of
@@
 %
-In the present work, our goal is to take a step further in modeling of
+In the present work, our goal is to take a step further in the modeling of
 jet driven molecular outflows. The present model aims to consistently derive observed emission
@@
 transitions, by combining axisymmetric MHD simulations of
-radiative jet propagation. In particular, we evolve the jet dynamical
+radiative jet propagation with time-dependent chemistry and 3D radiative
+transfer. In particular, we evolve the jet dynamical
 quantities in conjunction with different non-equilibrium cooling
 prescriptions of varying complexities. The most complex is that of
-molecular cooling along with H$_{2}$ chemistry. This prescription
+molecular cooling along with hydrogen chemistry. This prescription
 allows us to track the formation and destruction of 
-HI, HII and H2 along with the flow dynamics. 
+HI, HII and H$_{2}$ along with the flow dynamics. 
 The final state of the jet obtained for each cooling model is then
 post-processed using a non-LTE radiative line transfer code
-to obtain emission maps, spectra and PV digram. These emission maps
-are further processed using ALMA-CASA pipeline to obtain synthetic
-images of molecular outflows.
+to obtain emission maps, spectra and PV digrams. These emission maps
+are further processed using the Common Astronomy Software Applications
+package (CASA) to obtain synthetic ALMA images of molecular outflows.
 %
@@
 \subsection{Numerical code and Equations}
-For our study, we carry out axisymmetric numerical ideal MHD simulations using the PLUTO code \citep{Mignone:2007p644} which is based on a conservative scheme of Godunov type.
+For our study, we carry out numerical axisymmetric ideal MHD simulations using the PLUTO code \citep{Mignone:2007p644} which is based on a conservative scheme of Godunov type.
 We have modified the original code to incorporate molecular cooling
@@
 to gravity are neglected for this problem as the domain of interest is
-far away from the central object (i.e., star).  
-%
-
-The cooling function $\Lambda$ which dependents on temperature $T$, mass density $\rho$ and
+far away from the central object.  
+%
+
+The cooling function $\Lambda$ which depends on temperature $T$, mass density $\rho$ and
 chemical abundances {\bf{X}}, appears in the
@@
 + \nabla \cdot\left[ \rho E \vec{v} + (P + \frac{B^2}{8\pi})\vec{v}\right]  
-- \vec{B}(\vec{v}\cdot\vec{B}) = \Lambda(\rho,T,{\bf{X}}),
+- \vec{B}(\vec{v}\cdot\vec{B}) = -\Lambda(\rho,T,{\bf{X}}),
 \end{equation}
@@
 magnetic fields, $\nabla \cdot \vec{B} = 0$, which is numerically achieved by construction 
-since using the Powell's eight wave formulation.
+using the Powell's eight wave formulation \citep{Powell:1999p14822}.
+
 \subsection{Initial Condition}
@@
 $R_{\rm j}$ along the vertical axis, $R_{\rm j}$ being the radius of
-the jet. The domain is resolved by an uniform grid with 200 cells in
+the jet. The domain of interest is about 3000\,AU away from the
+central source extends up to 0.1\,pc. Numerically, it is resolved by an uniform grid with 200 cells in
 radial and 1000 cells in vertical direction. For simplicity, we choose this medium
@@
 velocity of $v_{\rm jet,0}$ = 100 km/s as is the case for most low mass stellar jets
-specially the low velocity component. The constant jet velocity is
+especially the low velocity component. The constant jet velocity is
 superimposed with periodic pulsation of the form,
@@
 \caption{Summary from parameter runs.}
-\begin{tabular}{l | l | l | l | l | l }
+\begin{tabular}{c | c | c | c | c | c | c }
 \hline
-Run & Cooling Mode & $\eta$ & Peak Intensity [K] & $\Delta$v [km s$^{-1}$] \\
+Run & Cooling Mode & $\eta$ & \multicolumn{2}{|c|}{Top Hat Profile
+  $\delta = 1$} & \multicolumn{2}{|c|}{Gaussian Profile $\delta =
+  1$}\\
 \hline\hline
-adi1010 & Nil (Adiabatic) & 10 & &\\
-pow1010 & Power law & 10 & &\\
-atm1010 & Atomic & 10 & &\\
-atm210 & Atomic & 2 & &\\
-tab1010 & Tabulated & 10 & &\\
-tab210 & Tabulated & 2 & &\\
-mol1010 & Molecular & 10 & &\\
-mol310 & Molecular & 3 & &\\
+&&& $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] & $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] \\
+\hline
+adi1010 & Nil (Adiabatic) & 10 & 2.91 & $>$40 & 0.25 & 40.0 \\
+pow1010 & Power law & 10 & 0.64 & 8.0 & 0.02 & 10.0\\
+atm1010 & Atomic & 10 & 2.04 & 36.0 & 0.58 & 38.0 \\
+atm210 & Atomic & 2 & 3.21 & 18.0 & 0.64 & 20.0 \\
+tab1010 & Tabulated & 10 & 0.75 & 11.0 & 0.09 & 10.0 \\
+tab210 & Tabulated & 2 & 2.89 & 8.0 & 1.0 & 9.0 \\
+mol1010 & Molecular & 10 & 1.10 & 10.0 & 0.1 & 11.0 \\
+mol310 & Molecular & 3 & 3.3 & 14.0 & 0.66 & 12.0\\
 \hline
@@
 \caption{Summary of radiative transfer runs with different SiO fractional abundance
-  profiles for dynamical simulation with molecular cooling and $\eta=3$.}
+  profiles for dynamical simulation with molecular cooling and
+  $\eta=3$. The integrated intensity of the brightest lobe assuming a single disk
+  observation with a beam width of $15\,\arcsec$ is listed along with the
+  corresponding spectral width.}
 \begin{tabular}{l | l | l | l | l}
 \hline
-Profile & $\delta$ = v$_{\rm jet}$/v$_{\rm s}$ & Peak Intensity [K] & $\Delta$v [km s$^{-1}$]\\ 
+Profile & $\delta$ = v$_{\rm jet}$/v$_{\rm s}$ & $\int T_{\rm MB}dV$
+[K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$]\\ 
 \hline\hline
-Top Hat & 1.0 & & \\
-Top Hat & 1/$(1.0 + \eta(z)^{-0.5})$ & & \\
-Gaussian & 1.0 &
-& \\
-Gaussian & 1/$(1.0 + \eta(z)^{-0.5})$ &
-& \\
+Top Hat & 1.0 & 3.3 & 14.0 \\
+Top Hat & 1/$(1.0 + \eta(z)^{-0.5})$ & 4.9 & 14.0 \\
+Gaussian & 1.0 & 0.66
+& 12.0 \\
+Gaussian & 1/$(1.0 + \eta(z)^{-0.5})$ & 1.1
+& 12.0 \\
 %Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{\figpath/J2-1_mom0maps_cooling.png}
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/diffcool_EMgaussprof.png}
  \caption{A plot of the integrated SiO J2-1 emission from 5 models, 
 each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
-\label{cooling2-1} % This plots needs to be changed.
-\end{figure}
+\label{cooling2-1} 
+\end{figure*}
 
@@
 
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/EM_gaussandth.png}
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/EM_gaussandth.png}
  \caption{Variation of 2-$>$1 SiO emission for runs with molecular
@@
 \label{fig:diffabunem}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/PV_gaussandth.png}
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/PV_gaussandth.png}
  \caption{Contour maps of position-velocity diagram for the internal
@@
 \label{fig:pvdiffabun}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/ALMAmaps2.png}
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/ALMAmaps2.png}
  \caption{Channel maps from ALMA 5-4 with 45 deg. at channels 10,20,30,40.}
-\label{grid}
-\end{figure}
+\label{fig:almafig}
+\end{figure*}
 
@@
 
-\subsection{EHV component and J-type shocks}
+\subsection{EHV component and Molecular bullets}
 \label{ssec:EHV}
-C-type vs J-type shocks. \cite{Gueth:1998p14058} shows that SiO
-emission has counterparts to H$_2$ emission and prefers the J-shock
-formation of SiO. Formation of molecules formed behind the shock.
+Multiline mm-wave surveys of SiO emission towards a sample of molecular
+outflows have shown that these outflows exhibit both low and high
+velocity SiO emission possibly arising from two distinct regimes. The slow
+component in case of a typical outflow L1448 is believed to arise from
+the shell of accelerated ambient gas with SiO abundance
+lower by two orders of magnitude than regions emitting the high velocity component.
+\cite{Codella:1999p12584}. In addition, an interesting feature of EHV
+gas is seen in many young molecular outflows. The origin of EHV
+component is still a mystery, however, recent high resolution
+observations have tried to study the composition of such extremely high
+velocity gas \cite{Tafalla:2010p14759}. Typically, EHV gas feature in
+high density gas tracers (like CO and SiO) 
+and show significantly weak emission of $\sim$ 0.1\,K.
+%
+
+In IRAS 04166+2706, \cite{SantiagoGarcia:2009p13972} have shown 
+that the EHV CO(2-1) emission is mapping a jet-like
+feature that runs along the middle and consists of a collection of
+discrete peaks. These peaks of EHV emission are placed located in a
+perfect symmetry on both sides of the outflow lobe. This symmetry
+indicate that such EHV peaks might arise from events that took place
+near the central source and have since propagated in the flow
+\cite{Bachiller:1990p11196, Tafalla:2011p14051}. The dynamical 
+model in conjunction with proper radiative transfer calculations presented here 
+agrees very well with the above scenario. The {\em{bullets}} in our
+work are injected into the flow in a sinusoidal manner along with a
+collimated atomic jet. These pulsating ejections do interact with the medium
+via shocks and exciting high velocity gas. Cooling associated with
+molecules and tracing of H$_{2}$ chemistry with the flow allows us to
+consistently identify the regions where molecular hydrogen is formed
+and disassociated (see fig.~\ref{fig:Hmolform}). The SiO emission that we
+obtain from our radiative transfer calculations is associated with
+regions where shocked H$_{2}$ gas is present. A contour map of SiO
+emission obtain from the reference run is shown in
+figure~\ref{fig:ltconts}. Such a model can very well explain the
+shocked SiO velocity components observed in L1157 molecular outflow \cite{Gueth:1998p14058}. 
+%
+
+Further, we find SiO emission coming from velocities 
+of the order of 40-60 km\,s$^{-1}$ (see figs.~\ref{empvspec60} and
+~\ref{empvspec45}). Such a velocity range is typically associated with
+EHV gas seen in majority of the outflows \cite{Tafalla:2011p14051}. Additionally,
+the EHV peaks show a distinct sawtooth pattern in the PV diagram
+\cite{SantiagoGarcia:2009p13972}. Such a sawtooth pattern is very
+similar to the pattern that we see in PV diagrams from
+our models (see figs.~\ref{empvspec60} and ~\ref{empvspec45}). 
+All of the above striking similarities from observations of EHV gas
+and synthetic spectra and PV diagrams gives a very formidable backing
+to the idea that such an emission could arise due to shock interactions of
+internal knots in the flow. In the section below we further compare
+the line ratios and intensities from our results with single dish
+measurements of typical outflows with EHV emission.
 
 \subsection{Line transitions and ratio}
-Different line transition trace different components of SiO
-emission. The low level transitions trace the region where the jet
-interacts with molecular medium. The clumpy nature in its emission is
-from the turbulent nature of its interaction. The higher transitions
-trace a much more collimated region along with the terminal shock. 
-As seen by \cite{Chandler:2001p14376} and \cite{Hirano:2006p14411}.
-% \begin{figure*}
-%  \includegraphics[width=2.\columnwidth]{\figpath/linejets_thnolog.png}
-%  \caption{SiO emission from different line transitions for the run with molecular
-%    cooling having $\eta$ = 3 and $\beta$ = 10 using top-hat fractional
-%    abundance profile. }
-% \label{grid}
-% \end{figure*}
+Numerous molecular outflows with jet-like bullets have been
+observationally studied till date. In particular, H7-11
+\citep{Bachiller:1998p14725}, IRAS 04166+2706
+\citep{SantiagoGarcia:2009p13972, Tafalla:2010p14759}, HH211 \citep{Nisini:2002p14418}
+L1448 \citep{Bachiller:1991p14732,Nisini:2007p13128,
+  Tafalla:2010p14759} and L1157 \citep{Nisini:2007p13128} have
+shown clear signatures of EHV component. Among them L1448, HH211 and
+L1157 have been studied in details using an extensive multi-line
+survey of SiO. Such a multi-frequency analysis helps to understand the dependence of
+excitation conditions for these lines on velocity, based on existing shock
+models.  
+%
+
+Figure~\ref{fig:ltconts} show symmetrical contour maps of integrated 
+emission convolved with a 2\arcsec beam coming from different line
+transitions for our reference model. The most
+striking feature seen in that figure is the progressive shift of
+emitting region from the interface to internal knots with increase in
+excitation energies of different lines. In particular, the lowest
+transition J=1-$>$0 shows most of the emission coming from the
+interface between the jet and ambient medium, along with emission from
+the dense knots formed at the base of the flow. While, emission coming
+due to high energy transitions, J=5-$>$4 and 8-$>$7, 
+is more concentrated in the inner jet regions and arise mainly from
+the shocks due to internal knots. These high level transitions
+also show an evidence of sub-structure close to the primary bow shock.
+Such a trend in emission with excitation energies coming from different SiO line transitions
+have been observed in many young outflows (for e.g., {\it{L1448}}
+bullets \citep{Nisini:2007p13128}, {\it{HH211}}
+\citep{Chandler:2001p14376, Nisini:2002p14418,
+  Hirano:2006p14411}). 
+%
 
@@
      magenta}), 0.5({\it cyan}), 0.1({\it black}).} 
-\label{grid}
+\label{fig:ltconts}
 \end{figure*}
 
-Advantage of non-LTE modeling over LVG \cite{Cabrit:2007p13804}, \cite{Lee:2008p13697}. 
-Line ratios $\sim$ 1 can be explained well for low mass stars and 
-\cite{Leurini:2013p13165} for high mass stars. \\
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/LineRatio_imshkv60.png}
+\cite{Nisini:2007p13128} have shown that the current
+plane-parallel shock models fit reasonably well the physical
+conditions traced by the SiO emission i.e., temperature $\lesssim$
+1000\,K and H$_{2}$ number density $\sim$ 10$^{5}$-10$^{6}$
+cm$^{-3}$. They can also fit the observed fractional SiO abundance of
+$\sim$ 10$^{-7}$ in these outflows. However, they fail to predict all
+the line profiles and in particular their similarities for low and
+high excitation lines. Line emission for SiO from our model also traces similar
+physical environment. Fig~\ref{fig:Hmolform} shows that regions close
+to the internal knot have temperatures up to 1000\,K and molecular
+hydrogen density of the order of 10$^{5}$ cm$^{-3}$ about half that of the total
+hydrogen density in that region. These regions are where bulk of the
+SiO emission is obtained in our models. Additionally, the internal
+knots move with velocity of 70-90 km\,s$^{-1}$, indicating a
+fractional SiO abundance between 10$^{-6}$ to 10$^{-8}$, depending on the
+choice of abundance profile (see fig~\ref{abun}). 
+The line profile shapes obtained from this study fit reasonable well with that observed by
+\cite{Nisini:2007p13128}, especially for the bullets seen in
+L1448. Interestingly, we see in our models, where we relax the plane parallel
+approximation, the line profiles are equally broadened for low as well
+as high excitation lines. The top panel of fig.~\ref{fig:lineratio} shows spectra for three line
+transitions for the reference run but with an angle of inclination,
+$\phi$ = 60$^{\circ}$ and convolved with a single dish beam of
+15\arcsec. Additionally, the predicted integrated
+intensities also lie within a factor of two from the values of L1448 bullets
+observed with JCMT and IRAM (Table 2 of \citealt{Nisini:2007p13128}  and
+table~\ref{tab:result2} of this work).
+%
+
+The variation of integrated single dish emission with upper transition
+levels J$_{\rm up}$ for different abundance profiles is shown in the
+right panel of fig.~\ref{fig:lineratio}. It is clear, that a emission
+obtained using a top hat profile is brighter as compared to one
+obtained with a gaussian profile, due to its obvious high estimate of
+SiO abundance in regions of interest. However, curves obtained from
+both these profiles show a very similar shape of a distinct rise followed by a fall in
+integrated emission for higher transitions with a peak in
+emission for J$_{\rm up}$ = 3. Similar profiles are also predicted and
+used to estimate the physical conditions assuming optically
+thin emission from LVG modeling for L1448 and L1157
+\cite{Nisini:2007p13128}. However, this usual approach did not give
+accurate results for line ratios SiO(8-7)/(5-4) and SiO(5-4)/(2-1)
+in case of HH212. Values $\approx$ 1 for both ratios were
+only achieved in optically thick LTE regime
+\citep{Cabrit:2007p13804, Lee:2008p13697}. 
+Similar values are also obtained for molecular outflows from massive
+young stellar object IRAS 17233–3606\cite{Leurini:2013p13165}.
+These line ratios from the present
+non-LTE radiative transfer model are shown in the bottom left panel of
+fig.~\ref{fig:lineratio}. Their values lie very close to unity as
+indicated from observations. In summary, the
+shape, ratio and peak intensity of the spectra obtained from our model
+fit very well to observed values implying
+that SiO emission from our model is tracing the regions with right physical
+conditions that are required to emit SiO in gas phase via shocks.
+
+\begin{figure*}
+ \includegraphics[width=2.\columnwidth]{\figpath/LineRatio_THDeq1.png}
  \caption{{\em{Top}} Line profiles in SiO J = 2-1, 5-4 and 8-7 at one
    the inner knot for the molecular cooling run with $\eta$ = 3 and
-   $\beta$ = 10 using top hat abundance profile. The profiles are
+   $\beta$ = 10 using top hat abundance profile with $\delta$ = 1. The profiles are
    obtained when the angle of inclination is 60$^{\circ}$ with respect
- to line of sight. {\em{Bottom}} Line temperature ratios T(8-7)/T(5-4)
-and T(2-1)/T(5-4), as a function of velocity}
-\label{grid}
-\end{figure}
-
-\subsection{Limitations}
+ to line of sight. {\em{Bottom left}} Line intensity ratios SiO(8-7)/(5-4)
+and SiO(5-4)/(2-1), as a function of velocity. {\em{Bottom right}}
+Variation of integrated intensity with upper line transition J$_{\rm
+  up}$ for two abundance profiles.}
+\label{fig:lineratio}
+\end{figure*}
+
+\subsection{Caveats and Steps Ahead}
 Better handle on Molecular fraction in jets.\\
 Zero order approximation of SiO fractional abundance profile.\\ 
-Wider CO and H2O component.\\
+Since SiO in gas phase for 0 years with our abundance. While SiO takes
+10$^{4}$ years. History of SiO in gas phase and proper chemistry to get
+abundance.
+
+Wider CO and H2O WISH survey component.\\
 

### 2013-08-29 PAPER/ms_final_bv.tex
ALMA section 1/2 done

@@
 \begin{figure}
- \includegraphics[width=84mm]{\figpath/eta2Beta10.png}
+ \includegraphics[width=84mm]{\figpath/grid.png}
  \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate for points in the r,z plane.
@@
 to study the molecular outflows in more details.\\
-Figure 6. for ALMA --
+
+In order to see the interior structure of the molecular outflow, high resolution interferometric observations are needed.
+To demonstrate how jets similar to those we have modeled would look through such observations we have performed synthetic Atacama Large Millimetre Array (ALMA) observations using the Common Astronomy Software Applications package (CASA).
+The output from the radiative transfer were scalled to 300pc and used as the sky models for observations of the J=2-1, J=5-4 and J=8-7 lines at freqencies of 86.85, 217.10 and 347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7.
+The observations were simulated using cycle 1 ALMA for 30 minutes total integration time, in the configurations c32-6, c32-4 and c32-3 for the three lines, giving beam sizes of 0.72'', 0.47'' and 0.58'' and sensitivities of 0.05, 0.07 and 0.09$\,$mJy/beam for the three lines (as calculated by the ALMA online sensitivity calculator) with velocity resolutions of $sim$1$\,$km/s.
 
@@
  \includegraphics[width=2.\columnwidth]{\figpath/ALMAmaps2.png}
- \caption{Channel maps from ALMA 5-4 with 45 deg. at channels 10,20,30,40.}
+ \caption{{\bf Left:} The intensity map in the channel of the peak of the J5-4 emission.
+The heat map shows the 5-4 line intensity, the blue contours show the J=8-7 line intensity and the green contours show the J=2-1 line intensity (both in steps of 10mJy/beam) (this is arbitrary, could we do integrated intensity here instead?).
+{\bf Right:} The PV diagram taken along the axis of the jet, showing a 'zig-zag' pattern between the knots of the jet and broad emission at the bow shock.}
 \label{fig:almafig}

### 2013-08-30 PAPER/ms_final_bv.tex
Added new figs and text

--- 2013-08-29 PAPER/ms_final_bv.tex
@@
 \subsection{Comparison of cooling prescription}
+\label{ssec:coolres}
 Importance of cooling prescriptions\\
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/imshkvh_21_90_empvspec.png}
- \caption{Emission map ({\it top left}), PV diagram ({\it top right}
+ \includegraphics[width=1.\columnwidth]{\figpath/refrun_21_90_emspecpv.png}
+ \caption{Integrated Emission map ({\it top left}), PV diagram ({\it top right}
    and spectra ({\it bottom} for the
-   2-$>$1 SiO transition for the run with molecular cooling with
-   $\eta$ = 3 and fractional abundance of functional form is used
- along with $\delta < $ 1. The jet is assumed to be in the plane of
- sky implying an angle of inclination of $90^{\circ}$. The horizontal
+   2-$>$1 SiO transition for the reference run. 
+   The jet is assumed to be in the plane of sky implying an angle of
+   inclination of $90^{\circ}$. The horizontal
  {\it white dashed} line marks the cuts where the spectra is taken
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/imshkvh_21_60_empvspec.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/refrun_21_60_emspecpv.png}
  \caption{Same as figure~\ref{empvspec90} but with angle of
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/imshkvh_21_45_empvspec.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/refrun_21_45_emspecpv.png}
  \caption{Same as figure~\ref{empvspec90} but with angle of
@@
 is more concentrated in the inner jet regions and arise mainly from
-the shocks due to internal knots. These high level transitions
-also show an evidence of sub-structure close to the primary bow shock.
-Such a trend in emission with excitation energies coming from different SiO line transitions
+the shocks due to internal knots. Such a trend in emission with excitation energies coming from different SiO line transitions
 have been observed in many young outflows (for e.g., {\it{L1448}}
@@
 \citep{Chandler:2001p14376, Nisini:2002p14418,
-  Hirano:2006p14411}). 
+  Hirano:2006p14411}). Further, the evolved post-shock gas near the
+primary bow shock also show bright emission for these high J transitions. 
+This gas is linked to the Rayleigh-Taylor instability associated with cooling flows (see
+section~\ref{ssec:coolres}). The sub-structure seen close to the
+primary bow shock with high resolution does give a sense of clumpiness
+in the flow backing the suggestions to explain clumpy SiO emission by
+\citealt{Chandler:2001p14376}.
 %
@@
 Similar values are also obtained for molecular outflows from massive
-young stellar object IRAS 17233–3606\cite{Leurini:2013p13165}.
+young stellar object IRAS 17233-3606 \cite{Leurini:2013p13165}.
 These line ratios from the present
@@
 fig.~\ref{fig:lineratio}. Their values lie very close to unity as
-indicated from observations. In summary, the
+indicated from observations. Further, we have estimated the optical
+depth in regions emitting SiO and find them to be optically thick with
+an optical depth $\tau \sim 10$. Thus, assuming optically thin SiO emission
+from molecular outflows especially from shocked dense knots would
+only provide upper limits. In summary, the
 shape, ratio and peak intensity of the spectra obtained from our model
@@
 
-\subsection{Caveats and Steps Ahead}
-Better handle on Molecular fraction in jets.\\
-Zero order approximation of SiO fractional abundance profile.\\ 
-Since SiO in gas phase for 0 years with our abundance. While SiO takes
-10$^{4}$ years. History of SiO in gas phase and proper chemistry to get
-abundance.
-
-Wider CO and H2O WISH survey component.\\
+\subsection{Slow Component and Grain Chemistry}
+%
+We have presented a formidable model to explain the EHV component seen
+in SiO emission from several young outflows. The reference model
+consistently solves for the H$_{2}$ chemistry in presence of
+appropriate cooling. The steady state temperature, density and velocities obtained from dynamical
+simulation is post-processed to obtain SiO maps, spectra and PV
+diagrams. One essential ingredient required for the radiative transfer modeling
+is the SiO fractional abundance and its dependence on shock velocity. 
+Though 1D models that study the formation of SiO in gas phase from grain-grain and grain-mantle
+collisions exsist, their focus is mainly on weaker shocks
+\cite{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800}. 
+The pulsating jet propogation model presented here have shock speeds
+reaching upto 100 km\,s$^{-1}$. For simplicity we have used two basic
+prescription of SiO abundance profile as a function of shock
+velocity. Though the shape of the profile is uncertain the upper and
+lower limits used are backed by observational evidences. Ideally for a consistent
+depedence of SiO abundance on shock velocity, one would have to also
+solve for silicon and SiO chemistry in a manner similar to that of
+H$_{2}$. Further by evolving the dynamical simulations with complex
+grain chemistry for more than 10$^{4}$ years (time to destroy SiO in
+gas phase \cite{Codella:1999p12584}),  one can trace the history of 
+SiO in molecular outflows. However, such a numerically expensive model 
+with complex chemistry is beyond the scope of this paper.  
+%
+
+The model presented in this paper target the very early phase of molecular
+outflows i.e., dynamical time scale of 1000 years.
+As discussed in sections above, the unqiue combination of pulsating
+jet with chemistry and cooling followed by non-LTE radiative transfer
+calculations has shown success in fiting the line shapes, integrated intensity and line ratios of SiO
+transitions arising from EHV gas. However, the synthetic spectra show
+no signatures of slow SiO component that accompanies EHV emission seen
+in many outflows. The physical mechanism for the origin of slow SiO component is still a matter
+of debate. One of the suggestion is it arises due to slowing down of
+shocked gas as they age. The time scale estimated for the shocked gas
+to slow down is of the same order of magnitude as the SiO destruction
+time scale i.e., 10$^{4}$ years \cite{Codella:1999p12584}. In this
+case, we will not be able to see the effect as the dynamical runs do
+not evolve beyond 10$^{3}$ years. However, we do see initial 
+hints of slowing down of more evolved gas in terms of the velocity
+shift of about 5-7 km\,s$^{-1}$ in peak emission between that
+coming from the freshly formed internal knots close to the base of the
+flow as compared to emission coming from more evolved gas near the
+primary bow shock. To ascertain this fact in more details, one would
+need to track the primary bow shock for 10$^{4}$ years
+using a larger simulation box and possibly with adaptive gridding 
+which will be considered for future simulations. Such a long term
+evolution will also help to provide a numerical model for the formation of HH objects
+which are belived to be slowed down and more evolved form of these
+young molecular bullets as suggested by \cite{Norman:1979p14858,
+  Hartigan:1987p11178}.
+%
+
+Alternative to this evolutinary
 

### 2013-08-30 PAPER/ms_final_bv.tex
added alma figures and new grid figure

--- 2013-08-29 PAPER/ms_final_bv.tex
@@
 The output from the radiative transfer were scalled to 300pc and used as the sky models for observations of the J=2-1, J=5-4 and J=8-7 lines at freqencies of 86.85, 217.10 and 347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7.
-The observations were simulated using cycle 1 ALMA for 30 minutes total integration time, in the configurations c32-6, c32-4 and c32-3 for the three lines, giving beam sizes of 0.72'', 0.47'' and 0.58'' and sensitivities of 0.05, 0.07 and 0.09$\,$mJy/beam for the three lines (as calculated by the ALMA online sensitivity calculator) with velocity resolutions of $sim$1$\,$km/s.
+The observations were simulated using cycle 1 ALMA for 30 minutes total integration time, in the configurations c32-6, c32-4 and c32-3 for the three lines, giving beam sizes of 0.72'', 0.47'' and 0.58'' and sensitivities of 0.05, 0.07 and 0.09$\,$mJy/beam for the three lines (as calculated by the ALMA online sensitivity calculator) with velocity resolutions of $\sim$1$\,$km/s.
 
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/ALMAmaps2.png}
- \caption{{\bf Left:} The intensity map in the channel of the peak of the J5-4 emission.
-The heat map shows the 5-4 line intensity, the blue contours show the J=8-7 line intensity and the green contours show the J=2-1 line intensity (both in steps of 10mJy/beam) (this is arbitrary, could we do integrated intensity here instead?).
-{\bf Right:} The PV diagram taken along the axis of the jet, showing a 'zig-zag' pattern between the knots of the jet and broad emission at the bow shock.}
+ \includegraphics[width=2.\columnwidth]{\figpath/ALMAmaps3.png}
+ \caption{{\bf Left:} The integrated intensity map of the three SiO lines simulatedn.
+The heat map shows the 5-4 line intensity (in units of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line intensity and the green contours show the J=2-1 line intensity.
+{\bf Right:} The PV diagram taken along the axis of the jet (in units of Jy/beam), showing the higher J transitions highlighting the knots of the jet and broad emission at the bow shock.
+In both pannels the ticks on the colourbar represent the contour levels, the levels not shown on the integrated intensity colourbar are double the previous level.}
 \label{fig:almafig}

### 2013-08-30 makeALMAplot.py

@@ -34,9 +34,9 @@ def Velarr(ang,V0, A):
     return arr1
 
 def fig11():
-    hdulist1 = pf.open('/home/pytd/documents/SiOJets_New/imagedless1Shock_J2-1_45deg_molcool_dirty.fits')
-    hdulist2 = pf.open('/home/pytd/documents/SiOJets_New/imagedless1Shock_J8-7_45deg_molcool_dirty.fits')
-    hdulist3 = pf.open('/home/pytd/documents/SiOJets_New/imagedless1Shock_J5-4_45deg_molcool_dirty.fits')
+    hdulist1 = pf.open('/import/phy-pc1064_a/Documents/SiOJets_New/run4ALMA/imageShock_J2-1_45deg_molcool_dirty.fits.gz')
+    hdulist2 = pf.open('/import/phy-pc1064_a/Documents/SiOJets_New/run4ALMA/imageShock_J5-4_45deg_molcool_dirty.fits.gz')
+    hdulist3 = pf.open('/import/phy-pc1064_a/Documents/SiOJets_New/run4ALMA/imageShock_J8-7_45deg_molcool_dirty.fits.gz')
     
     
     A = hdulist1[0].header
@@ -48,17 +48,17 @@ def fig11():
     VELarr2 = Velarr(pi/4.,100.0, A)
     print VELarr2[0]
 
-    clevs1 = [0.01,0.03, 0.05]
-    clevs2 = [0.01, 0.1, 0.2, 0.4,0.8,1.2] 
+    clevs1 = [0.0005, 0.001, 0.005, 0.025, 0.125]
+    clevs2 = [0.01,0.05, 0.1, 0.2, 0.4,0.8,1.2] 
     # Get ALMA images
     f1 = plt.figure(figsize=[11,8])
     plt.subplots_adjust(wspace=0.05)
     ax1 = f1.add_subplot(121)
     
-    im1 = imshow(hdulist2[0].data[:,:,:].sum(0),origin='image',vmin = 0.001, vmax = 0.35,cmap=cm.gist_heat)
+    im1 = imshow(hdulist1[0].data[:,:,:].sum(0),origin='image',vmin = 0.001, vmax = 0.25,cmap=cm.gist_heat)
     plt.colorbar(im1,ticks=clevs2)
-    im2 = contour(hdulist3[0].data[:,:,:].sum(0),levels=clevs2,colors='b',linewidths=1.0)
[…]

### 2013-10-02 PAPER/ms_final_bv.tex
added text
Added new figures and modified text

@@
 \label{sec:chem}
-\subsection{Power law cooling}
-\subsection{Atomic Cooling}
-\subsection{Tabulated Cooling}
-
 \subsection{Molecular Cooling}
 \label{ssec:molcool}
-The evolution of molecular, atomic and ionized hydrogen is governed by
-equations listed in Table~\ref{tab:chemeq}. In this cooling mode,
-these equations are evolved at each times using temperature dependent
-rates mentioned in the table along with their source. The code tracks
-the formation and destruction of three quantities viz., X(HI), X($H_{2}$)
-and X(HII) with a constraint that sum of all three should be unity.
-Further, these abundances are used to update the cooling
-function $\Lambda(n,T,{\bf{X}})$ to consistently derive the
-temperature for next advection step.
+Typically, early collimated outflows have cooling times shorter than
+the dynamical times implying that the radiative cooling plays a vital
+role in dynamics. In pursuit to study such it is necessary to evolve
+the dynamics in conjunction with full molecular chemistry and
+associated radiative processes. However, evolving a full complex
+network of chemical equations along with dynamics is a very
+computationally intensive task. As a result, we have focused only in
+evolving the chemical equations pertaining to atomic and molecular
+hydrogen. This prescription of molecular cooling has been added to the PLUTO
+code to study the chemical evolution of molecular outflows during the
+very early phases of star formation. In particular, the total hydrogen
+number density n$_{\rm H}$ comprises of contribution from atomic and
+molecular hydrogen i.e., n$_{\rm H}$ = n$_{HI}$ + n$_{H2}$. Whereas
+the contribution to electrons comes from the ionized hydrogen, n$_{\rm HII}$ and
+from negligible but fixed fraction of metals ($Z \sim 10^{-4}$).
+The chemical evolution of molecular, atomic and ionized hydrogen is governed by
+equations listed in Table~\ref{tab:chemeq}. 
+%
+
+Numerically, the
+non-homogenous parts of the equations~\ref{encons1} and \ref{chemevol} 
+are are solved separately from the advection step
+using operator splitting. Further, the rate equations are evolved at each advection time
+step using sub-stepping and adaptive Runge-Kutta methods.
+In doing so, the code tracks the formation and destruction of
+fractions of three species viz., X(HI), X($H_{2}$)
+and X(HII) based on the temperature dependent reaction rates specified
+in the table along with their references and shown in the left panel
+of figure~\ref{ssec:molcool}. The figure clearly shows that below
+1000\,K the formation of molecular hydrogen dominates over other
+chemical processes, whereas for hotter gas there exists a competition
+of different chemical processes elucidating the complex chemical interplay.
+The fractions of various hydrogen species are then used to update the cooling
+function $\Lambda(\rho,T,{\bf{X}})$ to consistently derive the
+temperature for next advection step. For low temperatures, we also
+take into account contribution to cooling rates from molecules like
+CO whose abundances with respect to $n_{\rm H2}$ are fixed to
+10$^{-5}$. Whereas, for each of the other molecules like OH, H$_{2}$O and atomic OI,
+the abundance is fixed to $5.\times10^{-6}$. The contribution from
+these molecules is only important when temperature is $<$ 100\,K as seen
+in the right panel of figure~\ref{ssec:molcool}.
 
@@
 
+\subsection{Additional Cooling Prescriptions}
+%
+For comparison we have also ran simulations of axisymmetric MHD jets
+with optically thin cooling prescriptions already existing in the public
+release of the PLUTO-4 code. They are power-law cooling, 
+simplified non-equilibrium (or atomic) cooling and tabulated
+cooling. Further we compare these radiative runs with an adiabatic jet 
+to cover a wide spectrum of jet thermodynamics. 
+%
+
+In case of power law cooling, the radiative losses denoted by
+$\Lambda(\rho,T,\bf{X})$ are proportional to
+$\rho^{2}T^{\alpha}$, with $\alpha$ = 0.5 representing bremsstrahlung
+cooling. The loss term is independent of the fraction of various
+species $\bf{X}$, therefore the fluid density $\rho$ is assumed to be
+all hydrogen for further processing of emission maps. Similarly, 
+for tabulated cooling prescription, the radiative losses are estimated
+based on fixed fraction of various species. However, the contribution
+for each specie is a complex function of density and temperature. The
+variation of cooling function $\Lambda$ with temperature is shown in
+the right panel of figure~\ref{fig:tempvar}. 
+The formulations which depend on the fractions of each specie and gas
+temperature of these variations are mainly adopted from the appendix of \cite{Smith:2003p9985}. 
+The fractions of all hydrogen species are kept fixed to their initial values, while that
+of CO, OH, H$_{2}$O and OI are same as that used for molecular cooling
+described above. The total cooling curve shown as the black solid line
+in the figure~\ref{fig:tempvar} is used for the case of tabulated
+cooling. For the atomic cooling, we distinguish between neutral
+and ionized gas by defining $f_{\rm n} = n_{\rm HI}/n_{\rm H}$ and
+evolve it using,
+\begin{equation}
+\frac{\partial f_{\rm n}}{\partial t} + {\bf{v}}\cdot\nabla f_{\rm n} =
+n_{\rm e} [-(c_{\rm r} + c_{\rm i})f_{\rm n} + c_{\rm r}]
+\end{equation}
+where, $n_{\rm e}$ is the number of electrons that come from ionized
+hydrogen and a very small fixed fraction of metals, c$_{\rm r}$ and c$_{\rm i}$ are the recombination and
+ionization rate coefficients that depend on the temperature T. In
+addition to losses by collisional ionization and radiative
+recombination, additional contribution to radiative losses come from various atomic line emissions from
+C,N,O,Mg,Si,Fe etc.
+%
+
+While these additional cooling prescriptions may not be a complete description of
+the chemical and radiative processes in early outflows, they are ideal
+to compare the results obtained from the more consistent newly added molecular
+cooling. Such a comparison is presented in section~\ref{ssec:coolres}.
+
 \section{Radiative Transfer}
@@
 \hline
-Profile & $\delta$ = v$_{\rm jet}$/v$_{\rm s}$ & $\int T_{\rm MB}dV$
+Profile & $\delta$ = v$_{\rm s}$/v$_{\rm jet}$ & $\int T_{\rm MB}dV$
 [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$]\\ 
@@
 \label{ssec:coolres}
-Importance of cooling prescriptions\\
+We have done a comparison study of jet dynamics with various cooling
+prescriptions, which are described in
+Sect.~\ref{sec:chem}. Figure~\ref{fig:coolcmpdyn} shows the density of the MHD
+jet at time $\sim$ 1000 years for these different cooling
+prescriptions. For this study, we have chosen a density contrast at the base of
+$\eta$ = 10 between the jet and ambient medium.
+It is clear from the figure, that the cooling plays a
+significant role in determining the thickness of the jet. The jets
+with no or very little cooling seems to be more thicker as compared to
+jets having dominant cooling. For example, the adiabatic jet
+has a widest bow shock at its apex and has the most prominent cocoon
+around it. While the jet with atomic cooling has a rather conical
+jet head with significantly less cocoon surrounding it. The cocoon is
+almost absent from the narrow jet with tabulated cooling. Instead, the jet
+seems to form a very high density shell due to cooling of the
+processed ambient gas. Further, the jet with tabulated cooling is more
+narrower as compared to the jet with molecular cooling. This clearly
+shows the feedback of chemistry on the cooling function. The cooling
+terms for both these jets are the same to begin with, however,
+for the molecular jet the cooling terms evolve with jet dynamics as the fraction of
+various hydrogen species change while the terms remain fixed to values
+shown in the right panel of fig~\ref{fig:tempvar} for the jet with tabulated
+cooling. Additionally, the material at primary bow shock for jet
+with tabulated and molecular cooling condenses forming dense knots. 
+Such a condensation is caused due to thermal instability and is 
+a typical feature of axi-symmetric radiative jets 
+\citep[see, for e.g,][]{Blondin:1990p2130,Cerqueira:1999p15052}.
+%
+
+The dynamical states for each of this cooling prescription are then 
+post-processed to obtain integrated J = 2-$>$1 SiO emission
+maps shown in figure~\ref{fig:coolcmpsio}. The differences in dynamical
+features are also reflected in the corresponding SiO emission
+maps. These maps are obtained assuming an angle of inclination of
+90$^\circ$ using the top hat abundance
+profile with $\delta = 1$ and they are further convolved with a beam
+having a FWHM of 2.5\arcsec. The
+emission features in jet with atomic and power-law cooling prescription do not have
+such a well defined lobe structure. For example, the emission from the jet with atomic
+cooling is mainly coming from regions close to R,Z = $\pm$
+10,80. In fact the emission from this region seems to be stronger than
+that coming from the conical jet head. In case of the jet with
+power-law cooling the emission seems to be mostly coming from the
+internal knots. The thin density layer formed at the interface of jet
+and the ambient medium do not show indication of any emission. 
+The emission coming from jets with
+tabulated and molecular cooling show a distinctive outflow lobe which
+is typically observed in case of young molecular outflows.
+SiO emission coming from internal knots in these jets also show a
+distinctive turbulent pattern consistent with observations.
+
 Bulk of emission comes from cooling instabilities.
@@
    $\eta$ = 10 and $\beta$ = 10.}
-\label{grid}
+\label{fig:coolcmpdyn}
 \end{figure*}
@@
 each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
-\label{cooling2-1} 
+\label{fig:coolcmpsio} 
 \end{figure*}
@@
 In order to see the interior structure of the molecular outflow, high resolution interferometric observations are needed.
-To demonstrate how jets similar to those we have modeled would look through such observations we have performed synthetic Atacama Large Millimetre Array (ALMA) observations using the Common Astronomy Software Applications package (CASA).
-The output from the radiative transfer were scalled to 300pc and used as the sky models for observations of the J=2-1, J=5-4 and J=8-7 lines at freqencies of 86.85, 217.10 and 347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7.
+To demonstrate how jets similar to those we have modeled would look through such observations we have performed synthetic Atacama Large Millimeter Array (ALMA) observations using the Common Astronomy Software Applications package (CASA).
+The output from the radiative transfer were scaled to 300pc and used as the sky models for observations of the J=2-1, J=5-4 and J=8-7 lines at frequencies of 86.85, 217.10 and 347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7.
 The observations were simulated using cycle 1 ALMA for 30 minutes total integration time, in the configurations c32-6, c32-4 and c32-3 for the three lines, giving beam sizes of 0.72'', 0.47'' and 0.58'' and sensitivities of 0.05, 0.07 and 0.09$\,$mJy/beam for the three lines (as calculated by the ALMA online sensitivity calculator) with velocity resolutions of $\sim$1$\,$km/s.
@@
  \includegraphics[width=2.\columnwidth]{\figpath/ALMAmaps3.png}
- \caption{{\bf Left:} The integrated intensity map of the three SiO lines simulatedn.
+ \caption{{\bf Left:} The integrated intensity map of the three SiO lines simulated.
 The heat map shows the 5-4 line intensity (in units of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line intensity and the green contours show the J=2-1 line intensity.
 {\bf Right:} The PV diagram taken along the axis of the jet (in units of Jy/beam), showing the higher J transitions highlighting the knots of the jet and broad emission at the bow shock.
-In both pannels the ticks on the colourbar represent the contour levels, the levels not shown on the integrated intensity colourbar are double the previous level.}
+In both panels the ticks on the color bar represent the contour levels, the levels not shown on the integrated intensity color bar are double the previous level.}
 \label{fig:almafig}
@@
 Though 1D models that study the formation of SiO in gas phase from grain-grain and grain-mantle
-collisions exsist, their focus is mainly on weaker shocks
+collisions exists, their focus is mainly on weaker shocks
 \cite{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800}. 
-The pulsating jet propogation model presented here have shock speeds
-reaching upto 100 km\,s$^{-1}$. For simplicity we have used two basic
+The pulsating jet propagation model presented here have shock speeds
+reaching up to 100 km\,s$^{-1}$. For simplicity we have used two basic
 prescription of SiO abundance profile as a function of shock
@@
 lower limits used are backed by observational evidences. Ideally for a consistent
-depedence of SiO abundance on shock velocity, one would have to also
+dependence of SiO abundance on shock velocity, one would have to also
 solve for silicon and SiO chemistry in a manner similar to that of
@@
 outflows i.e., dynamical time scale of 1000 years.
-As discussed in sections above, the unqiue combination of pulsating
+As discussed in sections above, the unique combination of pulsating
 jet with chemistry and cooling followed by non-LTE radiative transfer
-calculations has shown success in fiting the line shapes, integrated intensity and line ratios of SiO
+calculations has shown success in fitting the line shapes, integrated intensity and line ratios of SiO
 transitions arising from EHV gas. However, the synthetic spectra show
@@
 hints of slowing down of more evolved gas in terms of the velocity
-shift of about 5-7 km\,s$^{-1}$ in peak emission between that
+shift of about 7-10 km\,s$^{-1}$ in peak emission between that
 coming from the freshly formed internal knots close to the base of the
@@
 evolution will also help to provide a numerical model for the formation of HH objects
-which are belived to be slowed down and more evolved form of these
+which are believed to be slowed down and more evolved form of these
 young molecular bullets as suggested by \cite{Norman:1979p14858,
@@
 
-Alternative to this evolutinary
+An alternative hypothesis for the origin of the low velocity SiO
+component is that it could be formed by interaction of
 

### 2013-10-02 TALK/SiOModelTalk.tex
Added Talk folder

\documentclass[8pt,xcolor=dvipsnames]{beamer}
\usepackage[latin1]{inputenc}

\usetheme[height=7mm]{Berlin}
\usecolortheme[named=Brown]{structure}

\usepackage{time}       % date and time
\usepackage{graphicx}
\usepackage[T1]{fontenc}    % european characters
%\usepackage{courier}
\usepackage{animate}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amssymb,amsmath}  % use mathematical symbols
\usepackage{bookman}                  % use palatino as the default font
\setbeamercovered{transparent}
%\newcommand{figpath}{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS}

\title[SiO Outflows]{Modeling SiO Emission from early outflows}
\subtitle{Extremely High Velocity Component [ EHV ]}
\author[Bhargav Vaidya]{\textcolor{blue}{Bhargav Vaidya}\inst{1} \and  Thomas
  Douglas\inst{1} \and Paola Caselli\inst{1}}\institute[Uni. Leeds]{\inst{1}School of Physics and
  Astronomy, University of Leeds, Leeds.}
\date[2013]{AG Annual Meeting 2013}
\titlegraphic{\vskip30pt \hskip215pt\includegraphics[width=0.3\textwidth]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Leeds-logo.jpg}}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Outline}
\tableofcontents
\end{frame}

\section{Motivation}
\begin{frame}[t]
\frametitle{Motivation}
\small{
\begin{block}{EHV Emission}
\begin{itemize}
\item Observed for the first time in L1448 outflow (\alert{Bachiller
    1991})
\item Associated with primary jet (\alert{Santiago-Garcia, 2009}, {\it{IRAS 04166+2706}}). Observed in SiO, CO but no signatures in HCN or CS (\alert{Tafalla, 2010}).
\item How are they formed ? J-shocks or C-shocks ? Stationary 1D
  Models -- FAILS! (557 GHz \alert{Tafalla, 2013}) \textbf{NEED FOR A 2D MODEL!}
\end{itemize}
\end{block}
}
\vskip10pt
\begin{columns}[C]
\begin{column}{0.5\textwidth}
\includegraphics[height=4cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Tafalla2011.pdf}
\end{column}
\begin{column}{0.5\textwidth}
\includegraphics[height=4cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Tafalla2013.png}
\end{column}
\end{columns}
\end{frame}

\section{Numerical Approach}
\begin{frame}[t]
\frametitle{Methodology}
\begin{center}
\includegraphics[height=7cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/FlowChartJetProp.png}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Initial Conditions}
\begin{columns}[T]
    \begin{column}{.4\textwidth}
     \begin{block}{Molecular Ambient Medium}
       Cold (T$_{\rm amb}$ $\sim$ 50\,K) \\ with decreasing density\\
       (\alert{Caselli, P., 2011})

    \end{block}
    \end{column}
    \begin{column}{.6\textwidth}  
      \includegraphics[width=3cm,height=6cm, angle=-90]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/figure1_caselli.png}
    \end{column}
  \end{columns}
\vskip10pt 
\begin{columns}[T]
    \begin{column}{.4\textwidth}
     \begin{block}{Overdense MHD Jet}
       Propogating jet with \\ velocity perturbation \\
       $V_{\rm jet} = V_{\rm jet,0}[1 + sin(\frac{2\pi t}{70\, \rm
         yrs})]$\\
       (\alert{Stone\&Hardee, 2000})
    \end{block}
    \end{column}
    \begin{column}{.6\textwidth} 
      \hskip10pt
      \begin{tabular}{l l}
      \textbf{Quantity} & \textbf{Values}\\
      \hline\hline
      \smallskip
      $\eta$ & 2,3,10\\
      \smallskip
      $V_{\rm jet,0}$ & 100\, km\, s$^{-1}$\\
\smallskip
      Plasma $\beta_0$ & 10 $\sim$ 20$\mu$\,G \\
\smallskip
      $n_{\rm jet,0}$ & 10$^{5}$ cm$^{-3}$ \\
\smallskip
      $r_{\rm jet,0}$ & 160\,AU\\
\smallskip
      Composition & 1\% Ionic, 10\% Molecular,\\
      &89\% Atomic\\
      \hline
      \end{tabular}
    \end{column}
  \end{columns}

\end{frame}

\section{Cooling and Chemistry}
\begin{frame}
\frametitle{Cooling Prescriptions and H$_{2}$ Chemistry in PLUTO
 ( \alert{Mignone, 2007})}
\begin{columns}[C]
    \begin{column}{.5\textwidth}
     \begin{itemize}
     \item Adiabatic (No cooling)
     \item Power Law Cooling
     \item Atomic Cooling 
  \end{itemize}
    \end{column}
    \begin{column}{.5\textwidth} 
     \begin{itemize}
     \item Tabulated Cooling with {\em Fixed Initial Fractions}
     \item \textbf{Proper Molecular Cooling} (\alert{Vaidya et. al,
         \textit{in prep}, O'Sullivan's PhD Thesis})
     \end{itemize}

    \end{column}
  \end{columns}

\vskip10pt
\begin{columns}[C]
    \begin{column}{.5\textwidth}
      \includegraphics[width=5cm,height=5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/H2ReactionRates_paper.png}
    \end{column}
    \begin{column}{.5\textwidth}  
      \includegraphics[width=5cm,height=5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/H2CoolingFuncs_full.png}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]
\frametitle{Radiative Jet dynamics}
\begin{columns}[T]
    \begin{column}{.3\textwidth}
      \begin{block}{Impact of Cooling}
       \begin{itemize}
       \item $\eta$ = 10.0 \\
       \item Jet becomes thinner with more effective cooling \\
       \item Thermal Instabilities 
       \end{itemize}
       \end{block}
    \end{column}
    \begin{column}{.7\textwidth} 
     \includegraphics[width=8cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/jetplt1_1010.png}
    \end{column}
  \end{columns}

\begin{columns}[T]
    \begin{column}{.3\textwidth}
       \begin{block}{Impact of Shocks}
      \begin{itemize}
      \item $\eta$ = 3.0 \\
      \item {\em Iternal Knots} - Formation and Destruction \\
      \item {\em Primary Bow shock} - Ionized Hydrogen with  T $>$ 20,000\,K.\\ 
      \end{itemize}
    \end{block}
    \end{column}
    \begin{column}{.7\textwidth} 
      \includegraphics[width=6cm,height=4cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/molcjet_310_molform.png}

    \end{column}
  \end{columns}
\end{frame}

\section[Rad. Transfer]{Radiative Transfer : Post-Processing}
\begin{frame}
\frametitle{Grid and Abundance}
\begin{columns}[T]
    \begin{column}{.4\textwidth}
      Line Modelling\\
      Engine [\textbf{LIME}] (\alert{Brinch \& Hogerheijde, 2010}) 
      \includegraphics[width=3cm,height=6cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/grid.png} 
    \end{column}
    \begin{column}{.6\textwidth}
      \small{
        \begin{itemize}
          \item n(SiO)/n(H2) as a function of shock velocity
           \item 10$^{-12}$ in Dark clouds (\alert{Ziurys, 1989}),\\
            10$^{-6}$ in fast outflows (\alert{Dutrey, 1997}).
          \item $\delta = V_{\rm shock}/ V_{\rm jet} = f(\eta) <= 1$
         \end{itemize}
       }

      \includegraphics[width=5cm,height=5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/diffabunprof1.png}
      \end{column}
     \end{columns}   
\end{frame}

\begin{frame}[t]
\frametitle{Cooling and SiO Emission}
\tiny{
\begin{table}
\caption{Parameter runs with different cooling prescription and $\eta$ values}
\begin{tabular}{c | c | c | c | c | c | c }
\hline
Run & Cooling Mode & $\eta$ & \multicolumn{2}{|c|}{Top Hat Profile
  $\delta = 1$} & \multicolumn{2}{|c|}{Gaussian Profile $\delta =
  1$}\\
\hline\hline
&&& $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] & $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] \\
\hline
adi1010 & Nil (Adiabatic) & 10 & 2.91 & $>$40 & 0.25 & 40.0 \\
pow1010 & Power law & 10 & 0.64 & 8.0 & 0.02 & 10.0\\
atm1010 & Atomic & 10 & 2.04 & 36.0 & 0.58 & 38.0 \\
atm210 & Atomic & 2 & 3.21 & 18.0 & 0.64 & 20.0 \\
tab1010 & Tabulated & 10 & 0.75 & 11.0 & 0.09 & 10.0 \\
tab210 & Tabulated & 2 & 2.89 & 8.0 & 1.0 & 9.0 \\
mol1010 & Molecular & 10 & 1.10 & 10.0 & 0.1 & 11.0 \\
\color{red}{\textbf{mol310}} & Molecular & 3 & 3.3 & 14.0 & 0.66 & 12.0\\
\hline
\end{tabular}
\end{table}
}
\vskip10pt
\begin{columns}[T]

\begin{column}{0.3\textwidth}
  \begin{block}{Impact of Cooling}
    \begin{itemize}
      \item Jet flow with $\eta$ = 10 and $\beta$ = 10.0\\
      \item Integrated intensities with Gaussian Profile
        and $\delta < 1$.\\
      \item Convolved with a beam of FWHM = 2.5''
    \end{itemize}
  \end{block}
\end{column}

\begin{column}{0.7\textwidth}
 \includegraphics[width=8cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/diffcool_EMgaussprof.png}
\end{column}
\end{columns}
\end{frame}

\section[Results]{Results : Line Emission, Spectra, PV Diagrams}
\begin{frame}[t]
\frametitle{SiO Multi-Line Movies}
\small{
\begin{itemize}
\item Molecular Jet with $\eta$ = 3.0, $\beta$ = 10.0 \\
\item Line Intensities with Gaussian Profile with $\delta < 1$. \\
\item Jet is in plane of sky and convolved with a beam of 2.5''
\end{itemize}
}
\begin{tabular}{ccc}
\textbf{J = 2-$>$1} & \textbf{J = 5-$>$ 4} & \textbf{J = 8-$>$ 7}\\
\animategraphics[width=3.5cm,height=5.5cm,autoplay]{5}{Img21/Img21_}{0000}{0010}
& 
\animategraphics[width=3.5cm,height=5.5cm,autoplay]{5}{Img54/Img54_}{0000}{0010}
&
\animategraphics[width=3.5cm,height=5.5cm,autoplay]{5}{Img87/Img87_}{0000}{0010}

\end{tabular}
\end{frame}

\begin{frame}
\frametitle{HH 211 - SiO Multi-Line Emission}
\begin{tabular}{ccc}
\textbf{J = 1-$>$0} (\alert{Chandler, 2001}) & \textbf{J = 5-$>$ 4}
(\alert{Hirano, 2006}) &
\textbf{J = 8-$>$ 7} (\alert{Palau, 2006})\\

\includegraphics[width=3cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Chandler2001.png}
&
\includegraphics[width=3.5cm,height=2.5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Hirano2005.png}
&
\includegraphics[width=2.5cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Palau2006.png}
\end{tabular}
\vskip10pt
\begin{columns}[T]
\begin{column}{0.3\textwidth}
 \begin{itemize}
    \item {\color{Brown}Low excitation} : Interaction of jet and medium.
    \item {\color{Brown}High excitation}: Internal knots.
 \end{itemize}
\end{column}

\begin{column}{0.7\textwidth}
\includegraphics[width=7cm,height=3.5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/imshkvhcontomaps.png}
\end{column}
\end{columns} 
\end{frame}

\begin{frame}[c]
\frametitle{HH212 and L1448-mm : Spectra and Kinematics}
% \small{
% \begin{block}{Generic Features}
% \begin{itemize}
% \item L1448-mm : Weak line emission (T $\sim$ 0.3\,K) and peaks at 50
%   km\,s$^{-1}$ and a spectral width of about 20 km\,s$^{-1}$.\\
% \item SiO Multi-line analysis and LVG Modelling : Typical n(H$_{2}$)
%   $\sim$ 10$^{6}$ cm$^{-3}$ and Temperature of $>$ 500\,K.\\
% \item Line ratios from multi-line survey close to unity for both low
%   (HH212; ) and high mass (IRAS 17233-3606; ) young outflows. 
% \end{itemize}
% \end{block}
% }

\begin{columns}
 \begin{column}{0.33\textwidth}
Spectra (\alert{Codella, 1999})\\
 \includegraphics[width=4.0cm,height=4.0cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Codella1999.pdf}

 \end{column}

 \begin{column}{0.33\textwidth}
Line Ratios (\alert{Cabrit, 2007})\\
 \includegraphics[width=3.0cm,height=4.0cm,angle=-90]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Cabrit2007.png}

 \end{column}

\begin{column}{0.33\textwidth}
Kinematics (\alert{Nisini, 2007})\\
 \includegraphics[width=3.5cm,height=4.0cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Nisini2007_2.png}\\

 \end{column}
 \end{columns}
\vskip10pt

 \end{frame}

\begin{frame}
\frametitle{Model Spectra and Line Ratios}
\begin{columns}[T]
\begin{column}{0.4\textwidth}
\begin{itemize}
\item Single dish spectra, Gaussian
  abundance profile, $\delta <$ 1, Inclination of 60$^{\circ}$. \\
\item High velocity emission consistent with generic observational features. \\
\item Missing Slow component ?
\item Optically Thick or Thin ?\\
\end{itemize}
\end{column}
\begin{column}{0.6\textwidth}
\includegraphics[width=6cm,height=6cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/LineRatio_THDeq1.png}
\end{column}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{PV Diagrams}
\begin{columns}[T]
\begin{column}{0.5\textwidth}
\includegraphics[width=5cm,height=7cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/refrun_21_60_emspecpv.png}
\end{column}
\begin{column}{0.5\textwidth}
IRAS 04166+2706 (\alert{Santiago-Garcia, 2009}). 
\includegraphics[width=5cm,height=5cm,angle=-180]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Santiago2009.pdf}
\end{column}
\end{columns}

\end{frame}

\begin{frame}[c]
\frametitle{Effects of Abundance}
\begin{columns}[c]
\begin{column}{0.9\textwidth}
\includegraphics[width=9cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/EM_gaussandth.png}
\end{column}
\end{columns}
\vskip10pt
\begin{columns}[c]
\begin{column}{0.9\textwidth}
\includegraphics[width=9cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/PV_gaussandth.png}
\end{column}
\end{columns}

\end{frame}

\section{Summary}
\begin{frame}
\frametitle{Summary}
\begin{itemize}
\item Axi-symmetric MHD Jet propagation simulations with
  \alert{Molecular cooling and Hydrogen chemistry} for the context of studying molecular outflows in Class 0 phase.

\item Extremely High Velocity(EHV) emission of SiO seen in some young
  outflows are produced by \alert{interaction of internal knots with ambient
  medium via J-shocks}

\item Our model can very \alert{reproduce observational features} like :
  \begin{itemize}
    \item Integrated intensity of EHV emission.
    \item Spectral shape and line ratios seen in SiO emission from some of these Class 0 Outflows.
    \item Knotty features of PV diagrams. 
  \end{itemize}

\item \alert{Outlook}
\begin{itemize}
  \item Longer, 3D, AMR simulations which consistently produce
    internal knots (\alert{Gomez et. al 2013}).
  \item Consistent modeling for dust chemistry to have better
    constraints on SiO abundance.
  \item Slower wider component seen in chemical molecules like CO, H$_{2}$O (Herschel WISH
    Survey, \alert{Tafalla et. al., 2013}).
\end{itemize}

\item \alert{ALMA Maps !}
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{ALMA Maps}
\begin{columns}[T]
\begin{column}{0.3\textwidth}
\begin{block}{CASA Simulation}
\begin{itemize}
\item Source Distance : 300 pc 
\item Cycle 1 --  Bands(Beam Size) :  3(0.72''), 6(0.47'') and 7(0.58'') 
\item Integration time : 30 min
\item Velocity Resolution : 1 km s$^{-1}$
\end{itemize}
\end{block}
\end{column}
\begin{column}{0.7\textwidth}
\includegraphics[width=8.5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/ALMAmaps3.png}
\end{column}
\end{columns}
\end{frame}

\end{document}

### 2013-10-02 PAPER/ms_final_bv.tex
Added more text on cooling modes comparison

@@
 SiO emission coming from internal knots in these jets also show a
-distinctive turbulent pattern consistent with observations.
-
-Bulk of emission comes from cooling instabilities.
-figure nos. 2 -- Simulated images, emission maps for eta = 10.
+distinctive turbulent pattern consistent with
+observations. Additionally, strong emission also comes from the
+condensation formed at the primary bow shock due to thermal
+instability. 
+%
+
+In summary, different cooling prescriptions does influence the
+dynamics of MHD jet propagation in particular the thickness and
+structure of the primary bow shock. These dynamical differences are
+also reflected in SiO emission maps and spectra. Emission maps
+obtained from molecular cooling show a distinctive outflow lobe
+structure which is consistent with observations. The properties of 
+molecular cooling flows are described in details in the next section.
+
 \begin{figure*}

### 2013-10-03 PAPER/ms_final_bv.tex
minor changes and corrections to text

@@
 formation in dense molecular cores. They are ubiquitous in both
-massive and low star forming regions. These supersonic flows
-perpendicular to the underlying accretion disk plays a vital role in
-removing excess angular momentum and thereby aiding in the accretion. 
+massive and low mass star forming regions. These supersonic flows,
+perpendicular to the underlying accretion disk, play a vital role in
+removing excess angular momentum and thereby aiding in the accretion onto the protostar. 
 For low mass stars, they are believed to be launched by magneto-centrifugally forces and
@@
 envelope scales ($10^{2} - 10^{5}$\,AU) and parent cloud scales
-($10^{5} - 10^{6}$\,AU) \refer. Among them, the envelope scales are
-the ones where rich chemical evolution occurs as the jet interacts
+($10^{5} - 10^{6}$\,AU) \refer. Amongst these, it is at the envelope scale where rich chemical evolution occurs as the jet interacts
 with the molecular medium. In this region, the jet propagates into a
-relatively static medium inducing shocks that are interesting from the
+relatively static medium inducing shocks that are interesting from both a
 physical and chemical point of view. In addition to shocks, molecular
@@
 Bipolar molecular outflows from low and high mass stars
-have been studied in details over the past 
+have been studied in detail over the past 
 decade \citep[see reviews by][]{Bachiller:1996p4692,Arce:2007p798,
-Tafalla:2011p14051}. Advancement in millimeter interferometers have
-allowed to observe these outflows with high spatial resolution of
+Tafalla:2011p14051}. Advances in millimetre interferometery 
+allow observations of these outflows with spatial resolution of
 few arc seconds. A large number of studies related to young
-outflows are done using standard outflow and shock tracer
-like CO and SiO respectively. In addition to these molecular tracers,
+outflows are done using standard outflow and shock tracers,
+e.g. CO and SiO respectively. In addition to these molecular tracers,
 shocks from these outflows are detected in molecular hydrogen using
@@
 In the present work, our goal is to take a step further in the modeling of
-jet driven molecular outflows. The present model aims to consistently derive observed emission
-properties of molecular outflows, specifically various SiO line
+jet driven molecular outflows. The present model aims to consistently derive observed emission properties of molecular outflows, specifically various SiO line
 transitions, by combining axisymmetric MHD simulations of
@@
 The final state of the jet obtained for each cooling model is then
-post-processed using a non-LTE radiative line transfer code
+post-processed using a non-LTE line radiative transfer code
 to obtain emission maps, spectra and PV digrams. These emission maps
 are further processed using the Common Astronomy Software Applications
-package (CASA) to obtain synthetic ALMA images of molecular outflows.
-%
-
-In the next three section we describe our numerical setup, cooling
-prescriptions and radiative transfer line code respectively. In
+package (CASA) to obtain synthetic ALMA images of the resultant molecular outflows.
+%
+
+In the next three sections we describe our numerical setup, cooling
+prescriptions and radiative transfer code respectively. In
 Sect. 5, we will present results from the parameter survey and the
@@
 We model the propagation of jet as it interacts with the molecular
-cloud core much further from the central object, i.e., $>$ 1000\,AU. 
-Further away from the central source, the downward pull of gravity plays a
+cloud core at distances great enough so the the central object no longer has significant impact on the evolution of the outflow, i.e. $\gtrsim$ 1000\,AU. 
+At these distances from the central source, the downward pull of gravity plays a
 negligible role and the dynamics of jet is primarily governed by magnetic fields.
-The total magnetic field in jet is dominated by the toroidal
+The total magnetic field in the jet is dominated by the toroidal
 component. This is because the poloidal field decays as $z^{-2}$ as
 compared to $z^{-1}$ for toroidal field to maintain the force balance ($z$ is the vertical distance from source). 
-The hoop stress due to pinch force from toroidal magnetic fields maintains the
+The hoop stress due to pinch force from the toroidal magnetic fields maintains
 a highly collimated beam like structure for the jet.
@@
 represents the molecular cloud core. The numerical domain is axi-symmetric
-and in (r,z,$\phi$) cylindrical co-ordinates. Its extent in radial
-direction is 20 $R_{\rm j}$ and 100
-$R_{\rm j}$ along the vertical axis, $R_{\rm j}$ being the radius of
-the jet. The domain of interest is about 3000\,AU away from the
-central source extends up to 0.1\,pc. Numerically, it is resolved by an uniform grid with 200 cells in
-radial and 1000 cells in vertical direction. For simplicity, we choose this medium
+and in (r,z,$\phi$) cylindrical co-ordinates. Its extent 20 $R_{\rm j}$ in the radial
+direction and 100
+$R_{\rm j}$ along the vertical axis ($R_{\rm j}$ being the radius of
+the jet). The domain of interest is about 3000\,AU away from the
+central source extends up to 0.1\,pc. Numerically, it is resolved by an uniform grid with a domain of 200$\times$1000 cells in the radial and vertical directions. For simplicity, we choose this medium
 to be unmagnetized and non-turbulent. The density in the ambient
@@
 the ambient medium. The number density in the jet is kept fixed such
-that the density in ambient medium lies within a range of $10^{4}-10^{5}
+that the density in the ambient medium lies within a range of $10^{4}-10^{5}
 \rm cm^{-3}$. The pressure in the ambient molecular medium is
@@
 the dynamical times implying that the radiative cooling plays a vital
-role in dynamics. In pursuit to study such it is necessary to evolve
+role in dynamics. In order to study such outflows it is necessary to evolve
 the dynamics in conjunction with full molecular chemistry and
@@
 take into account contribution to cooling rates from molecules like
-CO whose abundances with respect to $n_{\rm H2}$ are fixed to
-10$^{-5}$. Whereas, for each of the other molecules like OH, H$_{2}$O and atomic OI,
-the abundance is fixed to $5.\times10^{-6}$. The contribution from
+CO, whose abundance with respect to $n_{\rm H2}$ is fixed to
+10$^{-5}$. For each of the other molecules contributing to the cooling function (like OH, H$_{2}$O and atomic OI)
+the abundance is fixed to $5\times10^{-6}$. The contribution from
 these molecules is only important when temperature is $<$ 100\,K as seen
@@
 % 
-For comparison we have also ran simulations of axisymmetric MHD jets
+For comparison, we also ran simulations of axisymmetric MHD jets
 with optically thin cooling prescriptions already existing in the public
@@
 In case of power law cooling, the radiative losses denoted by
-$\Lambda(\rho,T,\bf{X})$ are proportional to
+$\Lambda(\rho,T,{\bf X})$ are proportional to
 $\rho^{2}T^{\alpha}$, with $\alpha$ = 0.5 representing bremsstrahlung
 cooling. The loss term is independent of the fraction of various
-species $\bf{X}$, therefore the fluid density $\rho$ is assumed to be
+species ${\bf X}$, therefore the fluid density $\rho$ is assumed to be
 all hydrogen for further processing of emission maps. Similarly, 
 for tabulated cooling prescription, the radiative losses are estimated
-based on fixed fraction of various species. However, the contribution
-for each specie is a complex function of density and temperature. The
+based on a fixed fraction of various species. However, the contribution
+for each species is a complex function of density and temperature. The
 variation of cooling function $\Lambda$ with temperature is shown in
 the right panel of figure~\ref{fig:tempvar}. 
-The formulations which depend on the fractions of each specie and gas
+The formulations which depend on the fractions of each species and gas
 temperature of these variations are mainly adopted from the appendix of \cite{Smith:2003p9985}. 
@@
 where, $n_{\rm e}$ is the number of electrons that come from ionized
-hydrogen and a very small fixed fraction of metals, c$_{\rm r}$ and c$_{\rm i}$ are the recombination and
-ionization rate coefficients that depend on the temperature T. In
+hydrogen and a very small fixed fraction of metals, c$_{\rm r}$ and c$_{\rm i}$ are the recombination and ionization rate coefficients that depend on the temperature T. In
 addition to losses by collisional ionization and radiative
-recombination, additional contribution to radiative losses come from various atomic line emissions from
-C,N,O,Mg,Si,Fe etc.
+recombination, additional contribution to radiative losses come from various atomic line emissions from C,N,O,Mg,Si,Fe etc.
 %
@@
 \label{sec:radtrans}
-Radiative transfer modeling used for post processing.
+%Radiative transfer modeling used for post processing.
 
@@
 The method of selecting these points is given in section \ref{subsec:gridding}.
-At each of these points, the density of the main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+ 0.5 n(H)), gas and dust temperatures, velocity, molecular abundances and unresolved turbulent velocity are specified.
+At each of these points, the density of the main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+ 0.5 n(H), assuming that atomic Hydrogen has half the SiO collisional cross section of molecular hydrogen and that ionised Hydrogen does not collide with SiO), gas and dust temperatures, velocity, molecular abundances and unresolved turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
@@
 These candidates then have their equivalent H$_2$ number density, and the number density of SiO, compared against those of a reference point in order to decide if the candidate point is to be used in the grid or not.
-Candidate grid points are selected at random in a cylindrical coordinates that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
+Candidate grid points are selected at random in a cylindrical coordinate system that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
 For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random coordinates, the H$_2$ density and SiO density at the candidate point (n and m, respectively) are compared against the densities of a reference point in the un-perturbed ambient medium multiplied by $\frac{4\eta}{5}$ (n$_0$ and m$_0$).
+After selection of random coordinates, the H$_2$ density and SiO density at the candidate point (n and m, respectively) are compared against the densities of a reference point in the un-perturbed ambient medium multiplied by a factor of $\frac{4\eta}{5}$ (n$_0$ and m$_0$).
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use.
@@
 as TMC1 \citep{Ziurys:1989p14699,MartinPintado:1992p14309}. Whereas, in
-outflows like L1448, SiO abundance can increase up to 10$^{-6}$ specially in
+outflows like L1448, SiO abundance can increase up to 10$^{-6}$ especially in
 molecular bullets moving with a projected velocity of 60
@@
 results. However, not all quantities needed for our study are well
-constraint by the observations, thus allowing us vary them as
+constrained by observations, thus allowing us vary them as
 free parameters. Such a parameter survey provides better handle on the range of allowed
@@
 the ambient medium denoted by $\eta$. The various cooling prescriptions used for the present study are
-described in details in section~\ref{sec:chem}. They differ in the
+described in detail in section~\ref{sec:chem}. They differ in the
 physical process that is responsible for cooling and chemistry. The
@@
 
-A value of $\eta > 1$, mean that
+A value of $\eta > 1$, means that
 that jet is over dense with respect to the medium. In all our runs with
@@
 over-dense by 10 times that of the ambient medium. Additionally, for
-the atomic, tabulated and molecular cooling runs we have used a
+the atomic, tabulated and molecular cooling runs we have also used a
 value of $\eta$ of the order of unity indicating similar densities in
@@
 parameter introduced here is $\delta$ which is essentially the ratio
-of shock velocity v$_{\rm s}$ and initial jet velocity v$_{\rm
+of shock velocity v$_{\rm s}$ and physical jet velocity v$_{\rm
   j}$ such that its value depends on density contrast $\eta$
@@
 \eta(z)^{-0.5})$, where $\eta(z)$ is the density contrast as a
-function of height from the base of the jet.
+function of height from the base of the jet, and is inversely proportional to the ambient density at the same height.
 
@@
 It is clear from the figure, that the cooling plays a
-significant role in determining the thickness of the jet. The jets
-with no or very little cooling seems to be more thicker as compared to
+significant role in determining the structure of the jet. The jets
+with no or very little cooling are much wider compared to
 jets having dominant cooling. For example, the adiabatic jet
@@
 seems to form a very high density shell due to cooling of the
-processed ambient gas. Further, the jet with tabulated cooling is more
-narrower as compared to the jet with molecular cooling. This clearly
+processed ambient gas. Further, the jet with tabulated cooling is narrower than the jet with molecular cooling. This clearly
 shows the feedback of chemistry on the cooling function. The cooling
@@
 for the molecular jet the cooling terms evolve with jet dynamics as the fraction of
-various hydrogen species change while the terms remain fixed to values
-shown in the right panel of fig~\ref{fig:tempvar} for the jet with tabulated
+various hydrogen species change over time. Whilest the terms remain fixed to initial values, shown in the right panel of fig~\ref{fig:tempvar}, for the jet with tabulated
 cooling. Additionally, the material at primary bow shock for jet
@@
 90$^\circ$ using the top hat abundance
-profile with $\delta = 1$ and they are further convolved with a beam
-having a FWHM of 2.5\arcsec. The
+profile with $\delta = 1$. They are then placed at a distance of 100$\,$pc and convolved with a beam with FWHM of 2.5\arcsec in order to create the maps shown. The 
 emission features in jet with atomic and power-law cooling prescription do not have
@@
 
-In summary, different cooling prescriptions does influence the
+In summary, different cooling prescriptions strongly influence the
 dynamics of MHD jet propagation in particular the thickness and
@@
 contributions to cooling from fixed fractions of other molecules like
-CO, OH etc. First three panels of figure~\ref{fig:Hfracsim} shows the density of
+CO, OH etc. First three panels of figure~\ref{fig:Hfracsim} show the density of
 various hydrogen species in the outflow for the simulation run with
@@
 few 10$^{3}$\, K. The mean molecular weight, $\mu$, gives an indication
-on which specie of hydrogen dominates in what regions of the flow. In
+on which species of hydrogen dominates in each region of the flow. In
 particular, a value of $\mu > 2.$ represents regions dominated by
@@
    The jet is assumed to be in the plane of sky implying an angle of
-   inclination of $90^{\circ}$. The horizontal
- {\it white dashed} line marks the cuts where the spectra is taken
- while the vertical {\it magenta dashed} line represents the cut for
- the PV digram.} 
+   inclination of $90^{\circ}$. The vertical {\it magenta dashed} line represents the cut for the PV digram and where this line is inctersected by the horizontal
+ {\it white dashed} lines marks the positions from which the spectra are taken.} 
 \label{empvspec90}
@@
 with angle of inclination of 60$^{\circ}$ and 45$^{\circ}$
-respectively. These runs are done assuming the the source has a
-velocity of 20 and 30 km s$^{-1}$ respectively.
-The spectra for low inclination angles are much broader
-and less bright at the same three positions in the flow (shown by
+respectively. The spectra for low inclination angles are much broader
+and have lower peak intensities at the same three positions in the flow (shown by
 three white dashed lines). The line 
@@
 intensity of the brightest knot is approximately 10\,K. 
-The PV diagrams in these runs are not anymore symmetric unlike the run
+The PV diagrams in these runs are not longer symmetric, unlike the run
 with the jet in plane of the sky. Instead, they show a distinct {\it zig-zag}

### 2013-10-03 PAPER/ms_final_bv.tex
Added Conclusion and Abstract

--- 2013-10-02 PAPER/ms_final_bv.tex
@@
    { For such a study, we have performed MHD simulations
-of jet propagation into a molecular cloud using the PLUTO
+of knotty jet propagation into a molecular cloud using the PLUTO
 code. Firstly, we evolve the jet dynamical quantities in conjunction
@@
 The final state of the jet obtained for each cooling model is then
-post-processed using a non-LTE radiative line transfer code, LIME,  to
+post-processed using a radiative line transfer code to
 obtain SiO emission maps, spectra and PV digrams.}
   % results heading (mandatory)
-   {We find that the strength of SiO
-emission depends strongly on the cooling prescription and SiO fractional
-abundance profile. We find that the bulk of SiO emission comes from
-the interface between
-the jet and the ambient molecular medium mainly excited to due to
-shocks. Further, we see that some SiO can be produced within the jet
-especially close to the bow shock due to instabilities associated with
-cooling. We have used these emission maps to give predictions for ALMA
-and single dish observations . Also, our model can very well reproduce the observed 
-spectra, line ratios and PV diagrams of young outflows from Class 0 sources.}
+   {Our model can sucessfully explain the signatures of extremely high
+     velocity (EHV) emission of SiO seen in early outflows. In particular,
+     the line intensities, spectra and PV diagrams obtained from our
+     model are very similar to that observed in case of outflows with
+     EHV emission. In addition, the ALMA predictions for such
+     early molecular outflows shows bright emission coming from young
+     internal knots and primary bow shock due to thermal
+     instability. Our multi-line modeling of SiO support
+     the observational feature for example seen in Herbig-Haro (HH211)
+     that higher line transitions trace
+     regions close to the axis of the jet. The dependence of emission on
+     different cooling prescription and abundance profiles is clearly
+     outlined from our parameter study.}
   % conclusions heading (optional), leave it empty if necessary 
@@
 An alternative hypothesis for the origin of the low velocity SiO
-component is that it could be formed by interaction of
+component is that it could be formed by interaction of wider slow
+shocks with the ambient medium. Generally it is assumed that the silicon material comes from dust
+grain cores and that it is necessary to fully destroy the dust grains
+to obtain some SiO in gas phase. However, some silicon material may be
+mixed with the ices on the dust grain surfaces. In such a scenario, 
+shocks with speeds of 20-30 km s$^{-1}$ might inject a significant
+amount of silicon into the gas phase from the mantles, without 
+completely destroying the grains. Testing such a scenario is beyond
+the scope of the present model. One would not only need proper
+treatment of dust physics but also two fluid model to study the impact
+of slow shocks in two dimensions. These models are indeed very
+important to study wide and slow emission from molecules like CO 
+as seen in some young outflows like L1157 \cite{GomezRuiz:2013p14549}
+and H$_{2}$O as seen from recent results of the Herschel-WISH survey
+\cite{Tafalla:2013p12586}.
 
 \section{Conclusion}
-We are the best in modeling SiO outflows.
+We have performed MHD simulations
+of interaction of knotty and radiative jet propagating 
+with a typical speed of 100 km s$^{-1}$ into a cold, non-magentized ambient
+molecular medium with some gradient in density. At large distance from
+the central source, the magnetic field in the jet is mainly due to
+toroidal component. The jet dynamical quantities are evolved in conjunction
+with different optically thin, non-equilibrium cooling prescriptions of varying complexities. 
+The most complex is that of molecular cooling along with
+H$_2$ chemistry. This prescription allows us to track the formation
+and destruction of HI, HII and H$_2$ along with the flow dynamics. 
+The final state of the jet obtained for each cooling model is then
+post-processed using a radiative line transfer code to
+obtain SiO emission maps, spectra and PV digrams. The main results
+obtained from our study are as follows :
+\begin{itemize}
+\item Different cooling prescriptions used for our model show a
+  significant influence in determing the thickness of the jet. An
+  efficient mode of cooling does reduce the size of coccon and results
+  in a more narrow jet. In addition, the primary bow shock structure
+  differs with various cooling modes. Also, one sees development of
+  thermal instability at the jet head which also show a significant emission in SiO
+  along with young internal knots that are formed close to the base of
+  the jet.
+\item Emission maps obtained from our reference run with molecular
+  cooling show a distinctive outflow lobe like structure. The
+  physical regions responsible of SiO emission in such early outflows
+  typically have molecular hydrogen densities n$\sim$ 10$^{6}$
+  cm$^{-3}$ and temperatures $>$ 500\,K which is consistent with
+  properties deduced from LVG modeling of real observational data of
+  young outflows.   
+\item Our multi-line study of SiO clearly shows how different
+  line transitions are sensitive to different regions in the jets. For
+  example, the SiO J = 1-$>$ 0 transition is mostly excited due to
+  inteaction of jet with ambient medium and could possibly be
+  turblent, while SiO J = 8-$>$ 7 trace the inner most jet regions as
+  they are excited only in the internal knots. This finding very well
+  supports the multi-line observational surveys done for young
+  molecular outflows, particularly, HH 211.
+\item Single-dish synthetic spectra obtained from our model typically
+  have intensity of 0.3\,K and peak around 50\,km\,s$^{-1}$ and have a
+  typical line width of 20\,km\,s$^{-1}$. Such modeled spectra are in
+  excellent agreement with charactertistic features of EHV emission of
+  SiO seen in young molecular outflows . In addition, the line ratios 
+  T(8-7)/T(5-4) and T(5-4)/T(2-1), predicted from our models have values close to
+  unity consistent with that obtained from observations. Further,
+  indications of formation of slow component due to slowing of the
+  older knots is clearly seen as a shift in spectra by
+  8-10\,km\,$s^{-1}$ in first 10$^{3}$ years of evolution.
+\item The predicted PV diagrams from our models show a distinctive
+  knot like features that are generally observed in outflows with EHV
+  emission.
+\item Emission from internal knots do depend on the chosen profile of
+  the abundance. On one extreme where all the internal knots 
+  is the top-hat profile with $\delta$ < 1, whereas, no emission in
+  seen in knots when a gaussian profile with $\delta$ = 1 is used. For
+  the remaining two possiblities, we observe that emission mainly
+  comes from knots close to the base of the flow and the condensation
+  formed at the primary shock due to thermal instability.
+\item Predicted ALMA maps also show characteristic features that are
+  consistent with young molecular outflows with EHV emission. 
+\end{itemize}
+
+In summary, this work for the first time provides a formidable model
+that explains the origin of EHV emission seen in SiO from 
+the inner regions of young molecular outflows.
 

### 2013-10-03 PAPER/ms_final_bv.tex

--- 2013-10-03 PAPER/ms_final_bv.tex
@@
 \subsection{Additional Cooling Prescriptions}
-% 
 For comparison, we also ran simulations of axisymmetric MHD jets
@@
 recombination, additional contribution to radiative losses come from various atomic line emissions from C,N,O,Mg,Si,Fe etc.
+
 %

### 2013-10-03 PAPER/ms_final_bv.tex
Spell check done

@@
   % results heading (mandatory)
-   {Our model can sucessfully explain the signatures of extremely high
+   {Our model can successfully explain the signatures of extremely high
      velocity (EHV) emission of SiO seen in early outflows. In particular,
@@
 The method of selecting these points is given in section \ref{subsec:gridding}.
-At each of these points, the density of the main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+ 0.5 n(H), assuming that atomic Hydrogen has half the SiO collisional cross section of molecular hydrogen and that ionised Hydrogen does not collide with SiO), gas and dust temperatures, velocity, molecular abundances and unresolved turbulent velocity are specified.
+At each of these points, the density of the main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+ 0.5 n(H), assuming that atomic Hydrogen has half the SiO collisional cross section of molecular hydrogen and that ionized Hydrogen does not collide with SiO), gas and dust temperatures, velocity, molecular abundances and unresolved turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
@@
 for the molecular jet the cooling terms evolve with jet dynamics as the fraction of
-various hydrogen species change over time. Whilest the terms remain fixed to initial values, shown in the right panel of fig~\ref{fig:tempvar}, for the jet with tabulated
+various hydrogen species change over time. Whilst the terms remain fixed to initial values, shown in the right panel of fig~\ref{fig:tempvar}, for the jet with tabulated
 cooling. Additionally, the material at primary bow shock for jet
@@
    The jet is assumed to be in the plane of sky implying an angle of
-   inclination of $90^{\circ}$. The vertical {\it magenta dashed} line represents the cut for the PV digram and where this line is inctersected by the horizontal
+   inclination of $90^{\circ}$. The vertical {\it magenta dashed} line represents the cut for the PV digram and where this line is intersected by the horizontal
  {\it white dashed} lines marks the positions from which the spectra are taken.} 
@@
 of interaction of knotty and radiative jet propagating 
-with a typical speed of 100 km s$^{-1}$ into a cold, non-magentized ambient
+with a typical speed of 100 km s$^{-1}$ into a cold, non-magnetized ambient
 molecular medium with some gradient in density. At large distance from
@@
 \item Different cooling prescriptions used for our model show a
-  significant influence in determing the thickness of the jet. An
-  efficient mode of cooling does reduce the size of coccon and results
+  significant influence in determine the thickness of the jet. An
+  efficient mode of cooling does reduce the size of cocoon and results
   in a more narrow jet. In addition, the primary bow shock structure
@@
   example, the SiO J = 1-$>$ 0 transition is mostly excited due to
-  inteaction of jet with ambient medium and could possibly be
-  turblent, while SiO J = 8-$>$ 7 trace the inner most jet regions as
+  interaction of jet with ambient medium and could possibly be
+  turbulent, while SiO J = 8-$>$ 7 trace the inner most jet regions as
   they are excited only in the internal knots. This finding very well
@@
   typical line width of 20\,km\,s$^{-1}$. Such modeled spectra are in
-  excellent agreement with charactertistic features of EHV emission of
+  excellent agreement with characteristic features of EHV emission of
   SiO seen in young molecular outflows . In addition, the line ratios 
@@
   seen in knots when a gaussian profile with $\delta$ = 1 is used. For
-  the remaining two possiblities, we observe that emission mainly
+  the remaining two possibilities, we observe that emission mainly
   comes from knots close to the base of the flow and the condensation

### 2013-10-04 PAPER/ms_final_bv.tex
Added more to Intro

@@
 
-\documentclass[useAMS,usenatbib,letters]{mn2e}
+\documentclass[useAMS,usenatbib]{mn2e}
 
@@
 shocks from these outflows are detected in molecular hydrogen using
-infra-red telescopes. Based on these observational studies, various
+infra-red telescopes. Also, energertic outflows like that of
+Orion source I show evidence of SiO masers very close to the launching
+region of a MHD disk wind \citep{Goddi:2009p8571, Vaidya:2013p12777}. 
+Based on these observational studies, various
 empirical properties for these outflows have been discovered. For
@@
 magnetic fields \citep{Raga:1995p12965, Smith:2003p9985}. 
+Recent models have also incorporated
+infall from envelope \citep{Rawlings:2013p14920} and radiation
+transfer \citep{Offner:2011p14861} to explain molecular 
+emission from Class 0 protostellar outflow sources.
 

### 2013-10-04 PAPER/ms_final_bv.tex
Added lines in the ALMA section

@@
 tracers like CO and SiO respectively. However, the exact nature of
-excitation of these molecules is not yet clear due to lack of models that
+the excitation of these molecules is not yet clear due to lack of models that
 simultaneously study the dynamics along with complex molecular chemistry.}
@@
 envelope scales ($10^{2} - 10^{5}$\,AU) and parent cloud scales
-($10^{5} - 10^{6}$\,AU) \refer. Amongst these, it is at the envelope scale where rich chemical evolution occurs as the jet interacts
+($10^{5} - 10^{6}$\,AU) \refer. Of these, it is at the envelope scale where rich chemical evolution occurs as the jet interacts
 with the molecular medium. In this region, the jet propagates into a
@@
 decade \citep[see reviews by][]{Bachiller:1996p4692,Arce:2007p798,
-Tafalla:2011p14051}. Advances in millimetre interferometery 
+Tafalla:2011p14051}. Advances in millimeter interferometer 
 allow observations of these outflows with spatial resolution of
-few arc seconds. A large number of studies related to young
+few arc seconds. A large number of studies observing young
 outflows are done using standard outflow and shock tracers,
@@
 shocks from these outflows are detected in molecular hydrogen using
-infra-red telescopes. Also, energertic outflows like that of
+infra-red telescopes. Also, energetic outflows like that of
 Orion source I show evidence of SiO masers very close to the launching
@@
 
-Even with a myriad of such empirical evidences, the exact nature of
+Even with a myriad of such empirical evidence, the exact nature of
 these SiO and CO outflows is not clear. For a complete understanding it is imperative
@@
 prescriptions and radiative transfer code respectively. In
-Sect. 5, we will present results from the parameter survey and the
+sections~\ref{sec:parasurvey} and \ref{sec:results}, we will present results from the parameter survey and the
 discussions along with predicted ALMA maps will be presented in
-Section 6 and 7, followed by conclusions.
+sections~\ref{sec:ALMAview} and \ref{sec:discussion}, followed by
+conclusions in section~\ref{sec:conclusion}
 
@@
 At these distances from the central source, the downward pull of gravity plays a
-negligible role and the dynamics of jet is primarily governed by magnetic fields.
+negligible role and the dynamics of the jet is primarily governed by magnetic fields.
 The total magnetic field in the jet is dominated by the toroidal
@@
 the jet). The domain of interest is about 3000\,AU away from the
-central source extends up to 0.1\,pc. Numerically, it is resolved by an uniform grid with a domain of 200$\times$1000 cells in the radial and vertical directions. For simplicity, we choose this medium
+central source and extends up to 0.1\,pc.
+Numerically, it is resolved by an uniform grid with a domain of 200$\times$1000 cells in the radial and vertical directions.
+For simplicity, we choose this medium
 to be unmagnetized and non-turbulent. The density in the ambient
 medium varies with vertical height $z$ as, $\rho_{\rm amb}\sim (\rho_0/z^{2})$
-consistent with observations \citep{Caselli:2011p13935}. The value of
+which is consistent with observations \citep{Caselli:2011p13935}. The value of
 $\rho_0$ depends upon the density contrast, $\eta$, between the jet and
@@
 Typically, early collimated outflows have cooling times shorter than
-the dynamical times implying that the radiative cooling plays a vital
+the dynamical times, implying that the radiative cooling plays a vital
 role in dynamics. In order to study such outflows it is necessary to evolve
@@
 \section{Parameter Survey}
+\label{sec:parasurvey}
 The results and analysis for the present work are divided in two parts,
@@
 evolved with cooling contributions for abundant molecules like CO, OH
-etc. The steady state density, temperature and velocity obtained from this 
+etc. The final state (at time $\sim$ 1000 yr) density, temperature and velocity obtained from this 
 run is post-processed to obtain the observational features
@@
 \section{Results}
-
+\label{sec:results}
 \subsection{Comparison of cooling prescription}
@@
 \section{ALMA view}
-ALMA view of the reference run and stress of applying our synthetic techniques
-to study the molecular outflows in more details.\\
-
-In order to see the interior structure of the molecular outflow, high resolution interferometric observations are needed.
-To demonstrate how jets similar to those we have modeled would look through such observations we have performed synthetic Atacama Large Millimeter Array (ALMA) observations using the Common Astronomy Software Applications package (CASA).
-The output from the radiative transfer were scaled to 300pc and used as the sky models for observations of the J=2-1, J=5-4 and J=8-7 lines at frequencies of 86.85, 217.10 and 347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7.
-The observations were simulated using cycle 1 ALMA for 30 minutes total integration time, in the configurations c32-6, c32-4 and c32-3 for the three lines, giving beam sizes of 0.72'', 0.47'' and 0.58'' and sensitivities of 0.05, 0.07 and 0.09$\,$mJy/beam for the three lines (as calculated by the ALMA online sensitivity calculator) with velocity resolutions of $\sim$1$\,$km/s.
+\label{sec:ALMAview}
+%
+In order to see the interior structure of the molecular outflow, high
+resolution interferometric observations are needed. To demonstrate how
+jets similar to those we have modeled would look through such
+observations we have performed synthetic Atacama Large Millimeter
+Array (ALMA) observations using the Common Astronomy Software
+Applications package (CASA). The output from the radiative transfer
+were scaled to 300pc and used as the sky models for observations of
+the J=2-1, J=5-4 and J=8-7 lines at frequencies of 86.85, 217.10 and
+347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7. The observations
+were simulated using cycle 1 ALMA for 30 minutes total integration
+time, in the configurations c32-6, c32-4 and c32-3 for the three
+lines, giving beam sizes of 0.72'', 0.47'' and 0.58'' and
+sensitivities of 0.05, 0.07 and 0.09$\,$mJy/beam for the three lines
+(as calculated by the ALMA online sensitivity calculator) with
+velocity resolutions of $\sim$1$\,$km/s.
+ Figure~\ref{fig:almafig}
+presents the AMLA prediction obtained from our reference run. The
+left panel shows the integrated emission of SiO J = 2-1 line while the right
+shows the PV diagram for the same line and over laid are
+the contours of SiO J = 5-4 and J = 8-7. The contour levels are marked
+on the color bar of each panel.
 
@@
 
+ALMA Cycle 0 observations have recently reported complex kinematic
+features of young bipolar molecular outflows. In particular,
+\cite{Arce:2013p14902} observed morphology, kinematics and entrainment
+mechanism of the HH 46/47 molecular outflow from a low mass nearby
+source (d = 450 pc) using CO(1-0). They find that the red
+lobe of the outflow exhibits a very complex structure with a
+collimated episodic wind whereas the outflow in the blue lobe is consistent with
+wide-angle wind model. Three major clumps in the red lobe along the
+outflow axis show a distinctive signature in emission maps. In
+addition, these clumps appear as {\em{wedges}} in the PV
+diagram. The observed {\em{wedges}} are very similar in structure to that 
+seen in the right panel of figure~\ref{fig:almafig}. A quantitative
+comparison is not possible due to obvious difference of molecular
+lines. Another source which is studied in details with ALMA band 7 is
+one of the most energetic, luminous molecular outflow
+G331.512-0.103 \cite{Merello:2013p15066}. Observations of this outflow
+associated with a high mass star reveal a compact, extremely young
+bipolar outflow and a symmetric outflowing shell. Further, their PV
+diagrams with SiO and H$^{13}$CO$^{+}$ show a characteristic peak at
+-45\,km\,s$^{-1}$ along the primary axis that could associated with a 
+molecular {\em bullet} of high-velocity dense material as predicted from our
+synthetic maps.
+
 \section{Discussion}
+\label{sec:discussion}
 Here we compare the various results with SiO observation of young low
@@
 \label{ssec:EHV}
-Multiline mm-wave surveys of SiO emission towards a sample of molecular
+Multiline mm-wavelength surveys of SiO emission towards a sample of molecular
 outflows have shown that these outflows exhibit both low and high
 velocity SiO emission possibly arising from two distinct regimes. The slow
-component in case of a typical outflow L1448 is believed to arise from
+component in the case of a typical outflow, L1448, is believed to arise from
 the shell of accelerated ambient gas with SiO abundance
@@
 the scope of the present model. One would not only need proper
-treatment of dust physics but also two fluid model to study the impact
+treatment of dust physics but also a two fluid model to study the impact
 of slow shocks in two dimensions. These models are indeed very
@@
 \section{Conclusion}
+\label{sec:conclusion}
 We have performed MHD simulations
@@
 with a typical speed of 100 km s$^{-1}$ into a cold, non-magnetized ambient
-molecular medium with some gradient in density. At large distance from
+molecular medium a density gradient. At large distance from
 the central source, the magnetic field in the jet is mainly due to
@@
   in a more narrow jet. In addition, the primary bow shock structure
-  differs with various cooling modes. Also, one sees development of
+  differs with various cooling modes. Also, with realistic cooling
+  functions one sees development of
   thermal instability at the jet head which also show a significant emission in SiO
@@
   the abundance. On one extreme where all the internal knots 
-  is the top-hat profile with $\delta$ < 1, whereas, no emission in
+  is the top-hat profile with $\delta <$ 1, whereas, no emission in
   seen in knots when a gaussian profile with $\delta$ = 1 is used. For

### 2013-10-06 PAPER/ms_final_bv.tex
Version submitted Paola 1

@@
 envelope scales ($10^{2} - 10^{5}$\,AU) and parent cloud scales
-($10^{5} - 10^{6}$\,AU) \refer. Of these, it is at the envelope scale where rich chemical evolution occurs as the jet interacts
+($10^{5} - 10^{6}$\,AU) (\refer : Frank et. al, 2013, PPVI). Of these, it is at the envelope scale where rich chemical evolution occurs as the jet interacts
 with the molecular medium. In this region, the jet propagates into a
@@
 We model the propagation of jet as it interacts with the molecular
-cloud core at distances great enough so the the central object no longer has significant impact on the evolution of the outflow, i.e. $\gtrsim$ 1000\,AU. 
+cloud core at distances $\gtrsim$ 1000\,AU. 
 At these distances from the central source, the downward pull of gravity plays a
@@
 survey of above mentioned parameters. The results shown in this work will be
-pertaining to the reference run and appropriate comparison will be
+pertaining to the reference run (unless otherwise mentioned) and appropriate comparison will be
 discussed with other runs.
@@
  \includegraphics[width=2.\columnwidth]{\figpath/diffcool_EMgaussprof.png}
- \caption{A plot of the integrated SiO J2-1 emission from 5 models, 
+ \caption{A plot of the integrated SiO J=2-$>$1 emission from 5 models, 
 each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
@@
  \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
- \caption{Fraction of hydrogen species in the run with molecular
+ \caption{Fraction of hydrogen species, temperature and mean molecular
+    weight in the run with molecular
     cooling having $\eta$ = 3 and $\beta$ = 10.}
@@
    points in the flow, viz. the interface of the knot with molecular
-   medium and at the bow shock}
+   medium and at the bow shock.}
 \label{fig:Hmolform}
@@
  \includegraphics[width=1.\columnwidth]{\figpath/refrun_21_90_emspecpv.png}
- \caption{Integrated Emission map ({\it top left}), PV diagram ({\it top right}
+ \caption{Integrated emission map ({\it top left}), PV diagram ({\it top right}
    and spectra ({\it bottom} for the
@@
 the emission maps. The knot closer to the base is the brightest
-showing a peak intensity of 50\,K. As one moves along the jet the
+showing a peak intensity of 25\,K. As one moves along the jet the
 intensity decreases and reaches to about 10\,K close to the bow shock.
@@
 primary bow shock also show bright emission for these high J transitions. 
-This gas is linked to the Rayleigh-Taylor instability associated with cooling flows (see
+This gas is linked to the thermal instability associated with cooling flows (see
 section~\ref{ssec:coolres}). The sub-structure seen close to the
@@
  \includegraphics[width=2.\columnwidth]{\figpath/imshkvhcontomaps.png}
- \caption{Contours of SiO emission for different line transitions
-   obtained for the run with molecular cooling with $\eta$ = 3 using
-   the functional form of the SiO fractional abundance with $\delta <$
-   1. The contour colors represent different intensities in Kelvins, i.e,
+ \caption{Symmetrical contour maps of multi-line integrated SiO
+   emission convolved with a 2\arcsec beam obtained using parameters of the reference run. The contour colors represent different intenties in Kelvins, i.e,
    30.0({\it red}), 10.0({\it green}), 5.0({\it blue}), 1.0({\it
@@
 high excitation lines. Line emission for SiO from our model also traces similar
-physical environment. Fig~\ref{fig:Hmolform} shows that regions close
+physical environment. Fig.~\ref{fig:Hmolform} shows that regions close
 to the internal knot have temperatures up to 1000\,K and molecular
-hydrogen density of the order of 10$^{5}$ cm$^{-3}$ about half that of the total
-hydrogen density in that region. These regions are where bulk of the
+hydrogen density of the order of 10$^{6}$ cm$^{-3}$ (also see fig.~\ref{grid}).
+These regions are where bulk of the
 SiO emission is obtained in our models. Additionally, the internal
@@
 in case of HH212. Values $\approx$ 1 for both ratios were
-only achieved in optically thick LTE regime
-\citep{Cabrit:2007p13804, Lee:2008p13697}. 
-Similar values are also obtained for molecular outflows from massive
+achieved for low mass in LTE regime \citep{Cabrit:2007p13804, Lee:2008p13697}. 
+and also for molecular outflows from massive
 young stellar object IRAS 17233-3606 \cite{Leurini:2013p13165}.
@@
 fig.~\ref{fig:lineratio}. Their values lie very close to unity as
-indicated from observations. Further, we have estimated the optical
-depth in regions emitting SiO and find them to be optically thick with
-an optical depth $\tau \sim 10$. Thus, assuming optically thin SiO emission
-from molecular outflows especially from shocked dense knots would
-only provide upper limits. In summary, the
-shape, ratio and peak intensity of the spectra obtained from our model
-fit very well to observed values implying
+indicated from observations. 
+%Further, we have estimated the optical
+%depth in regions emitting SiO and find them to be optically thick with
+%an optical depth $\tau \sim 10$. Thus, assuming optically thin SiO emission
+%from molecular outflows especially from shocked dense knots would
+%only provide upper limits. 
+In summary, the shape, ratio and peak intensity of the spectra
+obtained from our model fit very well to observed values implying
 that SiO emission from our model is tracing the regions with right physical
@@
    the inner knot for the molecular cooling run with $\eta$ = 3 and
-   $\beta$ = 10 using top hat abundance profile with $\delta$ = 1. The profiles are
+   $\beta$ = 10 for the reference run. The profiles are
    obtained when the angle of inclination is 60$^{\circ}$ with respect
@@
 collisions exists, their focus is mainly on weaker shocks
-\cite{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800}. 
+\citep{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800}. 
 The pulsating jet propagation model presented here have shock speeds
@@
 which are believed to be slowed down and more evolved form of these
-young molecular bullets as suggested by \cite{Norman:1979p14858,
-  Hartigan:1987p11178}.
+young molecular bullets as suggested by \cite{Norman:1979p14858} and
+  \cite{Hartigan:1987p11178}.
 %
@@
   properties deduced from LVG modeling of real observational data of
-  young outflows.   
+  young outflows like L1448-mm.
 \item Our multi-line study of SiO clearly shows how different
@@
   older knots is clearly seen as a shift in spectra by
-  8-10\,km\,$s^{-1}$ in first 10$^{3}$ years of evolution.
+  7-10\,km\,s$^{-1}$ in first 10$^{3}$ years of evolution.
 \item The predicted PV diagrams from our models show a distinctive
-  knot like features that are generally observed in outflows with EHV
-  emission.
+  knot like features that are generally observed in outflows like IRAS
+  04166+2706 which show EHV emission in both CO and SiO.
 \item Emission from internal knots do depend on the chosen profile of

### 2013-10-14 PAPER/Paola_1/ms_ver2.tex
Modified bib file and added Paola comments and ms_ver2.tex which incorporates the comments

--- 2013-10-06 PAPER/ms_final_bv.tex
@@
 
-\newcommand{\figpath}{PFIGS/}
+\newcommand{\figpath}{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{eq:shockjetvel}
-v_{\rm s} = \frac{v_{\rm j}}{1 + \eta^{-0.5}} = \frac{v_{\rm j}}{\delta}
+v_{\rm s} = \frac{v_{\rm j}}{1 + \eta^{-0.5}} = v_{\rm j}\delta
 \end{equation}
@@
 The results and analysis for the present work are divided in two parts,
-viz., the dynamical numerical simulations and the post-processing with
+viz., the dynamical numerical simulations and the
 radiative transfer code. For each part we have used certain parameters
@@
 results. However, not all quantities needed for our study are well
-constrained by observations, thus allowing us vary them as
+constrained by observations, thus they are considered as
 free parameters. Such a parameter survey provides better handle on the range of allowed
@@
 different cooling prescriptions, we have assumed the jet to be
-over-dense by 10 times that of the ambient medium. Additionally, for
-the atomic, tabulated and molecular cooling runs we have also used a
+over-dense by 10 times compared to the ambient medium. Additionally, for
+the atomic, tabulated and molecular cooling runs (see section~\ref{sec:chem}
+for description of different cooling prescriptions) we have also used a
 value of $\eta$ of the order of unity indicating similar densities in
@@
 respect to line of sight denoted by $\phi$. Section~\ref{ssec:sioabun}
-describes all the profiles used for the present study. The obvious
-choice for the inclination angle, $\phi$ is 90$^{\circ}$ indicating
+describes all the profiles used for the present study. $\phi$ = 90$^{\circ}$ indicates that
 the outflow is in the plane of the sky. 
@@
 The reference run in our calculation has density contrast $\eta$ = 3
-with a plasma beta, $\beta$ = 10. The jet for this run is 89\% atomic,
+with a plasma beta $\beta$ = 10. The jet for this run is 89\% atomic,
 10\% molecular and 1\% ionized to begin with. This jet enters the
@@
 evolved with cooling contributions for abundant molecules like CO, OH
-etc. The final state (at time $\sim$ 1000 yr) density, temperature and velocity obtained from this 
-run is post-processed to obtain the observational features
+etc. The final state (at time $\sim$ 1000 yr), i.e, density, temperature and velocity obtained from this 
+run are given in input to the radiative transfer code to obtain the observational features
 corresponding to SiO molecule. 
 For the radiative transfer calculation, the source in the reference
-run is stationary and the jet is in plane of the sky ($\phi =
+run is stationary and the jet is in the plane of the sky ($\phi =
 90^{\circ}$). A gaussian profile is used for the fractional abundance
@@
 the fractional abundance, v$_{\rm s}$, is less than the jet velocity in the
-flow, such that their ratio $\delta$ is given by 1./$(1.0 +
-\eta(z)^{-0.5})$, where $\eta(z)$ is the density contrast as a
-function of height from the base of the jet, and is inversely proportional to the ambient density at the same height.
+flow, such that their ratio $\delta$ is given by
+equation~\ref{eq:shockjetvel}, where $\eta$ is the density contrast as a
+function of height from the base of the jet.
 
@@
 %
-In order to see the interior structure of the molecular outflow, high
-resolution interferometric observations are needed. To demonstrate how
-jets similar to those we have modeled would look through such
-observations we have performed synthetic Atacama Large Millimeter
+In order to see the interior structure of the molecular outflow and
+test the model predictions, high
+resolution interferometric observations are needed. 
+We have performed synthetic Atacama Large Millimeter
 Array (ALMA) observations using the Common Astronomy Software
 Applications package (CASA). The output from the radiative transfer
-were scaled to 300pc and used as the sky models for observations of
+were scaled to a distance of 300pc and used as the sky models for observations of
 the J=2-1, J=5-4 and J=8-7 lines at frequencies of 86.85, 217.10 and
-347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7. The observations
+347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7, respectively. The observations
 were simulated using cycle 1 ALMA for 30 minutes total integration
@@
  Figure~\ref{fig:almafig}
-presents the AMLA prediction obtained from our reference run. The
+presents the ALMA prediction obtained from our reference run. The
 left panel shows the integrated emission of SiO J = 2-1 line while the right
@@
  \includegraphics[width=2.\columnwidth]{\figpath/ALMAmaps3.png}
- \caption{{\bf Left:} The integrated intensity map of the three SiO lines simulated.
-The heat map shows the 5-4 line intensity (in units of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line intensity and the green contours show the J=2-1 line intensity.
+ \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
+   and (8-7).
+The heat map shows the 2-1 line intensity (in units of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line intensity and the green contours show the J=5-4 line intensity.
 {\bf Right:} The PV diagram taken along the axis of the jet (in units of Jy/beam), showing the higher J transitions highlighting the knots of the jet and broad emission at the bow shock.
-In both panels the ticks on the color bar represent the contour levels, the levels not shown on the integrated intensity color bar are double the previous level.}
+In both panels the ticks on the color bar represent the contour levels.}
 \label{fig:almafig}
@@
 \cite{Arce:2013p14902} observed morphology, kinematics and entrainment 
-mechanism of the HH 46/47 molecular outflow from a low mass nearby
+of the HH 46/47 molecular outflow from a low mass nearby
 source (d = 450 pc) using CO(1-0). They find that the red
 lobe of the outflow exhibits a very complex structure with a
-collimated episodic wind whereas the outflow in the blue lobe is consistent with
+collimated episodic wind, whereas the outflow in the blue lobe is
+consistent with a
 wide-angle wind model. Three major clumps in the red lobe along the
-outflow axis show a distinctive signature in emission maps. In
-addition, these clumps appear as {\em{wedges}} in the PV
-diagram. The observed {\em{wedges}} are very similar in structure to that 
-seen in the right panel of figure~\ref{fig:almafig}. A quantitative
-comparison is not possible due to obvious difference of molecular
-lines. Another source which is studied in details with ALMA band 7 is
-one of the most energetic, luminous molecular outflow
-G331.512-0.103 \cite{Merello:2013p15066}. Observations of this outflow
+outflow axis appear as {\em{wedges}} in the PV
+diagram (similar to that seen in the right panel of fig~\ref{fig:almafig}). 
+A quantitative comparison is not possible due to the different
+molecule observed. Another source which is studied in details with ALMA band 7 is
+one of the most energetic, luminous molecular outflows
+G331.512-0.103 (\citealt{Merello:2013p15066}). Observations of this outflow
 associated with a high mass star reveal a compact, extremely young
@@
 -45\,km\,s$^{-1}$ along the primary axis that could associated with a 
-molecular {\em bullet} of high-velocity dense material as predicted from our
-synthetic maps.
+molecular {\em bullet} of high-velocity dense material as also found in our
+synthetic maps at inclination angles of 60$^{\circ}$ and 45$^{\circ}$.
 
@@
 \label{sec:discussion}
-Here we compare the various results with SiO observation of young low
+Here we compare our results with SiO observations of young low
 mass and high mass outflows.
@@
 the shell of accelerated ambient gas with SiO abundance
-lower by two orders of magnitude than regions emitting the high velocity component.
+lower by two orders of magnitude than regions emitting the high
+velocity component
 \cite{Codella:1999p12584}. In addition, an interesting feature of EHV
-gas is seen in many young molecular outflows. The origin of EHV
+gas is seen in many young molecular outflows. The origin of the EHV
 component is still a mystery, however, recent high resolution
-observations have tried to study the composition of such extremely high
-velocity gas \cite{Tafalla:2010p14759}. Typically, EHV gas feature in
-high density gas tracers (like CO and SiO) 
-and show significantly weak emission of $\sim$ 0.1\,K.
+observations show that EHV gas is seen in
+high density gas tracers (like CO and SiO) and the line have
+intensities $\sim$ 0.1 K (\citealt{Tafalla:2010p14759}).
 %
@@
 that the EHV CO(2-1) emission is mapping a jet-like
-feature that runs along the middle and consists of a collection of
-discrete peaks. These peaks of EHV emission are placed located in a
-perfect symmetry on both sides of the outflow lobe. This symmetry
+feature that consists of a collection of
+discrete peaks symmetrically placed on both outflow lobes. This symmetry
 indicate that such EHV peaks might arise from events that took place
 near the central source and have since propagated in the flow
-\cite{Bachiller:1990p11196, Tafalla:2011p14051}. The dynamical 
+\citep{Bachiller:1990p11196, Tafalla:2011p14051}. The dynamical 
 model in conjunction with proper radiative transfer calculations presented here 
@@
 collimated atomic jet. These pulsating ejections do interact with the medium
-via shocks and exciting high velocity gas. Cooling associated with
-molecules and tracing of H$_{2}$ chemistry with the flow allows us to
+via shocks and exciting high velocity gas. Including the cooling associated with
+molecules and the H$_{2}$ chemistry allows us to
 consistently identify the regions where molecular hydrogen is formed
@@
 regions where shocked H$_{2}$ gas is present. A contour map of SiO
-emission obtain from the reference run is shown in
+emission obtained from the reference run is shown in
 figure~\ref{fig:ltconts}. Such a model can very well explain the
-shocked SiO velocity components observed in L1157 molecular outflow \cite{Gueth:1998p14058}. 
+shocked SiO velocity components observed in the L1157 molecular outflow \cite{Gueth:1998p14058}. 
 %
@@
 ~\ref{empvspec45}). Such a velocity range is typically associated with
-EHV gas seen in majority of the outflows \cite{Tafalla:2011p14051}. Additionally,
+EHV gas seen in the majority of the outflows (\citealt{Tafalla:2011p14051}). Additionally,
 the EHV peaks show a distinct sawtooth pattern in the PV diagram
-\cite{SantiagoGarcia:2009p13972}. Such a sawtooth pattern is very
+(\citealt{SantiagoGarcia:2009p13972}). Such a sawtooth pattern is very
 similar to the pattern that we see in PV diagrams from
@@
 internal knots in the flow. In the section below we further compare
-the line ratios and intensities from our results with single dish
+the line ratios and intensities from our results with single-dish
 measurements of typical outflows with EHV emission.
@@
   Tafalla:2010p14759} and L1157 \citep{Nisini:2007p13128} have
-shown clear signatures of EHV component. Among them L1448, HH211 and
-L1157 have been studied in details using an extensive multi-line
+shown clear signatures of the EHV component. Among them, L1448, HH211 and
+L1157 have been studied in detail using an extensive multi-line
 survey of SiO. Such a multi-frequency analysis helps to understand the dependence of
@@
 
-Figure~\ref{fig:ltconts} show symmetrical contour maps of integrated 
-emission convolved with a 2\arcsec beam coming from different line
-transitions for our reference model. The most
-striking feature seen in that figure is the progressive shift of
+The most striking feature seen in the figure~\ref{fig:ltconts} is the progressive shift of
 emitting region from the interface to internal knots with increase in
@@
 interface between the jet and ambient medium, along with emission from
-the dense knots formed at the base of the flow. While, emission coming
-due to high energy transitions, J=5-$>$4 and 8-$>$7, 
+the dense knots formed at the base of the flow. On the other hand, SiO (5-4) and (8-7) emission, 
 is more concentrated in the inner jet regions and arise mainly from
 the shocks due to internal knots. Such a trend in emission with excitation energies coming from different SiO line transitions
-have been observed in many young outflows (for e.g., {\it{L1448}}
+have been observed in young outflows (for e.g., {\it{L1448}}
 bullets \citep{Nisini:2007p13128}, {\it{HH211}}
 \citep{Chandler:2001p14376, Nisini:2002p14418,
-  Hirano:2006p14411}). Further, the evolved post-shock gas near the
+  Hirano:2006p14411}. Further, the evolved post-shock gas near the
 primary bow shock also show bright emission for these high J transitions. 
-This gas is linked to the thermal instability associated with cooling flows (see
-section~\ref{ssec:coolres}). The sub-structure seen close to the
+This gas is linked to the thermal instability associated with
+radiative jets (see section~\ref{ssec:coolres}). The sub-structure seen close to the
 primary bow shock with high resolution does give a sense of clumpiness
-in the flow backing the suggestions to explain clumpy SiO emission by
-\citealt{Chandler:2001p14376}.
+in the flow backing the suggestions to explain clumpy SiO emission has
+also been observed by \cite{Chandler:2001p14376}.
 %
@@
 to the internal knot have temperatures up to 1000\,K and molecular
-hydrogen density of the order of 10$^{6}$ cm$^{-3}$ (also see fig.~\ref{grid}).
-These regions are where bulk of the
-SiO emission is obtained in our models. Additionally, the internal
-knots move with velocity of 70-90 km\,s$^{-1}$, indicating a
-fractional SiO abundance between 10$^{-6}$ to 10$^{-8}$, depending on the
-choice of abundance profile (see fig~\ref{abun}). 
-The line profile shapes obtained from this study fit reasonable well with that observed by
+hydrogen density of the order of 10$^{6}$ cm$^{-3}$ (also see
+fig.~\ref{grid}). These are the regions where the bulk of the SiO
+emission is present, with fractional abundances between 10$^{-6}$ to 10$^{-8}$.
+The line profiles shapes obtained from our study fit reasonable well with that observed by
 \cite{Nisini:2007p13128}, especially for the bullets seen in
-L1448. Interestingly, we see in our models, where we relax the plane parallel
-approximation, the line profiles are equally broadened for low as well
+L1448. Interestingly, in our models, the line profiles are equally broadened for low as well
 as high excitation lines. The top panel of fig.~\ref{fig:lineratio} shows spectra for three line
-transitions for the reference run but with an angle of inclination,
+transitions for the reference run but with an angle of inclination
 $\phi$ = 60$^{\circ}$ and convolved with a single dish beam of
@@
 levels J$_{\rm up}$ for different abundance profiles is shown in the
-right panel of fig.~\ref{fig:lineratio}. It is clear, that a emission
-obtained using a top hat profile is brighter as compared to one
-obtained with a gaussian profile, due to its obvious high estimate of
-SiO abundance in regions of interest. However, curves obtained from
+right panel of fig.~\ref{fig:lineratio}. It is clear that the emission
+obtained using a top hat profile is brighter than the one obtained
+with a Gaussian SiO profile. However, curves obtained from
 both these profiles show a very similar shape of a distinct rise followed by a fall in
 integrated emission for higher transitions with a peak in
-emission for J$_{\rm up}$ = 3. Similar profiles are also predicted and
-used to estimate the physical conditions assuming optically
-thin emission from LVG modeling for L1448 and L1157
-\cite{Nisini:2007p13128}. However, this usual approach did not give
-accurate results for line ratios SiO(8-7)/(5-4) and SiO(5-4)/(2-1)
-in case of HH212. Values $\approx$ 1 for both ratios were
-achieved for low mass in LTE regime \citep{Cabrit:2007p13804, Lee:2008p13697}. 
-and also for molecular outflows from massive
-young stellar object IRAS 17233-3606 \cite{Leurini:2013p13165}.
+emission for J$_{\rm up}$ = 3. \cite{Nisini:2007p13128} found that
+their homogeneous slab model coupled with LVG radiative transfer, did
+not reproduce the observed line ratios SiO(8-7)/(5-4) and
+SiO(5-4)/(2-1) of HH212. Values $\approx$ 1 for both ratios have been
+found in for low mass assuming LTE regime \citep{Cabrit:2007p13804,
+  Lee:2008p13697} and also for molecular outflows from massive
+young stellar object IRAS 17233-3606 (\citealt{Leurini:2013p13165}).
 These line ratios from the present
@@
 that SiO emission from our model is tracing the regions with right physical
-conditions that are required to emit SiO in gas phase via shocks.
+conditions that are required to emit SiO in the gas phase via shocks.
 
@@
 %
-We have presented a formidable model to explain the EHV component seen
-in SiO emission from several young outflows. The reference model
+We have presented a model able to explain the spectral characteristics
+of the SiO EHV component seen
+in several young outflows. The reference model
 consistently solves for the H$_{2}$ chemistry in presence of
 appropriate cooling. The steady state temperature, density and velocities obtained from dynamical
-simulation is post-processed to obtain SiO maps, spectra and PV
+simulation is used as input in the non-LTE radiative transfer code to obtain SiO maps, spectra and PV
 diagrams. One essential ingredient required for the radiative transfer modeling
@@
 The pulsating jet propagation model presented here have shock speeds
-reaching up to 100 km\,s$^{-1}$. For simplicity we have used two basic
-prescription of SiO abundance profile as a function of shock
-velocity. Though the shape of the profile is uncertain the upper and
-lower limits used are backed by observational evidences. Ideally for a consistent
+reaching up to 100 km\,s$^{-1}$. We have used two
+simplified SiO abundance profiles as a function of shock
+velocity. Though the shape of the profile is uncertain, the upper and
+lower limits used are backed by observational evidences. Ideally, for a consistent
 dependence of SiO abundance on shock velocity, one would have to also
 solve for silicon and SiO chemistry in a manner similar to that of
-H$_{2}$. Further by evolving the dynamical simulations with complex
-grain chemistry for more than 10$^{4}$ years (time to destroy SiO in
-gas phase \cite{Codella:1999p12584}),  one can trace the history of 
-SiO in molecular outflows. However, such a numerically expensive model 
-with complex chemistry is beyond the scope of this paper.  
-%
-
-The model presented in this paper target the very early phase of molecular
-outflows i.e., dynamical time scale of 1000 years.
+H$_{2}$. However, such a numerically expensive model 
+with complex chemistry is beyond the scope of this paper 
+as this could imply to include dust grains and sputtering 
+as well as grain-grain collisions (i.e. an MHD multi-fluid approach).  
+%
+
+The model presented in this paper targets the very early phases of molecular
+outflows i.e., dynamical time scales of 1000 years.
 As discussed in sections above, the unique combination of pulsating
@@
 no signatures of slow SiO component that accompanies EHV emission seen
-in many outflows. The physical mechanism for the origin of slow SiO component is still a matter
-of debate. One of the suggestion is it arises due to slowing down of
+in many outflows \citep[e.g.,][]{Lefloch:1998p13983,
+  Codella:1999p12584}. 
+The physical mechanism for the origin of the slow SiO component is still a matter
+of debate. \cite{Codella:1999p12584} suggest that it arises due to the slowing down of
 shocked gas as they age. The time scale estimated for the shocked gas
 to slow down is of the same order of magnitude as the SiO destruction
-time scale i.e., 10$^{4}$ years \cite{Codella:1999p12584}. In this
-case, we will not be able to see the effect as the dynamical runs do
-not evolve beyond 10$^{3}$ years. However, we do see initial 
+time scale i.e., 10$^{4}$ years (\citealt{Codella:1999p12584}). In this
+case, we do not expect to see the slow velocity SiO component, as our
+models stop at $\sim$ 1000 yr. However, we do see initial 
 hints of slowing down of more evolved gas in terms of the velocity
@@
 coming from the freshly formed internal knots close to the base of the
-flow as compared to emission coming from more evolved gas near the
+flow and that from the more evolved gas near the
 primary bow shock. To ascertain this fact in more details, one would
@@
 evolution will also help to provide a numerical model for the formation of HH objects
-which are believed to be slowed down and more evolved form of these
-young molecular bullets as suggested by \cite{Norman:1979p14858} and
+which are believed to be slowed down and more evolved forms of our
+young molecular bullets, as suggested by \cite{Norman:1979p14858} and
   \cite{Hartigan:1987p11178}.
@@
 shocks with the ambient medium. Generally it is assumed that the silicon material comes from dust
-grain cores and that it is necessary to fully destroy the dust grains
+grain cores and that it is necessary to sputter or vaporise such cores
 to obtain some SiO in gas phase. However, some silicon material may be
-mixed with the ices on the dust grain surfaces. In such a scenario, 
-shocks with speeds of 20-30 km s$^{-1}$ might inject a significant
+mixed with the ices on the dust grain surfaces (see discussion in \citealt{Schilke:1997p14140}) . In such a scenario, 
+shocks with speeds below 20 km s$^{-1}$ might inject a significant
 amount of silicon into the gas phase from the mantles, without 
-completely destroying the grains. Testing such a scenario is beyond
+completely destroying the grains. \cite{JimenezSerra:2010p15530} also found parsec-scale emission of SiO
+toward an infrared dark cloud suggesting that large scale shocks (may
+be triggered by cloud-cloud collisions \citealt{Henshaw:2013p15540}) may
+be responsible.
+Testing such scenarios is beyond
 the scope of the present model. One would not only need proper
@@
 important to study wide and slow emission from molecules like CO 
-as seen in some young outflows like L1157 \cite{GomezRuiz:2013p14549}
+as seen in some young outflows like L1157 (\citealt{GomezRuiz:2013p14549})
 and H$_{2}$O as seen from recent results of the Herschel-WISH survey
-\cite{Tafalla:2013p12586}.
+(\citealt{Tafalla:2013p12586}).
 
@@
 We have performed MHD simulations
-of interaction of knotty and radiative jet propagating 
+of episodic radiative jet propagating 
 with a typical speed of 100 km s$^{-1}$ into a cold, non-magnetized ambient
-molecular medium a density gradient. At large distance from
-the central source, the magnetic field in the jet is mainly due to
-toroidal component. The jet dynamical quantities are evolved in conjunction
+molecular medium with a density gradient. The jet dynamical quantities are evolved in conjunction
 with different optically thin, non-equilibrium cooling prescriptions of varying complexities. 
@@
 The final state of the jet obtained for each cooling model is then
-post-processed using a radiative line transfer code to
+used as input into a non-LTE radiative transfer code to
 obtain SiO emission maps, spectra and PV digrams. The main results
@@
 \begin{itemize}
-\item Different cooling prescriptions used for our model show a
-  significant influence in determine the thickness of the jet. An
-  efficient mode of cooling does reduce the size of cocoon and results
+\item Different cooling prescriptions used for our model
+  significantly influence thickness of the jet. An
+  efficient mode of cooling does reduce the size of the cocoon and results
   in a more narrow jet. In addition, the primary bow shock structure
@@
   functions one sees development of
-  thermal instability at the jet head which also show a significant emission in SiO
+  thermal instability at the jet head which also shows a significant emission in SiO
   along with young internal knots that are formed close to the base of
@@
   cm$^{-3}$ and temperatures $>$ 500\,K which is consistent with
-  properties deduced from LVG modeling of real observational data of
+  properties deduced from LVG modeling of observational data of
   young outflows like L1448-mm.
@@
   example, the SiO J = 1-$>$ 0 transition is mostly excited due to
-  interaction of jet with ambient medium and could possibly be
-  turbulent, while SiO J = 8-$>$ 7 trace the inner most jet regions as
+  the interaction of the jet with the ambient medium, while SiO J = 8-$>$ 7 trace the inner most jet regions as
   they are excited only in the internal knots. This finding very well
@@
   T(8-7)/T(5-4) and T(5-4)/T(2-1), predicted from our models have values close to
-  unity consistent with that obtained from observations. Further,
-  indications of formation of slow component due to slowing of the
-  older knots is clearly seen as a shift in spectra by
-  7-10\,km\,s$^{-1}$ in first 10$^{3}$ years of evolution.
+  unity consistent with observations. Further,
+  indications of the formation of the slow component due to the
+  slowing down of the
+  older knots is clearly seen as a shift of centroid velocities by
+  7-10\,km\,s$^{-1}$ in the first 10$^{3}$ years of evolution.
 \item The predicted PV diagrams from our models show a distinctive
   knot like features that are generally observed in outflows like IRAS
-  04166+2706 which show EHV emission in both CO and SiO.
+  04166+2706.
 \item Emission from internal knots do depend on the chosen profile of
@@
 
-In summary, this work for the first time provides a formidable model
+In summary, this work for the first time provides a model
 that explains the origin of EHV emission seen in SiO from 
@@
 \bibliographystyle{mn2e}
-\bibliography{bibfile}
+\bibliography{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/bibfile}
 \label{lastpage}

### 2013-10-15 PAPER/Paola_1/ms_ver2.tex
all but one comments from paola in rad trans section addressed

@@
 The method of selecting these points is given in section \ref{subsec:gridding}.
-At each of these points, the density of the main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+ 0.5 n(H), assuming that atomic Hydrogen has half the SiO collisional cross section of molecular hydrogen and that ionized Hydrogen does not collide with SiO), gas and dust temperatures, velocity, molecular abundances and unresolved turbulent velocity are specified.
+At each of these points, the density of the main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+ 0.5 n(H), assuming that atomic Hydrogen has half the SiO collisional cross section of molecular hydrogen and that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and unresolved turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
@@
 For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random coordinates, the H$_2$ density and SiO density at the candidate point (n and m, respectively) are compared against the densities of a reference point in the un-perturbed ambient medium multiplied by a factor of $\frac{4\eta}{5}$ (n$_0$ and m$_0$).
+After selection of random coordinates, the H$_2$ density and SiO density at the candidate point (n and m, respectively) are compared against the densities of a reference point in the un-perturbed ambient medium multiplied by a factor of $\frac{4\eta}{5}$ (n$_{ref}$ and m$_{ref}$), where $\eta$ is the density contrast between the jet and ambient medium.
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use.

### 2013-10-15 PAPER/Paola_1/ms_ver2.tex
addressed all but one comment on SiO Abundance

@@
 km\,s$^{-1}$ \citep{Dutrey:1997p11185}. Thus, there is
-a significant increase of 6 orders of magnitude from quiescent clouds
-to outflows crowded with shocks. Production of
+an increase of 6 orders of magnitude from quiescent clouds
+to outflows. Production of
 gaseous SiO due to slow C-type shocks has been suggested to occur via release of
@@
 case. Shocks due to such outflows will dissociate H$_{2}$ and will
-become J ({\em{jump}}) type shocks. Thus molecules observed in such
+become J ({\em{jump}}) type shocks. Thus, molecules observed in such
 energetic outflows must have been reformed in the flow as suggested by
 detailed models of J-shocks by \cite{Neufeld:1989p14322}. SiO formation in J shocks
-have also been modelled recently and have thought to be reasonable
-candidates of SiO line emission in molecular outflows and jets
+has also been modelled recently and has thought to be the source of
+the SiO line emission observed in molecular outflows and jets
 \citep{Guillet:2009p11229}.
@@
 prescribe a gaussian such that the peak SiO abundance of 10$^{-6}$ is at
-60\,km\,s$^{-1}$. While the value of n(SiO)/n(H$_{2}$) falls below
-10$^{-9}$ at 20 and 100 km s$^{-1}$. These functional dependences of SiO
+60\,km\,s$^{-1}$, while the value of n(SiO)/n(H$_{2}$) falls below
+10$^{-9}$ at 20 and 100 km s$^{-1}$
+\citep[e.g.,][also see
+section~\ref{sec:discussion}]{Lefloch:1998p13983}. 
+These functional dependences of SiO
 abundance on shock velocity are show in figure~\ref{abun}.  
-In addition to this if the temperature at the point is greater than
+In addition to this, if the temperature at the point is greater than
 92,000\,K (the temperature of the Si-O bond disassociation energy) 
-the abundance is reduced to 10$^{-12}$. 
+the abundance is reduced to 0. 
 %
@@
 same as the shock velocity. Considering that there is a density
-contrast in the simulation setup this assumption is will
-overestimate the shock velocity. In order to correct the same we also
+contrast in the simulation setup, this assumption is will
+overestimate the shock velocity. We also
 consider a case in which the shock speed of a dense plug accumulated
-between the jet and medium is estimated by balancing the the respective ram
+between the jet and medium is estimated by balancing the respective ram
 pressures \citep{Masson:1993p9661},

### 2013-10-15 PAPER/Paola_1/ms_ver2.tex
added all comments in the Introduction and Abstract

@@
   % context heading (optional)
-  {A bipolar, violent, collimated outflow is one of the first signposts of star
-formation. Such an outflow is believed to be launched magnetically from
-underlying accretion disk. As it propagates through the molecular
+  {A bipolar, collimated outflow is one of the first signposts of star
+formation. As it propagates through the molecular
 cloud, it injects energy and momentum via shocks 
@@
 velocity molecular outflows are extensively studied for both low mass
-and high mass stars. They are usually observed using standard sub-mm outflow and shocks
-tracers like CO and SiO respectively. However, the exact nature of
+and high mass stars. They are usually observed using standard outflow and shocks
+tracers like CO and SiO. However, the exact nature of
 the excitation of these molecules is not yet clear due to lack of models that
@@
   % methods heading (mandatory)
-   { For such a study, we have performed MHD simulations
+   { For such a study, we have performed Magneto-hydrodynamic (MHD) simulations
 of knotty jet propagation into a molecular cloud using the PLUTO
@@
 post-processed using a radiative line transfer code to
-obtain SiO emission maps, spectra and PV digrams.}
+obtain SiO emission maps, spectra and position-velocity (PV) digrams.}
   % results heading (mandatory)
@@
      model are very similar to that observed in case of outflows with
-     EHV emission. In addition, the ALMA predictions for such
+     EHV emission. In addition, the Atacama Large Millimeter Array (ALMA) predictions for such
      early molecular outflows shows bright emission coming from young
@@
      instability. Our multi-line modeling of SiO support
-     the observational feature for example seen in Herbig-Haro (HH211)
+     the observational feature seen in Herbig-Haro (HH 211)
      that higher line transitions trace
@@
 high mass stars, radiative forces also contribute to flow dynamics
-during the later evolutionary stages \cite{Vaidya:2011p8992}. 
+during the later evolutionary stages (\citealt{Vaidya:2011p8992}). 
 Typically, these jets are few parsec in size long and can be divided into
-three length-scale domains viz. source and disk scales (1-10$^{2}\,$AU),
+three length-scale domains, viz. source and disk scales (1-10$^{2}\,$AU),
 envelope scales ($10^{2} - 10^{5}$\,AU) and parent cloud scales
@@
 relatively static medium inducing shocks that are interesting from both a
-physical and chemical point of view. In addition to shocks, molecular
+physical and chemical point of view. In addition to jets, molecular
 material from the surroundings is entrained and accelerated to high
@@
 have been studied in detail over the past 
-decade \citep[see reviews by][]{Bachiller:1996p4692,Arce:2007p798,
+decade \citep[see reviews by][]{Bachiller:1996p4692, Beuther:2002p1149, Arce:2007p798,
 Tafalla:2011p14051}. Advances in millimeter interferometer 
@@
 Based on these observational studies, various
-empirical properties for these outflows have been discovered. For
-example, the CO outflows from single dish studies are seen to be
-highly collimated for both low and high mass stars
-\citep[for e.g.,][]{Gueth:1999p4683, Beuther:2002p3574} they are
-referred to as {\em{molecular jets}}. These outflows also exhibit a
-mass-velocity relation with a power law form $ dM(v)/dv \propto
-v^{-\gamma}$, where values of $\gamma$ range from 1 to 3 \cite{Downes:2003p9946}. Episodic
-knots believed to be caused by variable accretion events are a common property
-of young molecular outflows (for e.g. in L1577:
+empirical properties for these outflows have been discovered. 
+For example, the high resolution interferometric studies with
+CO (1-0) and SiO (2-1) have revealed highly collimated jet-like
+outflows (with opening angles less than a few degrees) they are
+referred to as {\em{molecular jets}}. HH 211 is the best example of
+such a molecular jet (\citealt{Gueth:1999p4683}).
+Episodic knots believed to be caused by variable accretion events are a common property
+of young molecular outflows usually observed with higher line
+transitions of CO and SiO (for e.g. in L1577:
 \citealt{Gueth:1998p14058}, in HH300: \citealt{Arce:2001p14064}). These knots show their signatures
-as {\em{wedges}} in the position-velocity (PV) diagrams \cite{Arce:2001p14065}. Also, most
-commonly observed in these outflows are signatures of rotation and
+as {\em{wedges}} in the PV diagrams \cite{Arce:2001p14065}. Also, 
+observed in these outflows are signatures of rotation and
 precision (for e.g., in DG Tau: \citealt{Bacciotti:2002p2084}).
@@
 
-Even with a myriad of such empirical evidence, the exact nature of
-these SiO and CO outflows is not clear. For a complete understanding it is imperative
-to compliment these observations with theoretical models. Many models
+Even with a myriad of such empirical evidences, the exact nature of
+moleular emission in outflows is not clear. For a complete understanding it is imperative
+to complement these observations with theoretical models. Many models
 based on hydro-simulations and steady state shock calculations
@@
 The most popular among them is the jet driven model as wind
-driven molecular outflows not only fail to match observed PV diagrams \cite{Cabrit:1992p14098}
+driven molecular outflows not only fail to match observed PV diagrams (\citealt{Cabrit:1992p14098})
 but also tend to sweep large quantity of material at the extremities
-of the lobes \cite{Masson:1992p14101}. While the jet driven models could successfully
+of the lobes (\citealt{Masson:1992p14101}). The jet driven models could successfully
 derive the global outflow shapes and mass velocity relations of CO
-outflows \citep{Raga:1993p9948, Masson:1993p9661} . There have also been some attempts to combine these two
-models into one \cite{Shang:2006p14268} to explain the global observational features. 
+outflows \citep{Raga:1993p9948,
+  Masson:1993p9661,Downes:2003p9946,Downes:2007p9514}. 
+There have also been some attempts to combine these two
+models into one (\citealt{Shang:2006p14268}) to explain the global observational features. 
 However, most of these dynamical models do not
@@
 dissociative J-type shocks models \citep{Neufeld:1989p11689, Schilke:1997p14140,Flower:2003p11236}. 
-The magneto-hydrodynamic (MHD) calculations by \cite{Glassgold:1991p13703} suggested that molecules
+The MHD calculations by \cite{Glassgold:1991p13703} suggested that molecules
 like SiO and CO could form within the jet. Similar conclusions of
 molecules surviving in steady state disk winds have also been shown
-\cite{Panoglou:2012p10039}. 
+(\citealt{Panoglou:2012p10039}). 
 Very few simulations have modelled the outflow
-dynamics including molecular chemistry but in absence of
+dynamics including molecular chemistry and in absence of
 magnetic fields \citep{Raga:1995p12965, Smith:2003p9985}. 
 Recent models have also incorporated
-infall from envelope \citep{Rawlings:2013p14920} and radiation
+infall from the envelope \citep{Rawlings:2013p14920} and radiation
 transfer \citep{Offner:2011p14861} to explain molecular 
@@
 transitions, by combining axisymmetric MHD simulations of
-radiative jet propagation with time-dependent chemistry and 3D radiative
+radiative jet propagation with time-dependent simple chemistry and 3D radiative
 transfer. In particular, we evolve the jet dynamical
@@
 The final state of the jet obtained for each cooling model is then
-post-processed using a non-LTE line radiative transfer code
+given as a input to a non-LTE line radiative transfer code
 to obtain emission maps, spectra and PV digrams. These emission maps
@@
 
-In the next three sections we describe our numerical setup, cooling
+In the next three sections~\ref{sec:numsetup}, \ref{sec:chem} and
+\ref{sec:radtrans}, we describe our numerical setup, cooling
 prescriptions and radiative transfer code respectively. In
@@
 sections~\ref{sec:ALMAview} and \ref{sec:discussion}, followed by
-conclusions in section~\ref{sec:conclusion}
+conclusions in section~\ref{sec:conclusion}.
 
 \section{Numerical Setup}
+\label{sec:numsetup}
 \subsection{Numerical code and Equations}
@@
 
-The evolution of the magnetic field is governed by induction equation,
+The evolution of the magnetic field is governed by the induction equation,
 %
@@
 %
-In addition to the above set of equations the code obeys the condition of divergence-free 
+In addition to the above set of equations, the code obeys the condition of divergence-free 
 magnetic fields, $\nabla \cdot \vec{B} = 0$, which is numerically achieved by construction 
@@
 
-\subsection{Initial Condition}
+\subsection{Physical Setup}
 We model the propagation of jet as it interacts with the molecular
@@
 \subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
-The radiative transfer program used is LIME (LIne Modeling Engine; \citealt{Brinch:2010p13078}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
-The method of selecting these points is given in section \ref{subsec:gridding}.
-At each of these points, the density of the main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+ 0.5 n(H), assuming that atomic Hydrogen has half the SiO collisional cross section of molecular hydrogen and that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and unresolved turbulent velocity are specified.
+The radiative transfer program used is LIME (LIne Modeling Engine;
+\citealt{Brinch:2010p13078}), which  calculates line intensities based
+on a weighted sample of randomly chosen points in a continuous 3D
+model. The method of selecting these points is given in section
+\ref{subsec:gridding}. At each of these points, the density of the
+main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+
+n(H), assuming that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and unresolved turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.

### 2013-10-20 PAPER/Paola_1/ms_ver2.tex
Added new figures and ran through all comments

@@
 \begin{document}
-\title{SiO Molecular Jets around young stars - A numerical perspective}
+%\title{SiO Molecular Jets around young stars - A numerical perspective}
+\title[EHV SiO component in Molecular Outflows]{Synthetic Observations of Extremely High Velocity (EHV) SiO component
+  in young molecular outflows}
 \author[B. Vaidya, Tom Douglas, Paola Caselli]{B. Vaidya$^{1}$\thanks{E-mail:
@@
      model are very similar to that observed in case of outflows with
-     EHV emission. In addition, the Atacama Large Millimeter Array (ALMA) predictions for such
+     EHV emission. In addition, the Atacama Large Millimeter Array
+     (ALMA) predictions for such
      early molecular outflows shows bright emission coming from young
      internal knots and primary bow shock due to thermal
-     instability. Our multi-line modeling of SiO support
+     instability. Our multi-line modeling of SiO supports
      the observational feature seen in Herbig-Haro (HH 211)
@@
 CO (1-0) and SiO (2-1) have revealed highly collimated jet-like
-outflows (with opening angles less than a few degrees) they are
+outflows (with opening angles less than a few degrees); they are
 referred to as {\em{molecular jets}}. HH 211 is the best example of
@@
 but also tend to sweep large quantity of material at the extremities
-of the lobes (\citealt{Masson:1992p14101}). The jet driven models could successfully
+of the lobes (\citealt{Masson:1992p14101}), while the jet driven models could successfully
 derive the global outflow shapes and mass velocity relations of CO
@@
 
-\subsection{Physical Setup}
+\subsection{Physical Model}
 We model the propagation of jet as it interacts with the molecular
-cloud core at distances $\gtrsim$ 1000\,AU. 
+cloud core material at distances $\gtrsim$ 1000\,AU. 
 At these distances from the central source, the downward pull of gravity plays a
@@
 component. This is because the poloidal field decays as $z^{-2}$ as
-compared to $z^{-1}$ for toroidal field to maintain the force balance ($z$ is the vertical distance from source). 
+compared to $z^{-1}$ for toroidal field to maintain the force balance
+($z$ is the vertical distance from the source). 
 The hoop stress due to pinch force from the toroidal magnetic fields maintains
@@
 medium varies with vertical height $z$ as, $\rho_{\rm amb}\sim (\rho_0/z^{2})$
-which is consistent with observations \citep{Caselli:2011p13935}. The value of
+which is consistent with observations \citep{Keto:2010p15549, Caselli:2011p13935}. The value of
 $\rho_0$ depends upon the density contrast, $\eta$, between the jet and
@@
 \begin{equation}
-v_{\rm jet} = v_{\rm jet,0}(1.0 + A\,sin(2.0\pi t/T_{\rm p}))
+v_{\rm jet} = v_{\rm jet,0}(1.0 + A\,sin(2.0\pi t/T_{\rm p})),
 \end{equation}
@@
 \begin{figure*}
- \includegraphics[width=1\columnwidth]{\figpath/H2ReactionRates.png}
- \includegraphics[width=1\columnwidth]{\figpath/H2CoolingFuncs.png}
+ \includegraphics[width=1\columnwidth]{\figpath/H2ReactionRates_paper.png}
+ \includegraphics[width=1\columnwidth]{\figpath/H2CoolingFuncs_full.png}
  \caption{Variation of $H_2$ chemistry reaction rates, $k_{i}$ and cooling
@@
 main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+
-n(H), assuming that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and unresolved turbulent velocity are specified.
+n(HI), assuming that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and unresolved turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/diffabunprof1.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/diffabun_profnew.pdf}%{\figpath/diffabunprof1.png}
  \caption{The different fractional SiO abundances as a function of
@@
 \centering
-\caption{Summary from parameter runs.}
+\caption{Summary from parameter runs. The parameter $\delta$, is the ratio of
+  shock to jet velocity and it depends on the density contrast $\eta$
+  as shown in eq.~\ref{eq:shockjetvel}}
 \begin{tabular}{c | c | c | c | c | c | c }
@@
 $\eta$ = 10 between the jet and ambient medium.
-It is clear from the figure, that the cooling plays a
+It is clear from the figure~\ref{fig:coolcmpdyn}, that the cooling plays a
 significant role in determining the structure of the jet. The jets
@@
 jets having dominant cooling. For example, the adiabatic jet
-has a widest bow shock at its apex and has the most prominent cocoon
+has the widest bow shock at its apex and has the most prominent shell
+of processed material, also known as the cocoon,
 around it. While the jet with atomic cooling has a rather conical
@@
 various hydrogen species change over time. Whilst the terms remain fixed to initial values, shown in the right panel of fig~\ref{fig:tempvar}, for the jet with tabulated
-cooling. Additionally, the material at primary bow shock for jet
+cooling. Additionally, the material at the primary bow shock for the jet
 with tabulated and molecular cooling condenses forming dense knots. 
@@
 
-The dynamical states for each of this cooling prescription are then 
-post-processed to obtain integrated J = 2-$>$1 SiO emission
+The dynamical states for each of this cooling prescriptions are then 
+given as inputs the radiative transfer code to obtain integrated J = 2-$>$1 SiO emission
 maps shown in figure~\ref{fig:coolcmpsio}. The differences in dynamical
@@
 90$^\circ$ using the top hat abundance
-profile with $\delta = 1$. They are then placed at a distance of 100$\,$pc and convolved with a beam with FWHM of 2.5\arcsec in order to create the maps shown. The 
-emission features in jet with atomic and power-law cooling prescription do not have
-such a well defined lobe structure. For example, the emission from the jet with atomic
-cooling is mainly coming from regions close to R,Z = $\pm$
-10,80. In fact the emission from this region seems to be stronger than
-that coming from the conical jet head. In case of the jet with
-power-law cooling the emission seems to be mostly coming from the
-internal knots. The thin density layer formed at the interface of jet
-and the ambient medium do not show indication of any emission. 
+profile with $\delta = 1$. They are then placed at a distance of
+100$\,$pc and convolved with a beam with FWHM of 2.0\arcsec in order
+to create the maps shown. 
+The emission from the jet with atomic
+cooling is coming from the conical jet head and younger knots closer
+to base of the flow. Additionally, features in the shell at Z $\sim$
+60, 80 also show evidence of faint emission. In case of the jet with
+power-law cooling the emission mostly arises from the
+internal knots. 
 The emission coming from jets with
-tabulated and molecular cooling show a distinctive outflow lobe which
-is typically observed in case of young molecular outflows.
-SiO emission coming from internal knots in these jets also show a
-distinctive turbulent pattern consistent with
-observations. Additionally, strong emission also comes from the
+tabulated and molecular cooling resembles that observed in young molecular outflows.
+Also in these outflows, strong emission arises from the
 condensation formed at the primary bow shock due to thermal
@@
 structure of the primary bow shock. These dynamical differences are
-also reflected in SiO emission maps and spectra. Emission maps
-obtained from molecular cooling show a distinctive outflow lobe
-structure which is consistent with observations. The properties of 
+also reflected in SiO emission maps. The molecular cooling in our
+model consistently takes into account the feedback of temperature and
+density variation to evolve the chemical species unlike the tabulated cooling
+where the fraction of chemical species remains fixed. Thus, for our reference
+run we will adopt the molecular cooling prescription and compare
+results with observations. The properties of
 molecular cooling flows are described in details in the next section.
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/diffcool_sim.pdf}%{\figpath/jetplt1_1010.png}
  \caption{Jet Volume Density for different cooling modes with
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/diffcool_EMgaussprof.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/diffcool_img.pdf}
  \caption{A plot of the integrated SiO J=2-$>$1 emission from 5 models, 
@@
 \subsection{Molecular cooling and H$_2$ Chemistry}
-In case of molecular outflows, the most appropriate form of cooling
-prescription among the ones described in sect.~\ref{sec:chem} is
-that which involves the evolution of H$_2$ chemistry along with
+The molecular cooling in our
+model includes the evolution of H$_2$ chemistry along with
 contributions to cooling from fixed fractions of other molecules like
-CO, OH etc. First three panels of figure~\ref{fig:Hfracsim} show the density of
-various hydrogen species in the outflow for the simulation run with
-$\eta$ = 3 and $\beta$ = 10. The jet is largely dominated by atomic
-and molecular hydrogen, however, the fraction of these species have
-considerably changed from their initial values within the
-jet. Ionized hydrogen is mainly formed at the tip
-of the bow as seen by the increase of fHII to 10\% from an initial value of
-1\% within the jet.
-%
-
-The last two panels of figure~\ref{fig:Hfracsim}
-show the temperature and mean molecular weight $\mu$. The
+CO, OH etc. The jet is largely dominated by atomic
+and molecular hydrogen. Ionized hydrogen is mainly formed at the tip
+of the bow.The
 highest temperature of $\sim$ 50000\,K is attained in our flow at the
@@
 jet and the ambient medium) is lower than 5000\,K. Also the relatively
-weaker shocks formed due to knots do not heat up the material beyond
-few 10$^{3}$\, K. The mean molecular weight, $\mu$, gives an indication
-on which species of hydrogen dominates in each region of the flow. In
-particular, a value of $\mu > 2.$ represents regions dominated by
-molecular hydrogen, while regions close to the bow shock have lowest
-values of $\mu$ where ionized hydrogen is present and along the jet the value
-$\mu$ is close to 1.3 suggesting an atomic jet. 
-%
-
-\begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
- \caption{Fraction of hydrogen species, temperature and mean molecular
-    weight in the run with molecular
-    cooling having $\eta$ = 3 and $\beta$ = 10.}
-\label{fig:Hfracsim}
-\end{figure*}
+weaker shocks formed nearby knots do not heat up the material beyond
+10$^{3}$\, K.
+%
+
+%\begin{figure*}
+% \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
+% \caption{Fraction of hydrogen species, temperature and mean molecular
+%    weight in the run with molecular
+%    cooling having $\eta$ = 3 and $\beta$ = 10.}
+%\label{fig:Hfracsim}
+%\end{figure*}
 
@@
 forming a density and temperature discontinuity. Such a jump in
-dynamical quantities play a crucial role in evolution of
+dynamical quantities plays a crucial role in the evolution of
 chemistry. For example, temperatures beyond few 1000\,K produced in the shocks could
 disassociate the molecules and can also lead to ionization if
-temperature reaches above 10$^{4}$\,K.
+the temperature becomes larger than 10$^{4}$\,K.
 %
@@
 
-For the reference run, the effect of shock in dynamical evolution of
-hydrogen fraction is presented in figure~\ref{fig:Hmolform}. The top
-panel of the figure shows number density of hydrogen in the jet. This
-hydrogen exists in three forms namely, molecular, atomic and
-ionized. The fraction of each of these forms are shown in bottom
-panels of figure~\ref{fig:Hmolform} at two representative regions in
-the jet marked with the arrow. The left bottom panel shows the
+For the reference run, the effect of the shock in the dynamical evolution of
+the hydrogen fraction is presented in figure~\ref{fig:Hmolform}. The top
+panel of the figure shows the hydrogen number density in the jet. 
+The fraction of all hydrogen forms are shown in bottom
+panels of figure~\ref{fig:Hmolform} along two representative regions in
+the jet marked with the arrows. The left bottom panel shows the
 vertical distribution of temperature, molecular and atomic fraction at the
@@
 knot with the medium raises that temperature to 1200\,K and
-accumulates the matter such the density in that region reaches up to
+accumulates the matter so that the density increases up to
 10$^{6}$ cm$^{-3}$. Behind the shock as the material cools, atoms
 combine together to form molecules as seen in the increase of fH2 from
-0.44 to 0.52. This rise in molecular fraction comes at an expense of
-reduction in atomic fraction from 0.56 to 0.48. Further away from the
-shock, these species tend to reach a quasi equilibrium as their
-fractions reach towards a value of 0.5. The ionized fraction is
+0.44 to 0.52. Further away from the
+shock, atomic and molecular hydrogen tend to reach a quasi equilibrium as their
+fractions reach a value of 0.5. The ionized fraction is
 extremely low in this region due to low temperatures. However at the
@@
 hydrogen species are destroyed, while ionized hydrogen shows an
-increase in its fraction as seen in the bottom right panel of
-figure~\ref{fig:Hmolform}. The peak in ionized fraction of 0.15
+increase in its fraction 
+(figure~\ref{fig:Hmolform}). The peak in ionized fraction of 0.15
 coincides with the peak in temperature profile as expected. The
@@
 
-In summary, the axi-symmetric jet flow with periodic knots 
-produce shocks of varied strengths giving rise to density, velocity and
-temperature distribution. Molecular cooling and chemistry also 
-allows us to evolve fractions of different hydrogen species along with the jet
-flow. These jet quantities are then post-processed with a radiative
-transfer code described in section~\ref{sec:radtrans} to obtain emission maps,
-spectra and PV diagrams.
+% In summary, the axi-symmetric jet flow with periodic knots 
+% produce shocks of varied strengths giving rise to density, velocity and
+% temperature distribution. Molecular cooling and chemistry also 
+% allows us to evolve fractions of different hydrogen species along with the jet
+% flow. These jet quantities are then post-processed with a radiative
+% transfer code described in section~\ref{sec:radtrans} to obtain emission maps,
+% spectra and PV diagrams.
 
@@
 spectra and position velocity diagrams from these data cubes. 
-Figure~\ref{empvspec90} shows all the possible outputs from the data
-cube for the J = 2-$>$1 transition for the reference run. 
+Figure~\ref{empvspec90} shows outputs from the data
+cube for SiO(2-1) in the reference run. 
 The top left panel in the figure shows the emission map for the jet
@@
 enhancement by cooling instability. The PV diagram shown in the top
-right panel is obtained along the jet as indicated by vertical magenta
-line. The position is shown in terms of pixels, where each pixel has a
-width of about 16\,AU. The channel numbers in the X-axis indicate
+right panel is obtained along the jet as indicated by the vertical magenta
+line in the left panel. The channel numbers in the X-axis indicate
 velocities. The whole velocity range of -20 km s$^{-1}$ to 20 km
@@
 maps. These features fade along the jet as the knots also disappear in
-the emission map. The region close to the bow shock as well gives
-indication of high velocity features which are seen as broad wings in
-the spectra. 
+the emission map. The region close to the bow shock also shows high
+velocity features.
 %
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/refrun_21_90_emspecpv.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/emspecpv_90.pdf}%{\figpath/refrun_21_90_emspecpv.png}
  \caption{Integrated emission map ({\it top left}), PV diagram ({\it top right}
-   and spectra ({\it bottom} for the
+   and spectra ({\it bottom}) for the
    2-$>$1 SiO transition for the reference run. 
@@
 The spectra at three different positions in the flow are shown in the
-bottom panel of figure~\ref{empvspec90}. These three positions are
-basically the two knots close to the base of the flow and region close
-to the bow shocks. They are marked by horizontal white dashed lines in
-the emission maps. The knot closer to the base is the brightest
-showing a peak intensity of 25\,K. As one moves along the jet the
+bottom panel of figure~\ref{empvspec90} (they are marked with blue
+crosses in top left panel). The knot closer to the base is the brightest
+showing a peak intensity of 25\,K. The
 intensity decreases and reaches to about 10\,K close to the bow shock.
-The line widths seen for this reference run with an angle of
-inclination of 90$^{\circ}$ are typically around 5-10 km s$^{-1}$.
+The line widths seen are typically around 5-10 km s$^{-1}$.
 These line widths increase substantially as the angle of inclination
-decreases. Figures~\ref{empvspec60} and \ref{empvspec45} show the
+decreases. Figure \ref{empvspec45} show the
 emission map, PV diagram and spectra for the same reference run but
-with angle of inclination of 60$^{\circ}$ and 45$^{\circ}$
-respectively. The spectra for low inclination angles are much broader
-and have lower peak intensities at the same three positions in the flow (shown by
-three white dashed lines). The line 
+with angle of inclination of 45$^{\circ}$
+respectively. The line 
 widths now are typically of the order of 20 km s$^{-1}$ and the peak
 intensity of the brightest knot is approximately 10\,K. 
-The PV diagrams in these runs are not longer symmetric, unlike the run
-with the jet in plane of the sky. Instead, they show a distinct {\it zig-zag}
+The PV diagrams in these runs are not longer symmetric. Instead, they show a distinct {\it zig-zag}
 pattern at each of the knots and region close to the bow shock.
 
+% \begin{figure}
+%  \includegraphics[width=1.\columnwidth]{\figpath/refrun_21_60_emspecpv.png}
+%  \caption{Same as figure~\ref{empvspec90} but with angle of
+%    inclination of $60^{\circ}$.} 
+% \label{empvspec60}
+% \end{figure}
+
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/refrun_21_60_emspecpv.png}
- \caption{Same as figure~\ref{empvspec90} but with angle of
-   inclination of $60^{\circ}$.} 
-\label{empvspec60}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/refrun_21_45_emspecpv.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/emspecpv_45.pdf}%{\figpath/refrun_21_45_emspecpv.png}
  \caption{Same as figure~\ref{empvspec90} but with angle of
@@
 
-%
-The predicted emission maps, spectra and PV diagrams are shown above to depend
-on the angle of inclination. In the next section, we focus on the
-dependence of these observational features on the 
-different fractional abundance profiles of SiO.
+% %
+% The predicted emission maps, spectra and PV diagrams are shown above to depend
+% on the angle of inclination. In the next section, we focus on the
+% dependence of these observational features on the 
+% different fractional abundance profiles of SiO.
 
@@
 \label{ssec:sioabunem}
-Input profiles in the radiative transfer code for the
-fractional abundance of SiO are a very modest approximation from 
-observed values (see sec~\ref{ssec:sioabun}). In
+The fractional abundance of SiO has been assumed to vary with shock velocity in
+a simplistic manner(see sec~\ref{ssec:sioabun}). In
 figure~\ref{fig:diffabunem}, we compare the maps for J = 2-$>$1
-emission for two different abundance profiles and ratio of jet to
-shock velocities. There is a striking difference with regards to
-emission from the internal knots in these images. All the internal
-knots show emission in the J=2-$>$1 line whilst using a top hat profile
-and accounting for shock speeds (i.e. $\delta < 1$). However, some of
+emission for two different abundance profiles and two different ratios of shock to
+jet velocities, $\delta$. There is a striking difference with regards to
+emission from the internal knots in these images. Using the top hat profile
+and accounting for shock speeds (i.e. $\delta < 1$) results in
+emission from  all the internal knots in the J=2-$>$1 line. However, some of
 these knots are not observed when using the same top-hat profile but
@@
 abundance profile. In particular, the case with $\delta$ = 1 only
-produce emission from the knot closest to the bow shock, while the internal
+produces emission from the knot closest to the bow shock, while the internal
 knots do not show any appreciable emission. Further, the emission from
@@
 a top-hat profile and $\delta < 1$. The peak emission and line widths at this knot
-are listed in table~\ref{tab:result2}
+are listed in table~\ref{tab:result2}.
 %
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/EM_gaussandth.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
  \caption{Variation of 2-$>$1 SiO emission for runs with molecular
@@
 different profiles (see
-~\ref{ssec:emspecpv}). Figure~\ref{fig:pvdiffabun} shows a zoomed
-version of the bottom four internal knots in form PV diagram for these
-different abundance profile. As expected, the signatures of knotty
-emission is missing for the case with gaussian profile with $\delta$ =
+~\ref{ssec:emspecpv}). Figure~\ref{fig:pvdiffabun} shows a zoomed in
+version of the bottom four internal knots in form of a PV diagram for these
+different abundance profiles. As expected, the signatures of knots 
+is missing for the case with gaussian profile with $\delta$ =
 1. Further, the wedges formed in panels 1 and 2 of the figure in
-general slightly more extended in position space as compared to ones
-formed in panel 4 of the same figure. This is indeed because of the
-discontinuous nature of top-hat abundance profile as the SiO is
+general are slightly more extended as compared to those
+formed in panel 4. This is indeed because of the
+discontinuous nature of the top-hat abundance profile as the SiO is
 enhanced to a maximum abundance for all velocities between 20 and 100
-km\,s$^{-1}$, which is not the case in a more continuos gaussian
+km\,s$^{-1}$, which is not the case in a more continuous gaussian
 distribution.
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/PV_gaussandth.png}
- \caption{Contour maps of position-velocity diagram for the internal
-   knots for 2-$>$1 SiO emission for runs with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance
+ \includegraphics[width=2.\columnwidth]{\figpath/diffabun_PV.pdf}%{\figpath/PV_gaussandth.png}
+ \caption{Position-velocity maps of SiO(2-1) for the internal
+   knots produced in the model with molecular
+   cooling, $\eta$ = 3, $\beta$ = 10 and different abundance
    profiles. The contours mark different levels of emission in Kelvins, viz.,
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/ALMAmaps3.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
  \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
    and (8-7).
-The heat map shows the 2-1 line intensity (in units of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line intensity and the green contours show the J=5-4 line intensity.
+The emission map shows the 5-4 line intensity (in units of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line intensity and the green contours show the J=2-1 line intensity.
 {\bf Right:} The PV diagram taken along the axis of the jet (in units of Jy/beam), showing the higher J transitions highlighting the knots of the jet and broad emission at the bow shock.
@@
 Further, we find SiO emission coming from velocities 
-of the order of 40-60 km\,s$^{-1}$ (see figs.~\ref{empvspec60} and
+of the order of 40-60 km\,s$^{-1}$ (see fig
 ~\ref{empvspec45}). Such a velocity range is typically associated with
@@
 similar to the pattern that we see in PV diagrams from
-our models (see figs.~\ref{empvspec60} and ~\ref{empvspec45}). 
+our models (see figs. \ref{empvspec45} and \ref{fig:almafig}). 
 All of the above striking similarities from observations of EHV gas
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/LineRatio_THDeq1.png}
- \caption{{\em{Top}} Line profiles in SiO J = 2-1, 5-4 and 8-7 at one
-   the inner knot for the molecular cooling run with $\eta$ = 3 and
-   $\beta$ = 10 for the reference run. The profiles are
+ \includegraphics[width=2.\columnwidth]{\figpath/singledish_new.pdf}%{\figpath/LineRatio_THDeq1.png}
+ \caption{{\em{Top}} Line profiles in SiO (2-1), (5-4) and (8-7) at one
+   the inner knots for the reference molecular cooling run with a top
+   hat abundance profile and $\delta = 1$. The profiles are
    obtained when the angle of inclination is 60$^{\circ}$ with respect

### 2013-10-24 PAPER/Paola_1/ms_ver2.tex
Added labels to molform figire

@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310_molform.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310_molform.pdf}
  \caption{Dependence of hydrogen fractions on the temperature at two
@@
 obtain from our radiative transfer calculations is associated with
-regions where shocked H$_{2}$ gas is present. A contour map of SiO
+regions slightly behind where the shocked H$_{2}$ gas is present
+as observed in case of L1157 molecular outflow
+\cite{Gueth:1998p14058}. A contour map of SiO
 emission obtained from the reference run is shown in
-figure~\ref{fig:ltconts}. Such a model can very well explain the
-shocked SiO velocity components observed in the L1157 molecular outflow \cite{Gueth:1998p14058}. 
-%
-
-Further, we find SiO emission coming from velocities 
+figure~\ref{fig:ltconts}. Further, we find SiO emission coming from velocities 
 of the order of 40-60 km\,s$^{-1}$ (see fig
-~\ref{empvspec45}). Such a velocity range is typically associated with
-EHV gas seen in the majority of the outflows (\citealt{Tafalla:2011p14051}). Additionally,
-the EHV peaks show a distinct sawtooth pattern in the PV diagram
-(\citealt{SantiagoGarcia:2009p13972}). Such a sawtooth pattern is very
-similar to the pattern that we see in PV diagrams from
-our models (see figs. \ref{empvspec45} and \ref{fig:almafig}). 
+~\ref{empvspec45}). Additionally, we see a distinct saw-tooth pattern
+in the PV diagrams from our models (see figs. \ref{empvspec45} and
+\ref{fig:almafig}). These predictions from our model very well
+resembles the characteristic features of EHV SiO emission 
+seen in the majority of the outflows \citep{SantiagoGarcia:2009p13972,
+  Tafalla:2011p14051, Arce:2013p14902}.
+%
+
 All of the above striking similarities from observations of EHV gas
@@
 to the idea that such an emission could arise due to shock interactions of
-internal knots in the flow. In the section below we further compare
-the line ratios and intensities from our results with single-dish
-measurements of typical outflows with EHV emission.
+internal knots in the flow.
 
@@
 1000\,K and H$_{2}$ number density $\sim$ 10$^{5}$-10$^{6}$
-cm$^{-3}$. They can also fit the observed fractional SiO abundance of
+cm$^{-3}$, assuming optically thin emission. 
+They can also fit the observed fractional SiO abundance of
 $\sim$ 10$^{-7}$ in these outflows. However, they fail to predict all
@@
 $\phi$ = 60$^{\circ}$ and convolved with a single dish beam of
-15\arcsec. Additionally, the predicted integrated
-intensities also lie within a factor of two from the values of L1448 bullets
-observed with JCMT and IRAM (Table 2 of \citealt{Nisini:2007p13128}  and
-table~\ref{tab:result2} of this work).
+15\arcsec to simulate observed integrated
+intensities of L1448 bullets observed with large beams from JCMT and
+IRAM. Intensities predicted from our model (see table~\ref{tab:result2}) lie within a factor of two
+from the observed values (Table 2 of \citealt{Nisini:2007p13128}).
 %
@@
 integrated emission for higher transitions with a peak in
-emission for J$_{\rm up}$ = 3. \cite{Nisini:2007p13128} found that
-their homogeneous slab model coupled with LVG radiative transfer, did
-not reproduce the observed line ratios SiO(8-7)/(5-4) and
-SiO(5-4)/(2-1) of HH212. Values $\approx$ 1 for both ratios have been
-found in for low mass assuming LTE regime \citep{Cabrit:2007p13804,
+emission for J$_{\rm up}$ = 3. These curves help tp predict the
+hydrogen number density and temperature in outflows. Physical
+conditions in outflows can also be studied by estimation of line ratios.
+Values $\approx$ 1 for line ratios SiO(8-7)/(5-4) and SiO(5-4)/(2-1) have been
+found in HH212 assuming LTE regime \citep{Cabrit:2007p13804,
   Lee:2008p13697} and also for molecular outflows from massive

### 2013-10-24 PAPER/Paola_1/ms_ver2.tex
added new hfrac figure

@@
 contributions to cooling from fixed fractions of other molecules like
-CO, OH etc. The jet is largely dominated by atomic
-and molecular hydrogen. Ionized hydrogen is mainly formed at the tip
-of the bow.The
-highest temperature of $\sim$ 50000\,K is attained in our flow at the
+CO, OH etc. Figure~\ref{fig:Hfracsim} shows the color composite image
+of various hydrogen fractions, (fHI (red), fH2 (green) and fHII
+(blue)), from the dynamical simulation with
+reference parameters. The jet beam is largely dominated by atomic
+hydrogen, while molecular hydrogen is seen to be formed in internal
+knots and region that is thermally instable. 
+Ionized hydrogen is mainly formed at the tip of the bow. 
+The highest temperature of $\sim$ 50000\,K is attained in our flow at the
 tip of the bow shock. While the temperature on the edges (i.e.,interface between
@@
 
-%\begin{figure*}
-% \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310.png}
-% \caption{Fraction of hydrogen species, temperature and mean molecular
-%    weight in the run with molecular
-%    cooling having $\eta$ = 3 and $\beta$ = 10.}
-%\label{fig:Hfracsim}
-%\end{figure*}
+\begin{figure}
+ \includegraphics[width=1.\columnwidth]{\figpath/hfracs_ref.pdf}
+ \caption{{\it{Left}} Color composite image of various hydrogen
+   fractions, fHI (red), fH$_{2}$ (green) and fHII (blue), for the
+   reference run. For better visualisation, the ionized hydrogen
+   fraction is enhanced by a factor of 100. The temperature of the jet
+ obtained from dynamical simulation is shown on the {\it{right}}.}
+\label{fig:Hfracsim}
+\end{figure}
 
@@
 They are : (1) The tip of the jet , (2) The edges of the jet and
-(3) intermediate knots. As the atomic jet propagates from the lower boundary 
+(3) intermediate knots. 
+As the atomic jet propagates from the lower boundary 
 into the cold molecular medium , it forms a strong shock resulting in
@@
 Values $\approx$ 1 for line ratios SiO(8-7)/(5-4) and SiO(5-4)/(2-1) have been
-found in HH212 assuming LTE regime \citep{Cabrit:2007p13804,
+found in HH212 \citep{Cabrit:2007p13804,
   Lee:2008p13697} and also for molecular outflows from massive
 young stellar object IRAS 17233-3606 (\citealt{Leurini:2013p13165}).
-These line ratios from the present
-non-LTE radiative transfer model are shown in the bottom left panel of
+The LVG modelling with optically thin approximation were unable to produce
+these line ratios. 
+In the non-LTE radiative transfer modeling, no assumption of optical
+depths or photon escape probablity are prescribed and line ratios are
+self consistently calculated and are shown in the bottom left panel of
 fig.~\ref{fig:lineratio}. Their values lie very close to unity as

### 2013-10-28 PAPER/Paola_1/ms_ver2.tex
Added the Physical Model in the paper

@@
 
-\newcommand{\rj}{R_{\rm jet}}
+\newcommand{\rj}{R$_{\rm jet}$}
 
@@
 Even with a myriad of such empirical evidences, the exact nature of
-moleular emission in outflows is not clear. For a complete understanding it is imperative
+molecular emission in outflows is not clear. For a complete understanding it is imperative
 to complement these observations with theoretical models. Many models
@@
 \subsection{Physical Model}
-We model the propagation of jet as it interacts with the molecular
-cloud core material at distances $\gtrsim$ 1000\,AU. 
+We model the propagation of an axi-symmetric jet
+in (r,z,$\phi$) cylindrical co-ordinates as it interacts with the
+ambient medium at distances $\gtrsim$ 1000\,AU. 
 At these distances from the central source, the downward pull of gravity plays a
-negligible role and the dynamics of the jet is primarily governed by magnetic fields.
-The total magnetic field in the jet is dominated by the toroidal
-component. This is because the poloidal field decays as $z^{-2}$ as
-compared to $z^{-1}$ for toroidal field to maintain the force balance
-($z$ is the vertical distance from the source). 
-The hoop stress due to pinch force from the toroidal magnetic fields maintains
-a highly collimated beam like structure for the jet.
-%
-
-The ambient medium with which the jet interacts primarily
-represents the molecular cloud core. The numerical domain is axi-symmetric
-and in (r,z,$\phi$) cylindrical co-ordinates. Its extent 20 $R_{\rm j}$ in the radial
-direction and 100
-$R_{\rm j}$ along the vertical axis ($R_{\rm j}$ being the radius of
-the jet). The domain of interest is about 3000\,AU away from the
-central source and extends up to 0.1\,pc.
-Numerically, it is resolved by an uniform grid with a domain of 200$\times$1000 cells in the radial and vertical directions.
-For simplicity, we choose this medium
+negligible role on the dynamics of the jet. The ambient medium with which the jet interacts primarily
+represents the molecular cloud core. We study the interaction within a
+radial extent of 20\,\rj\,\, and a vertical extent of 100\,\rj\,\,(\rj\,\, being the radius of
+the jet). Numerically, it is resolved by an uniform grid with a domain
+of 200$\times$1000 cells in the radial and vertical directions. For simplicity, we choose this medium
 to be unmagnetized and non-turbulent. The density in the ambient
 medium varies with vertical height $z$ as, $\rho_{\rm amb}\sim (\rho_0/z^{2})$
-which is consistent with observations \citep{Keto:2010p15549, Caselli:2011p13935}. The value of
+which is consistent with observations \citep{Keto:2010p15549,
+  Caselli:2011p13935}. The value of
 $\rho_0$ depends upon the density contrast, $\eta$, between the jet and
@@
 \rm cm^{-3}$. The pressure in the ambient molecular medium is
-set so to maintain a constant temperature of 50\,K. 
-%
-
-The jet enters into the medium through a nozzle of radius $R_{\rm jet}$
-from the lower boundary (z = 0). The jet density is fixed to
-be $10^{5} \rm cm^{-3}$ and it has a radius of $2.5\times10^{15} \rm cm \sim
-167\,AU$. The jet is injected into the domain with a typical 
-velocity of $v_{\rm jet,0}$ = 100 km/s as is the case for most low mass stellar jets
-especially the low velocity component. The constant jet velocity is
-superimposed with periodic pulsation of the form,
-\begin{equation}
-v_{\rm jet} = v_{\rm jet,0}(1.0 + A\,sin(2.0\pi t/T_{\rm p})),
-\end{equation}
-where the amplitude A is 0.25 and time period $T_{\rm p} = 70$
-years. The pressure at the surface of the jet is $10^{-10} \rm
-dyne\,\,cm^{-2}$ corresponding to a temperature of $T_{\rm jet} \sim
-4\times10^{3}\,K$. Inside the jet beam, a radial variation of thermal
+set so to maintain a constant temperature of 50\,K. Note, dense
+molecular cores through which young outflows propagate
+have lower temperatures ranging from 10-20\,K
+(\citealt{Rathborne:2007p15753}). As the jet is hypersonic in both
+cases, runs with lower ambient temperature of 10\,K do not show any 
+appreciable changes in final dynamical structure of the jet.
+
+%
+
+The jet enters into the medium through a nozzle of radius \rj\,\,
+from the lower boundary (z = 0). Optically visible jets from T-Tauri
+stars are just about spatially resolved for the nearest
+star forming regions i.e, their radii are of order
+100\,AU at a few thousand AU from the source \citep{Ray:2012p15733}.
+These jets have mass outflow rates of 10$^{-7}$ M$_{\odot}$
+yr$^{-1}$ \citep{Dougados:2010p15774}. Younger and 
+embedded jets in their Class 0 phase have
+outflow rates about 10-100 times higher than 
+corresponding jets from optically visible young stars
+\citep{Bally:2007p2340, Dionatos:2009p15670, Ray:2012p15733}. Also,
+these optically obscure jets are relatively slower with velocities
+ranging around 100 km\,s$^{-1}$ \citep{Bally:2007p2340} as compared to
+optically visible flows with velocities up to 500 km s$^{-1}$
+\citep[e.g,][]{Mundt:1987p15799}.
+For the present model, the jet is injected into the domain with a 
+velocity of $v_{\rm jet,0}$ = 100 km/s and set the jet density to
+$10^{5} \rm cm^{-3}$ within a radius of $2.5\times10^{15} \rm
+cm$. With these choices we obtain a mass outflow rate of 10$^{-6}$
+M$_{\odot}$ yr$^{-1}$. Most of the young outflows 
+show variable features possibly due to variable accretion rates
+or internal shocks inside the jet \cite{Bachiller:1996p4692}.
+We replicate such variability by superimposing the constant jet
+velocity with sinusoidal pulsation with an amplitude of 25
+km\,s$^{-1}$ with a periodicity of 70\,yr such that the dense knots
+are separated by a distance of $\sim$\,1000\,AU.
+
+Thermal and magnetic properties of jets from young stars are difficult
+to constraint because of their large variation not only within the jet
+but also in its surroundings. Forbidden line emissions from
+HH objects indicate excitation temperatures of the order
+of $\leq$10$^{4}$\,K \citep{Podio:2006p15921,
+  Bally:2007p2340}. However, in case of 
+young jets the temperature is
+considerably lower (i.e, by an order of magnitude) than found in jets from Class I/II
+sources as derived from various atomic lines in molecular jets from
+L-1448C and HH211 \citep{Dionatos:2009p15670,Dionatos:2010p15968}.  
+The temperature at the jet
+nozzle for our model has been set to 1000\,K. Thus, the jet is
+over-pressured by 60 times as compared with the ambient medium,
+assuming $\eta$ = 3.0. Inside the jet beam, a radial variation of thermal
 and magnetic pressure is adopted to maintain a magneto-static
-equilibrium. We adopt the
-same radial profiles used by \cite{Stone:2000p2650} for all our runs. 
-Based on these profiles, the toroidal magnetic field is assumed to be
-zero at the axis and achieves a maximum at some radius, $r_{\rm m}$
-inside the jet. The maximum value, $B_{\phi,\rm m}$, depends on the
-plasma $\beta$ which is kept fixed for all our runs to be at a value
-of 10.0. This corresponds to the maximum field strength, $B_{\phi,\rm m}$ $\sim
-16\mu\,G$.
-
+equilibrium for all our runs. 
+Based on these profiles (adopted from \citealt{Stone:2000p2650}), 
+the toroidal magnetic field is assumed to be
+zero at the axis and achieves a maximum at radius, $r_{\rm m} \sim 0.8$\rj\,\,
+inside the jet. Though measuring magnetic fields in
+most jets is not possible via unpolarized nebular lines, in some special
+cases like HH 34S and HH 111V, it has been measured to be 10 and 30
+$\mu\,G$ respectively \citep{Morse:1993p15960}. Considering the
+dependence of such weak magnetic fields on density and radial distance in velocity-variable flows, 
+\cite{Hartigan:2007p15768} has shown that at large distances of the 
+star these fields only play a minor role in the dynamics. Thus for all
+our runs the value of magnetic field strength, $B_{\phi}(r_{\rm m})$ 
+is set to be $\sim 37\mu\,G$.
 %
@@
 \label{sec:chem}
-\subsection{Molecular Cooling}
+\subsection{Molecular Chemistry}
 \label{ssec:molcool}
@@
 from negligible but fixed fraction of metals ($Z \sim 10^{-4}$).
-The chemical evolution of molecular, atomic and ionized hydrogen is governed by
-equations listed in Table~\ref{tab:chemeq}. 
-%
-
+%
 Numerically, the
@@
 step using sub-stepping and adaptive Runge-Kutta methods.
-In doing so, the code tracks the formation and destruction of
-fractions of three species viz., X(HI), X($H_{2}$)
-and X(HII) based on the temperature dependent reaction rates specified
-in the table along with their references and shown in the left panel
-of figure~\ref{ssec:molcool}. The figure clearly shows that below
-1000\,K the formation of molecular hydrogen dominates over other
-chemical processes, whereas for hotter gas there exists a competition
-of different chemical processes elucidating the complex chemical interplay.
-The fractions of various hydrogen species are then used to update the cooling
-function $\Lambda(\rho,T,{\bf{X}})$ to consistently derive the
-temperature for next advection step. For low temperatures, we also
-take into account contribution to cooling rates from molecules like
-CO, whose abundance with respect to $n_{\rm H2}$ is fixed to
-10$^{-5}$. For each of the other molecules contributing to the cooling function (like OH, H$_{2}$O and atomic OI)
-the abundance is fixed to $5\times10^{-6}$. The contribution from
-these molecules is only important when temperature is $<$ 100\,K as seen
-in the right panel of figure~\ref{ssec:molcool}.
-
-\begin{figure*}
- \includegraphics[width=1\columnwidth]{\figpath/H2ReactionRates_paper.png}
+The formation and destruction of
+fractions (denoted by \textbf{X}$_{i}$ in eq.~\ref{chemevol}) of three species, viz., fHI, f$H_{2}$
+and fHII are tracked by the code based on the temperature dependent reaction rates
+whose coefficients are specified 
+in the Table~\ref{tab:chemeq} along with their literature references.
+
+%and shown in the left panel
+%of figure~\ref{fig:tempvar}. The figure clearly shows that below
+%1000\,K, the rate coefficient of radiative recombination is the
+%most dominant. However at these temperatures, very few
+%electrons and ionized hydrogen are present in the initial ambient
+%medium, thus the corresponding rate for this reaction is not that
+%significant initially. At low temperatures corresponding to the molecular
+%cores, the rate of formation of molecular hydrogen dominates over other
+%chemical processes, whereas for gas temperatures $>$ 1000\,K there exists a competition
+%of different chemical processes elucidating the complex chemical interplay.
+
+\begin{figure}
+% \includegraphics[width=1\columnwidth]{\figpath/H2ReactionRates_paper.png}
  \includegraphics[width=1\columnwidth]{\figpath/H2CoolingFuncs_full.png}
- \caption{Variation of $H_2$ chemistry reaction rates, $k_{i}$ and cooling
+ \caption{Variation of the cooling
    function $\Lambda(n,T,{\bf{X}})$ with temperature for the initial
-   state (see Sect.~\ref{ssec:molcool})}
+   state}
 \label{fig:tempvar}
-\end{figure*}
+\end{figure}
 
@@
 
-\subsection{Additional Cooling Prescriptions}
-For comparison, we also ran simulations of axisymmetric MHD jets
+\subsection{Cooling Prescriptions}
+%
+Figure~\ref{fig:tempvar} shows the variation
+of the cooling function, $\Lambda(\rho,T,{\bf{X}})$, with gas
+temperature assuming conditions of initial ambient density. 
+Various processes that contribute to the cooling function in our model
+are listed in the figure. The formulations of these contributions
+are adopted from \citep[][and references therein]{Smith:2003p9985, OSullivan:2009p10078}.
+For low temperatures, we also 
+take into account contribution to cooling function from molecules like
+CO, whose abundance with respect to $n_{\rm H2}$ is fixed to
+10$^{-5}$. For each of the other molecules contributing to the cooling function (like OH, H$_{2}$O and atomic OI)
+the abundance is fixed to $5\times10^{-6}$. The contribution from
+these molecules is only important when temperature is $<$ 100\,K as seen
+in figure~\ref{fig:tempvar}. A substantial contribution to the cooling
+function, between T = 100\,K and 3000\,K, 
+comes from the vibrational and rotational transitions of
+molecular hydrogen. Whereas, for temperatures above 3000\,K the
+cooling is mainly via H$_{2}$ disassociation. The total curve for the
+whole temperature range obtained in our runs is shown in black.
+The fact that the initial ambient medium is largely molecular, cooling is also dominated by
+molecular processes. In our reference model (see ~\ref{ssec:refrun}), 
+we update this curve at each time step based on the fraction of
+various hydrogen species. Thus during the evolution, even
+contributions from collisional ionizations and excitations also become
+important in regions dominated by atomic and ionized hydrogen.
+%
+
+We also ran simulations of axisymmetric MHD jets
 with optically thin cooling prescriptions already existing in the public
@@
 simplified non-equilibrium (or atomic) cooling and tabulated
-cooling. Further we compare these radiative runs with an adiabatic jet 
-to cover a wide spectrum of jet thermodynamics. 
-%
-
-In case of power law cooling, the radiative losses denoted by
-$\Lambda(\rho,T,{\bf X})$ are proportional to
-$\rho^{2}T^{\alpha}$, with $\alpha$ = 0.5 representing bremsstrahlung
-cooling. The loss term is independent of the fraction of various
-species ${\bf X}$, therefore the fluid density $\rho$ is assumed to be
-all hydrogen for further processing of emission maps. Similarly, 
-for tabulated cooling prescription, the radiative losses are estimated
-based on a fixed fraction of various species. However, the contribution
-for each species is a complex function of density and temperature. The
-variation of cooling function $\Lambda$ with temperature is shown in
-the right panel of figure~\ref{fig:tempvar}. 
-The formulations which depend on the fractions of each species and gas
-temperature of these variations are mainly adopted from the appendix of \cite{Smith:2003p9985}. 
-The fractions of all hydrogen species are kept fixed to their initial values, while that
-of CO, OH, H$_{2}$O and OI are same as that used for molecular cooling
-described above. The total cooling curve shown as the black solid line
-in the figure~\ref{fig:tempvar} is used for the case of tabulated
-cooling. For the atomic cooling, we distinguish between neutral
-and ionized gas by defining $f_{\rm n} = n_{\rm HI}/n_{\rm H}$ and
-evolve it using,
-\begin{equation}
-\frac{\partial f_{\rm n}}{\partial t} + {\bf{v}}\cdot\nabla f_{\rm n} =
-n_{\rm e} [-(c_{\rm r} + c_{\rm i})f_{\rm n} + c_{\rm r}]
-\end{equation}
-where, $n_{\rm e}$ is the number of electrons that come from ionized
-hydrogen and a very small fixed fraction of metals, c$_{\rm r}$ and c$_{\rm i}$ are the recombination and ionization rate coefficients that depend on the temperature T. In
-addition to losses by collisional ionization and radiative
-recombination, additional contribution to radiative losses come from various atomic line emissions from C,N,O,Mg,Si,Fe etc.
-
-%
-
-While these additional cooling prescriptions may not be a complete description of
+cooling. While these additional cooling prescriptions may not be a complete description of
 the chemical and radiative processes in early outflows, they are ideal
 to compare the results obtained from the more consistent newly added molecular
-cooling. Such a comparison is presented in section~\ref{ssec:coolres}.
+cooling. In addition, we compare these radiative runs with an adiabatic jet 
+to cover a wide spectrum of jet thermodynamics. 
+Such a comparison is presented in section~\ref{ssec:coolres}.
 
@@
 \label{eq:shockjetvel}
-v_{\rm s} = \frac{v_{\rm j}}{1 + \eta^{-0.5}} = v_{\rm j}\delta
+v_{\rm s} = \frac{v_{\rm jet}}{1 + \eta^{-0.5}} = v_{\rm jet}\delta
 \end{equation}
-where v$_{\rm s}$ is the velocity of dense plug and v$_{\rm j}$ is the
+where v$_{\rm s}$ is the velocity of dense plug and v$_{\rm jet}$ is the
 jet velocity. A comparative view of using such velocity corrections and
@@
 value of $\eta$ of the order of unity indicating similar densities in
-the jet and the medium. 
-The magnetic field strength is kept to be fixed using $\beta = 10.0$,
-for all our runs. Table~\ref{tab:result1} lists all the runs with
+the jet and the medium. Table~\ref{tab:result1} lists all the runs with
 varying $\eta$ and cooling prescriptions, along with the peak
@@
 \hline
-adi1010 & Nil (Adiabatic) & 10 & 2.91 & $>$40 & 0.25 & 40.0 \\
-pow1010 & Power law & 10 & 0.64 & 8.0 & 0.02 & 10.0\\
-atm1010 & Atomic & 10 & 2.04 & 36.0 & 0.58 & 38.0 \\
-atm210 & Atomic & 2 & 3.21 & 18.0 & 0.64 & 20.0 \\
-tab1010 & Tabulated & 10 & 0.75 & 11.0 & 0.09 & 10.0 \\
-tab210 & Tabulated & 2 & 2.89 & 8.0 & 1.0 & 9.0 \\
-mol1010 & Molecular & 10 & 1.10 & 10.0 & 0.1 & 11.0 \\
-mol310 & Molecular & 3 & 3.3 & 14.0 & 0.66 & 12.0\\
+adi10 & Nil (Adiabatic) & 10 & 2.91 & $>$40 & 0.25 & 40.0 \\
+pow10 & Power law & 10 & 0.64 & 8.0 & 0.02 & 10.0\\
+atm10 & Atomic & 10 & 2.04 & 36.0 & 0.58 & 38.0 \\
+atm2 & Atomic & 2 & 3.21 & 18.0 & 0.64 & 20.0 \\
+tab10 & Tabulated & 10 & 0.75 & 11.0 & 0.09 & 10.0 \\
+tab2 & Tabulated & 2 & 2.89 & 8.0 & 1.0 & 9.0 \\
+mol10 & Molecular & 10 & 1.10 & 10.0 & 0.1 & 11.0 \\
+mol3 & Molecular & 3 & 3.3 & 14.0 & 0.66 & 12.0\\
 \hline
@@
 discussed with other runs.
-%
 
 The reference run in our calculation has density contrast $\eta$ = 3
-with a plasma beta $\beta$ = 10. The jet for this run is 89\% atomic,
-10\% molecular and 1\% ionized to begin with. This jet enters the
+with the initial jet density of 10$^{5}$ cm$^{-3}$. This jet enters the
 ambient medium with a velocity of v$_{\rm jet,0}$ = 100 km
-s$^{-1}$. The cooling in the jet is
-via molecular cooling prescription, whereby the hydrogen fractions are
-evolved with cooling contributions for abundant molecules like CO, OH
+s$^{-1}$ which is further superimposed by sinusoidal perturbations to
+replicate dense knots. The maximum value of toroidal magnetic field is
+set to be 37$\mu\,G$ at the base of the jet.
+\cite{Dionatos:2009p15670} have detected atomic lines
+towards a molecular jet from L1448-C indicating a presence of embedded
+atomic jet at low excitation. Additionally, they also detect pure
+rotational transitions from H$_{2}$ indicating presence of molecules
+along with the atomic jet. Line ratios from this source indicate that the
+atomic gas is characterized by an an ionization fraction of 1\%,
+which is considerably less as compared to ionization fraction of
+10-20\% measured in optical jets \cite{Bacciotti:1995p15970}.
+Initial jet composition is prescribed
+be 89\% atomic, 10\% molecular and 1\% ionized, in qualitative
+agreement of above observational results. 
+%
+
+The cooling in the reference jet is via molecular cooling prescription, whereby
+the initial hydrogen fractions are evolved using appropriate rate equations and with cooling 
+contributions for abundant molecules like CO, OH
 etc. The final state (at time $\sim$ 1000 yr), i.e, density, temperature and velocity obtained from this 
-run are given in input to the radiative transfer code to obtain the observational features
+run are given as inputs to the radiative transfer code to obtain the observational features
 corresponding to SiO molecule. 
@@
 run is stationary and the jet is in the plane of the sky ($\phi =
-90^{\circ}$). A gaussian profile is used for the fractional abundance
-of SiO.
-%TheSiO fractional abundance used is that obtained
-%from equation~\ref{eq:fracSio}. 
-Further, the shock velocity which determines
+90^{\circ}$). A gaussian profile without any upper cutoff is used for the fractional abundance
+of SiO. Further, the shock velocity which determines
 the fractional abundance, v$_{\rm s}$, is less than the jet velocity in the
@@
  \caption{Jet Volume Density for different cooling modes with
-   $\eta$ = 10 and $\beta$ = 10.}
+   $\eta$ = 10.}
 \label{fig:coolcmpdyn}
@@
  \caption{A plot of the integrated SiO J=2-$>$1 emission from 5 models, 
-each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
+each using a different method to calculate cooling and all with $\eta$=10.}
 \label{fig:coolcmpsio} 
 \end{figure*}
-
-% \subsection{Effects of changing $\eta$ and $\beta$}
-% figure nos. 2 -- Simulated images describing lengths, collimation and
-% emission for lower eta more stronger. 
-% \begin{figure*}
-%  \includegraphics[width=2.\columnwidth]{\figpath/jetplt2_diffetabeta.png}
-%  \caption{Jet Volume Density for atomic cooling with $\eta$ = 10 but $\beta$ = 1 and
-%    10 and that with tabulated cooling with $\beta$ = 10 but $\eta$ = 2
-%    and 10.}
-% \label{grid}
-% \end{figure*}
 
@@
  \caption{Variation of 2-$>$1 SiO emission for runs with molecular
-   cooling having $\eta$ = 3 and $\beta$ = 10 and different abundance profiles.}
+   cooling having different abundance profiles.}
 \label{fig:diffabunem}
@@
  \caption{Position-velocity maps of SiO(2-1) for the internal
-   knots produced in the model with molecular
-   cooling, $\eta$ = 3, $\beta$ = 10 and different abundance
+   knots produced in the model with reference parameters and different abundance
    profiles. The contours mark different levels of emission in Kelvins, viz.,
@@
 integrated emission for higher transitions with a peak in
-emission for J$_{\rm up}$ = 3. These curves help tp predict the
+emission for J$_{\rm up}$ = 3. These curves helps to to predict the
 hydrogen number density and temperature in outflows. Physical
@@
 young stellar object IRAS 17233-3606 (\citealt{Leurini:2013p13165}).
-The LVG modelling with optically thin approximation were unable to produce
+The local velocity gradient (LVG) slab modeling with optically thin approximation were unable to produce
 these line ratios. 
-In the non-LTE radiative transfer modeling, no assumption of optical
-depths or photon escape probablity are prescribed and line ratios are
+In the non-LTE (non local thermodynamic equilibrium) radiative transfer modeling, no assumption of optical
+depths or photon escape probability are prescribed and line ratios are
 self consistently calculated and are shown in the bottom left panel of

### 2013-10-28 PAPER/Paola_1/ms_ver2.tex
Added discussion on molecular abundance

@@
 take into account contribution to cooling function from molecules like
-CO, whose abundance with respect to $n_{\rm H2}$ is fixed to
-10$^{-5}$. For each of the other molecules contributing to the cooling function (like OH, H$_{2}$O and atomic OI)
-the abundance is fixed to $5\times10^{-6}$. The contribution from
-these molecules is only important when temperature is $<$ 100\,K as seen
-in figure~\ref{fig:tempvar}. A substantial contribution to the cooling
+CO, whose abundance with respect to $n_{\rm H}$ is fixed to a
+value of 10$^{-5}$ as measured in dense cores like L1554 \refer. 
+For each of the other molecules contributing to the cooling function (like OH, H$_{2}$O and atomic OI)
+the abundance is fixed to values of $5\times10^{-6}$. Note, the
+uncertain abundance values are rather arbitrary for these molecules. 
+However, their contribution is only important when temperature is $<$
+100\,K as seen in figure~\ref{fig:tempvar}. As the internal shocks, where most
+of the molecular hydrogen is produced maintain temperatures higher
+than 100\,K and densities $\sim$10$^{6}$ cm$^{-3}$, cooling due to these molecules do not
+play a significant role even if the arbitrary abundance is increased
+by a factor of 10 \citep{Smith:2003p9985}. Instead, a substantial contribution to the cooling
 function, between T = 100\,K and 3000\,K, 
 comes from the vibrational and rotational transitions of
-molecular hydrogen. Whereas, for temperatures above 3000\,K the
+molecular hydrogen plays and a very crucial role during the jet
+evolution. Whereas, for temperatures above 3000\,K the
 cooling is mainly via H$_{2}$ disassociation. The total curve for the

### 2013-10-29 PAPER/Paola_1/ms_ver2.tex
a few small re-wordings

@@
 
-\newcommand{\figurepath}{.}
+\newcommand{\figurepath}{./PFIGS}
 
@@
 
-\newcommand{\figpath}{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/}
+%\newcommand{\figpath}{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/}
+\newcommand{\figpath}{./PFIGS/}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 decade \citep[see reviews by][]{Bachiller:1996p4692, Beuther:2002p1149, Arce:2007p798,
-Tafalla:2011p14051}. Advances in millimeter interferometer 
+Tafalla:2011p14051}. Advances in millimeter interferometery 
 allow observations of these outflows with spatial resolution of
@@
 ranging around 100 km\,s$^{-1}$ \citep{Bally:2007p2340} as compared to
-optically visible flows with velocities up to 500 km s$^{-1}$
+optically visible flows with velocities up to 500 km$\,$s$^{-1}$
 \citep[e.g,][]{Mundt:1987p15799}.
@@
 profiles based on limited empirical evidences. The most simple among
-them is the top hat profile in which the SiO abundance is a low value of
-10$^{-12}$ below 20 km s$^{-1}$ and above 100 km s$^{-1}$ and a
-maximum value of 10$^{-6}$ between these two velocities.
-In order to get rid of a discontinuous change of abundance, we also
+these are the step profile, where the abundance of SiO is 10$^{-12}$ below 20 km$\,$s$^{-1}$ and 10$^{-6}$ at greater velocities, and the top hat profile, in which the SiO abundance is the same as the step profile but returns to 10$^{-12}$ at velocities greater than 100 km$\,$s$^{-1}$.
+In order to get rid of discontinuous changes in abundance, we also
 prescribe a gaussian such that the peak SiO abundance of 10$^{-6}$ is at
 60\,km\,s$^{-1}$, while the value of n(SiO)/n(H$_{2}$) falls below
-10$^{-9}$ at 20 and 100 km s$^{-1}$
+10$^{-9}$ at 20 and 100 km$\,$s$^{-1}$
 \citep[e.g.,][also see
@@
 \hline\hline
-&&& $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] & $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] \\
+&&& $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km$\,$s$^{-1}$] & $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km$\,$s$^{-1}$] \\
 \hline
@@
 Profile & $\delta$ = v$_{\rm s}$/v$_{\rm jet}$ & $\int T_{\rm MB}dV$
-[K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$]\\ 
+[K-km\,s$^{-1}$] & $\Delta$v [km$\,$s$^{-1}$]\\ 
 \hline\hline
@@
 line in the left panel. The channel numbers in the X-axis indicate
-velocities. The whole velocity range of -20 km s$^{-1}$ to 20 km
+velocities. The whole velocity range of -20 km$\,$s$^{-1}$ to 20 km
 s$^{-1}$ is uniformly divided into 80 channels. High velocity features
@@
 intensity decreases and reaches to about 10\,K close to the bow shock.
-The line widths seen are typically around 5-10 km s$^{-1}$.
+The line widths seen are typically around 5-10 km$\,$s$^{-1}$.
 These line widths increase substantially as the angle of inclination
@@
 respectively. The line 
-widths now are typically of the order of 20 km s$^{-1}$ and the peak
+widths now are typically of the order of 20 km$\,$s$^{-1}$ and the peak
 intensity of the brightest knot is approximately 10\,K. 
@@
 young stellar object IRAS 17233-3606 (\citealt{Leurini:2013p13165}).
-The local velocity gradient (LVG) slab modeling with optically thin approximation were unable to produce
-these line ratios. 
-In the non-LTE (non local thermodynamic equilibrium) radiative transfer modeling, no assumption of optical
-depths or photon escape probability are prescribed and line ratios are
-self consistently calculated and are shown in the bottom left panel of
-fig.~\ref{fig:lineratio}. Their values lie very close to unity as
-indicated from observations. 
-%Further, we have estimated the optical
-%depth in regions emitting SiO and find them to be optically thick with
-%an optical depth $\tau \sim 10$. Thus, assuming optically thin SiO emission
-%from molecular outflows especially from shocked dense knots would
-%only provide upper limits. 
+Radiative transfer modelling using a homogenous slab of material and large velocity gradient (LVG) photon escape probability have been unable to reproduce these line ratios. 
+In the 3D non-LTE (non local thermodynamic equilibrium) radiative transfer modeling presented in this work, no assumption of optical depths or photon escape probability are prescribed and line ratios are
+self consistently calculated. The line ratios are shown in the bottom left panel of
+fig.~\ref{fig:lineratio}. Their values lie very close to unity, in agreement with observations. 
 In summary, the shape, ratio and peak intensity of the spectra
@@
 The pulsating jet propagation model presented here have shock speeds
-reaching up to 100 km\,s$^{-1}$. We have used two
+reaching up to 100 km\,s$^{-1}$. We have used four
 simplified SiO abundance profiles as a function of shock
@@
 with complex chemistry is beyond the scope of this paper 
-as this could imply to include dust grains and sputtering 
+as this could require including dust grains and sputtering 
 as well as grain-grain collisions (i.e. an MHD multi-fluid approach).  
@@
 mixed with the ices on the dust grain surfaces (see discussion in \citealt{Schilke:1997p14140}) . In such a scenario, 
-shocks with speeds below 20 km s$^{-1}$ might inject a significant
+shocks with speeds below 20 km$\,$s$^{-1}$ might inject a significant
 amount of silicon into the gas phase from the mantles, without 
@@
 of episodic radiative jet propagating 
-with a typical speed of 100 km s$^{-1}$ into a cold, non-magnetized ambient
+with a typical speed of 100 km$\,$s$^{-1}$ into a cold, non-magnetized ambient
 molecular medium with a density gradient. The jet dynamical quantities are evolved in conjunction

### 2013-10-29 PAPER/Paola_1/ms_ver2.tex
Final comments of Paola

--- 2013-10-28 PAPER/Paola_1/ms_ver2.tex
@@
 maximum value of 10$^{-6}$ between these two velocities.
+Shock velocities $>$ 100 km s$^{-1}$ can lead to the 
+ionisation of hydrogen and thereby effectively reduce the number
+of collision centers for SiO resulting in a weaker emission. 
+However, we also consider a step function dependence of SiO abundance
+on shock velocity to incorporate cases where we allow for reformation
+of atomic and molecular species.
 In order to get rid of a discontinuous change of abundance, we also
@@
 60\,km\,s$^{-1}$, while the value of n(SiO)/n(H$_{2}$) falls below
-10$^{-9}$ at 20 and 100 km s$^{-1}$
-\citep[e.g.,][also see
-section~\ref{sec:discussion}]{Lefloch:1998p13983}. 
+10$^{-9}$ at 20 and 100 km s$^{-1}$. Such a huge variation in SiO
+abundance may indeed be the case in regions where SiO is seen
+in widespread \citep[e.g.,][also see section~\ref{sec:discussion}]
+{Lefloch:1998p13983}. Also along with a Gaussian profile, we consider
+the case where we extent the abundance of 10$^{-6}$ beyond 60 km\,s$^{-1}$. 
 These functional dependences of SiO
-abundance on shock velocity are show in figure~\ref{abun}.  
+abundance on shock velocity are shown in figure~\ref{abun}.  
 In addition to this, if the temperature at the point is greater than
@@
 \item Emission from internal knots do depend on the chosen profile of
-  the abundance. On one extreme where all the internal knots 
-  is the top-hat profile with $\delta <$ 1, whereas, no emission in
+  the abundance. On one extreme where all the internal knots emit SiO  
+  with a step profile with $\delta =$ 1 and a top-hat profile with
+  $\delta < 1$, whereas, no emission in
   seen in knots when a gaussian profile with $\delta$ = 1 is used. For
-  the remaining two possibilities, we observe that emission mainly
+  the remaining cases, we observe that emission mainly
   comes from knots close to the base of the flow and the condensation
@@
 that explains the origin of EHV emission seen in SiO from 
-the inner regions of young molecular outflows.
+the inner regions of young molecular outflows. The unique combination
+of axisymmetric jet propogation model with molecular cooling and
+non-LTE radiative transfer calculations can sucessfully predict most
+of the observed properties of SiO emission from young molecular
+outflows from Class 0 stages. This model provides an excellent
+template to compare current ALMA obervations and can also predict
+signatures of thermal instabilities which can be tested with upcoming
+ALMA observations. In future, we would like to extent our
+model to full three dimensions and evolve the jet for longer time
+scales to explore slow velocity component, precession and 
+slew of other instabilities. Additionally, we would also like to have
+a better handle on SiO abundance not only from observations but also
+by including dust micro-physics in our model.
 

### 2013-10-29 PAPER/Paola_1/ms_ver2.tex
Minor final corrections print to read 1

@@
 The final state of the jet obtained for each cooling model is then
-post-processed using a radiative line transfer code to
+given as an input to a radiative line transfer code to
 obtain SiO emission maps, spectra and position-velocity (PV) digrams.}
@@
 ranging around 100 km\,s$^{-1}$ \citep{Bally:2007p2340} as compared to
-optically visible flows with velocities up to 500 km s$^{-1}$
+optically visible flows with velocities up to 500\,km\,s$^{-1}$
 \citep[e.g,][]{Mundt:1987p15799}.
@@
   profiles for dynamical simulation with molecular cooling and
-  $\eta=3$. The integrated intensity of the brightest lobe assuming a single disk
+  $\eta=3$. The integrated intensity assuming a single disk
   observation with a beam width of $15\,\arcsec$ is listed along with the
@@
 
-% In summary, the axi-symmetric jet flow with periodic knots 
-% produce shocks of varied strengths giving rise to density, velocity and
-% temperature distribution. Molecular cooling and chemistry also 
-% allows us to evolve fractions of different hydrogen species along with the jet
-% flow. These jet quantities are then post-processed with a radiative
-% transfer code described in section~\ref{sec:radtrans} to obtain emission maps,
-% spectra and PV diagrams.
-
 \subsection{Emission Maps, Spectra and PV diagrams}
@@
 figure~\ref{fig:diffabunem}, we compare the maps for J = 2-$>$1
-emission for two different abundance profiles and two different ratios of shock to
+emission at an inclination angle of 90$^{\circ}$ for three different abundance profiles and two different ratios of shock to
 jet velocities, $\delta$. There is a striking difference with regards to
@@
 produces emission from the knot closest to the bow shock, while the internal
-knots do not show any appreciable emission. Further, the emission from
+knots do not show any appreciable emission. The step function and
+gaussian step (not shown) with $delta = 1$ produces very similar
+features as that of the top hat profile with $\delta < 1$.
+Further, the emission from
 the knot closer to the bow shock varies considerably with different
@@
 is missing for the case with gaussian profile with $\delta$ =
-1. Further, the wedges formed in panels 1 and 2 of the figure in
+1. Further, the wedges formed in panels 1, 2 and 5 of the figure in
 general are slightly more extended as compared to those
@@
 \item Emission maps obtained from our reference run with molecular
-  cooling show a distinctive outflow lobe like structure. The
+  cooling show a distinctive collimated outflow structure. The
   physical regions responsible of SiO emission in such early outflows
@@
 the inner regions of young molecular outflows. The unique combination
-of axisymmetric jet propogation model with molecular cooling and
-non-LTE radiative transfer calculations can sucessfully predict most
+of axisymmetric jet propagation model with molecular cooling and
+non-LTE radiative transfer calculations can successfully predict most
 of the observed properties of SiO emission from young molecular
 outflows from Class 0 stages. This model provides an excellent
-template to compare current ALMA obervations and can also predict
+template to compare current ALMA observations and can also predict
 signatures of thermal instabilities which can be tested with upcoming

### 2013-10-29 PAPER/Paola_1/ms_ver2.tex
Paper draft 2 submitted to Paola

@@
      early molecular outflows shows bright emission coming from young
-     internal knots and primary bow shock due to thermal
+     internal knots and bow shock due to thermal
      instability. Our multi-line modeling of SiO supports
@@
 For the present model, the jet is injected into the domain with a 
-velocity of $v_{\rm jet,0}$ = 100 km/s and set the jet density to
-$10^{5} \rm cm^{-3}$ within a radius of $2.5\times10^{15} \rm
+velocity of $v_{\rm jet,0}$ = 100 km/s and the jet density is set to
+$10^{5} \rm cm^{-3}$ within a jet radius of $2.5\times10^{15} \rm
 cm$. With these choices we obtain a mass outflow rate of 10$^{-6}$
@@
 show variable features possibly due to variable accretion rates
-or internal shocks inside the jet \cite{Bachiller:1996p4692}.
+or internal shocks inside the jet \citep[e.g.][]{Bachiller:1996p4692}.
 We replicate such variability by superimposing the constant jet
@@
 and magnetic pressure is adopted to maintain a magneto-static
-equilibrium for all our runs. 
-Based on these profiles (adopted from \citealt{Stone:2000p2650}), 
+equilibrium for all our runs \citealt{Stone:2000p2650}. 
+Based on these profiles, 
 the toroidal magnetic field is assumed to be
@@
 dependence of such weak magnetic fields on density and radial distance in velocity-variable flows, 
-\cite{Hartigan:2007p15768} has shown that at large distances of the 
+\cite{Hartigan:2007p15768} has shown that at large distances from the 
 star these fields only play a minor role in the dynamics. Thus for all
@@
    function $\Lambda(n,T,{\bf{X}})$ with temperature for the initial
-   state}
+   state.}
 \label{fig:tempvar}
@@
 CO, whose abundance with respect to $n_{\rm H}$ is fixed to a
-value of 10$^{-5}$ as measured in dense cores like L1554 \refer. 
+value of 10$^{-5}$ as measured in dense cores like L1544 \citep{Keto:2010p15549}. 
 For each of the other molecules contributing to the cooling function (like OH, H$_{2}$O and atomic OI)
@@
 same as the shock velocity. Considering that there is a density
-contrast in the simulation setup, this assumption is will
+contrast in the simulation setup, this assumption will
 overestimate the shock velocity. We also
@@
 viz., the dynamical numerical simulations and the
-radiative transfer code. For each part we have used certain parameters
+radiative transfer analysis. For each part we have used certain parameters
 and the effect of changing them is studied. Ideally all these parameters should come from observational
@@
 of shock velocity v$_{\rm s}$ and physical jet velocity v$_{\rm
-  j}$ such that its value depends on density contrast $\eta$
+  jet}$ such that its value depends on density contrast $\eta$
 (see Eq.~\ref{eq:shockjetvel}).
@@
 which is considerably less as compared to ionization fraction of
-10-20\% measured in optical jets \cite{Bacciotti:1995p15970}.
+10-20\% measured in optical jets \citep{Bacciotti:1995p15970}.
 Initial jet composition is prescribed
@@
 for the molecular jet the cooling terms evolve with jet dynamics as the fraction of
-various hydrogen species change over time. Whilst the terms remain fixed to initial values, shown in the right panel of fig~\ref{fig:tempvar}, for the jet with tabulated
-cooling. Additionally, the material at the primary bow shock for the jet
+various hydrogen species change over time. Whilst the terms remain fixed to initial values, shown in the fig~\ref{fig:tempvar}, for the jet with tabulated
+cooling. Additionally, the material at the bow shock for the jet
 with tabulated and molecular cooling condenses forming dense knots. 
@@
 The dynamical states for each of this cooling prescriptions are then 
-given as inputs the radiative transfer code to obtain integrated J = 2-$>$1 SiO emission
+given as inputs to the radiative transfer code to obtain integrated J = 2-$>$1 SiO emission
 maps shown in figure~\ref{fig:coolcmpsio}. The differences in dynamical
@@
 to base of the flow. Additionally, features in the shell at Z $\sim$
-60, 80 also show evidence of faint emission. In case of the jet with
+60, 75 also show evidence of faint emission. In case of the jet with
 power-law cooling the emission mostly arises from the
@@
 Also in these outflows, strong emission arises from the
-condensation formed at the primary bow shock due to thermal
+condensation formed at the bow shock due to thermal
 instability. 
@@
 dynamics of MHD jet propagation in particular the thickness and
-structure of the primary bow shock. These dynamical differences are
+structure of the bow shock. These dynamical differences are
 also reflected in SiO emission maps. The molecular cooling in our
@@
 right panel is obtained along the jet as indicated by the vertical magenta
-line in the left panel. The channel numbers in the X-axis indicate
-velocities. The whole velocity range of -20 km s$^{-1}$ to 20 km
-s$^{-1}$ is uniformly divided into 80 channels. High velocity features
+line in the left panel. The velocities are show along the X-axis. High velocity features
 are clearly seen in regions corresponding to the knots in the emission
@@
    The jet is assumed to be in the plane of sky implying an angle of
-   inclination of $90^{\circ}$. The vertical {\it magenta dashed} line represents the cut for the PV digram and where this line is intersected by the horizontal
- {\it white dashed} lines marks the positions from which the spectra are taken.} 
+   inclination of $90^{\circ}$. The vertical {\it magenta dashed} line
+   represents the cut for the PV digram and green crosses marks the positions from which the spectra are taken.} 
 \label{empvspec90}
@@
 The spectra at three different positions in the flow are shown in the
-bottom panel of figure~\ref{empvspec90} (they are marked with blue
+bottom panel of figure~\ref{empvspec90} (they are marked with green
 crosses in top left panel). The knot closer to the base is the brightest
@@
 respectively. The line 
-widths now are typically of the order of 20 km s$^{-1}$ and the peak
-intensity of the brightest knot is approximately 10\,K. 
+widths now are typically of the order of 20 km s$^{-1}$. 
 The PV diagrams in these runs are not longer symmetric. Instead, they show a distinct {\it zig-zag}
@@
 The fractional abundance of SiO has been assumed to vary with shock velocity in
-a simplistic manner(see sec~\ref{ssec:sioabun}). In
+a simplistic manner (see sec~\ref{ssec:sioabun}). In
 figure~\ref{fig:diffabunem}, we compare the maps for J = 2-$>$1
@@
 knots do not show any appreciable emission. The step function and
-gaussian step (not shown) with $delta = 1$ produces very similar
+gaussian step (not shown) with $\delta = 1$ produces very similar
 features as that of the top hat profile with $\delta < 1$.
@@
 using a value of $\delta <$ 1. This process is further validated by
-the lack of emission from internal knots in panel 4 of the
+the lack of emission from internal knots in panel 3 of the
 fig~\ref{fig:diffabunem}. 
@@
  \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
-   and (8-7).
-The emission map shows the 5-4 line intensity (in units of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line intensity and the green contours show the J=2-1 line intensity.
-{\bf Right:} The PV diagram taken along the axis of the jet (in units of Jy/beam), showing the higher J transitions highlighting the knots of the jet and broad emission at the bow shock.
-In both panels the ticks on the color bar represent the contour levels.}
+   and (8-7). The emission map shows the 5-4 line intensity (in units
+   of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line
+   intensity and the green contours show the J=2-1 line intensity. The
+   jet is inclined at an angle of 60$^{\circ}${\bf Right:} The PV
+   diagram taken along the axis of the jet for the 5-4 line (in units
+   of Jy/beam), showing the higher J transitions highlighting the
+   knots of the jet and broad emission at the bow shock. 
+   In both panels the ticks on the color bar represent the different contour levels.}
 \label{fig:almafig}
@@
   Hirano:2006p14411}. Further, the evolved post-shock gas near the
-primary bow shock also show bright emission for these high J transitions. 
+bow shock also show bright emission for these high J transitions. 
 This gas is linked to the thermal instability associated with
 radiative jets (see section~\ref{ssec:coolres}). The sub-structure seen close to the
-primary bow shock with high resolution does give a sense of clumpiness
+bow shock with high resolution does give a sense of clumpiness
 in the flow backing the suggestions to explain clumpy SiO emission has
@@
    emission convolved with a 2\arcsec beam obtained using parameters of the reference run. The contour colors represent different intenties in Kelvins, i.e,
-   30.0({\it red}), 10.0({\it green}), 5.0({\it blue}), 1.0({\it
+   20.0({\it red}), 10.0({\it green}), 5.0({\it blue}), 1.0({\it
      magenta}), 0.5({\it cyan}), 0.1({\it black}).} 
@@
 these line ratios. 
-In the non-LTE (non local thermodynamic equilibrium) radiative transfer modeling, no assumption of optical
+In the present non-LTE radiative transfer modeling, no assumption of optical
 depths or photon escape probability are prescribed and line ratios are
@@
 %
-We have presented a model able to explain the spectral characteristics
+We have presented a model that is able to explain the spectral characteristics
 of the SiO EHV component seen
@@
 The pulsating jet propagation model presented here have shock speeds
-reaching up to 100 km\,s$^{-1}$. We have used two
+reaching up to 100 km\,s$^{-1}$. We have used few
 simplified SiO abundance profiles as a function of shock
@@
 flow and that from the more evolved gas near the
-primary bow shock. To ascertain this fact in more details, one would
-need to track the primary bow shock for 10$^{4}$ years
+bow shock. To ascertain this fact in more details, one would
+need to track the bow shock for 10$^{4}$ years
 using a larger simulation box and possibly with adaptive gridding 
@@
   efficient mode of cooling does reduce the size of the cocoon and results
-  in a more narrow jet. In addition, the primary bow shock structure
+  in a more narrow jet. In addition, the bow shock structure
   differs with various cooling modes. Also, with realistic cooling
@@
   comes from knots close to the base of the flow and the condensation
-  formed at the primary shock due to thermal instability.
+  formed at the bow shock due to thermal instability.
 \item Predicted ALMA maps also show characteristic features that are
@@
 of axisymmetric jet propagation model with molecular cooling and
-non-LTE radiative transfer calculations can successfully predict most
+non-LTE radiative transfer calculations can successfully reproduce most
 of the observed properties of SiO emission from young molecular
-outflows from Class 0 stages. This model provides an excellent
+outflows. This model provides an excellent
 template to compare current ALMA observations and can also predict
 signatures of thermal instabilities which can be tested with upcoming
-ALMA observations. In future, we would like to extent our
-model to full three dimensions and evolve the jet for longer time
-scales to explore slow velocity component, precession and 
-slew of other instabilities. Additionally, we would also like to have
+ALMA observations. In future, we would like to extend our
+model to full three dimensions with adaptive mesh refinement
+and evolve the jet for longer time scales to explore slow velocity 
+component, precession and slew of other instabilities. Additionally, we would also like to have
 a better handle on SiO abundance not only from observations but also
@@
 %\section*{Acknowledgments}
-
+%BV would like to thank everyone.
+
+%\newpage
 \bibliographystyle{mn2e}

### 2013-11-26 PAPER/Paola_1/ms_ver2.tex
Added appendix to the paper to discuss the shock velocities

@@
 
+\appendix
+\section{Working surfaces and shocks}
+In this section we describe the mathematical derivation of estimating
+the speed of the working surface of the internal knot and shock speeds
+associated with it. We will follow the derivation as given in
+\citep{Raga:1990p16416,Raga:1992p16392}. Fig.~\ref{fig:interknot} shows a cartoon
+representation of a single internal knot formed in the jet. 
+The density and velocity upstream of the internal shock are
+$\rho_{1}$ and $u_{1}$, while, the downstream values are $\rho_{2}$
+and $u_{2}$ respectively. Note the velocities u$_1$ and u$_2$ are measured
+in a stationary frame of reference of the star. The velocity of the working surface is
+denoted by $v$, can be derived from the ram pressure balance between the upstream and
+downstream flow,
+\begin{equation}
+\rho_1 (u_1 - v)^{2} = \rho_2 (v - u_2)^{2}.
+\label{eq:ramPbal}
+\end{equation}
+This gives us the expression for $v$ as, 
+\begin{equation}
+v = \frac{u_1 + \zeta u_2}{1 + \zeta},
+\label{eq:velws}
+\end{equation} 
+where, $$\zeta = \sqrt{\frac{\rho_{2}}{\rho_1}}$$.
+
+\begin{figure}
+\includegraphics[width=1\columnwidth]{\figpath/Internalknot.pdf}
+\caption{Schematic diagram showing the structure of the internal
+  working surface. The faster upstream material with velocity u$_1$
+  catches the slower downstream material with velocity u$_2$ forming a
+two shock structure (u$_2 >$ v $>$ u$_1$). The in-between gas is squeezed out sideways
+forming the cocoon.}
+\label{fig:interknot}
+\end{figure}
+
+The parameter $\zeta$ is obtained in principle from the two
+dimensional snapshot of the jet density. In case of bow shock, the
+downstream medium is the stationary ambient medium (u$_2$ = 0), thus,
+eq.~\ref{eq:velws} will reduce to eq~\ref{eq:shockjetvel}.
+However for the internal knots, the variation of density and
+velocity for the reference run is shown in fig.~\ref{fig:1dvelrho}.
+As can be clearly seen, the value of $\zeta \approx$ 1 for most of the
+internal knots seen in our simulations. Thus, the velocity of the
+working surface simplifies to, 
+\begin{equation}
+v = \frac{u_1 + u_2}{2}.
+\label{eq:velwssimple}
+\end{equation}
+
+Additionally, the shock velocity (i.e, the velocity of the pre-shock
+flow with respect to the velocity of the working surface) of the
+upstream and downstream facing shocks have the same velocity given by \cite{Raga:1990p16416},
+\begin{equation}
+w = \frac{u_2 - u_1}{2} = 0.5\Delta u.
+\label{eq:shkvelws}
+\end{equation}
+
+\begin{figure}
+\includegraphics[width=1\columnwidth]{\figpath/jet_rhovel.pdf}
+\caption{Variation of jet velocity (blue) and density (red) as a
+  function of height close to the axis of the flow. The inset on the
+  bottom left of the figure shows a zoomed variation of velocity and
+  clearly marks the peak to peak difference between the upstream and
+  downstream components.}
+\label{fig:1dvelrho}
+\end{figure}
+
+The difference in the pre- and post-discontinuity velocities, $\Delta
+u$ is marked clearly in the fig.~\ref{fig:1dvelrho}. Typically, the
+difference in velocity values for our reference runs lie around 15-40 km s$^{-1}$. Thus, the
+shock velocity $w$ lies around 10-20 km s$^{-1}$. Similar values are
+also obtained for jets like HH 34 by \cite{Raga:1992p16392}.
+
+The variation of SiO abundance used for the present model is rather
+obtained from empirical values. In case of L1448, \cite{MartinPintado:1992p14309}
+have shown that for extreme velocities (obtained from shift in the
+spectra) of -40 to -50 km\,s$^{-1}$, the SiO abundance could be as
+large as $6\times10^{-7}$, while, it slightly reduces to
+$2\times10^{-7}$ for the velocity range of -60 to -50
+km\,s$^{-1}$. For the same source, typical {\em{shock}} (or working
+surface) velocities of the {\em{molecular bullets}} are estimated to
+lie around 80-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.
+\\
+{\color{red}
+WE HAVE TWO OPTIONS:\\ 
+1. Since the there is a empirical evidence with bulk gas motion. We
+can use just the jet velocity obtained from simulations.\\
+OR\\
+2. We can try to connect the working surface velocities from
+\cite{Dutrey:1997p11185} to abundance obtained by
+\cite{MartinPintado:1992p14309} and there by use the velocity of the
+working surface as an independent variable on the X axis of the
+abundance plot.
+}
+
 %\newpage

### 2013-11-26 PAPER/Paola_1/ms_ver2.tex
Added another section in Appendix on value of Gamma

@@
 spectra) of -40 to -50 km\,s$^{-1}$, the SiO abundance could be as
-large as $6\times10^{-7}$, while, it slightly reduces to
-$2\times10^{-7}$ for the velocity range of -60 to -50
+large as $6\times10^{-7}$, while, it slightly increases to
+$2\times10^{-6}$ for the velocity range of -60 to -50
 km\,s$^{-1}$. For the same source, typical {\em{shock}} (or working
@@
 
+\section{Treatment of Adiabatic Index $\gamma$}
+In dealing with a gas chemistry network which can have both monatomic and diatomic
+species, one is immediately presented with the issue of how to treat the adiabatic
+index, $\gamma$, of the gas, which directly influences the equation of
+state, eq.~\ref{EOS}, and thus the behaviour of the gas.
+In standard hydrodynamical codes the gas is generally
+assumed to be a monatomic ideal gas, with $\gamma$ = 5/3. 
+A diatomic gas, such as H$_{2}$, on the other hand, has a value of $\gamma$
+= 1.4 at low temperatures, decreasing to below 1.3
+at higher temperatures as the vibrational modes of the hydrogen molecule become
+excited. Thus, the value of $\gamma$ for a gas containing a mixture of atomic and
+molecular hydrogen requires a temperature-dependent calculation of the $\gamma$
+value for H$_2$ and a weighting of the values for the atomic and molecular components
+according to their abundance. \cite{Yoshida:2006p13376} have suggested
+a prescription of an effective $\gamma$ which takes into account the
+corresponding weights of each chemical species and is given by,
+\begin{equation}
+\frac{1}{\gamma_{\rm eff} - 1} = \frac{1}{\mu}\left[\sum_{i}\frac{X_{i}}{A_{i}}\frac{1}{(\gamma_{i} - 1)}\right]^{-1},
+\label{eq:gammaeff}
+\end{equation}
+where, i is the index for each specie and $\mu$ is the mean molecular
+weight. The mass fraction is added in the above equation following the
+correction suggested in \cite{OSullivan:2009p10078}.
+Additionally, the temperature dependence for example in case of
+H$_{2}$ molecule can be obtained using \cite{landau:1980},
+\begin{equation}
+\frac{1}{\gamma_{H_{2}} - 1} = \frac{1}{2}\left[ 5 +
+  2x^{2}\frac{e^{x}}{(e^{x} - 1)^{2}}\right],
+\label{eq:gammaH2}
+\end{equation}
+where the last term with  x = 6100 $K$/T accounts for the vibrational
+degree of freedom, with T being the gas temperature.
+%
+
+However, for such an implementation in large scale simulations one must first
+consider its cost, effectiveness, and even correctness. Although such
+a method would indeed yield a more correct $\gamma$ value for the gas
+mixture in conditions where the rotational and vibrational modes have
+had enough time to reach the level of excitation corresponding to
+the temperature of the gas, in cases where the gas has just been
+shocked, the method would produce an incorrect $\gamma$ value. 
+This is because the gas that passes through shock gets rapidly heated, 
+but this energy goes predominantly into the translational degrees of
+freedom of the gas. It is only with time that energy goes into the rotational and
+vibrational degrees of freedom of the gas through collisions. 
+\cite{Flower:2003p11236} maintains that therefore the adiabatic index of
+the post-shock gas has close to the ideal monatomic value of 5/3, 
+and that in order to calculate correctly its evolution as the gas 
+adjusts one would have to model the rotational and vibrational 
+levels of the hydrogen molecules in a time-dependent manner.
+%
+
+For large-scale simulations present here it is more practical to use
+the the standard value of 5/3 which is correct for the post-shock 
+and predominantly atomic parts of the flow but incorrect for the
+equilibrated parts of the flow with a significant fraction of molecular matter.
+Since in this case, as the shock regions and their effect on the molecular hydrogen content of 
+the ambient gas are of primary importance here, we opt for the more
+relevant, and also simpler, policy of keeping the normal $\gamma$
+value of 5/3 for our simulations.
+
 %\newpage

### 2013-12-09 PAPER/Paola_2/ms_ver3.tex
Added new version stage 0

--- 2013-11-26 PAPER/Paola_1/ms_ver2.tex
@@
 \definecolor{orange}{rgb}{1,0.5,0}
-\usepackage[colorlinks=True,citecolor=orange,urlcolor=blue,linkcolor=red]{hyperref}
+%\usepackage[colorlinks=True,citecolor=orange,urlcolor=blue,linkcolor=red]{hyperref}
 
@@
      the line intensities, spectra and PV diagrams obtained from our
-     model are very similar to that observed in case of outflows with
+     model are very similar to those observed in case of outflows with
      EHV emission. In addition, the Atacama Large Millimeter Array
@@
 during the later evolutionary stages (\citealt{Vaidya:2011p8992}). 
-Typically, these jets are few parsec in size long and can be divided into
+Typically, these jets are a few parsec in size long and can be divided into
 three length-scale domains, viz. source and disk scales (1-10$^{2}\,$AU),
@@
 decade \citep[see reviews by][]{Bachiller:1996p4692, Beuther:2002p1149, Arce:2007p798,
-Tafalla:2011p14051}. Advances in millimeter interferometer 
-allow observations of these outflows with spatial resolution of
+Tafalla:2011p14051}. Advances in millimeter interferometers 
+allow observations of these outflows with spatial resolution of a
 few arc seconds. A large number of studies observing young
@@
 of young molecular outflows usually observed with higher line
-transitions of CO and SiO (for e.g. in L1577:
+transitions of CO and SiO (e.g. in L1577:
 \citealt{Gueth:1998p14058}, in HH300: \citealt{Arce:2001p14064}). These knots show their signatures
@@
 observed in these outflows are signatures of rotation and
-precision (for e.g., in DG Tau: \citealt{Bacciotti:2002p2084}).
-%
-
-Even with a myriad of such empirical evidences, the exact nature of
+precession (for e.g., in DG Tau: \citealt{Bacciotti:2002p2084}).
+%
+
+Despite this large amount of data available, the exact nature of
 molecular emission in outflows is not clear. For a complete understanding it is imperative
@@
 outflows. Among them the two main models are that of wide-angled wind
-driven \cite{Shu:1991p14071} and jet driven outflow
-\cite{Canto:1991p14123}. 
+driven \citep{Shu:1991p14071} and jet driven outflow
+\citep{Canto:1991p14123}. 
 The most popular among them is the jet driven model as wind
@@
 The final state of the jet obtained for each cooling model is then
-given as a input to a non-LTE line radiative transfer code
+given as input to a non-LTE line radiative transfer code
 to obtain emission maps, spectra and PV digrams. These emission maps
@@
 \end{equation}
+The value of $\gamma$ is related to the degree of freedom for a
+mixture of gas and thus depends on the composition and temperature.
+We have adopted a constant value of 5/3 for the adiabatic index and
+have described its consequences in the appendix (see ~\ref{sec:treatgamma}).
 
@@
 stars are just about spatially resolved for the nearest
-star forming regions i.e, their radii are of order
+star forming regions i.e, their radii are of the order of
 100\,AU at a few thousand AU from the source \citep{Ray:2012p15733}.
@@
 cm$. With these choices we obtain a mass outflow rate of 10$^{-6}$
-M$_{\odot}$ yr$^{-1}$. Most of the young outflows 
+M$_{\odot}$ yr$^{-1}$, consistent with young jets. Most of the young outflows 
 show variable features possibly due to variable accretion rates
@@
 and magnetic pressure is adopted to maintain a magneto-static
-equilibrium for all our runs \citealt{Stone:2000p2650}. 
+equilibrium for all our runs (\citealt{Stone:2000p2650}). 
 Based on these profiles, 
@@
 the dynamical times, implying that the radiative cooling plays a vital
-role in dynamics. In order to study such outflows it is necessary to evolve
+role in their dynamics. In order to study such outflows it is necessary to evolve
 the dynamics in conjunction with full molecular chemistry and
@@
 non-homogenous parts of the equations~\ref{encons1} and \ref{chemevol} 
-are are solved separately from the advection step
+are solved separately from the advection step
 using operator splitting. Further, the rate equations are evolved at each advection time
@@
   \includegraphics[width=1.\columnwidth]{\figpath/diffabun_profnew.pdf}%{\figpath/diffabunprof1.png}
-  \caption{The different fractional SiO abundances as a function of
-    shock velocity, v$_{\rm s}$.}
+  \caption{{\bf{CHANGEFIG}} The different fractional SiO abundances as a function of
+    jet velocity, v$_{\rm jet}$.}
   \label{abun}
@@
 collisions exists, their focus is mainly on weaker shocks
-\citep{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800}. 
+\citep{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800, VanLoo:2013p16573}. 
 The pulsating jet propagation model presented here have shock speeds
@@
 \appendix
-\section{Working surfaces and shocks}
-In this section we describe the mathematical derivation of estimating
-the speed of the working surface of the internal knot and shock speeds
-associated with it. We will follow the derivation as given in
-\citep{Raga:1990p16416,Raga:1992p16392}. Fig.~\ref{fig:interknot} shows a cartoon
-representation of a single internal knot formed in the jet. 
-The density and velocity upstream of the internal shock are
-$\rho_{1}$ and $u_{1}$, while, the downstream values are $\rho_{2}$
-and $u_{2}$ respectively. Note the velocities u$_1$ and u$_2$ are measured
-in a stationary frame of reference of the star. The velocity of the working surface is
-denoted by $v$, can be derived from the ram pressure balance between the upstream and
-downstream flow,
-\begin{equation}
-\rho_1 (u_1 - v)^{2} = \rho_2 (v - u_2)^{2}.
-\label{eq:ramPbal}
-\end{equation}
-This gives us the expression for $v$ as, 
-\begin{equation}
-v = \frac{u_1 + \zeta u_2}{1 + \zeta},
-\label{eq:velws}
-\end{equation} 
-where, $$\zeta = \sqrt{\frac{\rho_{2}}{\rho_1}}$$.
-
-\begin{figure}
-\includegraphics[width=1\columnwidth]{\figpath/Internalknot.pdf}
-\caption{Schematic diagram showing the structure of the internal
-  working surface. The faster upstream material with velocity u$_1$
-  catches the slower downstream material with velocity u$_2$ forming a
-two shock structure (u$_2 >$ v $>$ u$_1$). The in-between gas is squeezed out sideways
-forming the cocoon.}
-\label{fig:interknot}
-\end{figure}
-
-The parameter $\zeta$ is obtained in principle from the two
-dimensional snapshot of the jet density. In case of bow shock, the
-downstream medium is the stationary ambient medium (u$_2$ = 0), thus,
-eq.~\ref{eq:velws} will reduce to eq~\ref{eq:shockjetvel}.
-However for the internal knots, the variation of density and
-velocity for the reference run is shown in fig.~\ref{fig:1dvelrho}.
-As can be clearly seen, the value of $\zeta \approx$ 1 for most of the
-internal knots seen in our simulations. Thus, the velocity of the
-working surface simplifies to, 
-\begin{equation}
-v = \frac{u_1 + u_2}{2}.
-\label{eq:velwssimple}
-\end{equation}
-
-Additionally, the shock velocity (i.e, the velocity of the pre-shock
-flow with respect to the velocity of the working surface) of the
-upstream and downstream facing shocks have the same velocity given by \cite{Raga:1990p16416},
-\begin{equation}
-w = \frac{u_2 - u_1}{2} = 0.5\Delta u.
-\label{eq:shkvelws}
-\end{equation}
-
-\begin{figure}
-\includegraphics[width=1\columnwidth]{\figpath/jet_rhovel.pdf}
-\caption{Variation of jet velocity (blue) and density (red) as a
-  function of height close to the axis of the flow. The inset on the
-  bottom left of the figure shows a zoomed variation of velocity and
-  clearly marks the peak to peak difference between the upstream and
-  downstream components.}
-\label{fig:1dvelrho}
-\end{figure}
-
-The difference in the pre- and post-discontinuity velocities, $\Delta
-u$ is marked clearly in the fig.~\ref{fig:1dvelrho}. Typically, the
-difference in velocity values for our reference runs lie around 15-40 km s$^{-1}$. Thus, the
-shock velocity $w$ lies around 10-20 km s$^{-1}$. Similar values are
-also obtained for jets like HH 34 by \cite{Raga:1992p16392}.
-
-The variation of SiO abundance used for the present model is rather
-obtained from empirical values. In case of L1448, \cite{MartinPintado:1992p14309}
-have shown that for extreme velocities (obtained from shift in the
-spectra) of -40 to -50 km\,s$^{-1}$, the SiO abundance could be as
-large as $6\times10^{-7}$, while, it slightly increases to
-$2\times10^{-6}$ for the velocity range of -60 to -50
-km\,s$^{-1}$. For the same source, typical {\em{shock}} (or working
-surface) velocities of the {\em{molecular bullets}} are estimated to
-lie around 80-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.
-\\
-{\color{red}
-WE HAVE TWO OPTIONS:\\ 
-1. Since the there is a empirical evidence with bulk gas motion. We
-can use just the jet velocity obtained from simulations.\\
-OR\\
-2. We can try to connect the working surface velocities from
-\cite{Dutrey:1997p11185} to abundance obtained by
-\cite{MartinPintado:1992p14309} and there by use the velocity of the
-working surface as an independent variable on the X axis of the
-abundance plot.
-}
 
 \section{Treatment of Adiabatic Index $\gamma$}
+\label{sec:treatgamma}
 In dealing with a gas chemistry network which can have both monatomic and diatomic
@@
 
-%\newpage
+\section{Working surfaces and shocks}
+\label{sec:worksurface}
+In this section we describe the mathematical derivation of estimating
+the speed of the working surface of the internal knot and shock speeds
+associated with it. We will follow the derivation as given in
+\citep{Raga:1990p16416,Raga:1992p16392}. Fig.~\ref{fig:interknot} shows a cartoon
+representation of a single internal knot formed in the jet. 
+The density and velocity upstream of the internal shock are
+$\rho_{1}$ and $u_{1}$, while, the downstream values are $\rho_{2}$
+and $u_{2}$ respectively. Note the velocities u$_1$ and u$_2$ are measured
+in a stationary frame of reference of the star. The velocity of the working surface is
+denoted by $v$, can be derived from the ram pressure balance between the upstream and
+downstream flow,
+\begin{equation}
+\rho_1 (u_1 - v)^{2} = \rho_2 (v - u_2)^{2}.
+\label{eq:ramPbal}
+\end{equation}
+This gives us the expression for $v$ as, 
+\begin{equation}
+v = \frac{u_1 + \zeta u_2}{1 + \zeta},
+\label{eq:velws}
+\end{equation} 
+where, $$\zeta = \sqrt{\frac{\rho_{2}}{\rho_1}}$$.
+
+\begin{figure}
+\includegraphics[width=1\columnwidth]{\figpath/Internalknot.pdf}
+\caption{Schematic diagram showing the structure of the internal
+  working surface. The faster upstream material with velocity u$_1$
+  catches the slower downstream material with velocity u$_2$ forming a
+two shock structure (u$_2 >$ v $>$ u$_1$). The in-between gas is squeezed out sideways
+forming the cocoon.}
+\label{fig:interknot}
+\end{figure}
+
+The parameter $\zeta$ is obtained in principle from the two
+dimensional snapshot of the jet density. In case of bow shock, the
+downstream medium is the stationary ambient medium (u$_2$ = 0), thus,
+eq.~\ref{eq:velws} will reduce to eq~\ref{eq:shockjetvel}.
+However for the internal knots, the variation of density and
+velocity for the reference run is shown in fig.~\ref{fig:1dvelrho}.
+As can be clearly seen, the value of $\zeta \approx$ 1 for most of the
+internal knots seen in our simulations. Thus, the velocity of the
+working surface simplifies to, 
+\begin{equation}
+v = \frac{u_1 + u_2}{2}.
+\label{eq:velwssimple}
+\end{equation}
+
+Additionally, the shock velocity (i.e, the velocity of the pre-shock
+flow with respect to the velocity of the working surface) of the
+upstream and downstream facing shocks have the same velocity given by \cite{Raga:1990p16416},
+\begin{equation}
+w = \frac{u_2 - u_1}{2} = 0.5\Delta u.
+\label{eq:shkvelws}
+\end{equation}
+
+\begin{figure}
+\includegraphics[width=1\columnwidth]{\figpath/jet_rhovel.pdf}
+\caption{Variation of jet velocity (blue) and density (red) as a
+  function of height close to the axis of the flow. The inset on the
+  bottom left of the figure shows a zoomed variation of velocity and
+  clearly marks the peak to peak difference between the upstream and
+  downstream components.}
+\label{fig:1dvelrho}
+\end{figure}
+
+The difference in the pre- and post-discontinuity velocities, $\Delta
+u$ is marked clearly in the fig.~\ref{fig:1dvelrho}. Typically, the
+difference in velocity values for our reference runs lie around 15-40 km s$^{-1}$. Thus, the
+shock velocity $w$ lies around 10-20 km s$^{-1}$. Similar values are
+also obtained for jets like HH 34 by \cite{Raga:1992p16392}.
+
+The variation of SiO abundance used for the present model is rather
+obtained from empirical values. In case of L1448, \cite{MartinPintado:1992p14309}
+have shown that for extreme velocities (obtained from shift in the
+spectra) of -40 to -50 km\,s$^{-1}$, the SiO abundance could be as
+large as $6\times10^{-7}$, while, it slightly increases to
+$2\times10^{-6}$ for the velocity range of -60 to -50
+km\,s$^{-1}$. For the same source, typical {\em{shock}} (or working
+surface) velocities of the {\em{molecular bullets}} are estimated to
+lie around 80-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.
+\\
+{\color{red}
+WE HAVE TWO OPTIONS:\\ 
+1. Since the there is a empirical evidence with bulk gas motion. We
+can use just the jet velocity obtained from simulations.\\
+OR\\
+2. We can try to connect the working surface velocities from
+\cite{Dutrey:1997p11185} to abundance obtained by
+\cite{MartinPintado:1992p14309} and there by use the velocity of the
+working surface as an independent variable on the X axis of the
+abundance plot.
+}
+
+\newpage
 \bibliographystyle{mn2e}

### 2013-12-14 PAPER/Paola_2/ms_ver3.tex
New figures added and corrected in the text

@@
 
-\newcommand{\figurepath}{.}
+\newcommand{\figurepath}{../PFIGS/}
 
@@
 
-\newcommand{\figpath}{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/}
+%\newcommand{\figpath}{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/}
+
+\newcommand{\figpath}{/home/phybva/SiOJets_New/PAPER/NEWFIGS}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 envelope scales ($10^{2} - 10^{5}$\,AU) and parent cloud scales
-($10^{5} - 10^{6}$\,AU) (\refer : Frank et. al, 2013, PPVI). Of these, it is at the envelope scale where rich chemical evolution occurs as the jet interacts
+($10^{5} - 10^{6}$\,AU) (\refer : Frank et. al, 2013, PPVI).
+Of these, it is at the envelope scale where rich
+chemical evolution occurs as the jet interacts
 with the molecular medium. In this region, the jet propagates into a
@@
 \begin{figure}
-% \includegraphics[width=1\columnwidth]{\figpath/H2ReactionRates_paper.png}
- \includegraphics[width=1\columnwidth]{\figpath/H2CoolingFuncs_full.png}
+%\includegraphics[width=1\columnwidth]{\figpath/H2CoolingFuncs_full.png}
+\includegraphics[width=1\columnwidth]{\figpath/pfig1.pdf}
  \caption{Variation of the cooling
@@
 \begin{figure}
- \includegraphics[width=84mm]{\figpath/grid.png}
+ \includegraphics[width=84mm]{\figpath/pfig2.pdf}%grid.png
  \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate for points in the r,z plane.
@@
  \begin{figure}
-  \includegraphics[width=1.\columnwidth]{\figpath/diffabun_profnew.pdf}%{\figpath/diffabunprof1.png}
+  \includegraphics[width=1.\columnwidth]{\figpath/pfig3.pdf}%{\figpath/diffabun_profnew.png}
   \caption{{\bf{CHANGEFIG}} The different fractional SiO abundances as a function of
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/diffcool_sim.pdf}%{\figpath/jetplt1_1010.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig4.pdf}%{\figpath/diffcool_sim.pdf}
  \caption{Jet Volume Density for different cooling modes with
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/diffcool_img.pdf}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig5.pdf}%diffcool_img.pdf}
  \caption{A plot of the integrated SiO J=2-$>$1 emission from 5 models, 
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/hfracs_ref.pdf}
+ \includegraphics[width=1.\columnwidth]{\figpath/pfig6.pdf}%hfracs_ref.pdf}
  \caption{{\it{Left}} Color composite image of various hydrogen
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/molcjet_310_molform.pdf}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig7.pdf}%molcjet_310_molform.pdf}
  \caption{Dependence of hydrogen fractions on the temperature at two
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/emspecpv_90.pdf}%{\figpath/refrun_21_90_emspecpv.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/pfig8.pdf}%emspecpv_90.pdf}%{\figpath/refrun_21_90_emspecpv.png}
  \caption{Integrated emission map ({\it top left}), PV diagram ({\it top right}
@@
 \begin{figure}
- \includegraphics[width=1.\columnwidth]{\figpath/emspecpv_45.pdf}%{\figpath/refrun_21_45_emspecpv.png}
+ \includegraphics[width=1.\columnwidth]{\figpath/pfig9.pdf}%emspecpv_45.pdf}%{\figpath/refrun_21_45_emspecpv.png}
  \caption{Same as figure~\ref{empvspec90} but with angle of
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig10.pdf}%diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
  \caption{Variation of 2-$>$1 SiO emission for runs with molecular
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/diffabun_PV.pdf}%{\figpath/PV_gaussandth.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig11.pdf}%diffabun_PV.pdf}%{\figpath/PV_gaussandth.png}
  \caption{Position-velocity maps of SiO(2-1) for the internal
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig12_temp.pdf}%almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
  \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/imshkvhcontomaps.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig13.pdf}%imshkvhcontomaps.png}
  \caption{Symmetrical contour maps of multi-line integrated SiO
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/singledish_new.pdf}%{\figpath/LineRatio_THDeq1.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig14.pdf}%singledish_new.pdf}%{\figpath/LineRatio_THDeq1.png}
  \caption{{\em{Top}} Line profiles in SiO (2-1), (5-4) and (8-7) at one
@@
 \begin{figure}
-\includegraphics[width=1\columnwidth]{\figpath/Internalknot.pdf}
+\includegraphics[width=1\columnwidth]{\figpath/pfigb1.pdf}%Internalknot.pdf}
 \caption{Schematic diagram showing the structure of the internal
@@
 \begin{figure}
-\includegraphics[width=1\columnwidth]{\figpath/jet_rhovel.pdf}
+\includegraphics[width=1\columnwidth]{\figpath/pfigb2.pdf}%jet_rhovel.pdf}
 \caption{Variation of jet velocity (blue) and density (red) as a
@@
 \bibliographystyle{mn2e}
-\bibliography{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/bibfile}
+\bibliography{../bibfile}
 \label{lastpage}

### 2013-12-15 PAPER/Paola_2/ms_ver3.tex
Captions done and new figs in paper

@@
   \includegraphics[width=1.\columnwidth]{\figpath/pfig3.pdf}%{\figpath/diffabun_profnew.png}
-  \caption{{\bf{CHANGEFIG}} The different fractional SiO abundances as a function of
+  \caption{The different fractional SiO abundances as a function of
     jet velocity, v$_{\rm jet}$.}
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig5.pdf}%diffcool_img.pdf}
- \caption{A plot of the integrated SiO J=2-$>$1 emission from 5 models, 
+ \caption{A plot of the integrated SiO(2-1) emission from 5 models, 
 each using a different method to calculate cooling and all with $\eta$=10.}
@@
  \includegraphics[width=1.\columnwidth]{\figpath/pfig6.pdf}%hfracs_ref.pdf}
- \caption{{\it{Left}} Color composite image of various hydrogen
+ \caption{{\it{Left}}: Color composite image of various hydrogen
    fractions, fHI (red), fH$_{2}$ (green) and fHII (blue), for the
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig7.pdf}%molcjet_310_molform.pdf}
- \caption{Dependence of hydrogen fractions on the temperature at two
-   points in the flow, viz. the interface of the knot with molecular
-   medium and at the bow shock.}
+ \caption{{\textit{Top}}: Number density, n$_\rm H$ [cm$^{-3}$], obtained from the reference run along with labels of typical jet features.{\textit{Bottom}}: Dependence of hydrogen fractions on the temperature at two
+   points in the flow, viz. the interface of the knot ({\it{left}}) with molecular
+   medium and at the bow shock ({\it{right}}).}
 \label{fig:Hmolform}
@@
    and spectra ({\it bottom}) for the
-   2-$>$1 SiO transition for the reference run. 
+   SiO(2-1) transition for the reference run. 
    The jet is assumed to be in the plane of sky implying an angle of
    inclination of $90^{\circ}$. The vertical {\it magenta dashed} line
-   represents the cut for the PV digram and green crosses marks the positions from which the spectra are taken.} 
+   represents the cut for the PV digram and {\it green} crosses marks the positions from which the spectra are taken.} 
 \label{empvspec90}
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig10.pdf}%diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
- \caption{Variation of 2-$>$1 SiO emission for runs with molecular
+ \caption{Variation of SiO(2-1) emission for runs with molecular
    cooling having different abundance profiles.}
@@
    profiles. The contours mark different levels of emission in Kelvins, viz.,
-   0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
+   0.1,0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
 \label{fig:pvdiffabun}
@@
  \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
-   and (8-7). The emission map shows the 5-4 line intensity (in units
+   and (8-7). The emission map shows the J=5-4 line intensity (in units
    of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line
@@
  \caption{Symmetrical contour maps of multi-line integrated SiO
-   emission convolved with a 2\arcsec beam obtained using parameters of the reference run. The contour colors represent different intenties in Kelvins, i.e,
-   20.0({\it red}), 10.0({\it green}), 5.0({\it blue}), 1.0({\it
-     magenta}), 0.5({\it cyan}), 0.1({\it black}).} 
+   emission convolved with a 2\arcsec beam obtained using parameters of the reference run.
+The contour colors represent different intensities in Kelvins, i.e, 50.0({\it red}), 30.0({\it green}), 20.0({\it blue}), 5.0({\it
+     magenta}), 2.0({\it cyan}), 0.1({\it black}).} 
 \label{fig:ltconts}
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig14.pdf}%singledish_new.pdf}%{\figpath/LineRatio_THDeq1.png}
- \caption{{\em{Top}} Line profiles in SiO (2-1), (5-4) and (8-7) at one
-   the inner knots for the reference molecular cooling run with a top
-   hat abundance profile and $\delta = 1$. The profiles are
+ \caption{{\em{Top}}: Line profiles in SiO (2-1), (5-4) and (8-7) at one
+   the inner knots for the reference molecular cooling run. The profiles are
    obtained when the angle of inclination is 60$^{\circ}$ with respect
- to line of sight. {\em{Bottom left}} Line intensity ratios SiO(8-7)/(5-4)
-and SiO(5-4)/(2-1), as a function of velocity. {\em{Bottom right}}
-Variation of integrated intensity with upper line transition J$_{\rm
-  up}$ for two abundance profiles.}
+ to line of sight. {\em{Bottom left}}: Line intensity ratios SiO(8-7)/(5-4)
+and SiO(5-4)/(2-1), as a function of velocity. {\em{Bottom right}}:
+Variation of normalised integrated intensity with upper line transition J$_{\rm
+  up}$ for the reference run.}
 \label{fig:lineratio}
@@
 lie around 80-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.
-\\
-{\color{red}
-WE HAVE TWO OPTIONS:\\ 
-1. Since the there is a empirical evidence with bulk gas motion. We
-can use just the jet velocity obtained from simulations.\\
-OR\\
-2. We can try to connect the working surface velocities from
-\cite{Dutrey:1997p11185} to abundance obtained by
-\cite{MartinPintado:1992p14309} and there by use the velocity of the
-working surface as an independent variable on the X axis of the
-abundance plot.
-}
+
+%\\
+%{\color{red}
+%WE HAVE TWO OPTIONS:\\ 
+%1. Since the there is a empirical evidence with bulk gas motion. We
+%can use just the jet velocity obtained from simulations.\\
+%OR\\
+%2. We can try to connect the working surface velocities from
+%\cite{Dutrey:1997p11185} to abundance obtained by
+%\cite{MartinPintado:1992p14309} and there by use the velocity of the
+%working surface as an independent variable on the X axis of the
+%abundance plot.
+%}
 

### 2013-12-16 PAPER/Paola_2/ms_ver3.tex
Added text to the .tex file

@@
 We have adopted a constant value of 5/3 for the adiabatic index and
-have described its consequences in the appendix (see ~\ref{sec:treatgamma}).
+have discussed the applicability for such a choice in the appendix 
+(see ~\ref{sec:treatgamma}).
 
@@
 molecular bullets moving with a projected velocity of 60
-km\,s$^{-1}$ \citep{Dutrey:1997p11185}. Thus, there is
+km\,s$^{-1}$ \citep{MartinPintado:1992p14309, Dutrey:1997p11185}. Thus, there is
 an increase of 6 orders of magnitude from quiescent clouds
@@
 the temperature becomes larger than 10$^{4}$\,K.
-%
+%\it{Top}: Number density,  obtained from the reference run along with labels of typical jet features.}
+
+%
+
 \begin{figure*}
  \includegraphics[width=2.\columnwidth]{\figpath/pfig7.pdf}%molcjet_310_molform.pdf}
- \caption{{\textit{Top}}: Number density, n$_\rm H$ [cm$^{-3}$], obtained from the reference run along with labels of typical jet features.{\textit{Bottom}}: Dependence of hydrogen fractions on the temperature at two
-   points in the flow, viz. the interface of the knot ({\it{left}}) with molecular
-   medium and at the bow shock ({\it{right}}).}
+ \caption{{\it Top}: Number density, n$_{\rm H}$ [cm$^{-3}$], obtained from the reference 
+ run along with labels of typical jet features. {\it Bottom}: Dependence of hydrogen fractions on the temperature at two
+  points in the flow, viz. the interface of the knot {\it left} with molecular
+ medium and at the bow shock {\it right}.}
 \label{fig:Hmolform}

### 2013-12-16 PAPER/Paola_2/ms_ver3.tex
Corrected fig9 and fig12

@@
 outflows have velocities of the order of 100 km\,s$^{-1}$ as in the present
-case. Shocks due to such outflows will dissociate H$_{2}$ and will
-become J ({\em{jump}}) type shocks. Thus, molecules observed in such
-energetic outflows must have been reformed in the flow as suggested by
+case. In case of L1448, the typical velocities of working surfaces (internal knots) 
+lie within a range of 80-150 km\,s$^{-1}$ and the SiO abundance 
+lie around 10$^{-7}$ to 10$^{-6}$ for such high velocity bullets \citep{Dutrey:1997p11185}. 
+Shocks due to such outflows could dissociate H$_{2}$ and molecules observed in such
+energetic outflows could have been reformed in the flow as suggested by
 detailed models of J-shocks by \cite{Neufeld:1989p14322}. SiO formation in J shocks
@@
 \citep{Guillet:2009p11229}.
+%
+
+Further, the velocities obtained from the dynamical simulations are in fact the
+jet flow velocities. They can well be different from the shock
+velocities depending upon the density contrast between the jet and
+ambient medium. For the bow shock, one can estimate the shock velocity 
+by equating the pressures across the shock surface, \citep[e.g.,][]{Masson:1992p14101}
+\begin{equation}
+\label{eq:shockjetvel}
+v_{\rm s} = \frac{v_{\rm jet}}{1 + \eta^{-0.5}}
+\end{equation}
+where v$_{\rm s}$ is the velocity of the bow shock 
+and v$_{\rm jet}$ is the jet velocity. 
+Considering the dependence of ambient density on the vertical distance, 
+the density contrast at the bow shock increases to $\eta \sim 100$. 
+Thus, for such large $\eta$ values, one can very well 
+approximate the bow shock velocity to be the same as the jet flow velocity.  
+In case of internal knots, the above equation for the velocity of the working surface
+changes to eq.~\ref{eq:velws} \citep{Raga:1992p16392}. 
+As described in the appendix ~\ref{sec:worksurface}, the velocity of the internal 
+knots effectively reduces to an average of upstream and downstream 
+velocities across the knot and can as well be approximated 
+to be same as flow velocity. However, the shock velocity 
+in the frame of reference of the knot can be considerably different than the flow velocity 
+and is expressed as a difference between the upstream and downstream velocities.  
+In the present models, these internal shock velocities are $\leq$ 20 km\,s$^{-1}$. 
+Steady state calculations of shocked grain 
+micro-physics described above, takes into account 
+these internal shock velocities to estimate 
+SiO abundances. While, observations measure bulk velocities of the 
+flow and relate molecular abundances to the same. 
 %
@@
 dependence of SiO abundance on shock speeds, we prescribe these
-profiles based on limited empirical evidences. The most simple among
-them is the top hat profile in which the SiO abundance is a low value of
-10$^{-12}$ below 20 km s$^{-1}$ and above 100 km s$^{-1}$ and a
-maximum value of 10$^{-6}$ between these two velocities.
-Shock velocities $>$ 100 km s$^{-1}$ can lead to the 
-ionisation of hydrogen and thereby effectively reduce the number
-of collision centers for SiO resulting in a weaker emission. 
-However, we also consider a step function dependence of SiO abundance
-on shock velocity to incorporate cases where we allow for reformation
-of atomic and molecular species.
-In order to get rid of a discontinuous change of abundance, we also
-prescribe a gaussian such that the peak SiO abundance of 10$^{-6}$ is at
+profiles based on limited empirical evidences 
+and approximate the variation of SiO abundances on jet flow velocities.   
+The most simple and extreme choice among
+them is the step profile in which the SiO abundance is a low value of
+10$^{-12}$ below 20 km\,s$^{-1}$ and a maximum value of 10$^{-6}$ beyond. 
+Such a choice effectively reduces to assuming a constant value of high abundance for the 
+flow velocities seen in our model. In order to compare such a choice, 
+we also apply a top-hat profile where above 100 km\,s$^{-1}$, abundance value 
+is set again to a low value of 10$^{-12}$.
+In order to get rid of an arbitrary discontinuous change of abundance, we also
+prescribe a Gaussian such that the peak SiO abundance of 10$^{-6}$ is at
 60\,km\,s$^{-1}$, while the value of n(SiO)/n(H$_{2}$) falls below
@@
 the case where we extent the abundance of 10$^{-6}$ beyond 60 km\,s$^{-1}$.   
-These functional dependences of SiO
-abundance on shock velocity are shown in figure~\ref{abun}.  
 In addition to this, if the temperature at the point is greater than
@@
 the abundance is reduced to 0. 
+These functional dependence of SiO abundance on jet flow velocities are shown in figure~\ref{abun} 
+and a comparative view is further discussed in Sec~\ref{ssec:sioabunem}.
 %
@@
  \end{figure}
-
-Further, the velocities obtained from the dynamical simulations are in fact the
-jet flow velocities. They can well be different from the shock
-velocities depending upon the density contrast between the jet and
-ambient medium. For the present study, we will consider two
-cases. Firstly, the most simple one in which the jet flow velocity is
-same as the shock velocity. Considering that there is a density
-contrast in the simulation setup, this assumption will
-overestimate the shock velocity. We also
-consider a case in which the shock speed of a dense plug accumulated
-between the jet and medium is estimated by balancing the respective ram
-pressures \citep{Masson:1993p9661},
-\begin{equation}
-\label{eq:shockjetvel}
-v_{\rm s} = \frac{v_{\rm jet}}{1 + \eta^{-0.5}} = v_{\rm jet}\delta
-\end{equation}
-where v$_{\rm s}$ is the velocity of dense plug and v$_{\rm jet}$ is the
-jet velocity. A comparative view of using such velocity corrections and
-functional forms of SiO abundances are discussed in
-Sec~\ref{ssec:sioabunem}.
-
 % The fractional abundance is given by the equation:
@@
 \begin{figure*}
- \includegraphics[width=2.\columnwidth]{\figpath/pfig12_temp.pdf}%almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
+ \includegraphics[width=2.\columnwidth]{\figpath/pfig12.pdf}%almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
  \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)

### 2013-12-16 PAPER/Paola_2/ms_ver3.tex
Modified text 1

@@
 results with observations. The runs with different fractional
-abundance profiles are described in table~\ref{tab:result2}. A
-parameter introduced here is $\delta$ which is essentially the ratio
-of shock velocity v$_{\rm s}$ and physical jet velocity v$_{\rm
-  jet}$ such that its value depends on density contrast $\eta$
-(see Eq.~\ref{eq:shockjetvel}).
+abundance profiles are described in section~\ref{ssec:sioabunem}
 
@@
 \centering 
-\caption{Summary from parameter runs. The parameter $\delta$, is the ratio of
-  shock to jet velocity and it depends on the density contrast $\eta$
-  as shown in eq.~\ref{eq:shockjetvel}}
+\caption{Summary of parameter runs for different cooling prescriptions and density contrasts using two abundance profiles.}
 \begin{tabular}{c | c | c | c | c | c | c }
 \hline
-Run & Cooling Mode & $\eta$ & \multicolumn{2}{|c|}{Top Hat Profile
-  $\delta = 1$} & \multicolumn{2}{|c|}{Gaussian Profile $\delta =
-  1$}\\
+Run & Cooling Mode & $\eta$ & \multicolumn{2}{|c|}{Top Hat Profile} & \multicolumn{2}{|c|}{Gaussian Profile}\\
 \hline\hline
@@
 
-\begin{table*}
-\centering
-\caption{Summary of radiative transfer runs with different SiO fractional abundance
-  profiles for dynamical simulation with molecular cooling and
-  $\eta=3$. The integrated intensity assuming a single disk
-  observation with a beam width of $15\,\arcsec$ is listed along with the
-  corresponding spectral width.}
-\begin{tabular}{l | l | l | l | l}
-\hline
-Profile & $\delta$ = v$_{\rm s}$/v$_{\rm jet}$ & $\int T_{\rm MB}dV$
-[K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$]\\ 
-\hline\hline
-Top Hat & 1.0 & 3.3 & 14.0 \\
-Top Hat & 1/$(1.0 + \eta(z)^{-0.5})$ & 4.9 & 14.0 \\
-Gaussian & 1.0 & 0.66
-& 12.0 \\
-Gaussian & 1/$(1.0 + \eta(z)^{-0.5})$ & 1.1
-& 12.0 \\
-%Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
-%& \\
-%Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
-%& \\
-\hline
-\end{tabular}
-\label{tab:result2}
-\end{table*}
+%\begin{table*}
+%\centering
+%\caption{Summary of radiative transfer runs with different SiO fractional abundance
+%  profiles for dynamical simulation with molecular cooling and
+%  $\eta=3$. The integrated intensity assuming a single disk
+%  observation with a beam width of $15\,\arcsec$ is listed along with the
+%  corresponding spectral width.}
+%\begin{tabular}{l | l | l | l | l}
+%\hline
+%Profile & $\delta$ = v$_{\rm s}$/v$_{\rm jet}$ & $\int T_{\rm MB}dV$
+%[K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$]\\ 
+%\hline\hline
+%Top Hat & 1.0 & 3.3 & 14.0 \\
+%Top Hat & 1/$(1.0 + \eta(z)^{-0.5})$ & 4.9 & 14.0 \\
+%Gaussian & 1.0 & 0.66
+%& 12.0 \\
+%Gaussian & 1/$(1.0 + \eta(z)^{-0.5})$ & 1.1
+%& 12.0 \\
+%%Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
+%%& \\
+%%Functional & 100.0 & $(1.0 + \eta(z)^{-0.5})$ &
+%%& \\
+%\hline
+%\end{tabular}
+%\label{tab:result2}
+%\end{table*}
 
@@
 run is stationary and the jet is in the plane of the sky ($\phi =
-90^{\circ}$). A gaussian profile without any upper cutoff is used for the fractional abundance
-of SiO. Further, the shock velocity which determines
-the fractional abundance, v$_{\rm s}$, is less than the jet velocity in the
-flow, such that their ratio $\delta$ is given by
-equation~\ref{eq:shockjetvel}, where $\eta$ is the density contrast as a
-function of height from the base of the jet.
+90^{\circ}$). A Gaussian profile with a step is used for the fractional abundance
+of SiO.
 
@@
 90$^\circ$ using the top hat abundance
-profile with $\delta = 1$. They are then placed at a distance of
-100$\,$pc and convolved with a beam with FWHM of 2.0\arcsec in order
+profile. They are then placed at a distance of
+16.7$\,$pc and convolved with a beam with FWHM of 2.0\arcsec in order
 to create the maps shown. 
@@
 interface of the knot and the ambient medium. The interaction of the
-knot with the medium raises that temperature to 1200\,K and
+knot with the medium raises that temperature to 1000\,K and
 accumulates the matter so that the density increases up to
@@
 bottom panel of figure~\ref{empvspec90} (they are marked with green
-crosses in top left panel). The knot closer to the base is the brightest
-showing a peak intensity of 25\,K. The
-intensity decreases and reaches to about 10\,K close to the bow shock.
+crosses in top left panel). The knot closer to the base and the region near the bow shock 
+shows a peak integrated intensity of 15-20\,K. Whereas, the integrated 
+intensity decreases and reaches to about 5\,K in the middle of the jet.
 The line widths seen are typically around 5-10 km s$^{-1}$.
@@
 \label{ssec:sioabunem}
-The fractional abundance of SiO has been assumed to vary with shock velocity in
+The fractional abundance of SiO has been assumed to vary with jet flow velocity in
 a simplistic manner (see sec~\ref{ssec:sioabun}). In
 figure~\ref{fig:diffabunem}, we compare the maps for J = 2-$>$1
-emission at an inclination angle of 90$^{\circ}$ for three different abundance profiles and two different ratios of shock to
-jet velocities, $\delta$. There is a striking difference with regards to
-emission from the internal knots in these images. Using the top hat profile
-and accounting for shock speeds (i.e. $\delta < 1$) results in
+emission at an inclination angle of 90$^{\circ}$ for four different abundance profiles. 
+There is a striking difference with regards to
+emission from the internal knots in these images. Using the step profile results in
 emission from  all the internal knots in the J=2-$>$1 line. However, some of
-these knots are not observed when using the same top-hat profile but
-assuming the shock velocity to be same as the jet velocity (i.e.,
-$\delta$ = 1). Similar qualitative characteristics are seen in case of a gaussian
-abundance profile. In particular, the case with $\delta$ = 1 only
-produces emission from the knot closest to the bow shock, while the internal
-knots do not show any appreciable emission. The step function and
-gaussian step (not shown) with $\delta = 1$ produces very similar
-features as that of the top hat profile with $\delta < 1$.
-Further, the emission from
-the knot closer to the bow shock varies considerably with different
-profiles and value of $\delta$. It is the brightest for the case with
-a top-hat profile and $\delta < 1$. The peak emission and line widths at this knot
-are listed in table~\ref{tab:result2}.
+these knots are not observed when using the same top-hat profile. 
+Similar qualitative characteristics are seen in case of a Gaussian
+abundance profile. In particular, the case without a step beyond 60\,km\,s$^{-1}$
+produces emission from the region closest to the bow shock and the lower most knot, 
+while the internal knots do not show any appreciable emission. While, the 
+Gaussian profile with a step produces very similar
+features as that of the step profile effectively making the initial rising part 
+of the curve redundant. 
 %
@@
 simulations. We see that the velocity of internal knots lie around
-70-90\,km\,s$^{-1}$, while the pulsed jet was injected with a mean of
+80-90\,km\,s$^{-1}$, as the pulsed jet was injected with a mean of
 100\,km\,s$^{-1}$. The knots slow down during the evolutionary
@@
 z^{-2}$. Thus, the younger knots suffer the most deceleration closer
-to the base of flow. This fact is taken into account when the shock
-velocity is consistently calculated using the density contrast and
-using a value of $\delta <$ 1. This process is further validated by
-the lack of emission from internal knots in panel 3 of the
-fig~\ref{fig:diffabunem}. 
+to the base of flow. This process is further validated by
+the decreasing abundance profile giving rise to 
+lack of emission from internal knots in panel 3 of the fig~\ref{fig:diffabunem}. 
 %
@@
 different abundance profiles. As expected, the signatures of knots 
-is missing for the case with gaussian profile with $\delta$ =
-1. Further, the wedges formed in panels 1, 2 and 5 of the figure in
+is missing for the case with Gaussian profile without a step.
+Further, the wedges formed in panels 1, 2 and 4 of the figure in
 general are slightly more extended as compared to those
-formed in panel 4. This is indeed because of the
+formed in panel 3. This is indeed because of the
 discontinuous nature of the top-hat abundance profile as the SiO is
 enhanced to a maximum abundance for all velocities between 20 and 100
-km\,s$^{-1}$, which is not the case in a more continuous gaussian
+km\,s$^{-1}$, which is not the case in a more continuous Gaussian
 distribution.
@@
 Applications package (CASA). The output from the radiative transfer
-were scaled to a distance of 300pc and used as the sky models for observations of
+were scaled to a distance of 300\,pc and used as the sky models for observations of
 the J=2-1, J=5-4 and J=8-7 lines at frequencies of 86.85, 217.10 and
 347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7, respectively. The observations
-were simulated using cycle 1 ALMA for 30 minutes total integration
+were simulated using cycle 2 ALMA for 25 minutes total integration
 time, in the configurations c32-6, c32-4 and c32-3 for the three
@@
 presents the ALMA prediction obtained from our reference run. The
-left panel shows the integrated emission of SiO J = 2-1 line while the right
+left panel shows the integrated emission of SiO J = 5-4 line while the right
 shows the PV diagram for the same line and over laid are
-the contours of SiO J = 5-4 and J = 8-7. The contour levels are marked
+the contours of SiO J = 2-1 and J = 8-7. The contour levels are marked
 on the color bar of each panel.
@@
 figure~\ref{fig:ltconts}. Further, we find SiO emission coming from velocities 
-of the order of 40-60 km\,s$^{-1}$ (see fig
+of the order of 40-70 km\,s$^{-1}$ (see fig
 ~\ref{empvspec45}). Additionally, we see a distinct saw-tooth pattern
@@
 intensities of L1448 bullets observed with large beams from JCMT and
-IRAM. Intensities predicted from our model (see table~\ref{tab:result2}) lie within a factor of two
-from the observed values (Table 2 of \citealt{Nisini:2007p13128}).
-%
-
-The variation of integrated single dish emission with upper transition
-levels J$_{\rm up}$ for different abundance profiles is shown in the
-right panel of fig.~\ref{fig:lineratio}. It is clear that the emission
-obtained using a top hat profile is brighter than the one obtained
-with a Gaussian SiO profile. However, curves obtained from
-both these profiles show a very similar shape of a distinct rise followed by a fall in
+IRAM. Intensities predicted from our reference model, $\int T_{\rm MB} dV$ = 5.76 for SiO(2-1), 
+lie within a factor of two from the observed values (Table 2 of \citealt{Nisini:2007p13128}).
+%
+
+The variation of normalized integrated single dish emission with upper transition
+levels J$_{\rm up}$ for the reference run is shown in the
+right panel of fig.~\ref{fig:lineratio}. The curve obtained 
+show a very similar shape of a distinct rise followed by a fall in
 integrated emission for higher transitions with a peak in
-emission for J$_{\rm up}$ = 3. These curves helps to to predict the
-hydrogen number density and temperature in outflows. Physical
+emission for J$_{\rm up}$ = 3. Such a curve is used for kinematic studies and 
+helps to predict the hydrogen number density and temperature in outflows. Physical
 conditions in outflows can also be studied by estimation of line ratios.
@@
 \citep{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800, VanLoo:2013p16573}. 
-The pulsating jet propagation model presented here have shock speeds
-reaching up to 100 km\,s$^{-1}$. We have used few
-simplified SiO abundance profiles as a function of shock
+The pulsating jet propagation model presented here have flow speeds
+reaching up to 120 km\,s$^{-1}$. We have used few
+simplified SiO abundance profiles as a function of jet
 velocity. Though the shape of the profile is uncertain, the upper and
@@
 \item Single-dish synthetic spectra obtained from our model typically
-  have intensity of 0.3\,K and peak around 50\,km\,s$^{-1}$ and have a
+  have intensity of 0.3-0.5\,K and peak around 50\,km\,s$^{-1}$ and have a
   typical line width of 20\,km\,s$^{-1}$. Such modeled spectra are in
@@
   the abundance. On one extreme where all the internal knots emit SiO  
-  with a step profile with $\delta =$ 1 and a top-hat profile with
-  $\delta < 1$, whereas, no emission in
-  seen in knots when a gaussian profile with $\delta$ = 1 is used. For
+  with a step profile whereas, no emission in
+  seen in knots when a Gaussian profile without a step is used. For
   the remaining cases, we observe that emission mainly

### 2013-12-17 PAPER/Paola_2/ms_ver3.tex
Modified text III

@@
 cases, runs with lower ambient temperature of 10\,K do not show any 
-appreciable changes in final dynamical structure of the jet.
+appreciable changes in final dynamical structure of the jet. Therefore, by choosing a 
+slightly higher ambient temperature we get the same results for jet dynamics and 
+in turn the computations are less expensive especially considering the stiff 
+rate equations used to model cooling in flows.
 
@@
 $10^{5} \rm cm^{-3}$ within a jet radius of $2.5\times10^{15} \rm
-cm$. With these choices we obtain a mass outflow rate of 10$^{-6}$
+cm$. Outside this radius, the physical quantities are fixed to their ambient values.
+With these choices, we obtain a mass outflow rate of 10$^{-6}$
 M$_{\odot}$ yr$^{-1}$, consistent with young jets. Most of the young outflows 
@@
 The temperature at the jet
-nozzle for our model has been set to 1000\,K. Thus, the jet is
-over-pressured by 60 times as compared with the ambient medium,
+nozzle for our model has been set to 1000\,K to be consistent with values obtained for young jets. 
+Thus, the jet is over-pressured by 60 times as compared with the ambient medium,
 assuming $\eta$ = 3.0. Inside the jet beam, a radial variation of thermal
@@
 comes from the vibrational and rotational transitions of
-molecular hydrogen plays and a very crucial role during the jet
+molecular hydrogen during the initial stages of jet
 evolution. Whereas, for temperatures above 3000\,K the
@@
 we update this curve at each time step based on the fraction of
-various hydrogen species. Thus during the evolution, even
-contributions from collisional ionizations and excitations also become
+various hydrogen species. Thus during the evolution, 
+contributions from collisional ionizations and excitations become
 important in regions dominated by atomic and ionized hydrogen.
-%
-
-We also ran simulations of axisymmetric MHD jets
+%tabulated
+
+We also ran simulations of axi-symmetric MHD jets
 with optically thin cooling prescriptions already existing in the public
 release of the PLUTO-4 code. They are power-law cooling, 
-simplified non-equilibrium (or atomic) cooling and tabulated
+simplified non-equilibrium (or atomic) cooling \citep{Tesileanu:2008p429} and tabulated
 cooling. While these additional cooling prescriptions may not be a complete description of
@@
 as TMC1 \citep{Ziurys:1989p14699,MartinPintado:1992p14309}. Whereas, in
-outflows like L1448, SiO abundance can increase up to 10$^{-6}$ especially in
-molecular bullets moving with a projected velocity of 60
-km\,s$^{-1}$ \citep{MartinPintado:1992p14309, Dutrey:1997p11185}. Thus, there is
+outflows like L1448, SiO abundance can increase up to 10$^{-6}$ 
+\citep{MartinPintado:1992p14309, Dutrey:1997p11185}. Thus, there is
 an increase of 6 orders of magnitude from quiescent clouds
@@
 outflows have velocities of the order of 100 km\,s$^{-1}$ as in the present
-case. In case of L1448, the typical velocities of working surfaces (internal knots) 
-lie within a range of 80-150 km\,s$^{-1}$ and the SiO abundance 
-lie around 10$^{-7}$ to 10$^{-6}$ for such high velocity bullets \citep{Dutrey:1997p11185}. 
+case. In case of L1448, \cite{MartinPintado:1992p14309}
+have shown that for extreme velocities (obtained from shift in the
+spectra) of -40 to -50 km\,s$^{-1}$, the SiO abundance could be as
+large as $6\times10^{-7}$, while, it slightly increases to
+$2\times10^{-6}$ for the velocity range of -60 to -50
+km\,s$^{-1}$. For the same source, typical working
+surface velocities of the {\em{molecular bullets}} are estimated to
+lie around 60-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.
 Shocks due to such outflows could dissociate H$_{2}$ and molecules observed in such
@@
 is set again to a low value of 10$^{-12}$. 
+With such extreme choices we are over-estimating the abundance values in 
+regions with processed velocities (i.e, jet interface), however, 
+in regions close to internal knots the abundance values will be within a factor of 2. 
 In order to get rid of an arbitrary discontinuous change of abundance, we also
@@
 hydrogen, while molecular hydrogen is seen to be formed in internal
-knots and region that is thermally instable. 
+knots and region that is thermally in-stable. 
 Ionized hydrogen is mainly formed at the tip of the bow. 
@@
  \includegraphics[width=1.\columnwidth]{\figpath/pfig6.pdf}%hfracs_ref.pdf}
- \caption{{\it{Left}}: Color composite image of various hydrogen
+ \caption{{\it{Left}}: Colour composite image of various hydrogen
    fractions, fHI (red), fH$_{2}$ (green) and fHII (blue), for the
@@
 associated with a high mass star reveal a compact, extremely young
-bipolar outflow and a symmetric outflowing shell. Further, their PV
+bipolar outflow and a symmetric out-flowing shell. Further, their PV
 diagrams with SiO and H$^{13}$CO$^{+}$ show a characteristic peak at
@@
 \label{ssec:EHV}
-Multiline mm-wavelength surveys of SiO emission towards a sample of molecular
+Multi-line mm-wavelength surveys of SiO emission towards a sample of molecular
 outflows have shown that these outflows exhibit both low and high
@@
 
-The variation of SiO abundance used for the present model is rather
-obtained from empirical values. In case of L1448, \cite{MartinPintado:1992p14309}
-have shown that for extreme velocities (obtained from shift in the
-spectra) of -40 to -50 km\,s$^{-1}$, the SiO abundance could be as
-large as $6\times10^{-7}$, while, it slightly increases to
-$2\times10^{-6}$ for the velocity range of -60 to -50
-km\,s$^{-1}$. For the same source, typical {\em{shock}} (or working
-surface) velocities of the {\em{molecular bullets}} are estimated to
-lie around 80-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.
-
 %\\

### 2013-12-22 TALK/PizzaTalk_fin.tex
Added Talk folder

--- 2013-10-02 TALK/SiOModelTalk.tex
@@
 \author[Bhargav Vaidya]{\textcolor{blue}{Bhargav Vaidya}\inst{1} \and  Thomas
-  Douglas\inst{1} \and Paola Caselli\inst{1}}\institute[Uni. Leeds]{\inst{1}School of Physics and
+  Douglas\inst{1} \and Paola Caselli\inst{1}}\institute[]{\inst{1}School of Physics and
   Astronomy, University of Leeds, Leeds.}
-\date[2013]{AG Annual Meeting 2013}
+\date[2013]{Pizza Meeting}
 \titlegraphic{\vskip30pt \hskip215pt\includegraphics[width=0.3\textwidth]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Leeds-logo.jpg}}
@@
 
-\begin{frame}
-\titlepage
-\end{frame}
+%\begin{frame}
+%\titlepage
+%\end{frame}
 
-\begin{frame}
-\frametitle{Outline}
-\tableofcontents
-\end{frame}
-
-\section{Motivation}
-\begin{frame}[t]
-\frametitle{Motivation}
-\small{
-\begin{block}{EHV Emission}
-\begin{itemize}
-\item Observed for the first time in L1448 outflow (\alert{Bachiller
-    1991})
-\item Associated with primary jet (\alert{Santiago-Garcia, 2009}, {\it{IRAS 04166+2706}}). Observed in SiO, CO but no signatures in HCN or CS (\alert{Tafalla, 2010}).
-\item How are they formed ? J-shocks or C-shocks ? Stationary 1D
-  Models -- FAILS! (557 GHz \alert{Tafalla, 2013}) \textbf{NEED FOR A 2D MODEL!}
-\end{itemize}
-\end{block}
-}
-\vskip10pt
-\begin{columns}[C]
-\begin{column}{0.5\textwidth}
-\includegraphics[height=4cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Tafalla2011.pdf}
-\end{column}
-\begin{column}{0.5\textwidth}
-\includegraphics[height=4cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Tafalla2013.png}
-\end{column}
-\end{columns}
-\end{frame}
-
-\section{Numerical Approach}
-\begin{frame}[t]
-\frametitle{Methodology}
-\begin{center}
-\includegraphics[height=7cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/FlowChartJetProp.png}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\frametitle{Initial Conditions}
-\begin{columns}[T]
-    \begin{column}{.4\textwidth}
-     \begin{block}{Molecular Ambient Medium}
-       Cold (T$_{\rm amb}$ $\sim$ 50\,K) \\ with decreasing density\\
-       (\alert{Caselli, P., 2011})
-
-    \end{block}
-    \end{column}
-    \begin{column}{.6\textwidth}  
-      \includegraphics[width=3cm,height=6cm, angle=-90]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/figure1_caselli.png}
-    \end{column}
-  \end{columns}
-\vskip10pt 
-\begin{columns}[T]
-    \begin{column}{.4\textwidth}
-     \begin{block}{Overdense MHD Jet}
-       Propogating jet with \\ velocity perturbation \\
-       $V_{\rm jet} = V_{\rm jet,0}[1 + sin(\frac{2\pi t}{70\, \rm
-         yrs})]$\\
-       (\alert{Stone\&Hardee, 2000})
-    \end{block}
-    \end{column}
-    \begin{column}{.6\textwidth} 
-      \hskip10pt
-      \begin{tabular}{l l}
-      \textbf{Quantity} & \textbf{Values}\\
-      \hline\hline
-      \smallskip
-      $\eta$ & 2,3,10\\
-      \smallskip
-      $V_{\rm jet,0}$ & 100\, km\, s$^{-1}$\\
-\smallskip
-      Plasma $\beta_0$ & 10 $\sim$ 20$\mu$\,G \\
-\smallskip
-      $n_{\rm jet,0}$ & 10$^{5}$ cm$^{-3}$ \\
-\smallskip
-      $r_{\rm jet,0}$ & 160\,AU\\
-\smallskip
-      Composition & 1\% Ionic, 10\% Molecular,\\
-      &89\% Atomic\\
-      \hline
-      \end{tabular}
-    \end{column}
-  \end{columns}
-
-\end{frame}
-
-\section{Cooling and Chemistry}
-\begin{frame}
-\frametitle{Cooling Prescriptions and H$_{2}$ Chemistry in PLUTO
- ( \alert{Mignone, 2007})}
-\begin{columns}[C]
-    \begin{column}{.5\textwidth}
-     \begin{itemize}
-     \item Adiabatic (No cooling)
-     \item Power Law Cooling
-     \item Atomic Cooling 
-  \end{itemize}
-    \end{column}
-    \begin{column}{.5\textwidth} 
-     \begin{itemize}
-     \item Tabulated Cooling with {\em Fixed Initial Fractions}
-     \item \textbf{Proper Molecular Cooling} (\alert{Vaidya et. al,
-         \textit{in prep}, O'Sullivan's PhD Thesis})
-     \end{itemize}
-
-    \end{column}
-  \end{columns}
-
-\vskip10pt
-\begin{columns}[C]
-    \begin{column}{.5\textwidth}
-      \includegraphics[width=5cm,height=5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/H2ReactionRates_paper.png}
-    \end{column}
-    \begin{column}{.5\textwidth}  
-      \includegraphics[width=5cm,height=5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/H2CoolingFuncs_full.png}
-    \end{column}
-  \end{columns}
-\end{frame}
-
-\begin{frame}[t]
-\frametitle{Radiative Jet dynamics}
-\begin{columns}[T]
-    \begin{column}{.3\textwidth}
-      \begin{block}{Impact of Cooling}
-       \begin{itemize}
-       \item $\eta$ = 10.0 \\
-       \item Jet becomes thinner with more effective cooling \\
-       \item Thermal Instabilities 
-       \end{itemize}
-       \end{block}
-    \end{column}
-    \begin{column}{.7\textwidth} 
-     \includegraphics[width=8cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/jetplt1_1010.png}
-    \end{column}
-  \end{columns}
-
-\begin{columns}[T]
-    \begin{column}{.3\textwidth}
-       \begin{block}{Impact of Shocks}
-      \begin{itemize}
-      \item $\eta$ = 3.0 \\
-      \item {\em Iternal Knots} - Formation and Destruction \\
-      \item {\em Primary Bow shock} - Ionized Hydrogen with  T $>$ 20,000\,K.\\ 
-      \end{itemize}
-    \end{block}
-    \end{column}
-    \begin{column}{.7\textwidth} 
-      \includegraphics[width=6cm,height=4cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/molcjet_310_molform.png}
-
-    \end{column}
-  \end{columns}
-\end{frame}
-
-\section[Rad. Transfer]{Radiative Transfer : Post-Processing}
-\begin{frame}
-\frametitle{Grid and Abundance}
-\begin{columns}[T]
-    \begin{column}{.4\textwidth}
-      Line Modelling\\
-      Engine [\textbf{LIME}] (\alert{Brinch \& Hogerheijde, 2010}) 
-      \includegraphics[width=3cm,height=6cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/grid.png} 
-    \end{column}
-    \begin{column}{.6\textwidth}
-      \small{
-        \begin{itemize}
-          \item n(SiO)/n(H2) as a function of shock velocity
-           \item 10$^{-12}$ in Dark clouds (\alert{Ziurys, 1989}),\\
-            10$^{-6}$ in fast outflows (\alert{Dutrey, 1997}).
-          \item $\delta = V_{\rm shock}/ V_{\rm jet} = f(\eta) <= 1$
-         \end{itemize}
-       }
-
-      \includegraphics[width=5cm,height=5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/diffabunprof1.png}
-      \end{column}
-     \end{columns}   
-\end{frame}
-
-\begin{frame}[t]
-\frametitle{Cooling and SiO Emission}
-\tiny{
-\begin{table}
-\caption{Parameter runs with different cooling prescription and $\eta$ values}
-\begin{tabular}{c | c | c | c | c | c | c }
-\hline
-Run & Cooling Mode & $\eta$ & \multicolumn{2}{|c|}{Top Hat Profile
-  $\delta = 1$} & \multicolumn{2}{|c|}{Gaussian Profile $\delta =
-  1$}\\
-\hline\hline
-&&& $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] & $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] \\
-\hline
-adi1010 & Nil (Adiabatic) & 10 & 2.91 & $>$40 & 0.25 & 40.0 \\
-pow1010 & Power law & 10 & 0.64 & 8.0 & 0.02 & 10.0\\
-atm1010 & Atomic & 10 & 2.04 & 36.0 & 0.58 & 38.0 \\
-atm210 & Atomic & 2 & 3.21 & 18.0 & 0.64 & 20.0 \\
-tab1010 & Tabulated & 10 & 0.75 & 11.0 & 0.09 & 10.0 \\
-tab210 & Tabulated & 2 & 2.89 & 8.0 & 1.0 & 9.0 \\
-mol1010 & Molecular & 10 & 1.10 & 10.0 & 0.1 & 11.0 \\
-\color{red}{\textbf{mol310}} & Molecular & 3 & 3.3 & 14.0 & 0.66 & 12.0\\
-\hline
-\end{tabular}
-\end{table}
-}
-\vskip10pt
-\begin{columns}[T]
-
-\begin{column}{0.3\textwidth}
-  \begin{block}{Impact of Cooling}
-    \begin{itemize}
-      \item Jet flow with $\eta$ = 10 and $\beta$ = 10.0\\
-      \item Integrated intensities with Gaussian Profile
-        and $\delta < 1$.\\
-      \item Convolved with a beam of FWHM = 2.5''
-    \end{itemize}
-  \end{block}
-\end{column}
-
-\begin{column}{0.7\textwidth}
- \includegraphics[width=8cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/diffcool_EMgaussprof.png}
-\end{column}
-\end{columns}
-\end{frame}
-
-\section[Results]{Results : Line Emission, Spectra, PV Diagrams}
-\begin{frame}[t]
-\frametitle{SiO Multi-Line Movies}
-\small{
-\begin{itemize}
-\item Molecular Jet with $\eta$ = 3.0, $\beta$ = 10.0 \\
-\item Line Intensities with Gaussian Profile with $\delta < 1$. \\
-\item Jet is in plane of sky and convolved with a beam of 2.5''
-\end{itemize}
-}
+\begin{frame}[l]
+\frametitle{HH212 : A classic young jet.}
 \begin{tabular}{ccc}
-\textbf{J = 2-$>$1} & \textbf{J = 5-$>$ 4} & \textbf{J = 8-$>$ 7}\\
-\animategraphics[width=3.5cm,height=5.5cm,autoplay]{5}{Img21/Img21_}{0000}{0010}
-& 
-\animategraphics[width=3.5cm,height=5.5cm,autoplay]{5}{Img54/Img54_}{0000}{0010}
-&
-\animategraphics[width=3.5cm,height=5.5cm,autoplay]{5}{Img87/Img87_}{0000}{0010}
-
+\includegraphics[scale=0.13]{hh212_best.pdf} & \includegraphics[scale=0.18]{codella_hh212_f3.pdf} & \includegraphics[scale=0.16]{knot_ang85.pdf} \\
+\tiny{McCaughrean 2002} & \tiny{Codella 2007} & \tiny{Present work SiO(8-7)}\\
 \end{tabular}
@@
 
-\begin{frame}
-\frametitle{HH 211 - SiO Multi-Line Emission}
-\begin{tabular}{ccc}
-\textbf{J = 1-$>$0} (\alert{Chandler, 2001}) & \textbf{J = 5-$>$ 4}
-(\alert{Hirano, 2006}) &
-\textbf{J = 8-$>$ 7} (\alert{Palau, 2006})\\
-
-\includegraphics[width=3cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Chandler2001.png}
-&
-\includegraphics[width=3.5cm,height=2.5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Hirano2005.png}
-&
-\includegraphics[width=2.5cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Palau2006.png}
-\end{tabular}
-\vskip10pt
-\begin{columns}[T]
-\begin{column}{0.3\textwidth}
- \begin{itemize}
-    \item {\color{Brown}Low excitation} : Interaction of jet and medium.
-    \item {\color{Brown}High excitation}: Internal knots.
- \end{itemize}
-\end{column}
-
-\begin{column}{0.7\textwidth}
-\includegraphics[width=7cm,height=3.5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/imshkvhcontomaps.png}
-\end{column}
-\end{columns} 
+\begin{frame}[T]
+\frametitle{3D Modelling of Young Stellar Jets}
+Re-collimation shocks and wiggles!
+\animategraphics[autoplay,loop,scale=0.23]{2}{ImgJet3d/contourjet1.}{0000}{0060}
 \end{frame}
-
-\begin{frame}[c]
-\frametitle{HH212 and L1448-mm : Spectra and Kinematics}
-% \small{
-% \begin{block}{Generic Features}
-% \begin{itemize}
-% \item L1448-mm : Weak line emission (T $\sim$ 0.3\,K) and peaks at 50
-%   km\,s$^{-1}$ and a spectral width of about 20 km\,s$^{-1}$.\\
-% \item SiO Multi-line analysis and LVG Modelling : Typical n(H$_{2}$)
-%   $\sim$ 10$^{6}$ cm$^{-3}$ and Temperature of $>$ 500\,K.\\
-% \item Line ratios from multi-line survey close to unity for both low
-%   (HH212; ) and high mass (IRAS 17233-3606; ) young outflows. 
-% \end{itemize}
-% \end{block}
-% }
-
-\begin{columns}
- \begin{column}{0.33\textwidth}
-Spectra (\alert{Codella, 1999})\\
- \includegraphics[width=4.0cm,height=4.0cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Codella1999.pdf}
-
- \end{column}
-
- \begin{column}{0.33\textwidth}
-Line Ratios (\alert{Cabrit, 2007})\\
- \includegraphics[width=3.0cm,height=4.0cm,angle=-90]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Cabrit2007.png}
-
- \end{column}
-
-\begin{column}{0.33\textwidth}
-Kinematics (\alert{Nisini, 2007})\\
- \includegraphics[width=3.5cm,height=4.0cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Nisini2007_2.png}\\
-
- \end{column}
- \end{columns}
-\vskip10pt
-
- \end{frame}
-
-\begin{frame}
-\frametitle{Model Spectra and Line Ratios}
-\begin{columns}[T]
-\begin{column}{0.4\textwidth}
-\begin{itemize}
-\item Single dish spectra, Gaussian
-  abundance profile, $\delta <$ 1, Inclination of 60$^{\circ}$. \\
-\item High velocity emission consistent with generic observational features. \\
-\item Missing Slow component ?
-\item Optically Thick or Thin ?\\
-\end{itemize}
-\end{column}
-\begin{column}{0.6\textwidth}
-\includegraphics[width=6cm,height=6cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/LineRatio_THDeq1.png}
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}
-\frametitle{PV Diagrams}
-\begin{columns}[T]
-\begin{column}{0.5\textwidth}
-\includegraphics[width=5cm,height=7cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/refrun_21_60_emspecpv.png}
-\end{column}
-\begin{column}{0.5\textwidth}
-IRAS 04166+2706 (\alert{Santiago-Garcia, 2009}). 
-\includegraphics[width=5cm,height=5cm,angle=-180]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/Santiago2009.pdf}
-\end{column}
-\end{columns}
-
-\end{frame}
-
-\begin{frame}[c]
-\frametitle{Effects of Abundance}
-\begin{columns}[c]
-\begin{column}{0.9\textwidth}
-\includegraphics[width=9cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/EM_gaussandth.png}
-\end{column}
-\end{columns}
-\vskip10pt
-\begin{columns}[c]
-\begin{column}{0.9\textwidth}
-\includegraphics[width=9cm,height=3cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/PV_gaussandth.png}
-\end{column}
-\end{columns}
-
-\end{frame}
-
-\section{Summary}
-\begin{frame}
-\frametitle{Summary}
-\begin{itemize}
-\item Axi-symmetric MHD Jet propagation simulations with
-  \alert{Molecular cooling and Hydrogen chemistry} for the context of studying molecular outflows in Class 0 phase.
-
-\item Extremely High Velocity(EHV) emission of SiO seen in some young
-  outflows are produced by \alert{interaction of internal knots with ambient
-  medium via J-shocks}
-
-\item Our model can very \alert{reproduce observational features} like :
-  \begin{itemize}
-    \item Integrated intensity of EHV emission.
-    \item Spectral shape and line ratios seen in SiO emission from some of these Class 0 Outflows.
-    \item Knotty features of PV diagrams. 
-  \end{itemize}
-
-\item \alert{Outlook}
-\begin{itemize}
-  \item Longer, 3D, AMR simulations which consistently produce
-    internal knots (\alert{Gomez et. al 2013}).
-  \item Consistent modeling for dust chemistry to have better
-    constraints on SiO abundance.
-  \item Slower wider component seen in chemical molecules like CO, H$_{2}$O (Herschel WISH
-    Survey, \alert{Tafalla et. al., 2013}).
-\end{itemize}
-
-\item \alert{ALMA Maps !}
-\end{itemize}
-\end{frame}
-
-\begin{frame}[t]
-\frametitle{ALMA Maps}
-\begin{columns}[T]
-\begin{column}{0.3\textwidth}
-\begin{block}{CASA Simulation}
-\begin{itemize}
-\item Source Distance : 300 pc 
-\item Cycle 1 --  Bands(Beam Size) :  3(0.72''), 6(0.47'') and 7(0.58'') 
-\item Integration time : 30 min
-\item Velocity Resolution : 1 km s$^{-1}$
-\end{itemize}
-\end{block}
-\end{column}
-\begin{column}{0.7\textwidth}
-\includegraphics[width=8.5cm]{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/ALMAmaps3.png}
-\end{column}
-\end{columns}
-\end{frame}
-
 \end{document}

### 2013-12-22 TALK/TifrTalk.tex
Added Talk folder

\documentclass[8pt,xcolor=dvipsnames]{beamer}
\usepackage[latin1]{inputenc}

\usetheme[height=7mm]{Berlin}
\usecolortheme[named=Brown]{structure}

\usepackage{time}       % date and time
\usepackage{graphicx}
\usepackage[T1]{fontenc}    % european characters
%\usepackage{courier}
\usepackage{animate}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{amssymb,amsmath}  % use mathematical symbols
\usepackage{bookman}                  % use palatino as the default font
\setbeamercovered{transparent}
\newcommand{\figpath}{/home/phybva/SiOJets_New/PAPER/NEWFIGS/}

\title[YSO Outflows]{Outflows from Young Stellar Objects}
\subtitle{MHD, Radiation \& Chemistry}
\author[Bhargav Vaidya]{\textcolor{blue}{Bhargav Vaidya}\inst{1}}
\institute[Uni. Leeds]{\inst{1}School of Physics and Astronomy, University of Leeds, Leeds.}
\date[2014]{Visitor Seminar TIFR 2014}
%\titlegraphic{\vskip30pt \hskip215pt\includegraphics[width=0.3\textwidth]{\figpath/Leeds-logo.jpg}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Outline}
\tableofcontents
\end{frame}

\section{Introduction}
\begin{frame}{Star formation : What do we know}

\end{frame}

\begin{frame}{Star formation : Feedback}
\end{frame}

\begin{frame}{Present challenges}
\end{frame}

\section{Motivation}
\begin{frame}{Outflow Evolutionary Picture}
\end{frame}

\begin{frame}{Chemistry in outflows}
\end{frame}

\begin{frame}{Molecular bullets and EHV emission}
\end{frame}

\section{Methods : Numerical Simulations}
\begin{frame}{Numerical code}
\end{frame}

\begin{frame}{Launching and Propagation}
\end{frame}

\begin{frame}{Radiation force}
\end{frame}

\begin{frame}{Chemistry and Cooling}
\end{frame}

\section{Outflow Dynamics : Launching}
\begin{frame}{MHD Acceleration}
\end{frame}

\begin{frame}{Collimation and Radiation}
\end{frame}

\begin{frame}{Force Parameters and its impact}
\end{frame}

\begin{frame}{Resistive effects}
\end{frame}

\begin{frame}{A case of Orion Source I}
\end{frame}

\section{Outflow dynamics : Propagation}
\begin{frame}{Molecular Interplay}
\end{frame}

\begin{frame}{Spectra and PV digrams}
\end{frame}

\begin{frame}{Multi-Line survey : Emission}
\end{frame}

\begin{frame}{Multi-line survey : Line Ratios}
\end{frame}

\begin{frame}{Focussing on a single knot}
\end{frame}

\begin{frame}{Rotation or Wiggles?}
\end{frame}

\section{Summary}
\begin{frame}{Conclusions}
\end{frame}

\end{document}

### 2013-12-23 TALK/TifrTalk.tex
Added text to Tifr talk
Added text to TIFRtalk.tex

@@
 \setbeamercovered{transparent}
-\newcommand{\figpath}{/home/phybva/SiOJets_New/PAPER/NEWFIGS/}
+\newcommand{\figpath}{/home/phybva/SiOJets_New/TALK/NEWFIGS}
+\newcommand{\spic}[2]{\includegraphics[scale=#1]{#2}}
+\newcommand{\myref}[1]{{\small{\color{red}{(#1)}}}}
 
@@
 \institute[Uni. Leeds]{\inst{1}School of Physics and Astronomy, University of Leeds, Leeds.}
-\date[2014]{Visitor Seminar TIFR 2014}
+\date[2014]{{\large{Astro Seminar, TIFR}}\\ {\small{January 13, 2014}}}
 %\titlegraphic{\vskip30pt \hskip215pt\includegraphics[width=0.3\textwidth]{\figpath/Leeds-logo.jpg}
@@
 \begin{frame}
-\titlepage
+\vspace*{0.5cm}\titlepage  
+  \vspace*{0.1cm}\textcolor{red}{{\textit{Collaborators:}}}\\
+  \tiny{Paola Caselli (Uni. Leeds), Thomas Douglas (Uni. Leeds), Oliver Porth (Uni. Leeds), \\
+  Christian Fendt (MPIA), Henrik Beuther (MPIA), Somayeah Sheiknezami (MPIA),\\
+  Ciraco Goddi (JIVE),  Andrea Mignone (Uni. Torino).\\}
+%\titlepage
 \end{frame}
@@
 \begin{frame}{Star formation : Feedback}
+Talk about winds and outflows
 \end{frame}
@@
 \begin{frame}{Numerical code}
+
 \end{frame}
@@
 \section{Outflow dynamics : Propagation}
+\begin{frame}{Cooling in Jets}
+\end{frame}
 \begin{frame}{Molecular Interplay}
+\begin{columns}
+\begin{column}{0.4\textwidth}
+\spic{0.2}{\figpath/pfig6.pdf}
+\end{column}
+\hfill
+\begin{column}{0.6\textwidth}
+\spic{0.2}{\figpath/pfig7.pdf}
+\end{column}
+\end{columns}
 \end{frame}
 
-\begin{frame}{Spectra and PV digrams}
+\begin{frame}{SiO Abundance and Jet Velocity}
 \end{frame}
 
-\begin{frame}{Multi-Line survey : Emission}
+\begin{frame}{Spectra and PV diagrams : SiO (2-1)}
+\begin{columns}
+\begin{column}{0.48\textwidth}
+\spic{0.17}{\figpath/pfig8.pdf}\\
+\hspace{0.2cm} $\phi = \pi/2$ (Plane of Sky)
+\end{column}
+\hfill
+\begin{column}{0.48\textwidth}
+\spic{0.17}{\figpath/pfig9.pdf}\\
+\hspace{0.2cm}$\phi = \pi/4$ 
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Multi-Line survey : Emission I}
+Movies Here.
+\end{frame}
+
+\begin{frame}{Multi-Line survey : Emission II}
+\end{frame}
+
+\begin{frame}{Case of L1448 \myref{Nisini 2007}}
+\begin{columns}[t]
+\begin{column}{0.25\textwidth}
+\spic{0.1}{\figpath/Nisini2007_f1.pdf}\\
+Contours SiO 2-1
+\end{column}
+%\hfill
+
+\begin{column}{0.40\textwidth}
+ \spic{0.25}{\figpath/Nisini2007_f4.pdf}\\
+ Spectral Features
+\end{column}
+%\hfill
+
+\begin{column}{0.25\textwidth}
+\spic{0.25}{\figpath/Nisini2007_f6.pdf} \\
+Kinematic Study (LVG) 
+\end{column}
+%\hfill
+
+\end{columns}
 \end{frame}
@@
 \begin{frame}{Multi-line survey : Line Ratios}
+
+\begin{columns}[T]
+\begin{column}{0.35\textwidth}
+\begin{itemize}
+\item EHV emission of 0.5 K.
+\item Line ratios close to Unity. 
+\item Multi-line emission show a distinct fall at high J$_{\rm up}$.
+\end{itemize}
+\end{column}
+\hfill
+
+\begin{column}{0.75\textwidth}
+\spic{0.28}{\figpath/pfig14.pdf} 
+\end{column}
+\hfill
+
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Predictions for ALMA}
 \end{frame}
@@
 \begin{frame}{Focussing on a single knot}
+\begin{tabular}{c c}
+\spic{0.2}{\figpath/codella_hh212_f3.pdf} & \spic{0.2}{\figpath/knot_ang85.pdf} \\
+HH 212 \myref{Codella 2007} &\\
+\end{tabular}
 \end{frame}

### 2014-01-07 TALK/TifrTalk.tex
Added movie Slide to pdf
Added more slides

@@
 \setbeamercovered{transparent}
-\newcommand{\figpath}{/home/phybva/SiOJets_New/TALK/NEWFIGS}
+%\newcommand{\figpath}{/home/phybva/SiOJets_New/TALK/NEWFIGS}
+\newcommand{\figpath}{./NEWFIGS/}
 \newcommand{\spic}[2]{\includegraphics[scale=#1]{#2}}
 \newcommand{\myref}[1]{{\small{\color{red}{(#1)}}}}
+\newcommand{\movauto}[5]{\animategraphics[width=#1,height=#2,autoplay]{#3}{#4}{0000}{#5}}
+\newcommand{\movloop}[5]{\animategraphics[width=#1,height=#2,loop]{#3}{#4}{0000}{#5}}
 
@@
 \section{Outflow dynamics : Propagation}
+
 \begin{frame}{Cooling in Jets}
+\begin{columns}
+\begin{column}{0.3\textwidth}
+\vspace{-3cm}
+\begin{block}{Cooling is important}
+\begin{itemize}
+\item t$_{\rm cool} \sim n_0/\Lambda(T) <$ t$_{\rm dyn}$
+  \myref{e.g, Blondin, 1990}\\
+\item Cooling rate for a molecular medium with n$_0$ = 10$^{5}$ cm$^{-3}$
+\end{itemize}
+\end{block}
+\end{column}
+\begin{column}{0.6\textwidth}
+\spic{0.3}{\figpath/pfig1.pdf}
+\end{column}
+\end{columns}
 \end{frame}
+
+\begin{frame}{Cooling in Jets}
+\begin{block}{Dynamical Effects}
+\centering
+\begin{itemize}
+\item Thinner jets with less pronounced coccoon
+\item Enhanced density in the internal knots with instable features.
+\item Thermal Instability in bow-shock of the jet. 
+\end{itemize}
+\end{block}
+\centering
+\spic{0.23}{\figpath/pfig4.pdf}
+
+\end{frame}
+
 \begin{frame}{Molecular Interplay}
@@
 \begin{frame}{Multi-Line survey : Emission I}
-Movies Here.
+\small{
+\begin{itemize}
+\item Molecular Jet with $\eta$ = 3.0\\
+\item Line Intensities with Top Hat Profile. \\
+\item Jet is in plane of sky and convolved with a Gaussian beam of 2.5''
+\end{itemize}
+}
+\begin{tabular}{ccc}
+\textbf{J = 2-$>$1} & \textbf{J = 5-$>$ 4} & \textbf{J = 8-$>$ 7}\\
+\movauto{3.5cm}{5.5cm}{3}{Img21/Img21_}{0010}
+&
+\movauto{3.5cm}{5.5cm}{3}{Img54/Img54_}{0010}
+&
+\movauto{3.5cm}{5.5cm}{3}{Img87/Img87_}{0010}
+
+\end{tabular}
+
 \end{frame}
@@
 \begin{frame}{Predictions for ALMA}
+\begin{block}{ALMA Cycle 2}
+\textbf{Bands 3, 6, 7}: Assuming a source placed at 400 pc.[Orion - HH 212 \myref{Zinnecker,1998}] 
+\end{block}
+\begin{center}
+\spic{0.21}{\figpath/pfig12.pdf}
+\end{center}
 \end{frame}
@@
 
-\begin{frame}{Rotation or Wiggles?}
+\begin{frame}[t]{Rotation or Wiggles?}
+  \begin{center}
+  \movloop{8cm}{5cm}{61}{Img_3djet/contourjet1.}{0060}
+  \end{center}
 \end{frame}

### 2014-01-20 TALK/TifrTalk.tex
Final talk

@@
 \newcommand{\figpath}{./NEWFIGS/}
+\newcommand{\jlfigpath}{/Users/bhargavvaidya/THESIS/chapter3/figures/}
 \newcommand{\spic}[2]{\includegraphics[scale=#1]{#2}}
@@
 \section{Introduction}
-\begin{frame}{Star formation : What do we know}
-
+\begin{frame}[plain]
+\frametitle{Typical HII region}
+\begin{center}
+\spic{0.67}{\figpath/HII-region.jpg}
+\end{center}
 \end{frame}
 
-\begin{frame}{Star formation : Feedback}
-Talk about winds and outflows
+\begin{frame}[plain]
+\frametitle{Star formation : Dark clouds}
+Filamentary, dense Infra-red dark clouds are birth place of stars
+\myref{e.g.,Rathborne 2008}
+\spic{0.15}{\figpath/g11_k.png}
+\spic{0.3}{\figpath/g11_a_th.png}\\
+\begin{center}
+\spic{0.35}{\figpath/g11_850_th.png}
+\end{center}
 \end{frame}
 
-\begin{frame}{Present challenges}
+\begin{frame}
+\frametitle{Star formation : Feedback}
+\begin{columns}
+\begin{column}{0.45\textwidth}
+\begin{block}{Outflows}
+\begin{itemize}
+\item An ubiquitous feature in star forming regions. First signpost of formation.
+\item Driven magnetically from the underlying accretion disk. 
+\item Entrain molecules along the flow : Molecular Outflow.
+\item Stellar winds : Trigger star formation, Pollute ISM with new
+  metals. 
+\item 3 stages : Launching < 100 AU, Propogation few 100s AU to 0.1
+  pc, Interaction > 0.1 pc.   
+\end{itemize}
+\end{block}
+\end{column}
+\begin{column}{0.55\textwidth}
+M20 (Trifid Nebula) \spic{0.35}{\figpath/trigg_sf.jpg}\\
+Jets from YSOs \spic{0.14}{\figpath/jets_yso.JPG}
+\end{column}
+\end{columns}
 \end{frame}
 
+%\begin{frame}{Present challenges}
+%\end{frame}
+
 \section{Motivation}
-\begin{frame}{Outflow Evolutionary Picture}
+\begin{frame}{Outflow Evolutionary Picture \myref{Beuther \& Sheperd
+      2005, Vaidya 2011}}
+\begin{center}
+\spic{0.1}{/Users/bhargavvaidya/THESIS/Intro_Figs/evol_outflow_n.pdf}
+\end{center}
+\end{frame}
+
+\begin{frame}{Global Outflow Picture}
+\begin{columns}
+\begin{column}{1.0\textwidth}{\myref{Vaidya 2009}}
+\spic{0.33}{/Users/bhargavvaidya/THESIS/chapter2/figures/f5_col.pdf}
+\end{column}
+\end{columns}
 \end{frame}
@@
 \begin{frame}{Chemistry in outflows}
+\begin{block}{Young Class 0 Outflows}
+\begin{itemize}
+\item Largely studied in form of molecular outflows using sub-mm
+  telescopes.
+\item Bulk gas motion is traced by CO while SiO and H$_{2}$ (Infrared) traces the shocked regions. 
+\end{itemize}
+\end{block}
+
+\begin{block}{Class I jets}
+\begin{itemize}
+\item They are traced mainly using optical telescopes.
+\item Signatures of forbidden emission lines from various atomic
+  species.
+\item Lack or neglible molecular emission. 
+\end{itemize}
+\end{block}
 \end{frame}
@@
 \begin{frame}{Molecular bullets and EHV emission}
+\begin{columns}
+
+\begin{column}{0.4\textwidth}
+\begin{center}
+EHV Emission
+\myref{Tafalla 2011}\\
+\spic{0.33}{\figpath/EHVJets.png}
+\end{center}
+\end{column}
+\hspace{0.05\textwidth}
+\begin{column}{0.5\textwidth}
+\begin{center}
+PV Diagram \myref{Santiago-Garcia 2009}\\
+\spic{0.25}{\figpath/EHVJets_PV.png}\\
+1D Models fail \myref{Tafalla 2013} \\
+\spic{0.35}{\figpath/EHVJets_Spec.png}
+\end{center}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Goals}
+\begin{block}{Outflow Evolution}
+\begin{itemize}
+\item <1-> What is the physical motivation of widening of outflow with age and central mass.?
+\item <2-> Does the central massive star and hot inner disk play a role?  
+\item <3->How do magnetic fields fit into the picture of outflows dynamics?
+\end{itemize}
+\end{block}
+
+\begin{block}{EHV Emission}
+\begin{itemize}
+\item <4->What causes the EHV emission in young outflows?
+\item <5->Is 2D the answer to the failure of 1D models to predict spectra?
+\item <6->What happens if we extend the model to 3D? 
+\end{itemize}
+\end{block}
 \end{frame}
@@
 \begin{frame}{Numerical code}
+\begin{columns}
+\begin{column}{0.5\textwidth}
+\begin{block}{PLUTO}
+\begin{itemize}
+\item A modular code for computational astrophysics.
+\item Solve systems of conservation laws using the finite volume or
+  finite difference approach based on Godunov-type schemes.
+\item The static grid version of PLUTO is entirely written in the C programming language
+\item AMR module uses the Chombo library. 
+\end{itemize}
+\end{block}
+\end{column}
+\begin{column}{0.5\textwidth}
+\spic{0.26}{\figpath/Pluto_code_cover.png}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Launching Model}
+\begin{columns}
+\begin{column}{0.45\textwidth}{\textit{\color{red}{Cartoon Model}}}
+\spic{0.2}{\jlfigpath/f1.pdf}
+\end{column}
+\hspace{0.05\textwidth}
+\begin{column}{0.45\textwidth}{\textit{\color{red}{Simulation Box}}}
+\spic{0.3}{\jlfigpath/f2.pdf}
+\end{column}
+
+\end{columns}
+\end{frame}
+
+\section{Outflow Dynamics : Launching}
+\begin{frame}{Radiation force}
+\begin{block}{Castor Abbott \& Klein Model}
+\begin{itemize}
+\item \textit{Line Driving force:} Main driving mechanism from evolved
+  massive stars.
+\item \textit{Physics:} Momentum transfer from photon to the gas. 
+  Optical depth depends on local flow variables - Sobolev Approximation.
+\item \textit{Formulae:} $f_{\rm line} = f_{\rm cont} \mathcal{M}(t)$
+where $t$ is a function of $Q_0$ and $\alpha$.
+\end{itemize}
+\end{block}
+\begin{center}
+\begin{tabular}{l l}
+\hline
+Quantity & Value\\
+\hline\hline
+Stellar Mass & 30 M$_{\odot}$\\
+Plasma $\beta$ & 5.0\\
+R$_{\rm in}$ & 1.0 AU \\
+Eddington $\gamma$ & 0.236 \\
+Q$_0$ & 1400.0 \\
+$\alpha$ & 0.55 \\
+$\rho_0$ [g cm$^{-3}$] & $5.0\times10^{-14}$\\
+\hline
+\end{tabular}
+\end{center}
 
@@
 
-\begin{frame}{Launching and Propagation}
+\begin{frame}{MHD Acceleration}
+\begin{columns}
+\begin{column}{0.4\textwidth}
+\begin{block}{Impact of Stellar radiation force.}
+\begin{itemize}
+\item Initial MHD flow achieves a steady state.
+\item Jet perturbed after MHD steady state : Addition of radiation force from star or disk. 
+\item The flow ultimately achieves a steady state \textbf{BUT} with increase in
+  jet velocity.
+\item Intensity of the force scales with the jet launching radius. 
+\end{itemize}
+\end{block}
+\end{column}
+\begin{column}{0.6\textwidth}
+\spic{0.23}{\jlfigpath/f6_col.pdf}
+\end{column}
+\end{columns}
 \end{frame}
 
-\begin{frame}{Radiation force}
-\end{frame}
-
-\begin{frame}{Chemistry and Cooling}
-\end{frame}
-
-\section{Outflow Dynamics : Launching}
-\begin{frame}{MHD Acceleration}
-\end{frame}
-
-\begin{frame}{Collimation and Radiation}
+\begin{frame}{Collimation and Radiation \myref{Vaidya et. al. 2011}}
+\begin{columns}
+\begin{column}{0.4\textwidth}
+\begin{block}{Impact of Stellar radiation force.}
+\begin{itemize}
+\item Star's mass and luminosity - \myref{Hosokawa 2008}
+\item Collimation : Opening angles at critical points in the steady
+  flow.
+\item Without radiation -- Alfven point : Dotted line,
+  Magnetosonic-fast : Solid line.
+\item With radiation -- Alfven point : Stars, Magnetosonic-fast : dots.
+\item Radiation force from Central Star -- \textbf{WIDENS THE FLOW}
+\end{itemize}
+\end{block}
+\end{column}
+\begin{column}{0.6\textwidth}
+\spic{0.23}{\jlfigpath/f11.pdf}
+\end{column}
+\end{columns}
 \end{frame}
@@
 \begin{frame}{Force Parameters and its impact}
+\begin{tabular}{l l}
+Magnetic field & Density and $\alpha$ \\
+\spic{0.18}{\jlfigpath/f9.pdf} & \spic{0.18}{\jlfigpath/f10.pdf}
+\end{tabular}
+\end{frame}
+
+\begin{frame}{Fixing mass flux?}
+\begin{tabular}{l l}
+Floating mass flux & Direct Influence \\
+\spic{0.18}{\jlfigpath/f12.pdf} & \spic{0.18}{\jlfigpath/f13_col.pdf}
+\end{tabular}
 \end{frame}
@@
 \begin{frame}{Resistive effects}
+Diffusive Disk Jet Launching \myref{Sheikhnezami et. al 2012} 
+\begin{center}
+\spic{0.5}{\figpath/Res_diskjet.png}
+\end{center}
 \end{frame}
@@
 \begin{frame}{A case of Orion Source I}
+\begin{columns}
+\begin{column}{0.35\textwidth}{Orion Source I - Masers}
+\spic{0.06}{/Users/bhargavvaidya/MyProject/work/Orion_BN_KL/MNRAS/Revised/f1.pdf}
+\end{column}
+\hspace{0.05\textwidth}
+\begin{column}{0.55\textwidth}{Simulation Model}
+\spic{0.07}{/Users/bhargavvaidya/MyProject/work/Orion_BN_KL/MNRAS/Revised/f2.pdf}
+\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{A case of Orion Source I}
+\begin{block}{Simulation Results \myref{Vaidya 2013}}
+\begin{itemize}
+\item SiO Masers :  n (H$_{2}$) $\sim 10^{9} \rm cm ^{-3}$ and T $\sim$ 2000 K \myref{Goddi et. al. 2009} 
+\item \textit{Dark band} - R $<$ 14 AU. T and $\rho$ optimum to
+  produce SiO masers within 15-60 AU : Consistent with Observations 
+\item 3D Velocities lie within observed range and show signatures of
+  rotation \myref{Matthews 2010}
+\end{itemize}
+\end{block}
+\begin{columns}
+%\hspace{0.1\textwidth}
+\begin{column}{1.0\textwidth}
+\spic{0.27}{/Users/bhargavvaidya/MyProject/work/Orion_BN_KL/MNRAS/Revised/f3.pdf}
+\end{column}
+\end{columns}
 \end{frame}
@@
 \section{Outflow dynamics : Propagation}
+
+\begin{frame}{Chemistry in Jets}
+\begin{block}{Initial Setup}
+\begin{itemize}
+\item Young jets -- largely atomic \myref{Dionatos 2009}, Ionization
+  fraction around 1\% \myref{Bacciotti 1995}, Molecules survive in jet
+  \myref{Glassgold 1991}
+\item Axisymmetric dense jet ($\eta$ > 1) enters into a fully molecular ambient
+  medium with density varying in height - $\rho_{\rm amp} \sim z^{-2}$
+\item Simplified Hydrogen chemistry : Tracks fraction of H$_2$, HI and
+  HII. 
+\end{itemize}
+\end{block}
+\begin{columns}
+\hspace{-0.1\textwidth}
+\begin{column}{0.95\textwidth}
+\tiny{
+\begin{tabular}{l l l l}
+\hline
+No. & Reaction & Rate Coefficient ($\rm {cm}^{3} s^{-1}$) &
+Reference~\footnote{REFERENCES -- (1) \myref{Cen 1992 [Eq. 26a]};
+  (2) \myref{Woodall 2007 [UMIST Database]} (3)
+  \myref{Galli 1998 [Eq. H17]}; (4) \myref{Abel 1997
+  [Tab. 3 Eq. 13]}; (5) \myref{Hollenbach 1979 [Eq. 3.8]}}\\
+\hline
+1. & H + e$^{-}$ $\rightarrow$ H$^{+}$ + 2e$^{-}$ & $k_1$ = $5.85
+\times 10^{-11}$ $T^{0.5}$ \rm{exp}(-157,809.1/T)/(1.0 + $T_{5}^{0.5}$) & 1\\
+2. & H$^{+}$ + e$^{-}$ $\rightarrow$ H + h$\nu$ & $k_2$ =
+$3.5\times10^{-12} (T/300.0)^{-0.8}$ & 2\\
+3. & H$_{2}$ + e$^{-}$ $\rightarrow$ 2H + e$^{-}$ & $k_3$ =
+$4.4\times10^{-10} T^{0.35} \rm{exp}(-102,000.0/T)$ & 3\\
+4. & H$_{2}$ + H $\rightarrow$ 3H & $k_4$ = $1.067\times10^{-10}
+T_{\rm eV}^{2.012}(\rm{exp}(4.463/T_{\rm eV})^{-1}((1. + 0.2472 T_{\rm eV})^{3.512})^{-1} $& 4\\
+5. &H$_{2}$ + H$_{2}$ $\rightarrow$ H$_{2}$ + 2H & $k_5$ = $1.0\times 10^{-8} \rm{exp}(-84,100/T)$ & 2\\
+6. & H + H $\overset{\rm dust}\longrightarrow$ H$_{2}$ & $k_6 =
+3.0\times10^{-17}\sqrt{T_{2}}(1.0 + 0.4\sqrt{T_{2} + 0.15} + 0.2T_{2} + 0.8T_{2}^{2})$ & 5 \\
+\hline
+\end{tabular}
+}
+\end{column}
+\end{columns}
+\end{frame}
 
@@
 \begin{frame}{SiO Abundance and Jet Velocity}
+\begin{columns}
+\begin{column}{0.5\textwidth}
+\begin{block}{SiO in outflows}
+\begin{itemize}
+\item SiO production by grain-grain collision \myref{Caselli 1997},
+  mantle evaporation \myref{Schilke 1997},
+  gas-grain interaction (sputtering) \myref{Gusdorf 2008} 
+\item Empirical dependence of n(SiO)/n(H$_2$) on flow velocity.
+\item SiO Abundance - 10$^{-12}$ in quiescent dark clouds
+  \myref{Ziurys 1989}
+\item SiO Abundance - 10$^{-7}$ to 10$^{-6}$ in outflows with flow
+  speeds > 60 km s$^{-1}$ e.g. L1448 \myref{Martin-Pintado 1992,
+    Dutrey 1997}
+\end{itemize}
+\end{block}
+\end{column}
+\begin{column}{0.5\textwidth}
+\spic{0.2}{\figpath/pfig3.pdf}
+\end{column}
+\end{columns}
 \end{frame}
@@
 \begin{frame}{Multi-Line survey : Emission II}
+\begin{block}{Multi-line transitions : HH 211}
+\begin{itemize}
+\item Lower energy transitions - SiO J=1-0,2-1 show more turbulent
+  features.\myref{Chandler 2001}
+\item Higher energy transitions - SiO J=5-4,8-7 are more compact and
+  trace the inner most jet \myref{Hirano 2006, Palau 2006, Nisini 2007}
+\end{itemize}
+\end{block}
+\begin{columns}
+\begin{column}{0.95\textwidth}
+\spic{0.24}{/Users/bhargavvaidya/MyProject/work/Leeds_Uni/SiOJets_New/PAPER/PFIGS/imshkvcontomaps.png}
+\end{column}
+\end{columns}
 \end{frame}
@@
 \begin{frame}[t]{Rotation or Wiggles?}
-  \begin{center}
+\begin{columns}
+\begin{column}{0.3\textwidth}
+\begin{block}{Work in Progress}
+\begin{itemize}
+\item Extention to 3D opens up slew of instabilities.
+\item Self generated internal shocks create stationary knots.
+\item Wiggles are evident at later stages of evolution. 
+\end{itemize}
+\end{block}
+\end{column}
+\begin{column}{0.7\textwidth}
   \movloop{8cm}{5cm}{61}{Img_3djet/contourjet1.}{0060}
-  \end{center}
+\end{column}
+\end{columns}
 \end{frame}
@@
 \section{Summary}
-\begin{frame}{Conclusions}
+\begin{frame}[plain]
+\frametitle{Conclusions}
+\begin{block}{Outflow Evolution}
+\begin{itemize}
+\item Radiative Line force from star plays a crucial role in widening
+  the flow for stars with mass $>$ 30 M$_{\odot}$.
+\item The Collimation degree increases with increase in mass
+  (luminosity) and decrease in magnetic fields, density and line force
+  parameters.
+\item \textit{Radiation MHD Interplay} :  Magnetic fields initially drive the outflow and then radiative
+  force takes over to compliment the dynamics.
+\end{itemize}
+\end{block}
+\begin{block}{EHV Emission}
+\begin{itemize}
+\item Axisymmetric jet driven molecular outflows can very well
+  reproduce features of EHV emission.
+\item PV diagrams show a distinct zig-zag pattern specific of EHV
+  emission from young outflows.
+\item Higher energy transition lines traces compact knots in the flow
+  while jet interaction regions are traced by low excitation lines.
+\item \textit{Chemistry and Dyanmics} : Synthetic observations by
+  combining chemistry with dynamical models provides a link between
+  future observations and theory. 
+\item 3D Modelling with enhanced chemical network is the way forward.
+\end{itemize}
+\end{block}
 \end{frame}

### 2014-01-21 PAPER/Paola_2/ms_ver3.tex
Added Talk folder
Paper version 3 submitted to Paola
Modified text to ver 3 to accomodate Paola final comments

@@
 \definecolor{orange}{rgb}{1,0.5,0}
-%\usepackage[colorlinks=True,citecolor=orange,urlcolor=blue,linkcolor=red]{hyperref}
+\usepackage[colorlinks=True,citecolor=orange,urlcolor=blue,linkcolor=red]{hyperref}
 
@@
 
-\newcommand{\figpath}{/home/phybva/SiOJets_New/PAPER/NEWFIGS}
+\newcommand{\figpath}{../NEWFIGS}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\title{SiO Molecular Jets around young stars - A numerical perspective}
-\title[EHV SiO component in Molecular Outflows]{Synthetic Observations of Extremely High Velocity (EHV) SiO component
+\title[EHV SiO components in Molecular Outflows]{Synthetic Observations of Extremely High Velocity (EHV) SiO components
   in young molecular outflows}
-\author[B. Vaidya, Tom Douglas, Paola Caselli]{B. Vaidya$^{1}$\thanks{E-mail:
-B.Vaidya@leeds.ac.uk (BV)}, Tom Douglas$^{1}$, Paola Caselli$^{1}$\\
+\author[B. Vaidya, T. Douglas, P. Caselli]{Bhargav Vaidya$^{1}$\thanks{E-mail:
+B.Vaidya@leeds.ac.uk (BV)}, Thomas Douglas$^{1}$, Paola Caselli$^{1}$\\
 $^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2
@@
    {High 
-velocity molecular outflows are extensively studied for both low mass
-and high mass stars. They are usually observed using standard outflow and shocks
+velocity molecular outflows are extensively studied for both low-mass
+and high-mass stars. They are usually observed using standard outflow and shocks
 tracers like CO and SiO. However, the exact nature of
@@
 of knotty jet propagation into a molecular cloud using the PLUTO
-code. Firstly, we evolve the jet dynamical quantities in conjunction
-with different non-equilibrium cooling prescriptions of varying complexities. 
-The most complex is that of molecular cooling along with
+code. The jet dynamical quantities evolve in conjunction
+with different non-equilibrium cooling prescriptions of varying
+complexities, including molecular cooling along and
 H$_2$ chemistry. This prescription allows us to track the formation
@@
      (ALMA) predictions for such
-     early molecular outflows shows bright emission coming from young
-     internal knots and bow shock due to thermal
+     early molecular outflows show bright emission coming from young
+     internal knots and bow shocks due to thermal
      instability. Our multi-line modeling of SiO supports
@@
      that higher line transitions trace
-     regions close to the axis of the jet. The dependence of emission on
+     regions closer to the axis of the jet. The dependence of emission on
      different cooling prescription and abundance profiles is clearly
@@
 formation in dense molecular cores. They are ubiquitous in both
-massive and low mass star forming regions. These supersonic flows,
+massive and low-mass star forming regions. These supersonic flows,
 perpendicular to the underlying accretion disk, play a vital role in
 removing excess angular momentum and thereby aiding in the accretion onto the protostar. 
-For low mass stars, they are believed to be launched by magneto-centrifugally forces and
+For low-mass stars, they are believed to be launched by magneto-centrifugally forces and
 further collimated by magnetic hoop stress
 \citep[][]{Blandford:1982p892, Konigl:2000p607}. However, in case of
-high mass stars, radiative forces also contribute to flow dynamics
+high-mass stars, radiative forces also contribute to flow dynamics
 during the later evolutionary stages (\citealt{Vaidya:2011p8992}). 
-Typically, these jets are a few parsec in size long and can be divided into
+Typically, jets are a few parsec in size and can be divided into
 three length-scale domains, viz. source and disk scales (1-10$^{2}\,$AU),
@@
 
-Bipolar molecular outflows from low and high mass stars
+Bipolar molecular outflows from low and high-mass stars
 have been studied in detail over the past 
@@
 \citealt{Gueth:1998p14058}, in HH300: \citealt{Arce:2001p14064}). These knots show their signatures
-as {\em{wedges}} in the PV diagrams \cite{Arce:2001p14065}. Also, 
+as {\em{wedges}} in the PV diagrams (\citealt{Arce:2001p14065}). Also, 
 observed in these outflows are signatures of rotation and
-precession (for e.g., in DG Tau: \citealt{Bacciotti:2002p2084}).
+precession (e.g., in DG Tau: \citealt{Bacciotti:2002p2084}).
 %
@@
 molecular emission in outflows is not clear. For a complete understanding it is imperative
-to complement these observations with theoretical models. Many models
+to complement these observations with models. Many models
 based on hydro-simulations and steady state shock calculations
@@
 infall from the envelope \citep{Rawlings:2013p14920} and radiation
-transfer \citep{Offner:2011p14861} to explain molecular 
+transfer \citep{Offner:2011p14861, Offner:2013p16717} to explain molecular 
 emission from Class 0 protostellar outflow sources.
@@
 (\vec{v} \cdot \nabla) \vec{v}) =
-- \nabla P + \frac{1}{4\pi} (\nabla \times \vec{B}) \times \vec{B}
+- \nabla P + \frac{1}{4\pi} (\nabla \times \vec{B}) \times \vec{B},
 \end{equation}
@@
 and $\vec{B}$ the magnetic field vector with the poloidal and toroidal
-components - $\vec{B}_{\rm p}, {B}_{\phi}$. Note that the forces due
+components - $\vec{B}_{\rm p}, \vec{B}_{\phi}$. Note that the forces due
 to gravity are neglected for this problem as the domain of interest is
@@
 %
-where the total energy density of the flow $E$ comprises contributions from 
-the internal energy $\epsilon$, the mechanical energy and the magnetic energy,
+where the total energy density $E$ of the flow comprises contributions from 
+the internal energy $\epsilon$, the mechanical energy and the magnetic energy:
 %
@@
 We have adopted a constant value of 5/3 for the adiabatic index and
-have discussed the applicability for such a choice in the appendix 
-(see ~\ref{sec:treatgamma}).
+have discussed the applicability for such a choice (see appendix \ref{sec:treatgamma}).
 
@@
 to be unmagnetized and non-turbulent. The density in the ambient
-medium varies with vertical height $z$ as, $\rho_{\rm amb}\sim (\rho_0/z^{2})$
-which is consistent with observations \citep{Keto:2010p15549,
-  Caselli:2011p13935}. The value of
+medium varies with vertical height $z$ as $\rho_{\rm amb}\sim (\rho_0/z^{2})$
+which is consistent with observations at distances $\gtrsim$1000\,AU from the center. \citep[e.g.,][]{Keto:2010p15549}. The value of
 $\rho_0$ depends upon the density contrast, $\eta$, between the jet and
@@
 slightly higher ambient temperature we get the same results for jet dynamics and 
-in turn the computations are less expensive especially considering the stiff 
-rate equations used to model cooling in flows.
+in turn the computations are less expensive considering the large
+temperature gradient coupled with stiff rate equations used to model cooling in flows.
 
@@
 100\,AU at a few thousand AU from the source \citep{Ray:2012p15733}.
-These jets have mass outflow rates of 10$^{-7}$ M$_{\odot}$
+These jets have mass outflow rates of $\sim$ 10$^{-7}$ M$_{\odot}$
 yr$^{-1}$ \citep{Dougados:2010p15774}. Younger and 
@@
   Bally:2007p2340}. However, in case of 
-young jets the temperature is
+young jets, the temperature is
 considerably lower (i.e, by an order of magnitude) than found in jets from Class I/II
@@
 dependence of such weak magnetic fields on density and radial distance in velocity-variable flows, 
-\cite{Hartigan:2007p15768} has shown that at large distances from the 
-star these fields only play a minor role in the dynamics. Thus for all
+\cite{Hartigan:2007p15768} have shown that at large distances from the 
+star these fields only play a minor role in the dynamics. Thus, for all
 our runs the value of magnetic field strength, $B_{\phi}(r_{\rm m})$ 
@@
 \label{ssec:molcool}
-Typically, early collimated outflows have cooling times shorter than
+Typically, young collimated outflows have cooling times shorter than
 the dynamical times, implying that the radiative cooling plays a vital
@@
 number density n$_{\rm H}$ comprises of contribution from atomic and
-molecular hydrogen i.e., n$_{\rm H}$ = n$_{HI}$ + n$_{H2}$. Whereas
+molecular hydrogen i.e., n$_{\rm H}$ = n$_{\rm HI}$ + n$_{\rm H2}$. Whereas
 the contribution to electrons comes from the ionized hydrogen, n$_{\rm HII}$ and
@@
 The formation and destruction of
-fractions (denoted by \textbf{X}$_{i}$ in eq.~\ref{chemevol}) of three species, viz., fHI, f$H_{2}$
+fractions (denoted by \textbf{X}$_{i}$ in eq.~\ref{chemevol}) of three species, viz., fHI, fH$_{2}$
 and fHII are tracked by the code based on the temperature dependent reaction rates
 whose coefficients are specified 
-in the Table~\ref{tab:chemeq} along with their literature references.
+in Table~\ref{tab:chemeq} along with their literature references.
 
@@
 4. & H$_{2}$ + H $\rightarrow$ 3H & $k_4$ = $1.067\times10^{-10}
-T_{\rm eV}^{2.012}(\rm{exp}(4.463/T_{\rm eV})^{-1}((1. + 0.2472 T_{\rm eV})^{3.512})^{-1} $& 4\\
+T_{\rm eV}^{2.012}\rm{exp}(-(4.463/T_{\rm eV})(1. + 0.2472 T_{\rm eV})^{3.512}) $& 4\\
 5. &H$_{2}$ + H$_{2}$ $\rightarrow$ H$_{2}$ + 2H & $k_5$ = $1.0\times 10^{-8} \rm{exp}(-84,100/T)$ & 2\\
@@
 For low temperatures, we also 
-take into account contribution to cooling function from molecules like
+take into account contributions to the cooling function from molecules like
 CO, whose abundance with respect to $n_{\rm H}$ is fixed to a
-value of 10$^{-5}$ as measured in dense cores like L1544 \citep{Keto:2010p15549}. 
+value of 10$^{-5}$ assuming an average CO depletion factor across the
+envelope of $\sim$ 10 \citep[e.g.][]{Crapsi:2005p16655}. 
 For each of the other molecules contributing to the cooling function (like OH, H$_{2}$O and atomic OI)
@@
 uncertain abundance values are rather arbitrary for these molecules. 
-However, their contribution is only important when temperature is $<$
-100\,K as seen in figure~\ref{fig:tempvar}. As the internal shocks, where most
-of the molecular hydrogen is produced maintain temperatures higher
+For example, the adopted abundance of H$_{2}$O is higher than that found by
+\citealt{Caselli:2012p16713} in a pre-stellar core ($\lesssim$
+10$^{-7}$). Inspite of such over estimated abundance values, their
+contribution is only important when temperature is $<$100\,K as seen in
+figure~\ref{fig:tempvar}. As the internal shocks, where most
+of the molecular hydrogen is produced, maintain temperatures higher
 than 100\,K and densities $\sim$10$^{6}$ cm$^{-3}$, cooling due to these molecules do not
@@
 molecular hydrogen during the initial stages of jet
-evolution. Whereas, for temperatures above 3000\,K the
-cooling is mainly via H$_{2}$ disassociation. The total curve for the
+evolution. For temperatures above 3000\,K the
+cooling is mainly via H$_{2}$. The total curve for the
 whole temperature range obtained in our runs is shown in black.
@@
 we update this curve at each time step based on the fraction of
-various hydrogen species. Thus during the evolution, 
+various hydrogen species. Thus, during the evolution, 
 contributions from collisional ionizations and excitations become
@@
 \ref{subsec:gridding}. At each of these points, the density of the
-main collision partner (equivalent amount of H$_2$, given by n(H$_2$)+
-n(HI), assuming that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and unresolved turbulent velocity are specified.
+main collision partner (equivalent amount of H, given by n(H$_2$)+
+n(HI), assuming that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
@@
 \subsection{Grid construction} \label{subsec:gridding}
-In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
-These candidates then have their equivalent H$_2$ number density, and the number density of SiO, compared against those of a reference point in order to decide if the candidate point is to be used in the grid or not.
-Candidate grid points are selected at random in a cylindrical coordinate system that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
-For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random coordinates, the H$_2$ density and SiO density at the candidate point (n and m, respectively) are compared against the densities of a reference point in the un-perturbed ambient medium multiplied by a factor of $\frac{4\eta}{5}$ (n$_{ref}$ and m$_{ref}$), where $\eta$ is the density contrast between the jet and ambient medium.
+In order to construct the grid, candidate points are randomly selected
+from the volume to be simulated. These candidates then have their
+equivalent H$_2$ number density, and the number density of SiO,
+compared against those of a reference point in order to decide if the
+candidate point is to be used in the grid or not. Candidate grid
+points are selected at random in a cylindrical coordinate system that
+is linearly spaced in z and $\theta$ and logarithmically spaced in
+r. For each point to be selected, a random number $\alpha$ is drawn
+from the semi-open set [0,$\,$1) as a threshold. After selection of
+random coordinates, the H$_2$ number density and SiO number density at
+the candidate point (n and m, respectively) are compared against the
+number densities of a reference point in the un-perturbed ambient medium multiplied by a factor of $\frac{4\eta}{5}$ (n$_{ref}$ and m$_{ref}$), where $\eta$ is the density contrast between the jet and ambient medium.
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use.
@@
 Typically, extremely low abundance of SiO is
-found (n(SiO)/n(H2) $< 3\times10^{-12}$) in dark, dense clouds such
-as TMC1 \citep{Ziurys:1989p14699,MartinPintado:1992p14309}. Whereas, in
+found (n(SiO)/n(H$_{2}$) $< 3\times10^{-12}$) in dark, dense clouds such
+as TMC1 \citep{Ziurys:1989p14699,MartinPintado:1992p14309}. Whereas in
 outflows like L1448, SiO abundance can increase up to 10$^{-6}$ 
@@
 gaseous SiO due to slow C-type shocks has been suggested to occur via release of
-silicon from grain cores and from grain mantles. Various stationary
+silicon from grain cores and to a lesser extent from grain mantles. Various stationary
 shock models indicate a sudden abundance increase in SiO 
@@
 outflows have velocities of the order of 100 km\,s$^{-1}$ as in the present
-case. In case of L1448, \cite{MartinPintado:1992p14309}
+case. In L1448, \cite{MartinPintado:1992p14309}
 have shown that for extreme velocities (obtained from shift in the
@@
 lie around 60-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.
-Shocks due to such outflows could dissociate H$_{2}$ and molecules observed in such
-energetic outflows could have been reformed in the flow as suggested by
-detailed models of J-shocks by \cite{Neufeld:1989p14322}. SiO formation in J shocks
+Shocks due to such outflows could dissociate H$_{2}$, and molecules observed in such
+energetic outflows could have been reformed in the post-shock gas as suggested by
+detailed models of J-shocks by \cite{Neufeld:1989p14322}. SiO formation in J-shocks
 has also been modelled recently and has thought to be the source of
@@
 
-Further, the velocities obtained from the dynamical simulations are in fact the
+The velocities obtained from the dynamical simulations are the
 jet flow velocities. They can well be different from the shock
@@
 ambient medium. For the bow shock, one can estimate the shock velocity 
-by equating the pressures across the shock surface, \citep[e.g.,][]{Masson:1992p14101}
+by equating the pressures across the shock surface \citep[e.g.,][]{Masson:1992p14101}:
 \begin{equation}
@@
 \end{equation}
-where v$_{\rm s}$ is the velocity of the bow shock 
-and v$_{\rm jet}$ is the jet velocity. 
+where $v_{\rm s}$ is the velocity of the bow shock 
+and $v_{\rm jet}$ is the jet velocity. 
 Considering the dependence of ambient density on the vertical distance, 
@@
 velocities across the knot and can as well be approximated 
-to be same as flow velocity. However, the shock velocity 
+to be the same as the flow velocity. However, the shock velocity 
 in the frame of reference of the knot can be considerably different than the flow velocity 
@@
 these internal shock velocities to estimate 
-SiO abundances. While, observations measure bulk velocities of the 
-flow and relate molecular abundances to the same. 
+SiO abundances. On the other hand, molecular lines provide information
+about the bulk velocity of the flow.
 %
@@
 With such extreme choices we are over-estimating the abundance values in 
-regions with processed velocities (i.e, jet interface), however, 
-in regions close to internal knots the abundance values will be within a factor of 2. 
+the  jet interface, however, 
+in regions close to internal knots, the abundance values will be within a factor of 2. 
 In order to get rid of an arbitrary discontinuous change of abundance, we also
@@
 abundance may indeed be the case in regions where SiO is seen
-in widespread \citep[e.g.,][also see section~\ref{sec:discussion}]
+widespread \citep[e.g.,][also see section~\ref{sec:discussion}]
 {Lefloch:1998p13983}. Also along with a Gaussian profile, we consider
-the case where we extent the abundance of 10$^{-6}$ beyond 60 km\,s$^{-1}$.   
+the case where we consider an abundance of 10$^{-6}$ beyond 60 km\,s$^{-1}$.   
 In addition to this, if the temperature at the point is greater than
@@
 \label{sec:parasurvey}
-The results and analysis for the present work are divided in two parts,
-viz., the dynamical numerical simulations and the
+The results and analysis for the present work are divided in two parts: the dynamical numerical simulations and the
 radiative transfer analysis. For each part we have used certain parameters
@@
 varying $\eta$ and cooling prescriptions, along with the peak
-intensity and line widths at the bow shock.
+intensity and line widths of SiO(2-1) at the bow shock.
 %
@@
 the fractional abundance profile of SiO and the angle of inclination with
-respect to line of sight denoted by $\phi$. Section~\ref{ssec:sioabun}
-describes all the profiles used for the present study. $\phi$ = 90$^{\circ}$ indicates that
+respect to line of sight denoted by $i$. Section~\ref{ssec:sioabun}
+describes all the profiles used for the present study. $i$ = 90$^{\circ}$ indicates that
 the outflow is in the plane of the sky. 
 Additionally, we have used two other angles of inclination apart from the
-plane of the sky, i.e, $\phi = 45^{\circ}, 60^{\circ}$ to compare
+plane of the sky, i.e, $i = 45^{\circ}, 60^{\circ}$ to compare
 results with observations. The runs with different fractional
@@
 ambient medium with a velocity of v$_{\rm jet,0}$ = 100 km
-s$^{-1}$ which is further superimposed by sinusoidal perturbations to
+s$^{-1}$,  which is further superimposed by sinusoidal perturbations to
 replicate dense knots. The maximum value of toroidal magnetic field is
-set to be 37$\mu\,G$ at the base of the jet.
+set to be 37\,$\mu G$ at the base of the jet.
 \cite{Dionatos:2009p15670} have detected atomic lines
-towards a molecular jet from L1448-C indicating a presence of embedded
-atomic jet at low excitation. Additionally, they also detect pure
-rotational transitions from H$_{2}$ indicating presence of molecules
+towards a molecular jet from L1448-C, indicating a presence of an embedded
+atomic jet. Additionally, they also detect pure
+rotational transitions from H$_{2}$ indicating the presence of molecules
 along with the atomic jet. Line ratios from this source indicate that the
 atomic gas is characterized by an an ionization fraction of 1\%,
-which is considerably less as compared to ionization fraction of
+which is considerably less than as compared to ionization fraction of
 10-20\% measured in optical jets \citep{Bacciotti:1995p15970}.
-Initial jet composition is prescribed
+Initial jet composition is prescribed to
 be 89\% atomic, 10\% molecular and 1\% ionized, in qualitative
-agreement of above observational results. 
+agreement with above observational results. 
 %
@@
 run are given as inputs to the radiative transfer code to obtain the observational features
-corresponding to SiO molecule. 
+corresponding to SiO molecules. 
 For the radiative transfer calculation, the source in the reference
-run is stationary and the jet is in the plane of the sky ($\phi =
-90^{\circ}$). A Gaussian profile with a step is used for the fractional abundance
+run is stationary and the jet is in the plane of the sky ($i =
+90^{\circ}$). A Gauss Step (see fig~\ref{abun}) is used for the fractional abundance
 of SiO.
@@
 prescriptions, which are described in
-Sect.~\ref{sec:chem}. Figure~\ref{fig:coolcmpdyn} shows the density of the MHD
+Sect.~\ref{sec:chem}. Figure~\ref{fig:coolcmpdyn} shows the volume density of the MHD
 jet at time $\sim$ 1000 years for these different cooling
@@
 for the molecular jet the cooling terms evolve with jet dynamics as the fraction of
-various hydrogen species change over time. Whilst the terms remain fixed to initial values, shown in the fig~\ref{fig:tempvar}, for the jet with tabulated
+various hydrogen species change over time. On the contrary, the terms
+remain fixed to the initial values, shown in fig~\ref{fig:tempvar}, for the jet with tabulated
 cooling. Additionally, the material at the bow shock for the jet
 with tabulated and molecular cooling condenses forming dense knots. 
-Such a condensation is caused due to thermal instability and is 
+Such a condensation is due to thermal instability and is 
 a typical feature of axi-symmetric radiative jets 
@@
 The dynamical states for each of this cooling prescriptions are then 
-given as inputs to the radiative transfer code to obtain integrated J = 2-$>$1 SiO emission
+given as inputs to the radiative transfer code to obtain integrated SiO(2-1) emission
 maps shown in figure~\ref{fig:coolcmpsio}. The differences in dynamical
@@
 profile. They are then placed at a distance of
-16.7$\,$pc and convolved with a beam with FWHM of 2.0\arcsec in order
+16.7$\,$pc and convolved with a beam with FWHM of 2.0\arcsec, in order
 to create the maps shown. 
@@
 cooling is coming from the conical jet head and younger knots closer
-to base of the flow. Additionally, features in the shell at Z $\sim$
+to base of the flow. Additionally, features in the shell at Z/R$_{\rm jet}$ $\sim$
 60, 75 also show evidence of faint emission. In case of the jet with
-power-law cooling the emission mostly arises from the
+power-law cooling, the emission mostly arises from the
 internal knots. 
 The emission coming from jets with
-tabulated and molecular cooling resembles that observed in young molecular outflows.
+tabulated and molecular cooling resembles that observed in young
+molecular outflows, although the tabulated jet is narrower.
 Also in these outflows, strong emission arises from the
@@
 In summary, different cooling prescriptions strongly influence the
-dynamics of MHD jet propagation in particular the thickness and
+dynamics of MHD jet propagation, in particular the thickness and
 structure of the bow shock. These dynamical differences are
@@
 model consistently takes into account the feedback of temperature and
-density variation to evolve the chemical species unlike the tabulated cooling
+density variation to evolve the chemical species, unlike the tabulated cooling
 where the fraction of chemical species remains fixed. Thus, for our reference
@@
 
-\subsection{Molecular cooling and H$_2$ Chemistry}
+\subsection{Molecular cooling and H$_2$ chemistry}
 The molecular cooling in our
-model includes the evolution of H$_2$ chemistry along with
+model takes into account the evolution of H$_2$ chemistry along with
 contributions to cooling from fixed fractions of other molecules like
@@
 The highest temperature of $\sim$ 50000\,K is attained in our flow at the
-tip of the bow shock. While the temperature on the edges (i.e.,interface between
-jet and the ambient medium) is lower than 5000\,K. Also the relatively
+tip of the bow shock. While the temperature on the edges (i.e.,the interface between
+jet and the ambient medium) is lower than 5000\,K. Also, the relatively
 weaker shocks formed nearby knots do not heat up the material beyond
@@
 chemistry is evolved due to shocks.
-They are : (1) The tip of the jet , (2) The edges of the jet and
+They are : (1) the tip of the jet , (2) the edges of the jet and
 (3) intermediate knots. 
@@
 into the cold molecular medium , it forms a strong shock resulting in
-forming a density and temperature discontinuity. Such a jump in
+a density and temperature discontinuity. Such a jump in
 dynamical quantities plays a crucial role in the evolution of
@@
 panel of the figure shows the hydrogen number density in the jet. 
-The fraction of all hydrogen forms are shown in bottom
+The fraction of all hydrogen forms are shown in the bottom
 panels of figure~\ref{fig:Hmolform} along two representative regions in
@@
 interface of the knot and the ambient medium. The interaction of the
-knot with the medium raises that temperature to 1000\,K and
-accumulates the matter so that the density increases up to
+knot with the medium raises the temperature to 1000\,K and
+accumulates matter so that the density increases up to
 10$^{6}$ cm$^{-3}$. Behind the shock as the material cools, atoms
@@
 fractions reach a value of 0.5. The ionized fraction is
-extremely low in this region due to low temperatures. However at the
+extremely low ($< 10^{-3}$) in this region due to the low temperatures. However at the
 bow-shock, temperatures rise up to 20000\,K. Molecular
@@
 increase in its fraction 
-(figure~\ref{fig:Hmolform}). The peak in ionized fraction of 0.15
+(figure~\ref{fig:Hmolform}, bottom right panel). The peak in ionized fraction of 0.15
 coincides with the peak in temperature profile as expected. The
@@
 
-\subsection{Emission Maps, Spectra and PV diagrams}
+\subsection{Emission maps, spectra and PV diagrams}
 \label{ssec:emspecpv}
@@
 right panel is obtained along the jet as indicated by the vertical magenta
-line in the left panel. The velocities are show along the X-axis. High velocity features
+line in the left panel. The velocities are shown in the X-axis. High velocity features
 are clearly seen in regions corresponding to the knots in the emission
@@
 crosses in top left panel). The knot closer to the base and the region near the bow shock 
-shows a peak integrated intensity of 15-20\,K. Whereas, the integrated 
-intensity decreases and reaches to about 5\,K in the middle of the jet.
+shows a peak intensity of 15-20\,K. Whereas, the 
+intensity decreases and reaches about 5\,K in the middle of the jet.
 The line widths seen are typically around 5-10 km s$^{-1}$.
@@
 widths now are typically of the order of 20 km s$^{-1}$. 
-The PV diagrams in these runs are not longer symmetric. Instead, they show a distinct {\it zig-zag}
+The PV diagrams in these runs are no longer symmetric. Instead, they show a distinct {\it zig-zag}
 pattern at each of the knots and region close to the bow shock.
@@
 a simplistic manner (see sec~\ref{ssec:sioabun}). In
-figure~\ref{fig:diffabunem}, we compare the maps for J = 2-$>$1
+figure~\ref{fig:diffabunem}, we compare the maps for SiO(2-1)
 emission at an inclination angle of 90$^{\circ}$ for four different abundance profiles. 
@@
 emission from the internal knots in these images. Using the step profile results in
-emission from  all the internal knots in the J=2-$>$1 line. However, some of
-these knots are not observed when using the same top-hat profile. 
+emission from  all the internal knots in the SiO(2-1) line. However, some of
+the knots are not observed when using the top-hat profile. 
 Similar qualitative characteristics are seen in case of a Gaussian
-abundance profile. In particular, the case without a step beyond 60\,km\,s$^{-1}$
-produces emission from the region closest to the bow shock and the lower most knot, 
+abundance profile. In particular, the case where abundance decreases
+smoothly beyond 60\,km\,s$^{-1}$,
+produces emission only from the region closest to the bow shock and the lower most knot, 
 while the internal knots do not show any appreciable emission. While, the 
-Gaussian profile with a step produces very similar
+Gauss Step profile produces very similar
 features as that of the step profile effectively making the initial rising part 
-of the curve redundant. 
+of the curve unimportant. 
 %
@@
 The dependence of emission on SiO abundance profile is expected due to
-the distribution of jet velocity obtained from dynamical
+the distribution of jet velocities obtained from the dynamical
 simulations. We see that the velocity of internal knots lie around
@@
 Additionally, the internal knots show their distinct signatures in
-form of {\em Hubble wedges} as seen in the PV diagrams for these
+form of {\em wedges} as seen in the PV diagrams for these
 different profiles (see
@@
 were scaled to a distance of 300\,pc and used as the sky models for observations of
-the J=2-1, J=5-4 and J=8-7 lines at frequencies of 86.85, 217.10 and
+the J=2-1, J=5-4 and J=8-7 lines of SiO at frequencies of 86.85, 217.10 and
 347.33$\,$GHz, which fall in ALMA bands 3, 6 and 7, respectively. The observations
@@
 presents the ALMA prediction obtained from our reference run. The
-left panel shows the integrated emission of SiO J = 5-4 line while the right
-shows the PV diagram for the same line and over laid are
-the contours of SiO J = 2-1 and J = 8-7. The contour levels are marked
+left panel shows the integrated emission (as map and contours) 
+of SiO(2-1), (5-4) and (8-7) lines, while the right
+panel shows the PV diagram for the same lines. The contour levels are marked
 on the color bar of each panel.
@@
 A quantitative comparison is not possible due to the different
-molecule observed. Another source which is studied in details with ALMA band 7 is
+molecule observed. Another source which is studied in details, with ALMA band 7 is
 one of the most energetic, luminous molecular outflows
 G331.512-0.103 (\citealt{Merello:2013p15066}). Observations of this outflow
-associated with a high mass star reveal a compact, extremely young
+associated with a high-mass star reveal a compact, extremely young
 bipolar outflow and a symmetric out-flowing shell. Further, their PV
@@
 consistently identify the regions where molecular hydrogen is formed
-and disassociated (see fig.~\ref{fig:Hmolform}). The SiO emission that we
+and disassociated (see fig.~\ref{fig:Hmolform}). {\em The SiO emission that we
 obtain from our radiative transfer calculations is associated with
@@
 as observed in case of L1157 molecular outflow
-\cite{Gueth:1998p14058}. A contour map of SiO
+\cite{Gueth:1998p14058}}. A contour map of SiO
 emission obtained from the reference run is shown in
 figure~\ref{fig:ltconts}. Further, we find SiO emission coming from velocities 
-of the order of 40-70 km\,s$^{-1}$ (see fig
+of the order of 40-70 km\,s$^{-1}$, when $i$ = 45$^{\circ}$ (see fig
 ~\ref{empvspec45}). Additionally, we see a distinct saw-tooth pattern
@@
 \subsection{Line transitions and ratio}
-Numerous molecular outflows with jet-like bullets have been
+Numerous molecular outflows with jet-like SiO bullets have been
 observationally studied till date. In particular, H7-11
@@
 excitation energies of different lines. In particular, the lowest
-transition J=1-$>$0 shows most of the emission coming from the
+transition SiO(1-0) shows most of the emission coming from the
 interface between the jet and ambient medium, along with emission from
-the dense knots formed at the base of the flow. On the other hand, SiO (5-4) and (8-7) emission, 
+the dense knots formed at the base of the flow. On the other hand, SiO(5-4) and (8-7) emission, 
 is more concentrated in the inner jet regions and arise mainly from
 the shocks due to internal knots. Such a trend in emission with excitation energies coming from different SiO line transitions
-have been observed in young outflows (for e.g., {\it{L1448}}
+have been observed in young outflows (for {\it{L1448}}
 bullets \citep{Nisini:2007p13128}, {\it{HH211}}
@@
   Hirano:2006p14411}. Further, the evolved post-shock gas near the
-bow shock also show bright emission for these high J transitions. 
+bow shock also shows bright emission for these high J transitions. 
 This gas is linked to the thermal instability associated with
@@
 bow shock with high resolution does give a sense of clumpiness
-in the flow backing the suggestions to explain clumpy SiO emission has
-also been observed by \cite{Chandler:2001p14376}.
+in the flow, backing the suggestions to explain clumpy SiO emission 
+observed by \cite{Chandler:2001p14376}.
 %
@@
 They can also fit the observed fractional SiO abundance of
-$\sim$ 10$^{-7}$ in these outflows. However, they fail to predict all
+$\sim$ 10$^{-7}$ in these outflows. However, {\em they fail to predict all
 the line profiles and in particular their similarities for low and
-high excitation lines. Line emission for SiO from our model also traces similar
+high excitation lines, which we are able to obtain.} 
+Line emission for SiO from our model also traces similar
 physical environment. Fig.~\ref{fig:Hmolform} shows that regions close
@@
 emission is present, with fractional abundances between 10$^{-6}$ to 10$^{-8}$.
-The line profiles shapes obtained from our study fit reasonable well with that observed by
+The line profiles shapes obtained from our study fit reasonably well that observed by
 \cite{Nisini:2007p13128}, especially for the bullets seen in
-L1448. Interestingly, in our models, the line profiles are equally broadened for low as well
-as high excitation lines. The top panel of fig.~\ref{fig:lineratio} shows spectra for three line
+L1448. {\em Interestingly, in our models, the line profiles are equally broadened for low as well
+as high excitation lines}. The top panel of fig.~\ref{fig:lineratio} shows spectra for three line
 transitions for the reference run but with an angle of inclination
-$\phi$ = 60$^{\circ}$ and convolved with a single dish beam of
-15\arcsec to simulate observed integrated
+$i$ = 60$^{\circ}$ and convolved with a single dish beam of
+15\arcsec, to simulate observed integrated
 intensities of L1448 bullets observed with large beams from JCMT and
-IRAM. Intensities predicted from our reference model, $\int T_{\rm MB} dV$ = 5.76 for SiO(2-1), 
+IRAM. Intensities predicted from our reference model, $\int T_{\rm MB}
+dV$ = 5.76 K\,km\,s$^{-1}$ for SiO(2-1), 
 lie within a factor of two from the observed values (Table 2 of \citealt{Nisini:2007p13128}).
@@
 right panel of fig.~\ref{fig:lineratio}. The curve obtained 
-show a very similar shape of a distinct rise followed by a fall in
+shows a distinct rise followed by a fall in
 integrated emission for higher transitions with a peak in
-emission for J$_{\rm up}$ = 3. Such a curve is used for kinematic studies and 
-helps to predict the hydrogen number density and temperature in outflows. Physical
-conditions in outflows can also be studied by estimation of line ratios.
+emission for J$_{\rm up}$ = 3. 
 Values $\approx$ 1 for line ratios SiO(8-7)/(5-4) and SiO(5-4)/(2-1) have been
@@
   Lee:2008p13697} and also for molecular outflows from massive
-young stellar object IRAS 17233-3606 (\citealt{Leurini:2013p13165}).
+young stellar object in IRAS 17233-3606 (\citealt{Leurini:2013p13165}).
 The local velocity gradient (LVG) slab modeling with optically thin approximation were unable to produce
@@
 In summary, the shape, ratio and peak intensity of the spectra
-obtained from our model fit very well to observed values implying
-that SiO emission from our model is tracing the regions with right physical
-conditions that are required to emit SiO in the gas phase via shocks.
+obtained from our model fit very well the observed values implying
+that SiO emission from our model is tracing regions with physical
+conditions similar to those observed.
 
@@
 %
-We have presented a model that is able to explain the spectral characteristics
+We have presented a simple model that is able to explain the spectral characteristics
 of the SiO EHV component seen
 in several young outflows. The reference model
-consistently solves for the H$_{2}$ chemistry in presence of
-appropriate cooling. The steady state temperature, density and velocities obtained from dynamical
+consistently solves for the H$_{2}$ chemistry in the presence of
+appropriate cooling. The temperature, density and velocities obtained from dynamical
 simulation is used as input in the non-LTE radiative transfer code to obtain SiO maps, spectra and PV
@@
 is the SiO fractional abundance and its dependence on shock velocity. 
-Though 1D models that study the formation of SiO in gas phase from grain-grain and grain-mantle
+Though 1D models that study the formation of SiO in the gas phase from
+sputtering and grain-grain 
 collisions exists, their focus is mainly on weaker shocks
 \citep{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800, VanLoo:2013p16573}. 
-The pulsating jet propagation model presented here have flow speeds
+The pulsating jet propagation model presented here have bulk velocities
 reaching up to 120 km\,s$^{-1}$. We have used few
@@
 with complex chemistry is beyond the scope of this paper 
-as this could imply to include dust grains and sputtering 
-as well as grain-grain collisions (i.e. an MHD multi-fluid approach).  
+as this could imply to include grain processing and more gas-phase
+chemistry in an MHD multi-fluid approach.  
 %
@@
 The model presented in this paper targets the very early phases of molecular
-outflows i.e., dynamical time scales of 1000 years.
+outflows i.e., dynamical time scales of $\sim$ 1000 years.
 As discussed in sections above, the unique combination of pulsating
-jet with chemistry and cooling followed by non-LTE radiative transfer
+jet with simple chemistry and cooling followed by non-LTE radiative transfer
 calculations has shown success in fitting the line shapes, integrated intensity and line ratios of SiO
@@
 flow and that from the more evolved gas near the
-bow shock. To ascertain this fact in more details, one would
+bow shock. To ascertain this fact in more detail, one would
 need to track the bow shock for 10$^{4}$ years
@@
 completely destroying the grains. \cite{JimenezSerra:2010p15530} also found parsec-scale emission of SiO
-toward an infrared dark cloud suggesting that large scale shocks (may
-be triggered by cloud-cloud collisions \citealt{Henshaw:2013p15540}) may
+toward an infrared dark cloud, suggesting that large scale shocks
+(triggered by cloud-cloud collisions; \citealt{Henshaw:2013p15540}) may
 be responsible.
@@
 \item Different cooling prescriptions used for our model
-  significantly influence thickness of the jet. An
+  significantly influence the thickness of the jet. An
   efficient mode of cooling does reduce the size of the cocoon and results
-  in a more narrow jet. In addition, the bow shock structure
-  differs with various cooling modes. Also, with realistic cooling
-  functions one sees development of
-  thermal instability at the jet head which also shows a significant emission in SiO
+  in a more narrow jet. The bow shock structure
+  differs with various cooling modes. With realistic cooling
+  functions 
+  thermal instability develops at the jet head, which also shows a significant emission in SiO
   along with young internal knots that are formed close to the base of
@@
   typically have molecular hydrogen densities n$\sim$ 10$^{6}$
-  cm$^{-3}$ and temperatures $>$ 500\,K which is consistent with
+  cm$^{-3}$ and temperatures $>$ 500\,K, which is consistent with
   properties deduced from LVG modeling of observational data of
@@
   line transitions are sensitive to different regions in the jets. For
-  example, the SiO J = 1-$>$ 0 transition is mostly excited due to
-  the interaction of the jet with the ambient medium, while SiO J = 8-$>$ 7 trace the inner most jet regions as
-  they are excited only in the internal knots. This finding very well
+  example, the SiO(1-0) transition is mostly excited due to
+  the interaction of the jet with the ambient medium, while SiO(8-7) 
+  trace the inner most jet regions as
+  they are excited only in the internal knots. 
+  This finding very well
   supports the multi-line observational surveys done for young
-  molecular outflows, particularly, HH 211.
+  molecular outflows, particularly, HH 211. Our models
+  can also reproduce similarities in line profile shapes for low and high
+  excitation lines.
 \item Single-dish synthetic spectra obtained from our model typically
-  have intensity of 0.3-0.5\,K and peak around 50\,km\,s$^{-1}$ and have a
+  have intensities of 0.3-0.5\,K, peak around 50\,km\,s$^{-1}$ and have a
   typical line width of 20\,km\,s$^{-1}$. Such modeled spectra are in
   excellent agreement with characteristic features of EHV emission of
-  SiO seen in young molecular outflows . In addition, the line ratios 
+  SiO seen in young molecular outflows . The line ratios 
   T(8-7)/T(5-4) and T(5-4)/T(2-1), predicted from our models have values close to
@@
   older knots is clearly seen as a shift of centroid velocities by
-  7-10\,km\,s$^{-1}$ in the first 10$^{3}$ years of evolution.
+  7-10\,km\,s$^{-1}$ at the end of the first 10$^{3}$ years of evolution.
 \item The predicted PV diagrams from our models show a distinctive
-  knot like features that are generally observed in outflows like IRAS
+  saw-tooth features that are generally observed in outflows like IRAS
   04166+2706.
 \item Emission from internal knots do depend on the chosen profile of
-  the abundance. On one extreme where all the internal knots emit SiO  
-  with a step profile whereas, no emission in
+  the abundance. With the step profile all the internal knots emit SiO  
+  , whereas no emission in
   seen in knots when a Gaussian profile without a step is used. For
-  the remaining cases, we observe that emission mainly
+  the top-hat profile, we observe that emission mainly
   comes from knots close to the base of the flow and the condensation
@@
 
-In summary, this work for the first time provides a model
-that explains the origin of EHV emission seen in SiO from 
+In summary, this work for the first time provides a simplified model
+that explains the origin of the EHV emission seen in SiO from 
 the inner regions of young molecular outflows. The unique combination
@@
 template to compare current ALMA observations and can also predict
-signatures of thermal instabilities which can be tested with upcoming
-ALMA observations. In future, we would like to extend our
+signatures of thermal instabilities which can be tested with
+interferometric observations. In the future, we would like to extend our
 model to full three dimensions with adaptive mesh refinement
 and evolve the jet for longer time scales to explore slow velocity 
-component, precession and slew of other instabilities. Additionally, we would also like to have
-a better handle on SiO abundance not only from observations but also
+component, precession and other non-linear instabilities. Additionally, we would also like to have
+a better handle on SiO abundance, not only from observations but also
 by including dust micro-physics in our model.
@@
 state, eq.~\ref{EOS}, and thus the behaviour of the gas.
-In standard hydrodynamical codes the gas is generally
+In standard hydrodynamical codes, the gas is generally
 assumed to be a monatomic ideal gas, with $\gamma$ = 5/3. 
@@
 \end{equation}
-where, i is the index for each specie and $\mu$ is the mean molecular
+where i is the index for each specie and $\mu$ is the mean molecular
 weight. The mass fraction is added in the above equation following the
 correction suggested in \cite{OSullivan:2009p10078}.
-Additionally, the temperature dependence for example in case of
+Additionally, the temperature dependence in the case of
 H$_{2}$ molecule can be obtained using \cite{landau:1980},
@@
 
-However, for such an implementation in large scale simulations one must first
+However, for such an implementation in large scale simulations, one must first
 consider its cost, effectiveness, and even correctness. Although such
@@
 vibrational degrees of freedom of the gas through collisions. 
-\cite{Flower:2003p11236} maintains that therefore the adiabatic index of
-the post-shock gas has close to the ideal monatomic value of 5/3, 
+\cite{Flower:2003p11236} states that the adiabatic index of
+the post-shock gas close to the ideal monatomic value of 5/3, 
 and that in order to calculate correctly its evolution as the gas 
-adjusts one would have to model the rotational and vibrational 
+relaxes one would have to model the rotational and vibrational 
 levels of the hydrogen molecules in a time-dependent manner.
@@
 
-For large-scale simulations present here it is more practical to use
-the the standard value of 5/3 which is correct for the post-shock 
+For the large-scale simulations present here it is more practical to use
+the standard value of 5/3 which is correct for the post-shock 
 and predominantly atomic parts of the flow but incorrect for the
-equilibrated parts of the flow with a significant fraction of molecular matter.
-Since in this case, as the shock regions and their effect on the molecular hydrogen content of 
+equilibrated parts of the flow, with a significant fraction of molecular matter.
+As the shock regions and their effect on the molecular hydrogen content of 
 the ambient gas are of primary importance here, we opt for the more
-relevant, and also simpler, policy of keeping the normal $\gamma$
+relevant, and also simpler policy of keeping the normal $\gamma$
 value of 5/3 for our simulations.
@@
 \end{equation} 
-where, $$\zeta = \sqrt{\frac{\rho_{2}}{\rho_1}}$$.
+where, $$\zeta = \sqrt{\frac{\rho_{2}}{\rho_1}}.$$
 
@@
   catches the slower downstream material with velocity u$_2$ forming a
-two shock structure (u$_2 >$ v $>$ u$_1$). The in-between gas is squeezed out sideways
+two shock structure (u$_1 >$ v $>$ u$_2$). The in-between gas is squeezed out sideways
 forming the cocoon.}
@@
 velocity for the reference run is shown in fig.~\ref{fig:1dvelrho}.
-As can be clearly seen, the value of $\zeta \approx$ 1 for most of the
+The value of $\zeta$ is about 1 for most of the
 internal knots seen in our simulations. Thus, the velocity of the
@@
 flow with respect to the velocity of the working surface) of the
-upstream and downstream facing shocks have the same velocity given by \cite{Raga:1990p16416},
+upstream and downstream facing shocks have the same velocity given by \cite{Raga:1990p16416}:
 \begin{equation}
-w = \frac{u_2 - u_1}{2} = 0.5\Delta u.
+w = \frac{u_1 - u_2}{2} = 0.5\Delta u.
 \label{eq:shkvelws}
@@
 The difference in the pre- and post-discontinuity velocities, $\Delta
-u$ is marked clearly in the fig.~\ref{fig:1dvelrho}. Typically, the
+u$, is marked clearly in fig.~\ref{fig:1dvelrho}. Typically, the
 difference in velocity values for our reference runs lie around 15-40 km s$^{-1}$. Thus, the
@@
 
-\newpage
 \bibliographystyle{mn2e}

### 2014-01-22 PAPER/Paola_2/ms_ver3.tex
Modified fig captions I

@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig4.pdf}%{\figpath/diffcool_sim.pdf}
- \caption{Jet Volume Density for different cooling modes with
+ \caption{Logarithmic values of jet volume density in units of
+   cm$^{-3}$ obtained from dynamical simulations for different cooling
+   modes (labelled on the top of each panel) with
    $\eta$ = 10.}
@@
  \caption{A plot of the integrated SiO(2-1) emission from 5 models, 
-each using a different method to calculate cooling and all with $\eta$=10.}
+each using a different method to calculate cooling (labelled on the
+top of each panel) and all with $\eta$=10.}
 \label{fig:coolcmpsio} 
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig7.pdf}%molcjet_310_molform.pdf}
- \caption{{\it Top}: Number density, n$_{\rm H}$ [cm$^{-3}$], obtained from the reference 
+ \caption{{\it Top}: Logarithmic values of total hydrogen number density, n$_{\rm H}$),
+   in units of cm$^{-3}$, obtained from the reference 
  run along with labels of typical jet features. {\it Bottom}: Dependence of hydrogen fractions on the temperature at two
-  points in the flow, viz. the interface of the knot {\it left} with molecular
- medium and at the bow shock {\it right}.}
+  points in the flow, viz. at the interface of the knot ({\it left}) with molecular
+ medium and at the bow shock ({\it right}).}
 \label{fig:Hmolform}
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig10.pdf}%diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
- \caption{Variation of SiO(2-1) emission for runs with molecular
-   cooling having different abundance profiles.}
+ \caption{Integrated intensity maps of SiO(2-1) line in units of K, for runs with molecular
+   cooling and having different abundance profiles.}
 \label{fig:diffabunem}
@@
    knots produced in the model with reference parameters and different abundance
-   profiles. The contours mark different levels of emission in Kelvins, viz.,
+   profiles. The contours mark different levels of emission in K, viz.,
    0.1,0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
@@
    intensity and the green contours show the J=2-1 line intensity. The
-   jet is inclined at an angle of 60$^{\circ}${\bf Right:} The PV
+   jet is inclined at an angle of 60$^{\circ}$. {\bf Right:} The PV
    diagram taken along the axis of the jet for the 5-4 line (in units
@@
  \caption{{\em{Top}}: Line profiles in SiO (2-1), (5-4) and (8-7) at one
-   the inner knots for the reference molecular cooling run. The profiles are
+   of the inner knots for the reference molecular cooling run. The profiles are
    obtained when the angle of inclination is 60$^{\circ}$ with respect

### 2014-01-22 PAPER/Paola_2/ms_ver3.tex
Modified Figures and its captions II

@@
   in young molecular outflows}
-\author[B. Vaidya, T. Douglas, P. Caselli]{Bhargav Vaidya$^{1}$\thanks{E-mail:
-B.Vaidya@leeds.ac.uk (BV)}, Thomas Douglas$^{1}$, Paola Caselli$^{1}$\\
+\author[B. Vaidya, T. Douglas, P. Caselli]{B. Vaidya$^{1}$\thanks{E-mail:
+B.Vaidya@leeds.ac.uk (BV)}, T. A. Douglas$^{1}$, P. Caselli$^{1}$\\
 $^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2
@@
 envelope scales ($10^{2} - 10^{5}$\,AU) and parent cloud scales
-($10^{5} - 10^{6}$\,AU) (\refer : Frank et. al, 2013, PPVI).
+($10^{5} - 10^{6}$\,AU) \citep[e.g.,][and references therein]{Ray:2007p3306}.
 Of these, it is at the envelope scale where rich
@@
 \citealt{Caselli:2012p16713} in a pre-stellar core ($\lesssim$
-10$^{-7}$). Inspite of such over estimated abundance values, their
+10$^{-7}$). In-spite of such over estimated abundance values, their
 contribution is only important when temperature is $<$100\,K as seen in
@@
 \centering 
-\caption{Summary of parameter runs for different cooling prescriptions and density contrasts using two abundance profiles.}
+\caption{Summary of parameter runs for different cooling prescriptions
+  and density contrasts. Integrated
+  emission map for SiO(2-1) line in units of K-km\,s$^{-1}$ obtained
+  by convolving with a beam of 15\arcsec\,and the
+  corresponding line widths (in units of km\,s$^{-1}$) are listed for each of these runs for two different abundance profiles.}
 \begin{tabular}{c | c | c | c | c | c | c }
@@
 \hline\hline
-&&& $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] & $\int T_{\rm MB}dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] \\
+&&& $\int T dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] & $\int T dV$ [K-km\,s$^{-1}$] & $\Delta$v [km s$^{-1}$] \\
 \hline
@@
 profile. They are then placed at a distance of
-16.7$\,$pc and convolved with a beam with FWHM of 2.0\arcsec, in order
+16.7$\,$pc and convolved with a beam with FWHM of 2.0\arcsec\,in order
 to create the maps shown. 
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig5.pdf}%diffcool_img.pdf}
- \caption{A plot of the integrated SiO(2-1) emission from 5 models, 
+ \caption{A plot of the integrated SiO(2-1) emission from 5 models in
+   units of K-km\,s$^{-1}$, 
 each using a different method to calculate cooling (labelled on the
@@
  \includegraphics[width=1.\columnwidth]{\figpath/pfig6.pdf}%hfracs_ref.pdf}
- \caption{{\it{Left}}: Colour composite image of various hydrogen
+ \caption{{\it{Left}}: Color composite image of various hydrogen
    fractions, fHI (red), fH$_{2}$ (green) and fHII (blue), for the
@@
  \includegraphics[width=1.\columnwidth]{\figpath/pfig8.pdf}%emspecpv_90.pdf}%{\figpath/refrun_21_90_emspecpv.png}
- \caption{Integrated emission map ({\it top left}), PV diagram ({\it top right}
-   and spectra ({\it bottom}) for the
+ \caption{Integrated emission map ({\it top left}) in units of K-km\,s$^{-1}$, PV diagram ({\it top right}
+   in units of K and spectra ({\it bottom}) for the
    SiO(2-1) transition for the reference run. 
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig10.pdf}%diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
- \caption{Integrated intensity maps of SiO(2-1) line in units of K, for runs with molecular
+ \caption{Integrated intensity maps of SiO(2-1) line in units of K-km\,s$^{-1}$, for runs with molecular
    cooling and having different abundance profiles.}
@@
  \includegraphics[width=2.\columnwidth]{\figpath/pfig13.pdf}%imshkvhcontomaps.png}
- \caption{Symmetrical contour maps of multi-line integrated SiO
-   emission convolved with a 2\arcsec beam obtained using parameters of the reference run.
-The contour colors represent different intensities in Kelvins, i.e, 50.0({\it red}), 30.0({\it green}), 20.0({\it blue}), 5.0({\it
+ \caption{Contour maps of multi-line integrated SiO
+   emission convolved with a 2\arcsec\,beam obtained using parameters
+   of the reference run. The line transitions are labelled on the top
+   left corner of each panel. The contour colors represent different intensities in K-km\,s$^{-1}$, i.e, 50.0({\it red}), 30.0({\it green}), 20.0({\it blue}), 5.0({\it
      magenta}), 2.0({\it cyan}), 0.1({\it black}).} 
@@
 $i$ = 60$^{\circ}$ and convolved with a single dish beam of
-15\arcsec, to simulate observed integrated
+15\arcsec\,to simulate observed integrated
 intensities of L1448 bullets observed with large beams from JCMT and
@@
 and SiO(5-4)/(2-1), as a function of velocity. {\em{Bottom right}}:
-Variation of normalised integrated intensity with upper line transition J$_{\rm
+Variation of normalized integrated intensity with upper line transition J$_{\rm
   up}$ for the reference run.}
@@
 sputtering and grain-grain 
-collisions exists, their focus is mainly on weaker shocks
+collisions exists, their focus is mainly on weaker C-type shocks
 \citep{Schilke:1997p14140, Caselli:1997p14853, Gusdorf:2008p13800, VanLoo:2013p16573}. 
@@
 index, $\gamma$, of the gas, which directly influences the equation of
-state, eq.~\ref{EOS}, and thus the behaviour of the gas.
+state, eq.~\ref{EOS}, and thus the behavior of the gas.
 In standard hydrodynamical codes, the gas is generally

### 2014-02-07 PAPER/Paola_2/ms_ver3.tex
small text edit
tweak to rad trans section

@@
 main collision partner (equivalent amount of H, given by n(H$_2$)+
-n(HI), assuming that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and turbulent velocity are specified.
+n(HI), assuming that ionized Hydrogen does not collide with SiO and that atomic and molecular hydrogen have the same collisional cross secrions with SiO), gas temperature, velocity, molecular abundances and turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
@@
 cube for SiO(2-1) in the reference run. 
-The top left panel in the figure shows the emission map for the jet
-directed downwards. The notable features are the knots close to the
+The top left panel in the figure shows the emission map for the jet. The notable features are the knots close to the
 base of the jet and the emission near the bow shock due to density
